### 2022-03-31 Notes/overview.tex

\section{overview, general flow...}

\subsection{GBW\cite{gbw1998}}
for flavour $f$ and polarization $p$ \cite{gbw1998} \cite{cambqcd},
\begin{equation}
\sigma_{f,\;p}=\int_{0}^{1} d z \int d^2\mathbf{r}|\Psi_{f,\;p}|^2 \sigma_{dp}.
\end{equation}

photon wavefunctions are known (cf.  \cite{gbw1998}).

Original GBW model introduces $\sigma_{dp}$ in the form
\begin{equation}
\sigma_{GBW} (x, r )=\sigma_0 (1-e^{-\hat{r}^2}),
\end{equation}
where $\hat{r}^2$ which is the main object here to be defined as $\frac{r^2}{4 R^2_0(x)}$, with saturation scale \hyperlink{saturationscaleGBW}{$R^2_0$}, and modified \hyperlink{modifiedx}{$x$}.
In this model, there are three parameters to be fitted, namely $\sigma_0$, $\lambda$ and $x_0$.

\subsection{GBW-BK \cite{gbk2002}}
GBW-BK model introduces diple cross section $\sigma_{dp}$ in the form
\begin{equation}
\sigma_{GBWBK}(x,r)=\sigma_0\left(1-\exp\left(-\frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3\sigma_0}\right) \right)
\end{equation}

One important feature is,
\begin{equation}
\lim_{r \rightarrow 0}\sigma_{GBWBK} \simeq  -\frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is integrated gluon density. This is the limit $r \rightarrow 0$ of \hyperlink{ugd}{ $\sigma_{dp}$ in terms of unintegrated gluon density}.

\subsection{GBW-BK-S}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{notation, miscelaneous}

\begin{equation}
\hypertarget{modifiedx}{x}=x_{Bjorken}\left(1+\frac{4m^2_q}{Q^2}\right),
\end{equation}
where $m_q$ is effective quark mass.

The saturation scale in GBW \hypertarget{saturationscaleGBW}{$R^2_0$}, becomes in the limit $x\rightarrow 0$
\begin{equation}
R_0\rightarrow \frac{1}{GeV^2}\left(\frac{x}{x_0}\right)^\lambda,
\end{equation}
where $x_0$ and $\lambda$ to be fitted.

Scale $\mu^2$ in GBW-BK behaves like $\frac{const}{r^2}$ in small r region, and like a constant in large $r$ region.

Unintegrated gluon density\hypertarget{ugd}{$f(x,k^2)$} is related to the dipole cross section $\sigma_{dp}$ by% the fourier trransform
\cite{gbk2002}\cite{nikolaev1994}:

\begin{equation}
\sigma_{dp}=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^4} \alpha_s f(x,k^2) \left(1-e^{i \pairdot{k}{r}}\right).
\end{equation}

and hence the fourier transform
\begin{align}
\nabla^2_{\mathbf{r}} \sigma_{dp}&=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^2} \alpha_s f(x,k^2)  e^{i \pairdot{k}{r}}
\end{align}

unintegrated gluon density $f(x,k^2)$ is related to the integrated gluon density $g(x,Q^2)$ by 
 \begin{equation}
x g (x,Q^2)=\int f(x,k^2)d k^2 \theta(Q^2-k^2)/k^2.
\end{equation}

### 2022-03-31 Notes/overview.tex

@@
 \begin{equation}
-\lim_{r \rightarrow 0}\sigma_{GBWBK} \simeq  -\frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
+\lim_{r \rightarrow 0}\sigma_{GBWBK} \simeq  \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
 \end{equation}
 where $g(x,\mu^2)$ is integrated gluon density. This is the limit $r \rightarrow 0$ of \hyperlink{ugd}{ $\sigma_{dp}$ in terms of unintegrated gluon density}.
+
+The scale is proposed to be $\mu^2=\frac{C}{r^2}+{\mu^2_0}$.
 
@@
 \subsection{notation, miscelaneous}
+
+$k_g$ transverse momentum of gluon.\\
+$k_q$ transverse momentum of quark.\\
+$r$  dipole size.\\
+dipole scattering amplitude dissapears
+ for $r=0$ (cf. color trnsparency), and saturates to a constant for large $r$. cf.\cite{gbw1998}.
 
@@
 Unintegrated gluon density\hypertarget{ugd}{$f(x,k^2)$} is related to the dipole cross section $\sigma_{dp}$ by% the fourier trransform
-\cite{gbk2002}\cite{nikolaev1994}:
+\cite{gbk2002, nikolaev1994, nikolaev2001}:
 
 \begin{equation}
-\sigma_{dp}=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^4} \alpha_s f(x,k^2) \left(1-e^{i \pairdot{k}{r}}\right).
+\sigma_{dp}=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k_g}}{k_g^4} \alpha_s f(x,k_g^2) \left(1-e^{i \pairdot{k_g}{r}}\right).
 \end{equation}
@@
 \begin{align}
-\nabla^2_{\mathbf{r}} \sigma_{dp}&=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k}}{k^2} \alpha_s f(x,k^2)  e^{i \pairdot{k}{r}}
+\nabla^2_{\mathbf{r}} \sigma_{dp}&=\frac{2 \pi}{3} \int\frac{d^2 \mathbf{k_g}}{k_g^2} \alpha_s f(x,k_g^2)  e^{i \pairdot{k_g}{r}}.
 \end{align}
 
-unintegrated gluon density $f(x,k^2)$ is related to the integrated gluon density $g(x,Q^2)$ by 
+In the small $r$ limit\cite{nikolaev2001}, 
 \begin{equation}
-x g (x,Q^2)=\int f(x,k^2)d k^2 \theta(Q^2-k^2)/k^2.
+\sigma_{dp}(x,r)=\frac{\pi^2 r^2\alpha_s(\mu^2=\frac{C}{r^2}) x g(x,\mu^2=\frac{C}{r^2})}{3}.
 \end{equation}
+
+unintegrated gluon density $f(x,k_g^2)$ is related to the integrated gluon density $g(x,Q^2)$ by 
+ \begin{equation}
+x g (x,Q^2)=\int d k_g^2 f(x,k_g^2) \theta(Q^2-k_g^2)/k_g^2.
+\end{equation}

### 2022-09-14 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
document added

\documentclass[11pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\geometry{a4paper}

\usepackage[table]{xcolor}
\usepackage[utf8]{inputenc}
%\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{tabularx,ragged2e,booktabs,caption}
%\usepackage{breqn}
\usepackage{graphicx}
%\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{framed}
\usepackage{float}
\usepackage{rotating}
\usepackage[
%backend=bibtex,
%style=ieee
backend=bibtex,
style=phys
]{biblatex}
\addbibresource{./ref/golec.bib}
\addbibresource{./ref/gbw1998.bib}
\addbibresource{./ref/bgk2002.bib}
\addbibresource{./ref/impact.bib}
\addbibresource{./ref/cambqcd.bib}
\addbibresource{./ref/gbs2018.bib}
\addbibresource{./ref/gbs2006.bib}
\addbibresource{./ref/xiao2017.bib}
\addbibresource{./ref/minuit.bib}
\addbibresource{./ref/hera.bib}
\addbibresource{./ref/jk2006.bib}

\addbibresource{./ref/stasto2018.bib}
\addbibresource{./ref/stebel2020.bib}
\addbibresource{./ref/ellis1996.bib}
\addbibresource{./ref/bronstein.bib}
\addbibresource{./ref/mueller2016.bib}
\addbibresource{./ref/css1985.bib}
\addbibresource{./ref/prokudin2015.bib}
\addbibresource{./ref/collins2016.bib}

\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\begin{document}
\author{Tomoki Goda}
\title{ Effects of Sudakov form factor in\\ the
Golec-Biernat W\"usthoff saturation model}
\date{\today}
%\frontmatter
\maketitle
%\tableofcontents

\pagenumbering{arabic}
\numberwithin{equation}{section}
\numberwithin{table}{section}

\begin{abstract}

\end{abstract}

\section{Introduction}

In the dipole picture of deep inelastic scattering (DIS), a photon with virtuality $Q^2$ fluctuates into a pair of quark and antiquark, with momentum fractions $z$ and $(1-z)$ respectively, long before the interaction with the nucleon. Then the cross-section of inclusive DIS involves with the photon with polarization $P$, is factorized into the form \cite{gbw1998}%{\color{blue} correction. it is written `cf.' since this is not the original paper to have derived this factorization.  }
\begin{equation}
\sigma^{\gamma^* p}_{P}(x,Q^2)=\int d^2 \mathbf{r} \int^1_0 dz |\Psi_{P}(z,\mathbf{r})|^2 \sigma_{\mathrm{dp}}(x,r),
\label{eq:factorization}
\end{equation}
where the photon wave function, $\Psi_P(z, \mathbf{r}) $, describes the decay of a virtual photon into a quark-antiquark pair separated by the dipole size $r$, and the dipole cross-section, $\sigma_{\mathrm{dp}}(x,r)$, describes the interaction of the quark/antiquark with the target proton.

The photon wave functions read  \cite{gbw1998}%{\color{blue} the same reason as above.}
\begin{align}
|\Psi_{T}(z,r,Q)|^2 & =\alpha_{em}\frac{3}{2\pi^2}\sum_{f=\{u,d,c,\dots\}} e^2_f \left[ (z^2+(1-z)^2) \epsilon^2 K_1^2(\epsilon r) +m_f K_0^2(\epsilon r) \right],\\
|\Psi_{L}(z,r,Q)|^2 & =\alpha_{em}\frac{3}{2\pi^2}\sum_{f=\{u,d,c,\dots\}} e^2_f \left[ 4Q^2 z^2(1-z)^2 K_0^2(\epsilon r)
\right],
\end{align}
where 
\begin{equation}
\epsilon^2 =z(1-z) Q^2 +m_f^2,
\end{equation}
$m_f$ is the quark mass,
and $K_1(z)$ and $K_0(z)$ are the modified Bessel's functions.

 The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects. Therefore, it has to be modelled. In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play. The present study has roots in the Golec-Biernat W\"usthoff (GBW) model of the dipole cross-section \cite{gbw1998}, which describes the saturation effects in a very simple form.
In the next section, two models on which we develop our modified versions, namely the Golec-Biernat W\"usthoff (GBW) model\cite{gbw1998} and the Bartels Golec-Biernat Kowalski (BGK) model\cite{bgk2002}, are briefly summarized.  In sections 3 and 4, a summary of the modification is given. In section 5, the result of fitting to the data from the HERA\cite{hera} is presented. %{\color{blue}correction comment in summary}

\section{GBW and BGK models }
In Ref.~\cite{gbw1998}, the following form of the dipole cross-section was proposed:
\begin{equation}
\sigma_{\mathrm{GBW}}(x ,r )=\sigma_{0} \left(1-e^{-\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} }\right),
\label{eq:gbw}
\end{equation}
and the modified variable 
\begin{equation}
x_m=x \left(1+\frac{4 m_f^2}{Q^2}\right),
\label{eq:modx}
\end{equation}
where $m_f$ is an effective mass of a quark $f$,
was used in place of the Bjorken scaling variable $x$. In the rest of this paper, the subscript $m$ is dropped. Along with the above modification, effective mass of the light quarks $m_l=0.14\mathrm{GeV}$ was introduced in order to study the photoproduction limit ($Q^2\rightarrow0$) of DIS.

The GBW model incorporates two main features which characterize two regions of $r$ separated by the saturation scale $Q_s(x)$, which we discuss in detail later.
%\begin{itemize} 
%\item $\sigma_{\mathrm{GBW}}(x,r)|_{r\rightarrow 0 }\sim\frac{r^2}{4}Q_0 ^2\left(\frac{x_0}{x}\right)^{\lambda} $,
%\item $\sigma_{\mathrm{GBW}} (x,r)\sim \sigma_0 $ as $r$ rises ($r\sim 1$ fm).% \cite{golec}).
%\end{itemize}
The first behaviour, 
\begin{align}
&& \sigma(x,r)&\sim r^2 & r&\ll 2/Q_s(x),
\end{align}
is related to the QCD (colour transparency), that is to say that the smaller the dipole, the less visible (colourless) it is to the target. 
The second behaviour,
\begin{align}
&& \sigma(x,r)&\sim \sigma_0 & r&\gg 2/Q_s(x),
\end{align}
is related to the saturation phenomenon. \\
%{\color{green} move the folloing part to the section Saturation Scale ...}
%{\color{gray}
%The saturation scale $Q_s(x)$, which is an energy scale, below which saturation effects are important, was defined in terms of $r=R_0(x)$ where it was related to the saturation scale as
%\begin{equation}
%R_0(x)=2/Q_s(x).
%\end{equation}
%The model was constructed such that the saturation scale satisfies the condition
%\begin{equation}
%\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} =1.
%\label{eq:satdef}
%\end{equation}
%Hence,
%\begin{equation}
%Q_s^2(x) =Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
%\end{equation}
%The variables $r$ and  $Q$ are related in a way that the $z$ -integrated integrand in Eq.~(\ref{eq:factorization}) peaks around $r=2/Q$. Therefore one expects the behavoir of the dipole cross-section to be affect in the reigon about $Q^2\sim1/r^2$.
%}

%\subsection{Bartels Golec-Biernat Kowalski (DGLAP improved) Model }

%As it will be discussed later in detail (cf. Eq. \ref{eq:smallr}), in the small $r$ limit\cite{bgk2002}, 
The GBW model in the small-$r$ limit behaves as 
\begin{equation}
\sigma_{\mathrm{GBW}}\simeq\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
\end{equation}
However, the small-$r$ limit of the dipole cross-section is \cite{bgk2002}, 
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)\simeq \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is the integrated gluon distribution at the scale $\mu^2=\frac{C}{r^2}$.

In order to account for this behaviour, Bartels, Golec-Biernat and Kowalski \cite{bgk2002} proposed an improved version of the saturation model, in which the dipole cross-section is written in the form
\begin{equation}
\sigma_{\mathrm{BGK}} (x,r)=\sigma_0 \left[ 1-\exp\left( - \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0} \right) \right],
\label{eq:bgk}
\end{equation}
where $\mu^2=\frac{C}{r^2} + \mu_0^2$.

Now, the small-$r$ behaviour is enhanced with the gluon distribution $x g(x, \frac{C}{r^2})$, where the initial condition is set to be \cite{bgk2002}
\begin{equation}
x g(x,Q_0^2)=A_g x^{-\lambda_g} (1-x)^{5.6}.
\end{equation}
The constants $A_g$ and $\lambda_g$ are to be determined by a fit to experimental data.

The integrated gluon distribution, $g(x,\mu^2)$, follows DGLAP evolution \cite{gbs2018},
and thus the modification Eq.~(\ref{eq:bgk}) properly introduced the QCD behaviour in the large $Q^2\sim1/r^2$ region\footnote{The $z$-integrated integrand of Eq.~(\ref{eq:factorization}) peaks around $r\sim2/Q$ and thus the modification affects primarily the large-$Q$ region. }. 
While the modification improved the small-$r$ region, % due to the parametrization of $\mu^2$, 
in the large-$r$ region, where $\mu^2\simeq \mu_0^2$, $\sigma_{\mathrm{BGK}}$ recovers the form of GBW model as desired.

%{\color{gray}
%With the definition Eq.~(\ref{eq:satdef}), the saturation scale in the BGK model is given by
%\begin{equation}
%Q^2_s(x)= \frac{\pi^2 \alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0}.
%\end{equation}
%since $r$ correspondng to the saturation scale is 
%}
{\color{blue}
While, in principle, the dipole cross-section is impact-parameter, $b$, dependent \cite{impact}:\\
i.e.,
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)=\int d^2b N(x,r,b),
\label{eq:impact}
\end{equation} 
we will consider $b$-integrated dipole cross-section.
As one can see in Eq.~(\ref{eq:impact}), $\sigma_0$ is related to the effective size of the target.% $\sigma_0=2\pi R^2$.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{$k_T$ factorization, dipole cross section, unintegrated gluon distribution and more...}
\section{The Sudakov form factor }
In this section, we discuss how the Sudakov form factor is implemented in the above saturation models.%{\color{blue} and introduce unintegrated gluon distribution.}
The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by %\footnote{it can also be written$\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s f(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering the independence on the direction of $\mathbf{r}$.}
\cite{bgk2002}
\begin{align} 
\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s f(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
\label{eq:ugdtosigma}\\
\alpha_s \mathcal{F}(x,k^2) &= \frac{3 }{16 \pi^3}\int d^2 \mathbf{r} e^{i \pairdot{k}{r}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dp}}(x,r),
\label{eq:sigmatougd}
\end{align}
{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
where the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
\begin{equation}
\alpha_s(Q^2) x g(x,Q^2)=\int^{Q^2}_{0} d k^2 \alpha_s \mathcal{F}(x,k^2).
\end{equation}
Following the convention of Ref.~\cite{bgk2002}, we consider an object $\alpha_s\mathcal{F}(x,k^2)\equiv\alpha_s(k^2)\mathcal{F}(x,k^2)$.

By combining the earlier expressions Eqs.~(\ref{eq:ugdtosigma}) and (\ref{eq:sigmatougd}), one obtains
\begin{equation}
\sigma_{\mathrm{dp}}(x,r) =\int \frac{d^2 \mathbf{k}}{(2\pi)^2k^2}\left( 1- e^{i \pairdot{k}{r}}\right) \int d^2 \mathbf{{r'} } e^{i\pairdot{k}{{r'} }}\nabla^2_{\mathbf{{r'} }}\sigma_{\mathrm{dp}}(x,{r'} ).
\label{eq:dptodp}
\end{equation}
The Sudakov form factor, $S(r,Q^2)$, can be included by using the above formula and upgrading it to
\cite{xiao2017}
\begin{equation}
\sigma_{\mathrm{dp}}(x,r,Q^2) =\int \frac{d^2 \mathbf{k}}{(2\pi)^2 k^2} \left( 1- e^{i \pairdot{k}{r}}\right) \int d^2 \mathbf{ {r'} } e^{i\pairdot{k}{{r'} }}e^{-S({r'} ,Q^2)} \nabla^2_{\mathbf{{r'} }}\sigma_{\mathrm{dp}}(x,{r'} ).
\end{equation}
The dipole cross-section on the right hand side now depends on the hard scale, $Q^2$.

%Now, by integrating over angles,
%\begin{equation}
%\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^\infty_0 \frac{d k}{ k} \left( 1- J_0(k r) \right) \int^\infty_0 d {r'}  {r'}  J_0(k {r'} ) e^{-S_{pert}({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
%\end{equation}
%Finally, using 
%\begin{equation}
%\int^\infty_0 \frac{d k}{k} J_0({r'} k)(1-J_0(rk))=\log\left(\frac{r}{{r'} }\right)\theta(r-{r'} ),
%\end{equation}
%one obtains
%\begin{framed}
The above integral can be performed analytically, and one obtains
\begin{equation}
\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^r _0 d {r'}   {r'}  \log\left(\frac{r}{{r'} }\right) e^{-S({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
\label{eq:gbssigma}
\end{equation}
%\end{framed}
This form of the dipole cross-section does no longer saturate to a constant value unless $S(r,Q^2)=0$, but it rises logarithmically in the large-$r$ region:
\begin{equation}
\frac{\partial \sigma(x,r,Q^2)}{\partial \log (r)}\Big|_{r\rightarrow\infty}=\int^\infty_0 dr re^{-S(r,Q^2)}\nabla_r^2\sigma(x,r)\neq0.%=\mathrm{constant} .
\end{equation}   
% ( {\color{green}this is $\lim\limits_{k^2\rightarrow0} \alpha_s\mathcal{F}(x,k^2)$}).
This, in fact, is $\alpha_s\mathcal{F}(x,0,Q^2)$, and clearly suggests modification of the small-$k$ region of the unintegrated gluon density while the improvement by the DGLAP evolution (BGK model) affected the large-$k$ region.  
As discussed above, the saturation limit, $\sigma_0$, is related to the effective size of the target, and the logarithmic rise is associated with a proton without clear boundary \cite{gbw1998}.

In the present study, we focus on the leading order of the perturbative Sudakov factor\cite{xiao2017},
\begin{equation}
S^{(1)}_{pert}=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \log\left(\frac{Q^2}{\mu^2}\right).
\end{equation}
For the case of running coupling $\alpha_s(\mu^2)=\frac{1}{b_0 \log\left(\frac{\mu^2}{\Lambda_2}\right) }$, we get
%\begin{framed}
\begin{multline}
S^{(1)}_{pert}(r,Q) =\frac{C_A}{2 \pi b_0} \Big[-\log\left(\frac{Q^2}{\mu^2_b}\right) \\+\left(\frac{1+\alpha(\mu_b^2)  b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) }{\alpha(\mu_b^2)   b_0}\right) \log\left( 1+\alpha(\mu_b^2)   b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) \right) \Big],
\label{eq:sudakov}
\end{multline}
where $b_0=\frac{11 C_A-2 n_f}{12}$.
%\end{framed}
The lower limit of the integral $\mu_b=C_s/r$, where $C_s=2e^{-\gamma_E}$, and $\gamma_E \approx 0.577$ is the Euler-Mascheroni constant.\\
Two points have to be clarified in the above expression.
Firstly, the lower limit of the integration is restricted to the region $\mu_b<Q$ such that for $\mu_b>Q$, $S(r,Q)=0$. That is to say that in the limit $Q^2\rightarrow0$, the effect of the Sudakov factor nil. Consequently, for a fixed value of $Q^2$, the small-$r$ limit of the original dipole cross-section is recovered.   Such restriction is not present in the original CSS formula\cite{css1985} (See also Ref.~\cite{collins2016} for the improved treatment for small $r$.), but as we are concerned with relatively low values of $Q^2$, one needs to consider the region $1/r^2\sim k^2 >Q^2$.
In short, in the limit $Q\rightarrow 0$ we recover the original GBW/BGK model. Also in the limit $r \rightarrow 0$, again,  we recover the original GBW/BGK model.
Secondly, as the dipole size $r$ becomes large, the integration enters the non-perturbative region. In order to keep it perturbative, one can use so-called ``$b_*$-prescription'' \cite{css1985}, in which 
\begin{equation}
\mu_b^2=C_s^2/r_*^2= C_s^2/r^2+C_s^2/r_{\mathrm{max}}^2.
\end{equation}
The constant $r_{\mathrm{max}}$ is chosen such that in the large-$r$ region $\mu_b^2\simeq C_s^2/r_{\mathrm{max}}^2>>\Lambda_{\mathrm{QCD}}^2$.
In principle, one can include also the non-perturbative Sudakov factor\cite{css1985, prokudin2015}:
\begin{equation}
S(r,Q^2)= S_{pert}(r,Q^2)+S_{np}(r,Q^2),
\end{equation}
where we assume the form in Ref.~\cite{prokudin2015}
\begin{equation}
S_{np}(r,Q^2)=g_1r^2+g_2\log\left(\frac{r}{r_*}\right)\log\left(\frac{Q}{Q_0}\right).
\end{equation}
Considering that $\nabla^2_r \sigma$ in Eq.~(\ref{eq:gbssigma}) has a factor $e^{-a r^2}$, where $a$ is the appropriate factor in the respective models, it is apparent that the general behaviour of $S_{np}\sim r^2$ is already present in the models. 
The non-perturbative Sudakov factor is primarily important in the region $1/r<Q\lesssim 1/r_{\mathrm{max}}$. However, in such region, the second term is small compared to the first term, not only because of the suppression by $\log(Q/Q_0)$, but also because in the large-$r$ region, $r^2>\log\left({r}/{r_*}\right)$.  Therefore, one expects the contribution from the second term to be in the small region of not too small $Q$ and not too large $r$. One, however, needs to keep in mind that the Sudakov factor is in the integrand of the dipole cross-section Eq.~(\ref{eq:gbssigma}). That is to say that in the large-$r$ region of the dipole cross-section, it has effect from the small-$r'$ region of the integrand.
Nevertheless, the improvement by the non-perturbative Sudakov factor is less than 5\% for the BGK model and practically no improvement for the GBW model, and thus we neglect it in this study. Since diffractive DIS is more sensitive to the large-$r$ region, it may become necessary to include the non-perturbative factor in that case.

In this study, we shall employ an alternative form of $\mu_b$ proposed in Ref.~\cite{gbs2018}:
\begin{equation}
\mu_b^2= \frac{\mu_0^2}{1-e^{-r^2\frac{\mu_0^2}{C} }},
\label{eq:newstar}
\end{equation}
where $\mu_0^2=C/r_{\mathrm{max}}^2$ for both $g(x,\mu)$ and the Sudakov factor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The saturation scale and the critical line}
%{\color{red} this section may be largely unnecessary and will probably removed, but is kept for now.}\\
%\section{critical line and Satration scale}
The critical line is a line on the ($x,Q$) plane which separates regions where the saturation effects are important and  where the dipole cross section scales like $\sim r^2$.
The saturation scale $Q_s(x)$ is an energy scale at specific $x$. In other words, for a given $x$, saturation effects dominate below the scale $Q_s(x)$.

In order to study saturation in terms of the dipole cross-section, one defines saturation radius $R_0=2/Q_s$.  
Then, the critical line is defined as \cite{gbs2006}
\begin{equation}
\sigma(x,R_0)=a \sigma_0,
\end{equation}
where $a$ is a constant to be chosen.
In the GBW and BGK models it was set such that 
\begin{equation}
\sigma_0\left(1-e^{-\hat{r}}\right)=\sigma_0 \left(1-e^{-1}\right)\approx 0.63 \sigma_0.
\end{equation}
Hence, for the GBW model,  
\begin{equation}
Q_s^2(x) =Q_0^2\left(\frac{x_0}{x}\right)^{\lambda},
\end{equation}
and for the BGK model,
\begin{equation}
Q^2_s(x)= \frac{\pi^2 \alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0}.
\end{equation}

However, for the Sudakov-improved models, studied in this work, $\sigma_0$ is no longer a constant to which dipole cross-section converges.
% Hence, we employ two new definitions.
%Hence, one tries a definition, 
%\begin{equation}
%\frac{\partial^2 \sigma}{{\partial r}^2}=0
%\end{equation}
%That is, 
%\begin{equation}
%e^{-S(r,Q)}\nabla^2_r \sigma(x,r)-\frac{1}{r^2}\int^r_0 dr' r'  e^{-S(r',Q)}\nabla^2_{r'} \sigma(x,r')=0,
%\end{equation}  
%where this condition yields for GBW model
%\begin{equation}
%2-r^2Q_s^2=0.
%\label{eq:curvature}
%%\end{equation}
%({\color{red} this means $R_0^2 =2/ Q_s^2$ that is a factor of 2 different. so equivalent of taking a point $1-e^{-1/2}\simeq 0.393 $ not 0.632})
%Now, if one, instead choses a condition
%\begin{equation}
%\frac{\partial^2 \sigma}{\partial\log( R)^2}=0,
%\end{equation}
%then
%\begin{equation}
%R^2 e^{-S(R,Q)}\nabla^2\sigma(x,R)=0.
%\end{equation}
%And thus the condition is,
%\begin{equation}
%\nabla^2\sigma(x,R)=0
%\end{equation}
%and it is independent of the Sudakov factor.\\
%This definition yields for GBW model 
%\begin{equation}
%4-r^2Q_s^2=0,
%%\end{equation}
%recovering the original relation.
There for one needs to consider an alternative definition of the saturation scale.
As an alternative form, one considers the unintegrated gluon density $\alpha_s\mathcal{F}(x,k^2)$,
and defines in terms of the transverse momentum $k$ (i.e., the Fourier conjugate variable of $r$):
\begin{equation}
 \frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k^2}=0.
 \label{eq:peak}
\end{equation}
Then, for the GBW model 
\begin{equation}
\frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k}= \frac{4 k}{Q_s^4} { e^{-\frac{k^2}{Q_s^2}}} \left(Q_s^2-k^2\right).
\end{equation}
Therefore, Eq.~\ref{eq:peak} can also be used as a definition.
The saturation defined by Eq.~(\ref{eq:peak}) corresponds to the scale at with the density of gluons is at its maximum.

%Alternatively,  one considers the unintegrated gluon density \cite{jk2006} 
%\begin{equation}
%\phi(x,k^2,Q^2)=\frac{CF}{\alpha_s 2 \pi^3}\int d^2\frac{ \mathbf{r}}{r^2} e^{-i \pairdot{r}{k}} \sigma(x,r,Q^2)
%\end{equation}
%and defines in terms of the transverse momentum $k$, (i.e., fourier conjugate variable  of $r$):
%\begin{equation}
 %\frac{\partial k \phi(x,k^2,Q^2)}{\partial k^2}=0.
 %\label{eq:peak}
%\end{equation}
%The saturation scake $k_s^2$ obtained in this definition corresponds to the original GBW saturation scale  $R_0^2\simeq1/k^2_s$.

\section{Implementation and results}
In this study, the Sudakov factor (Eq.~(\ref{eq:sudakov})) is incorporated in the GBW and BGK models, as discussed earlier. %(Eq.~\ref{eq:gbssigma}). 
The values for $C_s$ and $\mu_{0s}^2$ in Eq.~(\ref{eq:newstar}) (The subscript $s$ was added to differentiate from those for the collinear gluon density.) for the Sudakov factor are fixed at 1.26$\approx (2e^{-\gamma_E})^2$ and 2 $\mathrm{GeV^2}$, 
and thus no additional fit parameters are needed. The choice of $\mu_{0s}^2$  is somewhat arbitrary, and if it was set higher, the effect of the non-perturbative Sudakov factor becomes more relevant. 
As we fit the model to the data up to $Q^2=650\;\mathrm{GeV^2}$, the charm and bottom quarks are included.  
The masses for the $c$ and $b$ quarks are 1.3 GeV and 4.6 GeV, respectively, which are the values used in Ref.~\cite{gbs2018}. As for the light quarks, a massive case with $m_l=$0.14 GeV, which is the value used originally in Ref.~\cite{gbw1998}, and the massless case were studied.  The Bjorken scaling variable $x$ was modified as in Eq.~(\ref{eq:modx}). %{\color{red}find the reason behind.}
The parameters in the GBW and BGK models (and their improved versions), $\{\sigma_0, x_0, \lambda\}$ and  $\{\sigma_0, A_g, \lambda_g, C, \mu_0\}$ respectively, are fitted to $F_2$ from the HERA data\cite{hera} in the range of $0.045\mathrm{GeV^2} \leq Q^2\leq 650 \mathrm{GeV^2}$ and $x \leq0.01$ using MINUIT\cite{minuit} package. % and integration subroutines from \textit{CERNLIB}\cite{cernlib}.
%The parameters are fitted to $F_2$ from the HERA data\cite{hera} in the range of $0.045\mathrm{GeV^2} \leq Q^2\leq 650 \mathrm{GeV^2}$ and $x \leq0.01$. \\
In the rest of this section, both GBW and BGK are discussed in parallel, and ``GBW'' may be used to mean GBW and its modified version (also denoted GBWS where necessary to differentiate) and likewise for the BGK model.

The results are summarized in Tabs.~\ref{table:GBWTable} and \ref{table:BGKTable}. As it was the case for Ref.~\cite{gbs2018}, the best results are obtained with massless light quarks for both the GBW and BGK models. Hence, in the rest of the paper, we only focus on the massless cases.
As one can see in Tab.~\ref{table:GBWTable}, changes in the parameters for the GBW/GBWS models are moderate, yet the GBWS fits show significant reduction of the $\chi^2$ value.
One noticeable change in the parameters of the BGK model is that $\lambda_g$ in the BGKS model is negative while  the value for the BGK model is positive. As discussed in Ref.~\cite{bgk2002}, the negative value of  $\lambda_g$ indicates that the initial condition of the gluon is valence-like and vanishes in the limit $x\rightarrow0$. Hence, the rise with $1/x$ is solely due to the DGLAP evolution.
\begin{table}[H]
\hfill
\input{./Plots/GBWS-Fix-S.tex}
\hfill
\caption{ The parameters and $\chi^2$ per degrees of freedom of the GBW(S) model for the fit with the HERA data ($Q^2<650\;\mathrm{ GeV^2}$). Two cases with massive light quarks and massless light quarks are fitted.   }
\label{table:GBWTable}
\end{table}
\begin{table}[H]
\hfill
\input{./Plots/BGKS-Fix-S.tex}
\hfill
\caption{ The parameters and $\chi^2$ per degrees of freedom  of the BGK(S) model for the fit with the HERA data ($Q^2<650\;\mathrm{GeV^2}$). Two cases with massive light quarks and massless light quarks are fitted.}
\label{table:BGKTable}
\end{table}

\begin{table}[H]
\hfill
\input{./Plots/GBWS-Q2.tex}\hfill
\input{./Plots/BGKS-Q2.tex}
\hfill
\caption{%{\color{red} need update.}\\
Comparison of the quality of fits with different upper limits $Q^2_{\mathrm{up}}\; \mathrm{(GeV^2)} $ of the hard scale. }
\label{table:Qup}
\end{table}

In Fig.~\ref{dipole}, log-log plots of the dipole cross-section are presented. One can see that the Sudakov factor suppresses the large-$r$ region, while the small-$r$ region is almost unchanged. The change in the small-$r$ region of the BGK model is due to the change in the fit parameters, and remains in the limit $Q\rightarrow0$, while the change in the large-$r$ region largely comes from the Sudakov factor and mostly disappears in the small-$Q^2$ region. 
Tab.~\ref{table:Qup} shows significant improvement in the GBW model for the high $Q_{\mathrm{up}}$, particularly for the 650$\mathrm{GeV^2}$ case, which indicates that the Sudakov factor has indeed introduced hard scale dependence in the model. For the small to medium $Q^2_{\mathrm{up}}$ cases, GBW and BGK models exhibit similar patterns in improvements, and show better effects for a greater range of $Q^2$.
What is important here is that the Sudakov-improved models have better tolerance for the wide range of the photon virtuality, and the Sudakov-improved BGK model has almost no deterioration for having wide range of $Q^2$.\\
Figs.~\ref{fig:gridGBW} and \ref{fig:gridBGK} show the $F_2$ plotted with the HERA data and the bottom histograms depict the difference in the $\chi^2$ value in each frame . 
The large-$Q^2$ region of the GBW model is modified significantly while the BGK model and the lower-$Q^2$ region of the GBW model show only slight change, mostly in the gradient. 
Fig.~\ref{fig:gridGBW} clearly shows that the highest improvement in the GBW model comes from the high-$Q^2$ region. The region of medium values of $Q^2$ also contribute but this is partly due to the large number of data points. (The bottom histogram is not per degrees of freedom.) As for the BGK model (Fig.~\ref{fig:gridBGK}), the improvement comes more evenly from all values of  $Q^2$, but the largest contribution comes from the medium to low-$Q^2$ region, particularly the region around $\mu_0$ and $\mu_{\mathrm{s0}}$.

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/dipole-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/dipole-BGK.png}
}
\caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=650\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
%\label{dipole-bgk}
\label{dipole}
\end{figure}

The effect of the Sudakov factor in the structure function, $F_2$, is shown in the Fig.~\ref{F2}. The changes are less obvious compared to the dipole cross-section, which is because the large-$r$ region, where the dipole cross-section was affected the most, is largely suppressed by the photon wave function.  Nonetheless, for both models the effect of the modification makes the increase of $F_2$ with $1/x$ milder (i.e. lowering the effective slope $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$. cf. Fig~\ref{slope}), %({\color{red} easier to see in the plot of the slope})
and to lower $F_2$ in the large and small-$Q^2$ region (This can also be seen in Figs.~\ref{fig:gridGBW} and \ref{fig:gridBGK}). 
The unintegrated gluon distributions obtained from the models are shown in Figs.~\ref{fig:gluon} and \ref{fig:gluon-x}. As discussed in the previous section, the unintegrated gluon distributions from the modified models do not vanish in the limit $k^2\rightarrow0$. Both models show large change in the distribution, and the distribution appears to be smeared out both over $k^2$ and $x$, particularly, towards the low-$k^2$ and low-$x$ regions. As a result of the smearing effect, one can see in the BGK model, that the region where the gluon density was negative is lifted up.   
Although the shape of the distribution changes, the position of the peak remains at about the same place, implying little modification to the saturation scale ( cf. Fig.~\ref{fig:critical}).

\begin{figure}[p]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-data-GBW1.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-data-GBW2.png}
}
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/F2-data-GBWhist.png}
}
\caption{Top: $F_2$. GBW (Dashed blue) and GBWS (Solid red) and HERA data (Error bars), with fixed values of $Q^2$. Bottom: $\chi^2/\text{(no. of points)}$, and the difference $\chi^2_{\mathrm{GBWS}}-\chi^2_{\mathrm{GBW}}$ between GBW and GBWS models. Significant improvement at large $Q^2$ is clearly visible.}
\label{fig:gridGBW}
\end{figure}

\begin{figure}[p]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-data-BGK1.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-data-BGK2.png}
}
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/F2-data-BGKhist.png}
}
\caption{
Top: $F_2$. BGK (Dashed blue) and BGKS (Solid red) and HERA data (Error bars), with fixed values of $Q^2$. Bottom: $\chi^2/\text{(no. of points)}$, and the difference $\chi^2_{\mathrm{BGKS}}-\chi^2_{\mathrm{BGK}}$ between BGK and BGKS models.}
\label{fig:gridBGK}
\end{figure}

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/F2-BGK.png}
}
\caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{F2}
\end{figure}

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-BGK.png}
}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon}
\end{figure}
\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-x-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/gluon-x-BGK.png}
}
\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\mathrm{GeV^2}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
\label{fig:gluon-x}
\end{figure}

As one can see in Fig.~\ref{dipole}, the dipole cross-section starts to bend somewhat earlier due to the Sudakov factor. For the small value of $Q^2$ near the expected saturation scale, the effect of the Sudakov factor is relatively small, yet this causes the saturation to take effect earlier and at the same time, the transition becomes slower. This means that the critical line becomes less clear as transition becomes milder over a wider range. % As discussed earlier, the definition of the saturation scale in terms of the dipole cross-section becomes less clear.
Comparisons of $x$-dependent saturation scale are presented in Fig.~\ref{fig:critical}. While the change in the GBW model  are only in the slope, the saturation scale of  BGK model becomes higher for the whole range of $x$, implying the saturation effect to show at slightly higher scale than expected from the original models.

%{\color{pink}Comparisons of $x$-dependent saturation scale are presented in Fig.~\ref{fig:critical}. While the change in GBW model from the definition Eq.~(\ref{eq:peak}) are only in the slope, the saturation scale of the BGK model and that of the GBW model from the definition Eq.~(\ref{eq:curvature}) becomes higher, implying the saturation effect to show at slightly higher scale than expected from the original models.} %{\color{red}$Q^2$ dependence of the saturation scale? what to show? ``peak'' version has no noticeable dependence. }

\begin{figure}[t]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/critical-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/critical-BGK.png}
}
\caption{Saturation scale $Q_S^2(x)$\\
%\caption{Saturation scale $Q_S^2(x)$  obtained from two different criteria:\\
%$\frac{\partial^2 \sigma }{\partial r^2}=0$ (Curvature) \& $\frac{\partial \alpha_s\mathcal{F}(x,k^2) }{\partial k}=0$ (Peak).\\ 
The line was plotted for $Q^2=650\;\mathrm{ GeV^2}$.\\Left: GBW, Right: BGK }
\label{fig:critical}
\end{figure}

\section{Summary}
In this paper we have presented the effects of the Sudakov form factor in the Golec-Biernat W\"ustfoff (GBW) model and the Bartels Golec-Biernat Kowalski (BGK) model. 
The leading order Sudakov factor was inserted in the model via modifying the unintegrated gluon density. This renders the dipole cross-section $Q^2$-dependent.
The results of fittings with the HERA data in the range $0.045\mathrm{GeV} \leq Q^2 \leq 650\mathrm{GeV}$ and $x\leq 10^{-2}$ have shown improvements in both models and most importantly, the BGK model exhibits good behaviour over a wide range of $Q^2$.  In terms of the dipole cross-section, the Sudakov factor modifies it in the region $1/r\lesssim Q$ by lowering initially and allowing logarithmic rise in the large-$r$ region.  This, in the light of the saturation effect, means that saturation starts earlier and the transition to the saturation region becomes slower. The effect is stronger for a large value of $Q^2$ and disappears when $Q^2=0$. In other words, the photoproduction is unaffected by the Sudakov factor and the sole change comes from the change in the fit parameters. The present study was conducted for inclusive DIS process, however diffractive DIS is even more sensitive to the large-$r$ region where the effect of the Sudakov factor is more prominent. Therefore, one may gain further insight on the effects by studying the diffractive processes,which we leave for future works.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
\printbibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Miscellaneous plots}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/slope-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/slope-BGK.png}
}
\caption{The $x$-slope of $F_2$  at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{slope}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-gluon-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-gluon-BGK.png}
}
\caption{Weizs\"acke-Williams gluon distrubution $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$.\\Left: GBW, Right: BGK
}
%\label{fig:gluon}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-critical-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/ww-critical-BGK.png}
}
\caption{Saturation scale $Q_s^2(x)$  obtained from the Weiz\"acker-Williams gluon distribution.
The crieria is analogous to Eq.~(\ref{eq:peak}) for $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$ but with an extra factor 2 as in the original GBW saturation scale.  i.e., $Q_s=2 k_s$.\\Left: GBW, Right: BGK }
%\label{fig:critical}
\end{figure}

\begin{figure}[H]
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/FL-GBW.png}
}
\resizebox{0.5\textwidth}{!}{
\includegraphics{./Plots/FL-BGK.png}
}
\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
Left: GBW, Right: BGK}
%\label{fig:critical}
\end{figure}

\end{document}

### 2022-09-14 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots subplots

@@
 The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects.
-Therefore, it has to be modelled.
+{\color{blue} Therefore, it has to be, to an extent, modelled.
+Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects.}\\
 In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play.
@@
 \section{The Sudakov form factor }
-In this section, we discuss how the Sudakov form factor is implemented in the above saturation models.%{\color{blue} and introduce unintegrated gluon distribution.}
-The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by %\footnote{it can also be written$\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s f(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering the independence on the direction of $\mathbf{r}$.}
+In this section, we discuss how the Sudakov form factor is implemented in the above saturation models. %{\color{blue} and introduce unintegrated gluon distribution.}
+The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
 \cite{bgk2002}
 \begin{align} 
-\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s f(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
+\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s \mathcal{F}(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
 \label{eq:ugdtosigma}\\
@@
 \end{align}
-{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
-where the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only?
-bgk)}
+%{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
+where the unintegrated gluon distribution is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
 \begin{equation}
@@
 
-\begin{figure}[t]
-\resizebox{0.5\textwidth}{!}{
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/dipole-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/dipole-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/dipole-BGK.png}
+%}
 \caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=650\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
@@
 
-\begin{figure}[t]
-\resizebox{0.5\textwidth}{!}{
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/F2-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/F2-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/F2-BGK.png}
+%}
 \caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
@@
 \end{figure}
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
+\includegraphics{./Plots/slope-GBW.png}
+}
+\caption{The $x$-slope of $F_2$,  $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$, at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
+\label{slope}
+\end{figure}
 
-\begin{figure}[t]
-\resizebox{0.5\textwidth}{!}{
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/gluon-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/gluon-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/gluon-BGK.png}
+%}
 \caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
@@
 \end{figure}
-\begin{figure}[t]
-\resizebox{0.5\textwidth}{!}{
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/gluon-x-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/gluon-x-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/gluon-x-BGK.png}
+%}
 \caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\mathrm{GeV^2}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
@@
 
-\begin{figure}[t]
-\resizebox{0.5\textwidth}{!}{
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/critical-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/critical-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/critical-BGK.png}
+%}
 \caption{Saturation scale $Q_S^2(x)$\\
@@
 \label{fig:critical}
+\end{figure}
+
+\begin{figure}[H]
+\resizebox{\textwidth}{!}{
+\includegraphics{./Plots/FL-GBW.png}
+}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/FL-BGK.png}
+%}
+\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
+The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
+Left: GBW, Right: BGK}
+%\label{fig:critical}
 \end{figure}
@@
 \begin{figure}[H]
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/slope-GBW.png}
-}
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/slope-BGK.png}
-}
-\caption{The $x$-slope of $F_2$  at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
-\label{slope}
-\end{figure}
-
-\begin{figure}[H]
-\resizebox{0.5\textwidth}{!}{
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/ww-gluon-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/ww-gluon-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/ww-gluon-BGK.png}
+%}
 \caption{Weizs\"acke-Williams gluon distrubution $\phi=k\int \frac{d^2r}{r^2} e^{-i r\cdot k} \sigma_{\mathrm{dp}}(x,r,Q^2)$.\\Left: GBW, Right: BGK
@@
 \begin{figure}[H]
-\resizebox{0.5\textwidth}{!}{
+\resizebox{\textwidth}{!}{
 \includegraphics{./Plots/ww-critical-GBW.png}
 }
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/ww-critical-BGK.png}
-}
+%\resizebox{0.5\textwidth}{!}{
+%\includegraphics{./Plots/ww-critical-BGK.png}
+%}
 \caption{Saturation scale $Q_s^2(x)$  obtained from the Weiz\"acker-Williams gluon distribution.
@@
 
-\begin{figure}[H]
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/FL-GBW.png}
-}
-\resizebox{0.5\textwidth}{!}{
-\includegraphics{./Plots/FL-BGK.png}
-}
-\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
-The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
-Left: GBW, Right: BGK}
-%\label{fig:critical}
-\end{figure}
-
 \end{document}

### 2022-09-14 saturation-ver2/Utilities/plotf2.py

@@ -160,7 +160,7 @@ def main():
         #chi+=pow((float(f2d[j])-float(f2c[j]))/float(f2e[j]),2)
         #count+=1
         ax1[pos[0]][pos[1]].set(  xscale="log" ,   yscale='linear')
-        ax1[pos[0]][pos[1]].text(xarr[0]*3, yarr[0]/1.05,"$Q^2$={val}".format(val=float(q2val)) )
+        ax1[pos[0]][pos[1]].text(xarr[0]*3, yarr[0]/1.05,"$Q^2={val}$".format(val=float(q2val)) )
         #ax1[pos[0]][pos[1]].yaxis.set_major_locator(plt.FixedLocator([0.01,0.05,0.1,0.5,1,2.5]))
         ax1[pos[0]][pos[1]].yaxis.set_major_locator(plt.LogLocator(base=10))
         ax1[pos[0]][pos[1]].yaxis.set_minor_locator(plt.NullLocator())
@@ -203,7 +203,7 @@ def main():
                 
         ax2[pos[0]][pos[1]].set(xscale="log" ,   yscale='linear' )
         #ax2[pos[0]][pos[1]].legend()
-        ax2[pos[0]][pos[1]].text(1.0e-4, 0.6,"$Q^2$={val}".format(val=float(q2val)) )
+        ax2[pos[0]][pos[1]].text(1.0e-4, 0.6,"$Q^2={val}$".format(val=float(q2val))) 
         #ax2[pos[0]][pos[1]].yaxis.set_major_locator(plt.FixedLocator([0.01,0.05,0.1,0.5,1,2.5]))
         ax2[pos[0]][pos[1]].yaxis.set_major_locator(plt.LogLocator(base=10))
         ax2[pos[0]][pos[1]].xaxis.set_major_locator(plt.FixedLocator([1.0e-6,1.0e-4,1.0e-2] ))
@@ -222,11 +222,11 @@ def main():
     fig1.set_figheight(8)
     fig1.set_figwidth(6)
     #fig.set_ylabel( "F_2" ,rotation="horizontal",loc='top')
-    fig1.supylabel("$F_2$",rotation="horizontal",x=0.02,y=0.95)
-    fig2.supylabel("$F_2$",rotation="horizontal",x=0.02,y=0.95)
+    fig1.supylabel("$F_2$",rotation="horizontal",x=0.02,y=0.95,fontsize=13)
+    fig2.supylabel("$F_2$",rotation="horizontal",x=0.02,y=0.95,fontsize=13)
     
[…]

### 2022-09-14 saturation-ver2/Utilities/tmd-gluon.c

@@ -9,7 +9,7 @@
 
 #include"./Parameters.h"
 
-#define PHI 1
+#define PHI 0 
 
 #include"./plot.c"
 #include"./tmd-gluon.h"
@@ -40,8 +40,8 @@ int main (int argc, char** argv){
 		printf("tmd-gluon:: file can't be opened. %s\n",file_name);
 		return 1;
 	}
-	for (int i=0; i<500; i++){
-		k=1.0e-1 + pow(10,-5+((double)7*i)/500);
+	for (int i=0; i<100; i++){
+		k= pow(10,-1+((double)2*i)/100);
 #if PHI==1
 		val=fill_arr_2(k, step);
 #else

### 2022-09-14 saturation-ver2/Utilities/ww-gluon.c

@@ -26,13 +26,13 @@ int main (int argc, char** argv){
 			return 1;
 	}
 	
-	for(int i=0;i<30; i++){
-		K=pow(10,-2+3*((double)i)/30);
+	for(int i=0;i<25; i++){
+		K=pow(10,-1+2*((double)i)/25);
 		val=ww_integral();
 		//val=ww_grad();
 		//val*=3.0/(4*PI);
 			
-		fprintf(file,"%.5e\t%.5e\n",K,K*val);
+		fprintf(file,"%.5e\t%.5e\n",K*K,K*val);
 	}
 	fclose(file);
 	

### 2022-09-14 saturation-ver2/Utilities/ww-gluon.h

@@ -63,7 +63,7 @@ double ww_integrand_grad(const double * r){
 
 double ww_integral(){
 	double res,err;
-	double max=(2)*PI*25/K, min=1.0e-5;
+	double max=(2)*PI*50/K, min=1.0e-5;
 	//int n=96;
 	//res=dgquad_(&ww_integrand,&min,&max,&n);
 	

### 2022-09-14 saturation-ver2/grid-plot.sh

@@ -5,9 +5,9 @@
 
 #./Utilities/plotf2.py -s ../Run1708/BGKS-Fix-S/Mass0.0-Qup650-Model3-Sud1/grid-plot ../Run1708/BGK/Mass0.0-Qup650-Model1-Sud0/fcn.txt ../Run1708/BGKS-Fix-S/Mass0.0-Qup650-Model3-Sud1/fcn.txt ../Run1708/BGKS-Fix-S/Mass0.0-Qup650-Model3-Sud1/data.txt
 
-SAVEDIR=..
+#SAVEDIR=..
 RESDIR=../Run2808
-#SAVEDIR=/media/tomoki/TOMOKI-USB/Saturation-Model/Saturation-Notes/Run2808
+SAVEDIR=../Document/Plots
 
 ./Utilities/plotf2.py -s ${SAVEDIR}/F2-data-GBW ${RESDIR}/GBW/Mass0.0-Qup650-Model0-Sud0 ${RESDIR}/GBWS-Fix-S/Mass0.0-Qup650-Model22-Sud1
 

### 2022-09-14 saturation-ver2/plot-all.sh

@@ -6,77 +6,63 @@ GBW=${DIR}/GBW/Mass0.0-Qup650-Model0-Sud0
 GBWS=${DIR}/GBWS-Fix-S/Mass0.0-Qup650-Model22-Sud1
 BGK=${DIR}/BGK/Mass0.0-Qup650-Model1-Sud0
 BGKS=${DIR}/BGKS-Fix-S/Mass0.0-Qup650-Model3-Sud1
-SAVE=/media/tomoki/TOMOKI-USB/Saturation-Model/Saturation-Notes/Run2808
+SAVE=../Document/Plots
 
 ./visualize-dipole.py \
 	-s ${SAVE}/dipole-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 ./visualize-slope.py \
 	-s ${SAVE}/slope-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 
 ./visualize-F2.py \
 	-s ${SAVE}/F2-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 
 ./visualize-FL.py \
 	-s ${SAVE}/FL-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 
 ./visualize-gluon.py \
 	-s ${SAVE}/gluon-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 ./visualize-gluon-x.py \
 	-s ${SAVE}/gluon-x-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 ./visualize-ww-gluon.py \
 	-s ${SAVE}/ww-gluon-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 ./visualize-critical.py \
 	-s ${SAVE}/critical-GBW \
 	${GBW} \
-	${GBWS}
+	${GBWS} \
+	${BGK} \
+	${BGKS}
+./visualize-ww-critical.py \
+	-s ${SAVE}/ww-critical-GBW \
+	${GBW} \
+	${GBWS} \
+	${BGK} \
+	${BGKS}
 	
[…]

### 2022-09-14 saturation-ver2/plot.sh

@@ -6,7 +6,7 @@ for dir in ../Run2808/*/M*
 do
 	for x in 2 4 6
 	do
-		for q2 in 5 100 650
+		for q2 in 1 5 50 100 650
 		do		
 			${dir}/dipole -in ${dir}/result.txt -out ${dir}/dipole-${q2}-${x}.txt -x ${x} -Q2 ${q2}
 			${dir}/tmd-gluon -in ${dir}/result.txt -out ${dir}/gluon-${q2}-${x}.txt -x ${x} -Q2 ${q2}
@@ -17,14 +17,14 @@ do
 		${dir}/F2-slope -in ${dir}/result.txt -out ${dir}/F2-slope-${x}.txt -x ${x}
 			
 	done
-	for q2 in 5 100 650
+	for q2 in 1 5 50 100 650
 	do	
 		for k in 0.5 1 2
 		do
 			${dir}/tmd-gluon-x -in ${dir}/result.txt -out ${dir}/gluon-x-${k}-${q2}.txt -Q2 ${q2} -k ${k}
 		done
 		${dir}/critical -in ${dir}/result.txt -out ${dir}/critical-${q2}.txt -Q2 ${q2}
-		${dir}/tmd-critical -in ${dir}/result.txt -out ${dir}/tmd-critical-${q2}.txt -Q2 ${q2}
+		#${dir}/tmd-critical -in ${dir}/result.txt -out ${dir}/tmd-critical-${q2}.txt -Q2 ${q2}
 		#echo "hello"
 	done
 	

### 2022-09-14 saturation-ver2/visualize-F2.py

@@ -34,37 +34,39 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True,sharex=True,sharey=True )
     leg=[]
+    name=['GBW', 'BGK']
+    for l in range(2): 
+        ax1[l].text(1.0e+1,1.0e-2,name[l],fontsize=25);
+        for j in ['2','4','6']:
+            with open(args[0+2*l]+'/F2-'+j+'.txt' ,"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+            ax1[l].text(float(data[0])/2,float(data[1]),"x=$10^{-"+j+"}$")
+            
+            with open(args[1+2*l]+'/F2-'+j+'.txt',"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
+            leg.append(ax1[l].plot(ri,dpi ,c='red',ls="-"))
+        ax1[l].set( xscale= 'log' ,   yscale='log' )
+        ax1[l].grid('true')
     
-    for j in ['2','4','6']:
-        with open(args[0]+'/F2-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-        ax1.text(float(data[0])/2,float(data[1]),"x=$10^{-"+j+"}$")
-        
-        with open(args[1]+'/F2-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-    
[…]

### 2022-09-14 saturation-ver2/visualize-FL.py

@@ -27,43 +27,43 @@ def main():
             saveflag=True
             print("SAVE")
         else:
-            print("Unknown") 
-        
-    
+            print("Unknown")  
     dp=[]
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True,sharex=True, sharey=True )
     leg=[]
-    for w in ['100', '200', '300']:   
-        with open(args[0]+'/FL-'+w+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-        ax1.text(float(data[0])/2,float(data[1]),"W="+w+'GeV')
-        
-        with open(args[1]+'/FL-'+w+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-    
-    ax1.legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
-    ax1.set( xscale= 'log' ,   yscale='linear' )
-    ax1.grid('true')
-    ax1.set_ylabel("$F_L$",rotation="vertical",loc='top')
-    ax1.set_xlabel("$Q^2 \\;(\\mathrm{GeV^2})$",rotation="horizontal",loc='right')
+    name=['GBW','BGK']
+    for l in range(2):
+        ax1[l].text(5.0e-1,1.0e-2,name[l],fontsize=25)
+        for w in ['100', '200', '300']:   
+            with open(args[0+2*l]+'/FL-'+w+'.txt' ,"r") as fi:
+                 dpi=[]
+                 ri=[]
+                 for i in fi:
+                     data=i.strip().split("\t")
+                     dpi.append(float(data[1]))
+                     ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+            ax1[l].text(float(data[0])/2,float(data[1]),"W="+w+'GeV')
+             
[…]

### 2022-09-14 saturation-ver2/visualize-critical.py

@@ -34,47 +34,45 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots(1,1 ,sharey=True,constrained_layout=True)
+    fig1,ax1=plt.subplots(1,2 ,sharey=True,constrained_layout=True)
     leg=[]
     #q2= ['100','650']
     #types= ['','tmd-']
     #names=['Curvature', 'Peak']
     types= ['tmd-']
-    names=['Peak']
-    for j in range(len(types)):
-        with open(args[0]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
+    j=0
+    name=['GBW','BGK']
+    for l in range(2):
+        ax1[l].text(1.0e-6,0.4,name[l],fontsize=25)
+        with open(args[0+2*l]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
             dpi=[]
             ri=[]
             for i in fi:
                 data=i.strip().split("\t")
                 dpi.append(float(data[1]))
                 ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-        ax1.set(xscale="log" ,   yscale='linear' )
-        ax1.grid('true')
+        leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+        ax1[l].set(xscale="log" ,   yscale='linear' )
+        ax1[l].grid('true')
         
         
-        with open(args[1]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
+        with open(args[1+2*l]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
             dpi=[]
             ri=[]
             for i in fi:
                 data=i.strip().split("\t")
                 dpi.append(float(data[1]))
                 ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        ax1.set(xscale="log" ,   yscale='log' )
-        ax1.grid('true')
-        #ax1.text(ri[len(dpi)//2]*2,dpi[len(dpi)//2]*1.5,names[j])
-        
-    ax1.legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
-    #ax1.legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
[…]

### 2022-09-14 saturation-ver2/visualize-dipole.py

@@ -34,37 +34,38 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True,sharey=True,sharex=True )
     leg=[]
-    
-    for j in ['2', '4', '6']:
-        with open(args[0]+'/dipole-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
+    name=['GBW','BGK']
+    for l in range(2): 
+        ax1[l].text(1,1.0e-5,name[l],fontsize=25)
+        for j in ['2', '4', '6']:
+            with open(args[0+2*l]+'/dipole-650-'+j+'.txt' ,"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
                 
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-        ax1.text(ri[0]/1.3,5*dpi[0],"x=$10^{-"+j+"}$")
-        with open(args[1]+'/dipole-650-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-    
-    ax1.legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
-    ax1.set( xscale= 'log' ,   yscale='log' )
-    ax1.grid('true')
-    ax1.set_ylabel("$\\sigma/\\sigma_0$",rotation="vertical",loc='top')
-    ax1.set_xlabel("$r\\;(\\mathrm{GeV}^{-1})$",rotation="horizontal",loc='right')
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+            ax1[l].text(ri[0]/1.3,5*dpi[0],"x=$10^{-"+j+"}$")
+            with open(args[1+2*l]+'/dipole-650-'+j+'.txt',"r") as fi:
+                dpi=[]
+                ri=[]
[…]

### 2022-09-14 saturation-ver2/visualize-gluon-x.py

@@ -34,49 +34,42 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True, sharey=True,sharex=True )
     leg=[]
-    #for k in ['100','650']:
-    for j in ['1']:
-        with open(args[0]+'/gluon-x-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-                    
-        with open(args[1]+'/gluon-x-100-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        
-        
-        with open(args[1]+'/gluon-x-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='magenta',ls="-"))
-        
-    
-    
-    ax1.legend([leg[0][0],leg[1][0],leg[2][0]],['Without Sudakov','With Sudakov $Q^2=100\\;\\mathrm{GeV}^2$','With Sudakov $Q^2=650\\;\\mathrm{GeV}^2$'])
+    q2= ['5','100','650']
+    name=['GBW',"BGK"]
+    for l in range(2): 
+        ax1[l].text(1.0e-7,0,name[l],fontsize=25);
+        for j in ['1']:
+            with open(args[0+2*l]+'/gluon-x-650-'+j+'.txt' ,"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
[…]

### 2022-09-14 saturation-ver2/visualize-gluon.py

@@ -34,48 +34,44 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True,sharey=True,sharex=True )
     leg=[]
-    #for k in ['100','650']:
-    for j in ['4']:
-        with open(args[0]+'/gluon-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-                    
-        with open(args[1]+'/gluon-100-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        
-        
-        with open(args[1]+'/gluon-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='magenta',ls="-"))
-        
-    
-    
-    ax1.legend([leg[0][0],leg[1][0],leg[2][0]],['Without Sudakov','With Sudakov $Q^2=100\\;\\mathrm{GeV}^2$','With Sudakov $Q^2=650\\;\\mathrm{GeV}^2$'])
+    name=['GBW','BGK']
+    for l in range(2):
+        ax1[l].text(1.0e-2,3.5,name[l],fontsize=25);
+        for j in ['4']:
+            with open(args[0+2*l]+'/gluon-650-'+j+'.txt' ,"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
[…]

### 2022-09-14 saturation-ver2/visualize-slope.py

@@ -34,37 +34,38 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2,constrained_layout=True,sharex=True,sharey=True )
     leg=[]
-    for j in ['2','4','6']:
-        with open(args[0]+'/F2-slope-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-        ax1.text(ri[(len(ri)//5)*3],dpi[(len(ri)//5)*3],"x=$10^{-"+j+"}$" )
-        with open(args[1]+'/F2-slope-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-    
-    ax1.legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
-    #ax1.set(title="",  ylabel="$\\frac{\\log\\partial F_2}{\\log\\partial x}$",    xlabel="$Q^2$",  xscale= 'log' ,   yscale='log' )
-    ax1.set( xscale= 'log' ,   yscale='linear' )
-    ax1.grid('true')
+    name=['GBW','BGK']
+    for l in range(2):
+        ax1[l].text(1.0e-2,0.35,name[l],fontsize=25)
+        for j in ['2','4','6']:
+            with open(args[0+2*l]+'/F2-slope-'+j+'.txt' ,"r") as fi:
+                 dpi=[]
+                 ri=[]
+                 for i in fi:
+                     data=i.strip().split("\t")
+                     dpi.append(float(data[1]))
+                     ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+            ax1[l].text(ri[(len(ri)//5)*3],dpi[(len(ri)//5)*3],"x=$10^{-"+j+"}$" )
+            with open(args[1+2*l]+'/F2-slope-'+j+'.txt',"r") as fi:
+                dpi=[]
[…]

### 2022-09-14 saturation-ver2/visualize-ww-critical.py

@@ -34,69 +34,47 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots(1,1 ,sharey=True,layout='constrained')
+    fig1,ax1=plt.subplots(1,2 ,sharey=True,layout='constrained')
     leg=[]
     #q2= ['100','650']
     #types= ['','tmd-','ww-']
     #names=['Curvature', 'Peak $\\alpha_s f$','Peak $\\Phi$']
     types= ['ww-']
-    names=['Peak $\\Phi$']
-    for j in range(len(types)):
-        with open(args[0]+'/ww-critical-650.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
- 
-        with open(args[1]+'/ww-critical-5.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        ax1.text(ri[0]*1.1,dpi[0],'$Q^2=5 \mathrm{GeV^2}$')
-       
-        with open(args[1]+'/ww-critical-100.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        ax1.text(ri[0]*1.1,dpi[0],'$Q^2=100 \mathrm{GeV^2}$')
- 
-        
-        with open(args[1]+'/ww-critical-650.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        ax1.set(xscale="log" ,   yscale='log' )
-        ax1.grid('true')
+    name=['GBW','BGK']
 
[…]

### 2022-09-14 saturation-ver2/visualize-ww-gluon.py

@@ -34,49 +34,41 @@ def main():
     dpi=[]
     r=[]
     ri=[]
-    fig1,ax1=plt.subplots( )
+    fig1,ax1=plt.subplots(1,2, constrained_layout=True,sharex=True,sharey=True)
     leg=[]
+    name=['GBW','BGK']
     #for k in ['100','650']:
-    for j in ['4']:
-        with open(args[0]+'/ww-gluon-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='blue',ls="--"))
-                    
-        with open(args[1]+'/ww-gluon-100-'+j+'.txt',"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append(ax1.plot(ri,dpi ,c='red',ls="-"))
-        
-        
-        with open(args[1]+'/ww-gluon-650-'+j+'.txt' ,"r") as fi:
-            dpi=[]
-            ri=[]
-            for i in fi:
-                data=i.strip().split("\t")
-                dpi.append(float(data[1]))
-                ri.append(float(data[0]))
-        leg.append( ax1.plot(ri,dpi ,c='magenta',ls="-"))
-        
-    
-    
-    ax1.legend([leg[0][0],leg[1][0],leg[2][0]],['Without Sudakov','With Sudakov $Q^2=100GeV^2$','With Sudakov $Q^2=650GeV^2$'])
+    for l in range(2):
+        ax1[l].text(1.0e-2,10,name[l],fontsize=25)
+        for j in ['4']:
+            with open(args[0+2*l]+'/ww-gluon-650-'+j+'.txt' ,"r") as fi:
+                dpi=[]
+                ri=[]
+                for i in fi:
+                    data=i.strip().split("\t")
+                    dpi.append(float(data[1]))
+                    ri.append(float(data[0]))
+            leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
+            for k in ['5','50','650']:            
[…]

### 2022-09-15 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots all fine

@@
 
+\usepackage{babel}
 \usepackage[table]{xcolor}
 \usepackage[utf8]{inputenc}
-%\usepackage{multicol}
+%\usepackage[T1]{fontenc}
 \usepackage{amsfonts}
+\usepackage{ragged2e}
 \usepackage{amsmath}
 \usepackage{amssymb}
-%\usepackage{fancyhdr}
-%\usepackage{tabularx,ragged2e,booktabs,caption}
-%\usepackage{breqn}
 \usepackage{graphicx}
-%\usepackage{subcaption}
 \usepackage{wrapfig}
@@
 \usepackage{ragged2e}
-\usepackage{framed}
 \usepackage{float}
 \usepackage{rotating}
+\usepackage{ulem}
+\usepackage{authblk}
+
 \usepackage[
+backend=bibtex,
+%style=ieee
+maxbibnames=3,
 %backend=bibtex,
-%style=ieee
-backend=bibtex,
-style=phys
+style=ieee
 ]{biblatex}
@@
 \addbibresource{./ref/jk2006.bib}
-
+\addbibresource{./ref/FL.bib}
 \addbibresource{./ref/stasto2018.bib}
@@
 \begin{document}
-\author{Tomoki Goda}
+\author{Krzystof Kutak, Sebastian Sapeta, Tomoki Goda
+}	 
 \title{ Effects of Sudakov form factor in\\ the
@@
 \end{equation}
-and the modified variable 
+and a modified variable 
 \begin{equation}
@@
 The GBW model incorporates two main features which characterize two regions of $r$ separated by the saturation scale $Q_s(x)$, which we discuss in detail later.
-%\begin{itemize} 
-%\item $\sigma_{\mathrm{GBW}}(x,r)|_{r\rightarrow 0 }\sim\frac{r^2}{4}Q_0 ^2\left(\frac{x_0}{x}\right)^{\lambda} $,
-%\item $\sigma_{\mathrm{GBW}} (x,r)\sim \sigma_0 $ as $r$ rises ($r\sim 1$ fm).% \cite{golec}).
-%\end{itemize}
 The first behaviour, 
@@
 is related to the saturation phenomenon. \\
-%{\color{green} move the folloing part to the section Saturation Scale ...}
-%{\color{gray}
-%The saturation scale $Q_s(x)$, which is an energy scale, below which saturation effects are important, was defined in terms of $r=R_0(x)$ where it was related to the saturation scale as
-%\begin{equation}
-%R_0(x)=2/Q_s(x).
-%\end{equation}
-%The model was constructed such that the saturation scale satisfies the condition
-%\begin{equation}
-%\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} =1.
-%\label{eq:satdef}
-%\end{equation}
-%Hence,
-%\begin{equation}
-%Q_s^2(x) =Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
-%\end{equation}
-%The variables $r$ and  $Q$ are related in a way that the $z$ -integrated integrand in Eq.~(\ref{eq:factorization}) peaks around $r=2/Q$.
-Therefore one expects the behavoir of the dipole cross-section to be affect in the reigon about $Q^2\sim1/r^2$.
-%}
 
-%\subsection{Bartels Golec-Biernat Kowalski (DGLAP improved) Model }
-
-%As it will be discussed later in detail (cf. Eq. \ref{eq:smallr}), in the small $r$ limit\cite{bgk2002}, 
 The GBW model in the small-$r$ limit behaves as 
@@
 
-%{\color{gray}
-%With the definition Eq.~(\ref{eq:satdef}), the saturation scale in the BGK model is given by
-%\begin{equation}
-%Q^2_s(x)= \frac{\pi^2 \alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0}.
-%\end{equation}
-%since $r$ correspondng to the saturation scale is 
-%}
-{\color{blue}
 While, in principle, the dipole cross-section is impact-parameter, $b$, dependent \cite{impact}:\\
@@
 As one can see in Eq.~(\ref{eq:impact}), $\sigma_0$ is related to the effective size of the target.% $\sigma_0=2\pi R^2$.
-}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this section, we discuss how the Sudakov form factor is implemented in the above saturation models. %{\color{blue} and introduce unintegrated gluon distribution.}
-The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
+The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $, considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
 \cite{bgk2002}
@@
 
-%Now, by integrating over angles,
-%\begin{equation}
-%\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^\infty_0 \frac{d k}{ k} \left( 1- J_0(k r) \right) \int^\infty_0 d {r'}  {r'}  J_0(k {r'} ) e^{-S_{pert}({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
-%\end{equation}
-%Finally, using 
-%\begin{equation}
-%\int^\infty_0 \frac{d k}{k} J_0({r'} k)(1-J_0(rk))=\log\left(\frac{r}{{r'} }\right)\theta(r-{r'} ),
-%\end{equation}
-%one obtains
-%\begin{framed}
 The above integral can be performed analytically, and one obtains
@@
 \begin{equation}
-S^{(1)}_{pert}=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \log\left(\frac{Q^2}{\mu^2}\right).
+S^{(1)}_\mathrm{pert}=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \log\left(\frac{Q^2}{\mu^2}\right).
 \end{equation}
@@
 \begin{multline}
-S^{(1)}_{pert}(r,Q) =\frac{C_A}{2 \pi b_0} \Big[-\log\left(\frac{Q^2}{\mu^2_b}\right) \\+\left(\frac{1+\alpha(\mu_b^2)  b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) }{\alpha(\mu_b^2)   b_0}\right) \log\left( 1+\alpha(\mu_b^2)   b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) \right) \Big],
+S^{(1)}_\mathrm{pert}(r,Q) =\frac{C_A}{2 \pi b_0} \Big[-\log\left(\frac{Q^2}{\mu^2_b}\right) \\+\left(\frac{1+\alpha(\mu_b^2)  b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) }{\alpha(\mu_b^2)   b_0}\right) \log\left( 1+\alpha(\mu_b^2)   b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) \right) \Big],
 \label{eq:sudakov}
@@
 %\end{framed}
-The lower limit of the integral $\mu_b=C_s/r$, where $C_s=2e^{-\gamma_E}$, and $\gamma_E \approx 0.577$ is the Euler-Mascheroni constant.\\
+The lower limit of the integral $\mu_b=C_\mathrm{S}/r$, where $C_\mathrm{S}=2e^{-\gamma_\mathrm{E}}$, and $\gamma_\mathrm{E} \approx 0.577$ is the Euler-Mascheroni constant.\\
 Two points have to be clarified in the above expression.
@@
 \begin{equation}
-\mu_b^2=C_s^2/r_*^2= C_s^2/r^2+C_s^2/r_{\mathrm{max}}^2.
+\mu_b^2=C_\mathrm{S}^2/r_*^2= C_\mathrm{S}^2/r^2+C_\mathrm{S}^2/r_{\mathrm{max}}^2.
 \end{equation}
-The constant $r_{\mathrm{max}}$ is chosen such that in the large-$r$ region $\mu_b^2\simeq C_s^2/r_{\mathrm{max}}^2>>\Lambda_{\mathrm{QCD}}^2$.
+The constant $r_{\mathrm{max}}$ is chosen such that in the large-$r$ region $\mu_b^2\simeq C_\mathrm{S}^2/r_{\mathrm{max}}^2>>\Lambda_{\mathrm{QCD}}^2$.
 In principle, one can include also the non-perturbative Sudakov factor\cite{css1985, prokudin2015}:
 \begin{equation}
-S(r,Q^2)= S_{pert}(r,Q^2)+S_{np}(r,Q^2),
+S(r,Q^2)= S_\mathrm{pert}(r,Q^2)+S_\mathrm{np}(r,Q^2),
 \end{equation}
@@
 \begin{equation}
-S_{np}(r,Q^2)=g_1r^2+g_2\log\left(\frac{r}{r_*}\right)\log\left(\frac{Q}{Q_0}\right).
+S_\mathrm{np}(r,Q^2)=g_1r^2+g_2\log\left(\frac{r}{r_*}\right)\log\left(\frac{Q}{Q_0}\right).
 \end{equation}
-Considering that $\nabla^2_r \sigma$ in Eq.~(\ref{eq:gbssigma}) has a factor $e^{-a r^2}$, where $a$ is the appropriate factor in the respective models, it is apparent that the general behaviour of $S_{np}\sim r^2$ is already present in the models.
+Considering that $\nabla^2_r \sigma$ in Eq.~(\ref{eq:gbssigma}) has a factor $e^{-a r^2}$, where $a$ is the appropriate factor in the respective models, it is apparent that the general behaviour of $S_\mathrm{np}\sim r^2$ is already present in the models.
 The non-perturbative Sudakov factor is primarily important in the region $1/r<Q\lesssim 1/r_{\mathrm{max}}$.
 However, in such region, the second term is small compared to the first term, not only because of the suppression by $\log(Q/Q_0)$, but also because in the large-$r$ region, $r^2>\log\left({r}/{r_*}\right)$.
-Therefore, one expects the contribution from the second term to be in the small region of not too small $Q$ and not too large $r$.
+Therefore, one expects the contribution of the second term to be comparatively smaller than that of the $\sim r^2$ term, and only possible region where it may contribute is confined in the small region of not too small $Q$ and not too large $r$.
 One, however, needs to keep in mind that the Sudakov factor is in the integrand of the dipole cross-section Eq.~(\ref{eq:gbssigma}).
 That is to say that in the large-$r$ region of the dipole cross-section, it has effect from the small-$r'$ region of the integrand.
-Nevertheless, the improvement by the non-perturbative Sudakov factor is less than 5\% for the BGK model and practically no improvement for the GBW model, and thus we neglect it in this study.
+Nevertheless, as we briefly discuss later in section~5, the improvement by the non-perturbative Sudakov factor is less than 5\% for the BGK model and practically no improvement for the GBW model, and thus we neglect it in this study.
 Since diffractive DIS is more sensitive to the large-$r$ region, it may become necessary to include the non-perturbative factor in that case.
 
-In this study, we shall employ an alternative form of $\mu_b$ proposed in Ref.~\cite{gbs2018}:
+In this study, we shall employ for both $g(x,\mu)$ and the Sudakov factor an alternative form of $\mu_b$ proposed in Ref.~\cite{gbs2018}:
 \begin{equation}
@@
 \end{equation}
-where $\mu_0^2=C/r_{\mathrm{max}}^2$ for both $g(x,\mu)$ and the Sudakov factor.
+where $\mu_0^2=C/r_{\mathrm{max}}^2$.
 
@@
 %recovering the original relation.
-There for one needs to consider an alternative definition of the saturation scale.
+Therefore, one needs to consider an alternative definition of the saturation scale.
 As an alternative form, one considers the unintegrated gluon density $\alpha_s\mathcal{F}(x,k^2)$,
@@
 Therefore, Eq.~\ref{eq:peak} can also be used as a definition.
-The saturation defined by Eq.~(\ref{eq:peak}) corresponds to the scale at with the density of gluons is at its maximum.
+The saturation defined by Eq.~(\ref{eq:peak}) corresponds to the scale at which the density of gluons is at its maximum.
 
@@
 \section{Implementation and results}
+\begin{table}[H]
+\hfill
+\input{./Plots/GBWSnp.tex}
+\hfill
+\input{./Plots/BGKSnp.tex}
+\hfill
+\caption{$\chi^2/\mathrm{dof}$ for fits with and without non-perturbative Sudakov factor, with 5 values of $\mu_{0\mathrm{S}}^2$ for the Sudakov factor.
+It is clear that when $\mu_{0\mathrm{S}}^2$ is set small, effects of non-perturbative Sudakov factor are negligible.
+}
+\label{table:Snp}
+\end{table}
+
 In this study, the Sudakov factor (Eq.~(\ref{eq:sudakov})) is incorporated in the GBW and BGK models, as discussed earlier. %(Eq.~\ref{eq:gbssigma}). 
-The values for $C_s$ and $\mu_{0s}^2$ in Eq.~(\ref{eq:newstar}) (The subscript $s$ was added to differentiate from those for the collinear gluon density.) for the Sudakov factor are fixed at 1.26$\approx (2e^{-\gamma_E})^2$ and 2 $\mathrm{GeV^2}$,
-and thus no additional fit parameters are needed. The choice of $\mu_{0s}^2$  is somewhat arbitrary, and if it was set higher, the effect of the non-perturbative Sudakov factor becomes more relevant. 
+The values for $C_\mathrm{S}$ and $\mu_{0\mathrm{S}}^2$ in Eq.~(\ref{eq:newstar}) (The subscript $\mathrm{S}$ was added to differentiate from those for the collinear gluon density.) for the Sudakov factor are fixed at 1.26$\approx (2e^{-\gamma_\mathrm{E}})^2$ and 2 $\mathrm{GeV^2}$, and thus no additional fit parameters are needed.
+The choice of $\mu_{0\mathrm{S}}^2$  is somewhat arbitrary, and if it was set higher, the effects of the non-perturbative Sudakov factor become more relevant.
+{\color{blue}This can be seen in Tab.~\ref{table:Snp}, that at sufficiently small value of $\mu_{0\mathrm{S}}^2$, one can neglect the non-perturbative Sudakov factor.
+While it is interesting to see in the BGK model, that inclusion of the non-perturbative factor indeed soften the dependence on the choice of $\mu_{0\mathrm{S}}$, since it is preferable to have less parameters for the technical purpose, we chose to use the above value of $\mu_{0\mathrm{S}}^2$ and omit non-perturbative factor.}
 As we fit the model to the data up to $Q^2=650\;\mathrm{GeV^2}$, the charm and bottom quarks are included.  
@@
 The region of medium values of $Q^2$ also contribute but this is partly due to the large number of data points.
-(The bottom histogram is not per degrees of freedom.) As for the BGK model (Fig.~\ref{fig:gridBGK}), the improvement comes more evenly from all values of  $Q^2$, but the largest contribution comes from the medium to low-$Q^2$ region, particularly the region around $\mu_0$ and $\mu_{\mathrm{s0}}$.
+(The bottom histogram is not per degrees of freedom.) As for the BGK model (Fig.~\ref{fig:gridBGK}), the improvement comes more evenly from all values of  $Q^2$, but the largest contribution comes from the medium to low-$Q^2$ region, particularly the region around $\mu_0$ and $\mu_{0\mathrm{S}}$.
 
@@
 %}
-\caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=650\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
+\caption{The dipole cross-section $\sigma_{\mathrm{dp}}$ at $Q^2=100\;\mathrm{GeV^2}$, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
 %\label{dipole-bgk}
@@
 The changes are less obvious compared to the dipole cross-section, which is because the large-$r$ region, where the dipole cross-section was affected the most, is largely suppressed by the photon wave function.
-Nonetheless, for both models the effect of the modification makes the increase of $F_2$ with $1/x$ milder (i.e.
-lowering the effective slope $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$.
+Nonetheless, for both models the effect of the modification makes the increase of $F_2$ with $1/x$ milder (i.e., lowering the effective slope $\lambda_\mathrm{eff}=-\frac{\partial \log F_2}{\log x}$.
 cf.
@@
 As a result of the smearing effect, one can see in the BGK model, that the region where the gluon density was negative is lifted up.
-Although the shape of the distribution changes, the position of the peak remains at about the same place, implying little modification to the saturation scale ( cf. Fig.~\ref{fig:critical}).
+Although the shape of the distribution changes, the position of the peak remains at about the same place, implying little modification to the saturation scale (cf. Fig.~\ref{fig:critical}).
 
@@
 }
-\caption{The $x$-slope of $F_2$,  $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$, at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
+\caption{The $x$-slope of $F_2$,  $\lambda_\mathrm{eff}=-\frac{\partial \log F_2}{\log x}$,  and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).
+The slope is generally lowered, and this can be seen also in Figs.~\ref{fig:gridGBW} and \ref{fig:gridBGK}\\Left: GBW, Right: BGK}
 \label{slope}
@@
 %}
-\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
+\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $x=10^{-4}$ and $Q^2=5, 50 , 500\; \mathrm{GeV^2}$ (from top to bottom).
+Notice the broadening effect of the Sudakov factor, particularly towards the small value of $k^2$.\\Left: GBW, Right: BGK}
 \label{fig:gluon}
@@
 %}
-\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\mathrm{GeV^2}$. Notice the broadening effect of the Sudakov factor.\\Left: GBW, Right: BGK}
+\caption{$\alpha_s\mathcal{F}(x,k^2)$ plotted for $k^2=1\;\mathrm{GeV^2}$ and $Q^2=5, 50 , 500\; \mathrm{GeV^2}$ (from top to bottom).
+Notice the broadening effect of the Sudakov factor, particularly towards the small value of $x$.\\Left: GBW, Right: BGK}
 \label{fig:gluon-x}
@@
 While the change in the GBW model  are only in the slope, the saturation scale of  BGK model becomes higher for the whole range of $x$, implying the saturation effect to show at slightly higher scale than expected from the original models.
-
+{\color{blue}Finally, we present the longitudinal sturucture function $F_L$ in Fig.~\ref{fig:FL} with H1 data \cite{FL}.
+Both the GBW and BGK models show similar effects from the Sudakov factor.
+The main effects are in the large-$Q^2$ region, and for both the models, $F_L$ is higher when the Sudakov factor is present.
+}
 %{\color{pink}Comparisons of $x$-dependent saturation scale are presented in Fig.~\ref{fig:critical}.
@@
 %}
-\caption{Saturation scale $Q_S^2(x)$\\
+\caption{Saturation scale $Q_s^2(x)$.
 %\caption{Saturation scale $Q_S^2(x)$  obtained from two different criteria:\\
 %$\frac{\partial^2 \sigma }{\partial r^2}=0$ (Curvature) \& $\frac{\partial \alpha_s\mathcal{F}(x,k^2) }{\partial k}=0$ (Peak).\\ 
-The line was plotted for $Q^2=650\;\mathrm{ GeV^2}$.\\Left: GBW, Right: BGK }
+The line was plotted for $Q^2=100\;\mathrm{ GeV^2}$.\\Left: GBW, Right: BGK }
 \label{fig:critical}
@@
 %}
-\caption{Longitudinal structure function $F_L$ at fixed $W=100, 200, 300$ GeV (from bottom to top).
-The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both GBW and BGK models.\\ 
+\caption{The longitudinal structure function, $F_L$, at fixed $W=100, 200, 300$ GeV (from bottom to top).
+The effects of the Sudakov factor is primarily in the large-$Q^2$ region, lifting up the line for both the GBW and BGK models.
+The data are from Ref.~\cite{FL}.\\
 Left: GBW, Right: BGK}
-%\label{fig:critical}
+\label{fig:FL}
 \end{figure}
@@
 In other words, the photoproduction is unaffected by the Sudakov factor and the sole change comes from the change in the fit parameters.
-The present study was conducted for inclusive DIS process, however diffractive DIS is even more sensitive to the large-$r$ region where the effect of the Sudakov factor is more prominent.
+The present study was conducted for inclusive DIS, however diffractive DIS is {\color{blue}even} more sensitive to the large-$r$ region where the effect of the Sudakov factor is more prominent.
 Therefore, one may gain further insight on the effects by studying the diffractive processes,which we leave for future works.

### 2022-09-15 saturation-ver2/Utilities/F2-slope.c

@@ -27,15 +27,16 @@ double f2_slope(double Q2, double**pars){
 	*(*(pars)+1)=Q2;
 	//printf("x== %.2e\t Q2== %.2e\n", pars[0][0],pars[0][1]);
 	//getchar();
-	double xdiff=0.01;
+	//double xdiff=0.01;
+	double xdiff=(**pars)/10; //this is just a choice. choosing the value of 10x, note its \Delta log10(x) so very small.
 	double logx=log10(**pars);
 	double f2[2];
-	simpson1dA(&f2_integrand,pars,1.0e-5,30,250,f2,&err);
+	simpson1dA(&f2_integrand,pars,1.0e-5,0.97,500,f2,&err);//f2 is not over r bur r=R/(1-R)
 	(*(*pars)) = pow(10.0, logx+xdiff);
-	simpson1dA(&f2_integrand,pars,1.0e-5,30,250,f2+1,&err);
+	simpson1dA(&f2_integrand,pars,1.0e-5,0.97,500,f2+1,&err);
 	//double slope = (log(f2[0]/ f2[1]) )/(log(10)*xdiff);
 	double slope = (log10(f2[0]/ f2[1]) )/(xdiff);
-	//printf("%f\n",res);
+	printf("%f\t%f\t%f\n",slope,*(f2),*(f2+1));
 	(*(*pars)) = pow(10.0, logx);
 	return slope;
 }

### 2022-09-15 saturation-ver2/Utilities/f2.h

@@ -8,7 +8,8 @@ extern double dgquad_(double (*)(const double*),  const double*, const double*, 
 extern double dadapt_(double(* )(const double*),double*,double*,int*,double*,double* ,double*,double*);
 
 static int FIX_W=0;
- 
+
+
 double mod_x_W(double x, double Q2,double W2,int fl){
 	double mass2;
 
@@ -48,7 +49,7 @@ double f2_integrand(double R, double ** par){
 
 	double value=0.0;
 
-if(FIX_W==1){
+	if(FIX_W==1){
 		double W2=pow(*(*(par)),2);
 		xm=mod_x_W(x, Q2, W2,fl);
 	}else{

### 2022-09-15 saturation-ver2/Utilities/plotf2.py

@@ -249,7 +249,7 @@ def main():
     chipp2=[sum(i) for i in (chi2)]
     print(sum([ sum(i) for i in chi2])/sum([ len(i) for i in chi2]))
     
-    diff=[chipp[i]-chipp2[i] for i in range(len(chipp)) ]
+    diff=[chipp2[i]-chipp[i] for i in range(len(chipp)) ]
     
     chipp=[sum(i)/len(i) for i in (chi1)]
     chipp2=[sum(i)/len(i) for i in (chi2)]

### 2022-09-15 saturation-ver2/plot.sh

@@ -22,9 +22,11 @@ do
 		for k in 0.5 1 2
 		do
 			${dir}/tmd-gluon-x -in ${dir}/result.txt -out ${dir}/gluon-x-${k}-${q2}.txt -Q2 ${q2} -k ${k}
+			${dir}/ww-gluon-x -in ${dir}/result.txt -out ${dir}/ww-gluon-x-${k}-${q2}.txt -Q2 ${q2} -k ${k}
 		done
-		${dir}/critical -in ${dir}/result.txt -out ${dir}/critical-${q2}.txt -Q2 ${q2}
-		#${dir}/tmd-critical -in ${dir}/result.txt -out ${dir}/tmd-critical-${q2}.txt -Q2 ${q2}
+		#${dir}/critical -in ${dir}/result.txt -out ${dir}/critical-${q2}.txt -Q2 ${q2}
+		${dir}/tmd-critical -in ${dir}/result.txt -out ${dir}/tmd-critical-${q2}.txt -Q2 ${q2}
+		#${dir}/ww-critical -in ${dir}/result.txt -out ${dir}/ww-critical-${q2}.txt -Q2 ${q2}
 		#echo "hello"
 	done
 	

### 2022-09-15 saturation-ver2/visualize-F2.py

@@ -64,7 +64,7 @@ def main():
     ax1[0].legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
     ax1[0].set_ylabel("$F_2$",rotation="vertical",loc='top',fontsize=13)
     ax1[1].set_xlabel("$Q^2 \\;(\\mathrm{GeV^2})$",rotation="horizontal",loc='right',fontsize=13)
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.95, left=0.11)
     if saveflag:

### 2022-09-15 saturation-ver2/visualize-FL.py

@@ -36,7 +36,7 @@ def main():
     leg=[]
     name=['GBW','BGK']
     for l in range(2):
-        ax1[l].text(5.0e-1,1.0e-2,name[l],fontsize=25)
+        ax1[l].text(1.0e-1,2.0e-1,name[l],fontsize=25)
         for w in ['100', '200', '300']:   
             with open(args[0+2*l]+'/FL-'+w+'.txt' ,"r") as fi:
                  dpi=[]
@@ -46,7 +46,7 @@ def main():
                      dpi.append(float(data[1]))
                      ri.append(float(data[0]))
             leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
-            ax1[l].text(float(data[0])/2,float(data[1]),"W="+w+'GeV')
+            ax1[l].text(float(data[0])/2,float(data[1])+0.01,"W="+w+'GeV')
              
             with open(args[1+2*l]+'/FL-'+w+'.txt',"r") as fi:
                 dpi=[]
@@ -56,12 +56,33 @@ def main():
                     dpi.append(float(data[1]))
                     ri.append(float(data[0]))
             leg.append(ax1[l].plot(ri,dpi ,c='red',ls="-"))
+###########################################            
+        with open('./data/H1FL.txt','r') as fi:
+            expdata=fi.readlines()
+            expdata=[i.strip().split() for i in expdata]
+            #expdata=np.transpose(expdata)
+            w=[np.sqrt(float(i[0])*(1-float(i[1]))/float(i[1])) for i in expdata]
+            #print(w)
+            expdata=[ [float(i[0]) for i in expdata], [float(i[2]) for i in expdata], [float(i[6]) for i in expdata]]
+            
+        #print(expdata)
+        ax1[l].scatter(expdata[0],expdata[1],c='g')
+        for i in range(len(expdata[0])):
+            #print(expdata[0][i],expdata[1][i],expdata[2][i])
+            ax1[l].errorbar(expdata[0][i],expdata[1][i],yerr=expdata[2][i],c='g')
+            if i%2==0:
+                ax1[l].text(expdata[0][i],0,'{0:.0f}'.format(w[i]),rotation=60)
+            else:
+                ax1[l].text(expdata[0][i],-0.05,'{0:.0f}'.format(w[i]),rotation=60)
+                
         ax1[l].set( xscale= 'log' ,   yscale='linear' )
[…]

### 2022-09-15 saturation-ver2/visualize-critical.py

@@ -44,7 +44,7 @@ def main():
     name=['GBW','BGK']
     for l in range(2):
         ax1[l].text(1.0e-6,0.4,name[l],fontsize=25)
-        with open(args[0+2*l]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
+        with open(args[0+2*l]+'/'+types[j]+'critical-100.txt' ,"r") as fi:
             dpi=[]
             ri=[]
             for i in fi:
@@ -56,7 +56,7 @@ def main():
         ax1[l].grid('true')
         
         
-        with open(args[1+2*l]+'/'+types[j]+'critical-650.txt' ,"r") as fi:
+        with open(args[1+2*l]+'/'+types[j]+'critical-100.txt' ,"r") as fi:
             dpi=[]
             ri=[]
             for i in fi:
@@ -71,7 +71,7 @@ def main():
     ax1[0].set_ylabel("$Q^2_s \\;(\\mathrm{GeV}^2)$",rotation="vertical",loc='top')
     ax1[1].set_xlabel("$x$",rotation="horizontal",loc='right')
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     if saveflag:
         fig1.savefig(save1)

### 2022-09-15 saturation-ver2/visualize-dipole.py

@@ -40,7 +40,7 @@ def main():
     for l in range(2): 
         ax1[l].text(1,1.0e-5,name[l],fontsize=25)
         for j in ['2', '4', '6']:
-            with open(args[0+2*l]+'/dipole-650-'+j+'.txt' ,"r") as fi:
+            with open(args[0+2*l]+'/dipole-100-'+j+'.txt' ,"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -50,7 +50,7 @@ def main():
                 
             leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
             ax1[l].text(ri[0]/1.3,5*dpi[0],"x=$10^{-"+j+"}$")
-            with open(args[1+2*l]+'/dipole-650-'+j+'.txt',"r") as fi:
+            with open(args[1+2*l]+'/dipole-100-'+j+'.txt',"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -59,11 +59,11 @@ def main():
                     ri.append(float(data[0]))
             leg.append(ax1[l].plot(ri,dpi ,c='red',ls="-"))
         ax1[l].set( xscale= 'log' ,   yscale='log' )
-        ax1[l].grid('true')
+        ax1[l].grid('true',which='major')
     ax1[0].legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
     ax1[0].set_ylabel("$\\sigma/\\sigma_0$",rotation="vertical",loc='top')
     ax1[1].set_xlabel("$r\\;(\\mathrm{GeV}^{-1})$",rotation="horizontal",loc='right')
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.95, left=0.11)
     if saveflag:

### 2022-09-15 saturation-ver2/visualize-gluon-x.py

@@ -36,12 +36,12 @@ def main():
     ri=[]
     fig1,ax1=plt.subplots(1,2,constrained_layout=True, sharey=True,sharex=True )
     leg=[]
-    q2= ['5','100','650']
+    q2= ['5','50','500']
     name=['GBW',"BGK"]
     for l in range(2): 
         ax1[l].text(1.0e-7,0,name[l],fontsize=25);
         for j in ['1']:
-            with open(args[0+2*l]+'/gluon-x-650-'+j+'.txt' ,"r") as fi:
+            with open(args[0+2*l]+'/gluon-x-500-'+j+'.txt' ,"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -67,7 +67,7 @@ def main():
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
     ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k^2)$',rotation="vertical",loc='top')
     ax1[1].set_xlabel("$x$",rotation="horizontal",loc='right')
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
     if saveflag:

### 2022-09-15 saturation-ver2/visualize-gluon.py

@@ -40,7 +40,7 @@ def main():
     for l in range(2):
         ax1[l].text(1.0e-2,3.5,name[l],fontsize=25);
         for j in ['4']:
-            with open(args[0+2*l]+'/gluon-650-'+j+'.txt' ,"r") as fi:
+            with open(args[0+2*l]+'/gluon-500-'+j+'.txt' ,"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -48,7 +48,7 @@ def main():
                     dpi.append(float(data[1]))
                     ri.append(float(data[0]))
             leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
-            q2=['5','50','650']
+            q2=['5','50','500']
             #sty=['-','_.',':']
             for k in range(len(q2)):
                 #print(k)
@@ -59,8 +59,8 @@ def main():
                         data=i.strip().split("\t")
                         dpi.append(float(data[1]))
                         ri.append(float(data[0]))
-                    pos=int(len(dpi)/2.5)
-                    ax1[l].text(ri[pos]*4,dpi[pos], '$Q^2={0}\\;\\mathrm{{ GeV^2}}$'.format(q2[k]) )
+                    pos=int(len(dpi)/2)
+                    ax1[l].text(ri[pos]*3,dpi[pos], '$Q^2={0}\\;\\mathrm{{ GeV^2}}$'.format(q2[k]) )
                 leg.append(ax1[l].plot(ri,dpi ,c='red',ls="-"))
 
         ax1[l].set( xscale= 'log' ,   yscale='linear' )
@@ -70,7 +70,7 @@ def main():
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
     ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k^2)$',rotation="vertical",loc='top')
     ax1[1].set_xlabel("$k^2\\;(\\mathrm{GeV}^2) $",rotation="horizontal",loc='right')
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
     if saveflag:

### 2022-09-15 saturation-ver2/visualize-slope.py

@@ -63,7 +63,7 @@ def main():
     #ax1.set_ylabel("$-\\frac{\\partial \\log F_2}{\\partial \\log x}$",rotation="vertical",loc='top')
     ax1[0].set_ylabel("$x-slope $",rotation="vertical",loc='top')
     ax1[1].set_xlabel("$Q^2$",rotation="horizontal",loc='right')
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.9, left=0.13)
     

### 2022-09-15 saturation-ver2/visualize-ww-critical.py

@@ -45,7 +45,7 @@ def main():
     for l in range(2):
         ax1[l].text(1.0e-6,0.4,name[l],fontsize=25)
         for j in range(len(types)):
-            with open(args[0+2*l]+'/ww-critical-650.txt' ,"r") as fi:
+            with open(args[0+2*l]+'/ww-critical-500.txt' ,"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -53,7 +53,7 @@ def main():
                     dpi.append(float(data[1]))
                     ri.append(float(data[0]))
             leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
-            for k in ['5','50', '650']:    
+            for k in ['5','50', '500']:    
                 with open(args[1+2*l]+('/ww-critical-{0}.txt'.format(k)) ,"r") as fi:
                     dpi=[]
                     ri=[]
@@ -71,7 +71,7 @@ def main():
     ax1[0].set_ylabel("$Q^2_s$",rotation="horizontal",loc='top')
     ax1[1].set_xlabel("$x$",rotation="horizontal",loc='right')
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)

### 2022-09-15 saturation-ver2/visualize-ww-gluon.py

@@ -41,7 +41,7 @@ def main():
     for l in range(2):
         ax1[l].text(1.0e-2,10,name[l],fontsize=25)
         for j in ['4']:
-            with open(args[0+2*l]+'/ww-gluon-650-'+j+'.txt' ,"r") as fi:
+            with open(args[0+2*l]+'/ww-gluon-500-'+j+'.txt' ,"r") as fi:
                 dpi=[]
                 ri=[]
                 for i in fi:
@@ -49,7 +49,7 @@ def main():
                     dpi.append(float(data[1]))
                     ri.append(float(data[0]))
             leg.append( ax1[l].plot(ri,dpi ,c='blue',ls="--"))
-            for k in ['5','50','650']:            
+            for k in ['5','50','500']:            
                 with open(args[1+2*l]+'/ww-gluon-{0}-'.format(k)+j+'.txt',"r") as fi:
                     dpi=[]
                     ri=[]
@@ -66,7 +66,7 @@ def main():
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
     ax1[0].set_ylabel('$\\Phi(x, k^2)$',rotation="vertical",loc='top')
     ax1[1].set_xlabel("$k^2$",rotation="horizontal",loc='right')
-    fig1.set_figheight(5)
+    fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
     if saveflag:

### 2022-09-21 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots updated

@@
 \addbibresource{./ref/FL.bib}
+\addbibresource{./ref/kutak2005.bib}
 \addbibresource{./ref/stasto2018.bib}
@@
 {\color{blue} Therefore, it has to be, to an extent, modelled.
-Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects.}\\
+Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov (BK) equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects.
+(see Ref.~\cite{kutak2005} for the comparison of a solution of the BK equation and the model we will discuss in the next section.)}\\
 In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play.

### 2022-09-21 saturation-ver2/visualize-F2.py

@@ -63,7 +63,7 @@ def main():
     
     ax1[0].legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
     ax1[0].set_ylabel("$F_2$",rotation="vertical",loc='top',fontsize=13)
-    ax1[1].set_xlabel("$Q^2 \\;(\\mathrm{GeV^2})$",rotation="horizontal",loc='right',fontsize=13)
+    ax1[1].set_xlabel("$Q^2 \\;[\\mathrm{GeV^2}]$",rotation="horizontal",loc='right',fontsize=13)
     fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.95, left=0.11)

### 2022-09-21 saturation-ver2/visualize-FL.py

@@ -81,7 +81,7 @@ def main():
 #################################################
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     ax1[0].set_ylabel("$F_L$",rotation="vertical",loc='top')
-    ax1[1].set_xlabel("$Q^2 \\;(\\mathrm{GeV^2})$",rotation="horizontal",loc='right')
+    ax1[1].set_xlabel("$Q^2 \\;[\\mathrm{GeV^2}]$",rotation="horizontal",loc='right')
     fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.95, left=0.11)

### 2022-09-21 saturation-ver2/visualize-critical.py

@@ -68,7 +68,7 @@ def main():
         ax1[l].grid('true')
 ################################# 
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
-    ax1[0].set_ylabel("$Q^2_s \\;(\\mathrm{GeV}^2)$",rotation="vertical",loc='top')
+    ax1[0].set_ylabel("$Q^2_s \\;[\\mathrm{GeV}^2]$",rotation="vertical",loc='top')
     ax1[1].set_xlabel("$x$",rotation="horizontal",loc='right')
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
     fig1.set_figheight(4)

### 2022-09-21 saturation-ver2/visualize-dipole.py

@@ -62,7 +62,7 @@ def main():
         ax1[l].grid('true',which='major')
     ax1[0].legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
     ax1[0].set_ylabel("$\\sigma/\\sigma_0$",rotation="vertical",loc='top')
-    ax1[1].set_xlabel("$r\\;(\\mathrm{GeV}^{-1})$",rotation="horizontal",loc='right')
+    ax1[1].set_xlabel("$r\\;[\\mathrm{GeV}^{-1}]$",rotation="horizontal",loc='right')
     fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.11, right=0.95, top=0.95, left=0.11)

### 2022-09-21 saturation-ver2/visualize-gluon.py

@@ -69,7 +69,7 @@ def main():
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
     ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k^2)$',rotation="vertical",loc='top')
-    ax1[1].set_xlabel("$k^2\\;(\\mathrm{GeV}^2) $",rotation="horizontal",loc='right')
+    ax1[1].set_xlabel("$k^2\\;[\\mathrm{GeV}^2] $",rotation="horizontal",loc='right')
     fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)

### 2022-09-21 saturation-ver2/visualize-ww-critical.py

@@ -68,7 +68,7 @@ def main():
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     #ax1.legend([leg[0][0],leg[3][0]],['Without Sudakov','With Sudakov'])
     #ax1.grid('true')
-    ax1[0].set_ylabel("$Q^2_s$",rotation="horizontal",loc='top')
+    ax1[0].set_ylabel("$Q^2_s\\;[\\mathrm{GeV^2}]$",rotation="horizontal",loc='top')
     ax1[1].set_xlabel("$x$",rotation="horizontal",loc='right')
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)
     fig1.set_figheight(4)

### 2022-09-21 saturation-ver2/visualize-ww-gluon.py

@@ -65,7 +65,7 @@ def main():
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
     ax1[0].set_ylabel('$\\Phi(x, k^2)$',rotation="vertical",loc='top')
-    ax1[1].set_xlabel("$k^2$",rotation="horizontal",loc='right')
+    ax1[1].set_xlabel("$k^2\\;[\\mathrm{GeV^2}]$",rotation="horizontal",loc='right')
     fig1.set_figheight(4)
     fig1.set_figwidth(10)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)

### 2023-01-04 saturation-ver3/Functions/cubaintegral.cc
optimizing...

@@ -27,10 +27,10 @@ extern PREC INT_PREC;
 #endif
 
 inline PREC modx(const PREC x, const PREC Q2, const  PREC mf2){
-	if(std::isnan(x+Q2+mf2+mf2/Q2)+std::isinf(x+Q2+mf2+mf2/Q2)!=0){
-				printf("modx:: Q2=%.3le x=%.3le mf2=%.3le\n",(double)Q2,(double)x,(double)mf2);
-				getchar();
-	}
+	//if(std::isnan(x+Q2+mf2+mf2/Q2)+std::isinf(x+Q2+mf2+mf2/Q2)!=0){
+	//			printf("modx:: Q2=%.3le x=%.3le mf2=%.3le\n",(double)Q2,(double)x,(double)mf2);
+	//			getchar();
+	//}
 #if MODX==1
 	return( (x*(1+4*mf2/Q2)));
 #else 
@@ -38,23 +38,18 @@ inline PREC modx(const PREC x, const PREC Q2, const  PREC mf2){
 #endif
 }
 
-double change_var(PREC*  __restrict var,PREC*  __restrict  jac,const PREC min, const PREC max){//This version is regular at max->Inf
-	PREC scale=0;	
-	scale=(max-min);
-	*jac=scale*2*(*var);
-	*var=min+scale*pow(*var,2);
-		
-	return *var;
+double change_var(PREC& var,PREC&  jac,const PREC min, const PREC max){//This version is regular at max->Inf
+	PREC scale=(max-min);
+	jac=scale*2*var;
+	var=min+scale*pow(var,2);
+	return var;
 }
-double change_var2(PREC*  __restrict var,PREC*  __restrict  jac,const PREC min, const PREC max){//This version is regular at max->Inf
-	PREC scale=0;
-	scale=(max-min);
-	PREC a1=*var;
-	PREC a2=1-a1;
-	PREC den=scale*a2+a1;
-	*jac=pow(scale/den,2);
-	*var=(min*(scale)*a2+max*a1)/den;	
-	return *var;
+double change_var2(PREC & var,PREC &  jac,const PREC min, const PREC max){//This version is regular at max->Inf
+	PREC scale=(max-min);
+	PREC den=scale*(1-var)+var;
+	jac=pow(scale/den,2);
[…]

### 2023-01-04 saturation-ver3/Functions/fcn.h

@@ -16,34 +16,34 @@
 	#define RFORMULA 0
 #endif
 
-extern double F2_kt(const  PREC,const  PREC,const PREC, const PREC*);
+extern double F2_kt(const  PREC,const  PREC,const PREC, const PREC(&)[]);
 //extern double F2_r(const double,double,double,double*);
 class KtFCN : public ROOT::Minuit2::FCNBase {
 	
 	
 	private:	
-		double *Q2_DATA=(double*)malloc(0);
-		double *X_DATA=(double*)malloc(0);
-		double *CS_DATA=(double*)malloc(0);
-		double *ERR_DATA=(double*)malloc(0);
+		double *__restrict Q2_DATA=(double*)malloc(0);
+		double *__restrict X_DATA=(double*)malloc(0);
+		double *__restrict CS_DATA=(double*)malloc(0);
+		double *__restrict ERR_DATA=(double*)malloc(0);
 		
 		void data_alloc(int n){
 			MAX_N=n;
-			Q2_DATA=(double*)realloc(Q2_DATA,MAX_N*sizeof(double));
-			X_DATA=(double*)realloc(X_DATA,MAX_N*sizeof(double));
+			Q2_DATA=(double*  )realloc(Q2_DATA,MAX_N*sizeof(double));
+			X_DATA=(double* )realloc(X_DATA,MAX_N*sizeof(double));
 			CS_DATA=(double*)realloc(CS_DATA,MAX_N*sizeof(double));
 			ERR_DATA=(double*)realloc(ERR_DATA,MAX_N*sizeof(double));
 		}
 		double Up() const {return 1;}
 		
 	public:
-		unsigned MAX_N=600;
-		KtFCN(std::string data_file ){
+		unsigned MAX_N=0;
+		explicit KtFCN(std::string data_file ){
 		//KtFCN(char* data_file){
 			data_alloc(500);
-			double alpha =1.0/137 ;//fine structure const 1/137;
-			double xmp0 = 0.93827;//proton mass in GeV
-			double units =1.0/389.40; //2.56819e-3; //micro-barn to GeV^-2
+			const double alpha =1.0/137 ;//fine structure const 1/137;
+			const double xmp0 = 0.93827;//proton mass in GeV
[…]

### 2023-01-04 saturation-ver3/Functions/main-2.cc

@@ -102,7 +102,10 @@ int main(int argc, char** argv){
 		upar.SetLimits(par_name[i],par_min[i],par_max[i]);//use migrad.removeLimits(<name>);
 	}
 	
+	ROOT::Minuit2::MnMachinePrecision prec;
+	prec.SetPrecision(1.0e-8);
 	INT_PREC=1.0e-2;
+	prec.SetPrecision(INT_PREC);
 	printf("*****************************\n");
 	printf("*** Simplex: eps=%.1e  ***\n",(double)INT_PREC);
 	printf("*****************************\n");
@@ -122,6 +125,7 @@ int main(int argc, char** argv){
 	save_res(((std::string)argv[1])+"/result.txt",&min,&theFCN,N_PAR-skip);
 	
 	INT_PREC=1.0e-3;
+	prec.SetPrecision(INT_PREC);
 	printf("*****************************\n");
 	printf("*** Simplex: eps=%.1e  ***\n",(double)INT_PREC);
 	printf("*****************************\n");
@@ -138,8 +142,6 @@ int main(int argc, char** argv){
 		
 	save_res(((std::string)argv[1])+"/result.txt",&min,&theFCN,N_PAR-skip);	
 
-	ROOT::Minuit2::MnMachinePrecision prec;
-	prec.SetPrecision(1.0e-8);
 
 	
 	ROOT::Minuit2::MnMigrad migrad(theFCN, min.UserParameters() ,0);
@@ -149,11 +151,12 @@ int main(int argc, char** argv){
 	
 
 	INT_PREC=1.0e-3;
+	prec.SetPrecision(INT_PREC);
 	printf("***************************\n");
 	printf("*** First: eps=%.1e  ***\n",(double)INT_PREC);
 	printf("***************************\n");
 	for(int i=0;i<10;i++){
-		min=migrad(20,1);
+		min=migrad(20,10);
 		flag=check_min(&min,N_PAR-skip);
 		if( flag==0){
 			min_prev=min;
@@ -172,13 +175,14 @@ int main(int argc, char** argv){
 	
 	save_res(((std::string)argv[1])+"/result.txt",&min,&theFCN,N_PAR-skip);	
 	INT_PREC=1.0e-4;
+	prec.SetPrecision(INT_PREC);
 	printf("***************************\n");
 	printf("*** Second: eps=%.1e  ***\n",(double)INT_PREC);
[…]

### 2023-01-04 Document/Sudakov effects and the dipole amplitude/Acta Phys Pol/low-x.tex

\documentclass{appolb}

\usepackage{ragged2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[
%backend=biber,
%style=ieee
maxbibnames=10,
%backend=bibtex,
natbib=true,
sorting=none
%backend=biber,
%style=apa
]{biblatex}
\addbibresource{./ref.bib}
\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\begin{document}
\title{Effects of the Sudakov form factor in the Golec-Biernat--W\"usthoff saturation model
\thanks{Presented at ``Diffraction and Low-$x$ 2022'', Corigliano Calabro (Italy), September 24-30, 2022.}
}
%\author{
%T.~Goda,$^1$, K.~Kutak$^{1,2}$ and S.~Sapeta$^1$\\\,\\
%$^1$ 
%{\small\it The H.\ Niewodnicza\'nski Institute of Nuclear Physics PAN,}\\ 
%{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\\,\\
%$^2$ 
%{\small\it Physics Department, Brookhaven National Laboratory,}\\
%{\small\it Upton, NY 11973, USA}\\
%}	 
\author{Tomoki Goda%, Sebastian Sapeta
\address{H. Niewodniczański Institute of Nuclear Physics,\\
	Radzikowskiego 152, 31-342 Cracow, Poland}\\
%	\vspace{3mm}
%	Krzysztof Kutak
%\address{ Physics Department, Brookhaven National Laboratory,\\
%Upton, NY 11973, USA\\
%H. Niewodniczański Institute of Nuclear Physics,\\
%	Radzikowskiego 152, 31-342 Cracow, Poland}\\
%Sebastian Sapeta
%\address{H. Niewodniczański Institute of Nuclear Physics,\\
%	Radzikowskiego 152, 31-342 Cracow, Poland}\\
}
%\address{
%in collaboration with K.~Kutak, S.~Sapeta
%}
%}
\maketitle
\begin{abstract}
We incorporate  the Sudakov form factor into the Golec-Biernat--W\"usthoff and Bartels--Golec-Biernat--W\"usthoff saturation models. The parameters are fitted to the HERA data. Both the models show considerable improvements in the fit quality.
\end{abstract}
\section{Introduction}
In the dipole picture of Deep Inelastic Scattering~(DIS), one can factorize the scattering cross section into the photon wave function $\Psi(z,x,Q)$ which describes the fluctuation of a photon with virtuality $Q^2$ splits into a quark--anti-quark pair with light-cone momentum fractions $z$ and $1-z$ respectively, and the dipole cross section $\sigma_\mathrm{dipole}(x,r)$ which describes the interaction of the $q\overline{q}$ pair of size $r$, with the proton~\cite{Golec-Biernat:1998zce, Kovchegov:2012mbw}. One may obtain $\sigma_\mathrm{dipole}$ from appropriate evolution equations such as Balitsky--Kovchegov~\cite{Balitsky:1995ub,Kovchegov:1999yj}
, however it is often useful to have a simple model.
The dipole cross section and the dipole unintegrated gluon distribution, $\mathcal{F}(x,k_t^2)$, are related to each other by~\cite{Golec-Biernat:1999qor,Bartels:2002cj}
\begin{align} 
    \sigma_{\mathrm{dipole}}(x,r) &= \frac{4 \pi}{N_c} \int\frac{d^2 \mathbf{k}_t }{k_t^2} \alpha_s \mathcal{F}(x, k_t^2) (1-e^{i {\mathbf{k}_t\cdot \mathbf{r}}}),
    \label{eq:ugdtosigma}\\
    \alpha_s \mathcal{F}(x,k_t^2) &= \frac{N_c }{4 \pi}\int \frac{d^2  \mathbf{r}}{(2\pi)^2} e^{i {\mathbf{k}_t\cdot \mathbf{r}}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dipole}}(x,r).
    \label{eq:sigmatougd}
\end{align}
We use these relations to incorporate the Sudakov form factor in the dipole cross section, which introduces the hard scale $Q^2$ dependence. As the hard scale dependence is subleading in the leading $\ln(1/x)$ approximation\cite{Kimber:1999xc, Kimber:2000bg}, one expects to improve the description of the moderate-$x$ region.

\section{GBW/BGK models, and the Sudakov form factor}
%In this section the, two models to which we incorporate the Sudakov factor, namely the Golec-Biernat--W\"usthoff (GBW)~\cite{Golec-Biernat:1998zce} and Bartels--Golec-Biernat--Kowalski (BGK)~\cite{Bartels:2002cj} models, are summarized.
The dipole cross section in the Golec-Biernat--W\"usthoff~(GBW) model reads~\cite{Golec-Biernat:1998zce}
\begin{align}
\sigma_\mathrm{GBW}(x,r) &=\sigma_0 \left(1-e^{-r^2 Q_s^2(x)/4}\right), & \mathrm{where}\;\; Q^2_s(x)&=\left(\frac{x_0}{x}\right)^{\lambda}.
\label{eq:sigma-gbw}
\end{align}
%The important feature of this form is that the dipole cross section behaves like $\sim r^2$ in the small-$r$ region while it saturates to a constant value $\sigma_0$ when $r$ is large. The separation of such regions are controlled by the $x$-dependent saturation  scale $Q_s^2(x)$.  
%In order to account for the correct small-$r$ limit of the dipole cross section, Bartels--Golec-Biernat--Kowalski~\cite{Bartels:2002cj} proposed an improved version in which
Whereas in Bartels--Golec-Biernat--Kowalski~(BGK) model~\cite{Bartels:2002cj},
$Q^2_s(x)= \frac{4\pi^2 \alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0} $,
%\begin{equation}
%\sigma_\mathrm{BGK}(x,r) \\=\sigma_0 \left[ 1-\exp\left( - \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0} \right) \right],
%\label{eq:sigma-bgk}
%\end{equation}
where $\mu^2=\frac{C}{r^2} + \mu_0^2$ and the initial condition for the gluon distribution $g(x,Q_0^2)=A_g x^{-\lambda_g}(1-x)^{5.6}$.
%With this improvement, DGLAP evolution was incorporated 
This enhances the large-$Q^2$~($\sim 1/r^2$) of the dipole cross section. \\
%\section{The Sudakov form factor}
In Ref.~\cite{Mueller:2012uf, Mueller:2016gko}, it was shown that resummation of $\ln(1/x)$ and $\ln(Q^2/k_t^2)$ can be achieved consistently, and in Ref.~\cite{Xiao:2017yya} the Sudakov factor for the dipole unintegrated gluon density was computed. 
Combining Eqs.~(\ref{eq:ugdtosigma})~and~(\ref{eq:sigmatougd}), and generalizing the formula following Ref.~\cite{Xiao:2017yya}, one obtains,
\begin{equation}
    \sigma_{\mathrm{dipole}}(x,r,Q^2) =\int^r _0 d {r'}   {r'}  \ln\left(\frac{r}{{r'} }\right)  e^{-S({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dipole}}(x,{r'} ),
    \label{eq:gbssigma}
\end{equation}
where we employ this Sudakov factor at the leading order~\cite{Xiao:2017yya}
\begin{equation}
    S^{(1)}_\mathrm{pert}(r,Q^2)=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \ln\left(\frac{Q^2}{\mu^2}\right),
    \label{eq:sudakov}
\end{equation}
and
 $\alpha_s(\mu^2)=\left(b_0 \ln\left(\mu^2/\Lambda^2_\text{QCD}\right) \right)^{-1}$. This formula (Eq.~(\ref{eq:gbssigma})) is general, that is, it can be used for any dipole cross section.
The lower limit $\mu_b^2=C/r^2$ where $C=(2e^{-\gamma_E})^2$. %However, commonly one uses so-called ``$b_*$-prsctiption''~\cite{Collins:1984kg, Prokudin:2015ysa} in which $\mu_b^2=C/r^2+\mu^2_0$ with some scale $\mu_0\gtrsim1\;\mathrm{GeV}$, 
%in order to freeze the Sudakov factor in the non-perturbative region. 
However, in this study, we shall employ, for both $g(x,\mu^2)$ and the Sudakov factor, an alternative form of $\mu$ and $\mu_b$ proposed in Ref.~\cite{Golec-Biernat:2017lfv} in order to freeze the value in the non-perturbative region: $
%\begin{equation}
    \mu^2= \mu_0^2/(1-\exp[{-r^2 \mu_0^2 / C  }]).
%    \label{eq:newstar}
%\end{equation}
$
%As discussed later, we neglect non-perturbative sudakov factor~\cite{Collins:1984kg, Prokudin:2015ysa} in the present study.\\
%Some comments are in order on the new dipole cross section, Eq.~(\ref{eq:gbssigma}).
%Firstly, the Sudakov-improved dipole cross section is now hard scale, $Q^2$, dependent, where the hard scale dependence is sub-leading in the leading $\ln(1/x)$ approximation.
%Secondly, 
As for the small values of $r$, we only allow the region $\mu_b^2<Q^2$  in the integration of Eq.~(\ref{eq:sudakov}), such that the contribution of the Sudakov factor is in the region $1/r^2\sim k^2_t\ll Q^2$. That is to say in the small-$Q^2$ or small-$r$ limit where $\mu_b^2>Q^2$, one simply recovers the original GBW/BGK dipole cross section.

\begin{figure*}[t]
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{./dipole.png}
		\caption{%$\sigma_{\mathrm{dipole}}/\sigma_0$ at $Q^2=100\;\mathrm{GeV^2}$,\\ $x=10^{-2},\;10^{-4},\; 10^{-6}$.% (from bottom to top).
		}
		\label{fig:dipole}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./gluon.png}
		\caption{%$\alpha_s\mathcal{F}(x,k_t^2,Q^2)$ at $x=10^{-4}$,\\$Q^2=5, \;50 ,\; 500\; \mathrm{GeV^2}$.% (from top to bottom). }%Notice the broadening effect of the Sudakov factor, particularly towards the small value of $k_t^2$.
		}
		\label{fig:gluon}
	\end{subfigure}
	\caption{Left: $\sigma_{\mathrm{dipole}}/\sigma_0$ at $Q^2=100\;\mathrm{GeV^2}$, $x=10^{-2},\;10^{-4},\; 10^{-6}$ (from bottom to top). Right: $\alpha_s\mathcal{F}(x,k_t^2,Q^2)$ at $x=10^{-4}$, $Q^2=5, \;50 ,\; 500\; \mathrm{GeV^2}$ (from top to bottom).
	}
\end{figure*}
\begin{figure*}[t]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./BGK-hardscale-175.png}
		%\subcaption{BGK, $Q^2=175\;\mathrm{GeV^2}$}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./KS-hardscale-180.png}
		%\subcaption{KS, $Q^2=180\;\mathrm{GeV^2}$}
	\end{subfigure}
	\caption{Comparisons of hard-scale-independent and hard-scale-dependent gluon densities. }
	\label{fig:3d}
	%\end{figure*}
%\begin{figure*}[t]
%\begin{subfigure}{0.8\textwidth}
%\centering
%   \includegraphics[width=\textwidth]{./critical.png}
%  \caption{Saturation scale $Q_s^2(x)$. The line was plotted for $Q^2=100\;\mathrm{ GeV^2}$.}
% \label{fig:critical}
%    \end{subfigure}
\end{figure*}
\begin{figure*}[t]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./F2-data-GBW-lim1.png}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{./F2-data-BGK-lim1.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{./F2-data-GBWhist.png}
		\subcaption{GBW}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{./F2-data-BGKhist.png}
		\subcaption{BGK}
	\end{subfigure}
	\caption{Top: Comparison of original (dashed blue) and Sudakov-improved (solid red) with  HEAR data (green error bars) at selected $Q^2=0.11,\;0.5,\;6.5,\;18,\;45,\;500\;\mathrm{GeV^2}$. Bottom: $\chi^2/\text{(no. of data)}$ at each $Q^2$.}
	\label{fig:grid}
\end{figure*}
\begin{table*}[t]
	\centering
	\begin{subtable}{0.65\textwidth}
		\centering
		\vspace{1mm}\resizebox{0.75\textwidth}{!}{
		\begin{tabular}{|c|c|c|c|c|}
		\hline
		  &  $\sigma_0 \;[\mathrm{mb}]$ &  $x_0 (10^{-4})$ &  $\lambda$ &  $\chi^2/\mathrm{dof}$ 
		\\\hline
		$\mathrm{GBW}$ & 19.1 & 2.58 & 0.322 & 4.44 \\ \hline
		$\mathrm{GBW+Sud}$& 18.6 & 3.11 & 0.299 & 2.66 \\ \hline
		\end{tabular} 
		}
		\vspace{1mm}
	\end{subtable}

	\centering
	\begin{subtable}{0.65\textwidth}
		\centering
		\vspace{1mm}
		\resizebox{\textwidth}{!}{
		\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		&  $\sigma_0\; [\mathrm{mb}]$ &  $A_{\mathrm{g}}$ &  $\lambda_{\mathrm{g}}$ &  $C$ &  $\mu_{0}^2\;[\mathrm{GeV^2}]$ &  $\chi^2/\mathrm{dof}$ 
		\\\hline
		$\mathrm{BGK}$ & 23.3 & 1.18 & 0.0832 & 0.329 & 1.87 & 1.56 \\ \hline
		$\mathrm{BGK+Sud}$ & 22.2 & 8.67 & -0.500 & 0.670 & 3.83 & 1.21 \\ \hline
		\end{tabular} 
		}
		\vspace{1mm}
	\end{subtable}
	\caption{ The parameters and $\chi^2$ per degrees of freedom of the GBW and BGK models (with and without the Sudakov factor, Eq.~(\ref{eq:sudakov})) for cases with mssless light quarks.}
	\label{table:fitresults}
	\vspace{2mm}
	\centering
	\begin{subtable}{0.33\textwidth}
		\centering 
		\resizebox{\textwidth}{!}{
		\begin{tabular}{|c|c|c|}
		\hline
		$Q_{\mathrm{up}}^2 \;[\mathrm{GeV^2}]$&  GBW & GBW+Sud 
		\\\hline
		5 & 1.55 & 1.55 \\ \hline
		%25 & 1.46  & 1.41 \\ \hline
		50 & 1.97  & 1.83 \\ \hline
		%100 & 2.36  & 2.15 \\ \hline
		650 & 4.44  & 2.66 \\ \hline
		\end{tabular} 
		}
	\end{subtable}
	\hspace{4mm}
	\begin{subtable}[t]{0.33\textwidth}
		\resizebox{\textwidth}{!}{
		\begin{tabular}{|c|c|c|}
		\hline
		$Q_{\mathrm{up}}^2 \;[\mathrm{GeV^2}]$&  BGK & BGK+Sud
		\\\hline
		5 & 1.63  & 1.59 \\ \hline
		%25 & 1.42 & 1.30 \\ \hline
		50 & 1.52  & 1.23 \\ \hline
		%100 & 1.55  & 1.25 \\ \hline
		650 & 1.56  & 1.21 \\ \hline
		\end{tabular}
		}
	\end{subtable}
	\caption{Comparison of the quality of fits with different upper limits $Q^2_{\mathrm{up}}\; \mathrm{[GeV^2]} $ of the hard scale. }
	\label{table:Qup}
\end{table*}
\section{Results}
The parameters in the Sudakov form factor is fixed at $C=(2^{-\gamma_E})^2\approx1.26$ and $\mu_{0S}^2=2\mathrm{GeV^2}$, and hence no new fit parameters are needed.
The parameters of GBW and BGK models $\{\sigma_0, x_0,\lambda\}$ and $\{\sigma_0,A_g,\lambda_g,C,\mu_0\}$ respectively are fitted to the HERA data~\cite{Abt:2017nkc} with $x<10^{-2}$ and $0.045\mathrm{GeV^2}\leq Q^2\leq 650\mathrm{GeV^2}$. % using MINUIT package~\cite{minuit}. 
As it was the case for Ref.~\cite{Golec-Biernat:2017lfv}, the fit qualities are better for the cases with massless light quarks, therefore we only present the results with the massless light quarks. Since for the range of $Q^2$ we are interested,  $c$, $b$ quarks contribute, and thus they are included with mass $m_c=1.3\;\mathrm{GeV}$, and $m_b=4.6\;\mathrm{GeV}$ respectively. The choice of  $\mu_{0S}^2$ is somewhat arbitrary, however, preliminary fits showed, for sufficiently small value of $\mu_{0S}^2$, the contribution of the non-perturbative Sudakov factor can be neglected. %Therefore, while it is interesting to see that non-perturbative Sudakov factor indeed compensates for the effect of $\mu_{0S}^2$, for simplicity, we chose $\mu_{0S}^2=2$.\\
The results of the fits are presented in Tab.~\ref{table:fitresults}. One can see that both the GBW and BGK models have improved considerably. One noticeable change in the parameters is that $\lambda_g$ of BGK model has become negative. As discussed in~\cite{Bartels:2002cj} this implies that the strong rise of the integrated gluon density, $g(x,\mu^2)$, at small $x$  is solely due to DGLAP evolution. While the full result of Tab.~\ref{table:fitresults} is fitted to the data $Q^2<650\mathrm{GeV}^2$,  Tab.~\ref{table:Qup} shows the fit results with several upper limit of $Q^2$, $Q_\mathrm{up}^2$. This clearly shows that the Sudakov-improved models have better tolerance for a wide range of $Q^2$. Particularly the fit quality of the BGK model no longer deteriorates as the range of $Q^2$ increases.
Fig.~\ref{fig:dipole} shows the comparison of the  GBW and BGK models with their Sudakov improved versions. The initial suppression and the logarithmic rise at large-$r$ region is due to the Sudakov factor, while the differences in the small-$r$ region are solely due to the changes in the parameters, thus remain in the small-$Q^2$ limit.
Fig.~\ref{fig:gluon} shows that the incorporation of the Sudakov factor smears out the unintegrated gluon density. Consequently, $\alpha \mathcal{F}(x,_t^2 Q^2) $ no longer vanishes in the limit  $k_t^2\rightarrow 0$, which is directly related to the logarithmic rise of the dipole cross section.  While the shape of the gluon density changes, the peaks are located at the same place for various  $Q^2$, indicating little effect to the saturation scale. %(Fig.~\ref{fig:critical}).
Furthermore, one notices in Fig.~\ref{fig:3d} that the differences in the gluon density of the BGK model with and without the Sudakov factor are qualitatively similar to those of Kutak-Sapeta~(KS) gluon distribution~\cite{vanHameren:2020rqt} with and without the Sudakov effects.
Fig.~\ref{fig:grid} shows comparison of the $ F_2$ structure function computed from the models and the HERA data at selected value of $Q^2$, and the $\chi^2/\text{(no. of data)}$ at each $Q^2$. One can see for the GBW model the main improvement is from the large-$Q^2$ region. As for the BGK model one can see in the moderate-$x$ region ($\sim 10^{-2}$), the curve is slightly lifted and fits better with the data.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[H]
%\centering
%    \begin{subtable}[H]{0.45\textwidth}
%        \centering
%        \resizebox{\textwidth}{!}{
%           % \input{./GBWSnp.tex}
%            \begin{tabular}{|c|c|c|}
%\hline%
%\footnotesize	$\mu_{0S}^2[\mathrm{GeV^2}]$ & \footnotesize $\mathrm{GBW+Sud_{pert}}$ & \footnotesize $\mathrm{GBW+Sud_{pert+np}}$\\\hline
% 1 & 2.71 & 2.72 \\\hline
% 2 & 2.66 & 2.67 \\\hline
% 3 & 2.64 & 2.65 \\\hline
% 4 & 2.64 & 2.64 \\\hline
% 5 & 2.64 & 2.65 \\\hline
% \end{tabular} 
%        }
%        \hspace{3mm}
%    \end{subtable}
%    \begin{subtable}[H]{0.45\textwidth}
%        \resizebox{\textwidth}{!}{
%            %\input{./BGKSnp.tex}
%\begin{tabular}{|c|c|c|}
%\hline
%\footnotesize	$\mu_{0S}^2[\mathrm{GeV^2}]$ & \footnotesize$\mathrm{BGK+Sud_{pert}}$ & \footnotesize $ \mathrm{BGK+Sud_{pert+np}}$\\\hline
% 1 & 1.18 & 1.17 \\\hline
% 2 & 1.21 & 1.17 \\\hline
% 3 & 1.25 & 1.21 \\\hline
% 4 & 1.29 & 1.21 \\\hline
% 5 & 1.32 & 1.22 \\\hline
% \end{tabular} 
%        }
%    \end{subtable}
%    \caption{$\chi^2/\mathrm{dof}$ of fits with and without the non-perturbative Sudakov factor, with 5 values of $\mu_{0S}^2$ for the Sudakov factor. It is clear that when $\mu_{0S}^2$ is set small, the effect of non-perturbative Sudakov factor is negligible. It is interesting to see that, for the BGK model, inclusion of the non-perturbative factor indeed weakens the dependence on the choice of $\mu_{0S}$.}
%	    \label{table:Snp}
%	    \vspace{3mm}
%\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5   
%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
We have incorporated the Sudakov form factor into the GBW and BGK saturation models. The results of fitting to the HERA data shows considerable improvements for both the models. The Sudakov-improved GBW model can describe the higher-$Q^2$ region better, and the BGK model shows better fit with the data in the moderate-$x$ region. More details can be found in the forthcoming publication Ref.~\cite{Goda:2022wsc}.\\
\section*{Acknowledments}
The research was conducted under a collaboration with S. Sapeta and K. Kutak. The project is partially supported by the European Union’s Horizon 2020 research and innovation program under grant agreement No. 824093, and the author is supported by the Polish National Science Centre grant no. 2017/27/B/ST2/02004.
\printbibliography

\end{document}

### 2023-01-09 saturation-ver3/kt-formula-report1/kt-formula-report1.tex

\documentclass[12pt]{article}

%\usepackage[T1]{fontenc}
%\usepackage{merriweather}
%\usepackage{librebaskerville}
\usepackage{xcolor}
\usepackage[]{geometry}

\geometry{left=2cm,right=2cm,top=2.5cm,bottom=2cm}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{decorations}
 \usetikzlibrary{snakes}
\begin{document}
\pagestyle{fancy}
\fancyhead[L]{\today}
\fancyhead[R]{Tomoki Goda}
%{\centering\huge On GBW model and $k_t$-factorization.}\hrule\vspace{2cm}

\section{Formula. etc}
\begin{figure}[t]
\centering
\resizebox{0.5\textwidth}{!}{
\begin{tikzpicture}
\draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
\draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
\draw(-0.5in , 0in)--(0.5in,0in)--(0.5in , -0.5in)--(-0.5in,-0.5in)--cycle ;
\draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
\draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
\draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
\draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
}
\caption{\footnotesize Kinematic variables of gluon contribution to $\mathcal{F}$.  The momentum fraction of gluon is $x/z$ as it has to contribute via the quark box.
}
\label{fig:gluon-kinem}
\end{figure}
For protom momentum $p$ and photon momentum $q$,  define $q'\equiv q+x p$. 
Then the Sudakov decomposition of $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) are
$\kappa=\alpha p-\beta q'+\kappa_t$, and $k=a p- bq'+k_t$.

Eq.~(3.9) of Kimber's thesis reads
\begin{multline}
F_2(x,Q^2)=\sum_f f_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_t^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s \mathcal{F}(x/z,k_t^2)\Theta(1-x/z)\\
\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
\label{eq:angle-integrated}
\end{multline}
where ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, 
\begin{equation}
\begin{split}
\frac{I_1}{2\pi}&=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}\\
\frac{I_2}{2\pi}&=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}}\\
\frac{I_3}{2\pi}&=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}\\
\frac{I_2}{2\pi}&=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}}
\end{split}
\end{equation}
for
\begin{equation}
\begin{split}
N_1&\equiv\beta(1-\beta)Q^2+m_f^2\\
N_2&\equiv{\kappa'}_t^2+(1-\beta)^2k_t^2\\
N_3&\equiv{\kappa'}_t^2-(1-\beta)^2k_t^2\\
N_4&\equiv{\kappa'}_t^2+\beta(1-\beta)k_t^2
\end{split}
\end{equation}
and
\begin{equation}
\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
\end{equation}

The other formulae( %Eqs.~(3.6)~and~(3.7) of Kimber's thesis with addition of scale $\mu$ as in 
Eqs.~(3.11)~and~(3.12) of Kimber's thesis ) are,
\begin{align}
\begin{split}
F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
\left[\beta^2+(1-\beta)^2\right]
\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right]\label{eq:angle-unintegratedT}
\end{split}\\
\begin{split}
F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}&\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)\\
&\left[
4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
\right],\label{eq:angle-unintegratedL}
\end{split}
\end{align}
where
\begin{equation}
\begin{split}
D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2\\
D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
\end{split}
\end{equation}
%In this case, one has additional integral of $\phi$
Except for the coupling, this is $\phi$,  the angular part of $\kappa_t$, unintegrated version of Eq.~(\ref{eq:angle-integrated}) .
The scale for $\alpha_s$ is suggested to be 
\begin{equation}
\mu^2=k^2_t+\kappa^2+m_f^2.
\label{eq:scale}
\end{equation}
Note, the integration limits of $k_t$ and $\kappa_t$ are removed as GBW gluon is not perturbative.

\section{Discussion}
\subsection{Theta function, integration limits and modified $x$}
The theta function restricts
\begin{equation}
1-x\left(1+\frac{{\kappa'}_t^2+m^2}{\beta(1-\beta)Q^2}+\frac{k_t^2}{Q^2}\right)>0.
\end{equation}
Consequently, the limit $Q^2\rightarrow0$ vanishes.
It seems, it may no longer be necessary to use massive light quarks and modified $x$.

Additionally, it restricts respectively,
\begin{align}
&\frac{1-x}{x}Q^2-4m^2>k^2,\\
&\frac{1}{4} \frac{1-x}{x}Q^2-m^2>{\kappa'}_t^2,\\
&\frac{1-\sqrt{1-\frac{4m^2}{\frac{1-x}{x} Q^2  }}}{2}<\beta< \frac{1+\sqrt{1-\frac{4m^2}{\frac{1-x}{x} Q^2  }}}{2},
\end{align}
consequently
\begin{align}
1>&\frac{4m^2}{\frac{1-x}{x} Q^2 }&& \rightarrow& x&<\frac{1}{1+\frac{4m^2}{Q^2}}.
\end{align}
That is, 
\begin{equation}
x_{m}<1.
\end{equation}
Now, considering that $x_m$ was $x$ of GBW gluon $\mathcal{F}(x,k^2)$, $x/z<1$ and the treatment of GBW with $x_m$ seem to correspond to each other.

\subsection{Which formula(e) to be used.}
Eq.~(\ref{eq:angle-integrated}) is relatively straight forward to implement, and \underline{\textbf{currently used}}. \\
Eqs.~(\ref{eq:angle-unintegratedT})~(\ref{eq:angle-unintegratedL}) are more difficut due to the additional angular integral. However, it is necessary should one intend to use the running coupling with argument suggested in Kimber's formula (Eq.~(\ref{eq:scale})).
\subsection{Preliminary data}
\begin{figure}
\includegraphics[width=0.5\textwidth]{./preliminary.png}
\includegraphics[width=0.5\textwidth]{./preliminary-dipole.png}
\caption{\footnotesize Preliminary result for \underline{\textbf{selected}} combinations of \{fixed $\alpha_s$ (``fix"), running $\alpha_s$ (``run")\}  $\otimes$ \{ modified $x$ (``mod"), Bjorken $x$ (``Bjor")\}  $\otimes$ \{$\sigma_\mathrm{dipole}$ formula (``r"), $\mathcal{F}$ formula (``")\}.
By running, it does not mean using Eqs.~(\ref{eq:angle-unintegratedT})~(\ref{eq:angle-unintegratedL}), but simply multiplying GBW $\mathcal{F}$ by $\frac{ \alpha(\mu^2) }{0.2}$, where $\alpha(\mu^2)=\frac{1}{b_0 \log\left(\frac{\mu^2}{\Lambda_\mathrm{QCD} }\right)}$ and $\mu^2=\max( k^2_t+{\kappa'}_t^2+m_f^2,2\Lambda_\mathrm{QCD})$. (!!NOTE!!, it is ${\kappa'}_t$ being used here, not $\kappa_t$ as in the Kimber's formula ! (cf. Eq.~(\ref{eq:scale})).\\
Left:$ \alpha_s\mathrm{F}$, Right: $\sigma/\sigma_0$. (note, it is not $\alpha_s(\mu^2)$ for running case when plotted.) $Q^2=100\mathrm{GeV^2}$, $x=10^{-4}$.
}
\end{figure}

\begin{itemize}
\item all comparable $\chi^2 $. 
\begin{itemize}
\item $\alpha, x_m\;\sim5.4$, 
\item $\alpha, x_B\;\sim4.4$,
\item $\alpha, x_m, r\;\sim4.4$, 
\item $\alpha(\mu), x_B\;\sim4.0$
\end{itemize}
$\rightarrow$ modification of $x$ is worsening.
Later shown, theta function should deal with the photo production. There may not be necessity any more.\\
\item most noteble difference is $\sigma_0$
\begin{itemize}
\item $\alpha, x_m\;\sim32$, 
\item $\alpha, x_B\;\sim33$,
\item $\alpha, x_m, r\;\sim19$, 
\item $\alpha(\mu), x_B\;\sim44$
\end{itemize}
$\rightarrow$ Generally the $k_t$ versions have much higher $\sigma_0$.
Note, Massive light quarks case has higher $\sigma_0$. Probably due  to the suppression by $x(1+4m^2/Q^2)$.

\section{Concluding Remarks}
\begin{itemize}
\item modified $x$ deteriorates the fit while there is no longer apparent necessity.
\item Even with incorrect(?) incorporation of $\alpha_s(\mu)$, it has positive effect on the fit. 
\item biggest difference in the fit paramaeters is the normalization $\sigma_0$. 
\end{itemize}
\end{itemize}

\section{Code, technicality}
The fitting program has been rewritten completely in order to accommodate C++  Minuit2 and OOP. \\
The repository is \\
\textit{ git@github.com:Tomoki-Goda/Saturation-Model.git }\\
At the early stage of development the integrations were done with private implementations of Gauss-Legendre quadrature, Curtis-Clenshaw quadrature, or CERNLIB subroutines(mostly DGAUSS). 
These functions (mostly the Clensaw-Curtis function is used for speed and flexibility) are not very tolerant for step by the theta function. Besides, the Clenshaw method has to take end points of the integration region, making it unsuitable for cases where integrand is numerically ill defined at the end points.
Cuba package has been implemented. Cuhre works similar to previous versions in terms of performance (except for possiblly better handling of failure). Vegas and Suave takes too long (possibly not optimized).

\section{Changes of variables}
For $x=[0,1]$ and $y=[a,b]$, one can use following changes of variables:
\begin{align}
y&=b x+a(1-x), \\
y&=a\left(\frac{b}{a}\right)^x,\\
y&=\frac{a(b-a)(1-x)+x b}{(b-a)(1-x)+x}.
\end{align}
Note, only the third one can be used for $a=0, b=\infty$, where $y=\frac{x}{1-x}$.

Then using this, 
\begin{equation}
\int^u_l dy f(y)=\int^1_0 \left(\frac{dy}{dx}\right) dx f(y(x;l,u)).
\end{equation}
For a multidimensional case, one may have
\begin{equation}
\begin{split}
\int^{u_1}_{l_1} dy_1\int^{u_2}_{l_2} dy_2 f(y_1,y_2)& \Theta(\dots)\\
=\int^1_0\int^1_0& \left(\frac{\partial y_1}{\partial x_1}\right) \left(\frac{\partial y_2}{\partial x_2}\right)dx_1 dx_2 f\left(y_1(x_1; l ,u ),y_2(x_2; l_2(x_1) ,u_2(x_1 ) )\right).
\end{split}
\end{equation}
\section{Peak}
Ignoring the theta function, and if we take limits $m_f^2\rightarrow0,\;\beta\rightarrow0$, 
the donominators of $I_i$, $N_1^2+2N_1N_2+N_3^2\rightarrow {\kappa'}_t^2-k_t^2$.
that is, when $\beta$ is small , one has a ridge at ${\kappa'}_t^2=k_t^2$ (We never actually hit the singular point as thetha function restrict lower limit of $\beta$. ).

When there is a integrable peak at $x\sim0$ of $[0,1]$, one may use $x\rightarrow {x'}^2$. 
consider when integrating 
\begin{equation}
\frac{1}{\sqrt{(x_1-x_2)^2}+\epsilon},
\end{equation}
for small $\epsilon$.
 then one use
\begin{align}
x_1 &\rightarrow (1-{x'}_1) x_2& x_2 &\rightarrow (1-{x'}_2) x_1
\end{align}
then
\begin{align}
x_2&\frac{1}{ ({x'}_1 x_2)+\epsilon}& x_1&\frac{1}{({x'}_2 x_1)+\epsilon}
\end{align}

\input{r-formula}
\end{document}

### 2023-01-24 saturation-ver2/Plotting/visualize-gluon-x.py
interpolation

@@ -68,7 +68,7 @@ def main():
     #ax1.legend([leg[0][0],leg[1][0],leg[2][0]],['Without Sudakov','With Sudakov $Q^2=100\\;\\mathrm{GeV}^2$','With Sudakov $Q^2=650\\;\\mathrm{GeV}^2$'])
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
-    ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k_t^2,Q^2)$',rotation="vertical",loc='top')
+    ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k_t^2)$',rotation="vertical",loc='top')
     fig1.set_figheight(4)
     fig1.set_figwidth(10.5)
     #fig1.subplots_adjust(bottom=0.1, right=0.95, top=0.95, left=0.1)

### 2023-01-24 saturation-ver2/Plotting/visualize-gluon.py

@@ -71,7 +71,7 @@ def main():
 #    ax1[0].legend([leg[0][0],leg[1][0],leg[2][0]],['Without Sudakov','With Sudakov $Q^2=100\\;\\mathrm{GeV}^2$','With Sudakov $Q^2=650\\;\\mathrm{GeV}^2$'])
     ax1[0].legend([leg[0][0],leg[1][0]],['Without Sudakov','With Sudakov'])
     #ax1.set(title="",  ylabel="$\\alpha_s f(x k^2)$",    xlabel="$k^2$",  xscale= 'log' ,   yscale='linear' )
-    ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k_t^2,Q^2)$',rotation="vertical",loc='top')
+    ax1[0].set_ylabel('$\\alpha_s \\mathcal{F}(x, k_t^2)$',rotation="vertical",loc='top')
     #fig1.canvas.draw()
     #fig1.set_layout_engine(None)
     fig1.set_figheight(4)

### 2023-01-24 saturation-ver3/Functions/fcn.h

@@ -10,6 +10,7 @@
 
 //#include"/home/tomoki/Numerics/clenshaw-curtis-gauss-legendre.hh"
 //#include"./clenshaw-curtis.hh"
+#include"./kt-formula.hh"
 #include<ctime>
 #include<chrono>
 
@@ -17,7 +18,7 @@
 	#define RFORMULA 0
 #endif
 
-extern double F2_kt(const  PREC,const  PREC,const PREC, const PREC(&)[]);
+//extern double F2_kt(const  PREC,const  PREC,const PREC, const PREC(&)[]);
 //extern double F2_r(const double,double,double,double*);
 class KtFCN : public ROOT::Minuit2::FCNBase {
 	
@@ -36,7 +37,6 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 			ERR_DATA=(double*)realloc(ERR_DATA,MAX_N*sizeof(double));
 		}
 		double Up() const {return 1;}
-		
 	public:
 		unsigned MAX_N=0;
 		explicit KtFCN(std::string data_file ){
@@ -93,6 +93,7 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 		
 		double operator()(const std::vector<double>& par)const{
 			std::chrono::system_clock walltime;
+			F2_kt F2;	
 			std::chrono::time_point start= walltime.now();
 
 			clock_t time=clock();
@@ -118,8 +119,8 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 				val=0;
 				//x=X_DATA[i];
 				//Q2=Q2_DATA[i];
-				val=F2_kt(X_DATA[i],Q2_DATA[i],0,sigpar);//summation over flavour is done at the level of integrand.
-				//printf("%.3e %.3e %.3e %.3e\n",val,CS_DATA[i],fabs(val-CS_DATA[i]),ERR_DATA[i]);	
+				val=F2(X_DATA[i],Q2_DATA[i],0,sigpar);//summation over flavour is done at the level of integrand.
+				//printf("%d: %.2e %.2e %.2e %.2e x=%.2e Q2=%.2e\n",i,val,CS_DATA[i],fabs(val-CS_DATA[i]),ERR_DATA[i],X_DATA[i],Q2_DATA[i]);	
 				chisq+=pow((val-CS_DATA[i])/ERR_DATA[i],2);
 #if SCATTER==1
 			printf("done %.3e\n",chisq/(i+1));

### 2023-01-24 saturation-ver3/Functions/test.cc

@@ -1,134 +1,0 @@
-#include<cmath>
-#include<iostream>
-#include<fstream>
-#include<vector>
-#include <gsl/gsl_errno.h> 
-#include <gsl/gsl_spline.h>
-#include <gsl/gsl_interp2d.h>
-#include <gsl/gsl_spline2d.h>
-#include"clenshaw.h"
-
-double par[]={25.0, 0.3,3.0e-4};
-double Q0=1;
-#define R_MIN 1.0e-6
-#define R_MAX 50
-double INT_PREC=1.0e-5;
-class Sigma{
-		const double* sigpar;
-		double x=0;
-	public:
-		void init(const double (&par)[]){
-			sigpar=par;
-		}
-		explicit Sigma(void){
-		}
-		~Sigma(){
-		}
-		double operator()(const double r,const double x){//,const double Q2,const double*sigpar)const {
-		 	this->x=x;
-		 	return((*this)(r));
-		 }
-		double operator()(const double r)const{
-			double sigma_0=sigpar[0];
-			double lambda=sigpar[1];
-			double x_0=sigpar[2];
-			if(x_0<1.0e-5||x_0>1.0e-3){
-				return 0;
-			}
-			if(lambda<0.05||lambda>0.95){
-				return 0;
-			}
-			
-			return( sigma_0*(1-exp( - pow(r * Q0, 2) * pow(x_0/x, lambda)/4)) );	
-		}
-};
-
-class Laplacian_Sigma{
-		Sigma sigma;
-		int r_npts;
-		gsl_interp_accel *  r_accel_ptr;
-		gsl_spline *  spline_ptr;
-		double *r_array,*sigma_array;
-		
-		
-		void free_approx(){
-			gsl_spline_free (spline_ptr);
-			gsl_interp_accel_free (r_accel_ptr);
-			free(r_array);
-			free(sigma_array);
-		}
-		
-		const double* sigpar;
-		//double x=0;
-		
-		int approximate(const double x){
-			double r;
-			for (int j = 0; j < r_npts; j++){
-				r=pow(10,-10+13*((double)j)/(r_npts-1));
-				r_array[j] = r;
-				sigma_array[j] = sigma(r,x);
-			}
-			
-			r_accel_ptr = gsl_interp_accel_alloc ();
-			spline_ptr = gsl_spline_alloc(gsl_interp_cspline, r_npts); // cubic spline
[…]

### 2023-01-24 saturation-ver3/Run/fixa-bjorx/control.h

@@ -1,7 +1,7 @@
 #define MASS_L2 0.0
 #define MASS_S2 0.0
 #define Q2_MAX 650.0
-#define MODEL 0
+#define MODEL 1 
 #define SUDAKOV 0
 #define NONLINEAR 1
 #define FEJER 1

### 2023-01-25 saturation-ver3/Functions/main.cc
gluon may be negative??

@@ -120,13 +120,13 @@ int main(int argc, char** argv){
 	
 	ROOT::Minuit2::MnMachinePrecision prec;
 	//prec.SetPrecision(1.0e-8);
-	INT_PREC=1.0e-3;
+	INT_PREC=5.0e-3;
 	//prec.SetPrecision(INT_PREC);
 	int flag=0;
 	double goal=1;
 	ROOT::Minuit2::MnSimplex simplex1(theFCN,upar,0);
-	std::cout<<"TEST RUN 5, eps = "<<INT_PREC<<std::endl;	
-	ROOT::Minuit2::FunctionMinimum min=simplex1(5,1);//Just initialization /check.
+	std::cout<<"TEST RUN 25, eps = "<<INT_PREC<<std::endl;	
+	ROOT::Minuit2::FunctionMinimum min=simplex1(25,1);//Just initialization /check.
 	ROOT::Minuit2::FunctionMinimum min_prev=min;
 	//ROOT::Minuit2::MnEigen eigen;
 	//min_prev=min;

### 2023-02-01 saturation-ver3/Functions/clenshaw.f
grid plot|

@@ -1,0 +1,164 @@
+C OPTIMIZED FOR GLUON 
+C NOT TO BE USED GENERALLY
+     
+      FUNCTION DCLENSHAW(FUNC,PAR, A, B, EPS,AEPS)
+      IMPLICIT NONE
+      EXTERNAL FUNC
+      DOUBLE PRECISION, DIMENSION(9):: X16
+      DATA X16(1) /1.000000000000000000000000000000D0/
+      DATA X16(2) /9.807852804032304506194118511447D-1/
+      DATA X16(3) /9.238795325112867619863336960547D-1/
+      DATA X16(4) /8.314696123025452498358628945367D-1/
+      DATA X16(5) /7.071067811865475460497457679922D-1/
+      DATA X16(6) /5.555702330196022565633495419049D-1/
+      DATA X16(7) /3.826834323650898141569391948192D-1/
+      DATA X16(8) /1.950903220161283203970903689557D-1/
+      DATA X16(9) /0.000000000000000000000000000000D0 /
+C
+      DOUBLE PRECISION, DIMENSION(9):: W16
+      DATA W16(1) /6.274509803921572703711007079619D-2/
+      DATA W16(2) /2.989496226976449054167638106882D-1/
+      DATA W16(3) /6.038586523452146797285979221456D-1/
+      DATA W16(4) /8.712444206551274286632311850505D-1/
+      DATA W16(5) /1.111651746945864560764091023555D0/
+      DATA W16(6) /1.305381314253626384086121496437D0/
+      DATA W16(7) /1.451790273891946807960151513108D0/
+      DATA W16(8) /1.540110916903405124741484817321D0/
+      DATA W16(9) /1.571281006575124188778813660861D0 /
+C
+      DOUBLE PRECISION, DIMENSION(5):: W8
+      DATA W8(1) /1.269841269841270256502063773496D-1/
+      DATA W8(2) /5.848745968640726177649829569567D-1/
+      DATA W8(3) /1.117460317460317429023630586917D0/
+      DATA W8(4) /1.446871434881959070257763581104D0/
[…]

### 2023-02-01 saturation-ver3/Functions/gluons.f

@@ -1,0 +1,105 @@
+C  CLACULATING OF XGPDF(X,Q^2) BY DGLAP EVOLUTION OF INITIAL CONDITION 
+C  XGPDF(X,Q^2_0)
+C ORIGINALLY WRITTEN BY S. SAPETA 
+C MODIFIED AND TRANSLATED TO FORTRAN BY T. GODA 
+C
+      INCLUDE "./clenshaw.f"
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C    GAMMA TILDE
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+      FUNCTION GAMMATILDE( N ) 
+      IMPLICIT NONE
+      EXTERNAL WPSIPG
+      DOUBLE COMPLEX GAMMATILDE,WPSIPG,N,N1,N2,N3,L1,L2,T1,T2,T3,CX
+      DOUBLE PRECISION M1,M2,RL
+      INTEGER K
+      DOUBLE PRECISION N_F,BETA,N_0, EULERGAMMA,LAMBDA2
+      COMMON /CONST/ N_F,BETA,N_0, EULERGAMMA
+      PARAMETER(K=0)
+      N1 = N+1D0;
+      N2 = N+2D0;
+      N3 = N+3D0;
+      L1 = DCONJG(N)*DCONJG(N1)
+      M1 = CDABS(N)*CDABS(N)*CDABS(N1)*CDABS(N1)
+      T1 = 1D0/M1*L1
+      L2 = DCONJG(N2)*DCONJG(N3)
+      M2 = CDABS(N2)*CDABS(N2)*CDABS(N3)*CDABS(N3)
+      T2 = 1D0/M2*L2
+      T3 = WPSIPG(N2,K);
+      CX = T1+T2-T3
+      RL = 11D0/2D0-N_F/3D0 -6D0*EULERGAMMA;
+      GAMMATILDE = 6D0*CX+RL
+      RETURN
+      END
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C    INTEGRAND OF GLUONS PDF 
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
[…]

### 2023-02-01 saturation-ver3/Functions/main.cc

@@ -122,14 +122,14 @@ int main(int argc, char** argv){
 	
 	ROOT::Minuit2::MnMachinePrecision prec;
 	//prec.SetPrecision(1.0e-8);
-	INT_PREC=5.0e-3;
-	N_APPROX=N_CHEB_R/5;
+	INT_PREC=5.0e-4;
+	N_APPROX=N_CHEB_R/2;
 	//prec.SetPrecision(INT_PREC);
 	int flag=0;
 	double goal=1;
 	ROOT::Minuit2::MnSimplex simplex1(theFCN,upar,0);
-	std::cout<<"TEST RUN 25, eps = "<<INT_PREC<<" N_APROX ="<<N_APPROX<<std::endl;	
-	ROOT::Minuit2::FunctionMinimum min=simplex1(25,1);//Just initialization /check.
+	std::cout<<"TEST RUN 15, eps = "<<INT_PREC<<" N_APROX ="<<N_APPROX<<std::endl;	
+	ROOT::Minuit2::FunctionMinimum min=simplex1(15,1);//Just initialization /check.
 	ROOT::Minuit2::FunctionMinimum min_prev=min;
 	//ROOT::Minuit2::MnEigen eigen;
 	//min_prev=min;

### 2023-02-01 saturation-ver3/Functions/plot-grid.cc

@@ -16,13 +16,12 @@
 #endif
 //#if GLUON_APPROX==1
 	#include"./interpolation.hh"
-//	typedef Approx_aF Gluon ;
-//	typedef Laplacian_Sigma SIGMA;
+	typedef Approx_aF Gluon ;
+	typedef Laplacian_Sigma SIGMA;
 //#else
 //	#include"./gluon-gbw.hh"
-//	typedef Gluon_GBW Gluon ;
-	typedef Dipole_Gluon Gluon;
-	typedef Sigma SIGMA;
+// 	typedef Gluon_GBW Gluon ;
+//	typedef Sigma SIGMA;
 
 //#endif
 //#include"./clenshaw.h"
@@ -57,7 +56,7 @@ extern PREC INT_PREC;
 	#define MU02 1
 #endif
 int N_APPROX=N_CHEB_R;
-double INT_PREC=1.0e-4;
+double INT_PREC=1.0e-5;
 int main(int argc , char** argv){
 	options opt=read_options(argc, argv);
 	std::vector<double> param(10,0);
@@ -67,7 +66,7 @@ int main(int argc , char** argv){
 		opt.path=getenv("DIR");
 	}	
 	sprintf(filenames,"%s/%s",opt.path.c_str(),opt.input_file_name.c_str());
-
+	printf("%s\n",filenames);
 	FILE* infile=fopen(filenames,"r");
 	read_parameters(infile,param);
 	fclose(infile);
@@ -75,46 +74,33 @@ int main(int argc , char** argv){
 
 
 	parameter(param,sigpar,sudpar);
-
+	//printf("Start, press any key\n");
+	//getchar();
 	SIGMA sigma;
-	sigma.init(sigpar);
+	sigma.init(N_CHEB_R+25,sigpar,'s');
+	printf("kinem set\n");
 	
-	printf("x= %.3e Q2=%.3e\n",opt.x,opt.Q2);	
-	sigma.set_kinem(opt.x);
-	
-	sprintf(filenames,"%s/%s-%.0lf-%.0lf.txt",opt.path.c_str(),"dipole",-log10(opt.x),opt.Q2);
+	sprintf(filenames,"%s/%s",opt.path.c_str(),"dipole-grid.txt");
 	FILE* outfile=fopen(filenames,"w");
-	if(outfile==NULL){
-		printf("can't open");
-	}else{
[…]

### 2023-02-06 saturation-ver3/kt-formula-report1/kt-formula-report1.tex
interpolation
gluon may be negative??
grid plot|
notes

@@
 Note, the integration limits of $k_t$ and $\kappa_t$ are removed as GBW gluon is not perturbative.
+\section{BGK}
+In order to use the GBK dipole, one needs to evaluate
+\begin{equation}
+\begin{split}
+	\alpha \mathcal{F}(x,k_t)&=\frac{3}{4\pi}\int \frac{d^2r}{(2\pi)^2}e^{-i\mathbf{r}\cdot\mathbf{k_t}}\nabla^2_r\sigma(x,r)\\
+&=\frac{3}{8\pi^2}\int dr r J_0(r k_t) \nabla^2_r\sigma(x,r).
+\end{split}
+\end{equation}
+While $\nabla^2_r\sigma(x,r)$ is relatively smooth function, $J_0(z)$ is oscillatory function imposing difficulty in integration. Thus one may approximate  $\nabla^2_r\sigma(x,r)$.
+
+\subsection{Alternatively...}
+$\nabla^2_r\sigma(x,r)$
+ of GBW is 
+\begin{equation}
+\sigma_0 Q_s^2 \left(1-\frac{Q_s^2}{4}r^2\right)e^{-\frac{Q_s^2}{4}r^2}.
+\end{equation}
+and since
+\begin{equation}
+	\frac{3}{4\pi} \nabla^2_r\sigma(x,r)=\int d^2ke^{-i\mathbf{r}\cdot\mathbf{k_t}}\alpha \mathcal{F}(x,k_t),
+\end{equation}
+small-$r$ limit is
+\begin{equation}
+\begin{split}
+	\lim_{r\rightarrow0}\frac{3}{4\pi} \nabla^2_r\sigma(x,r)&=\pi \int^{1/r}_0 dk^2\alpha \mathcal{F}(x,k_t)\\
+&=\pi \alpha xg(x,1/r).
+\end{split}
+\end{equation}
+For this, we can propose
+\begin{equation}
+Q_s^2=\frac{4\pi^2 \alpha x g(x,1/r)}{3\sigma_0},
+\end{equation}
+which is almost BGK.
+
+\subsection{On running coupling of BGK}
+\begin{equation}
+\sigma(x,r)=\frac{4\pi}{N_c}\int\frac{d^2\mathbf{k}_t}{k_t^2}\left(1-e^{-i\mathbf{k}_t\cdot \mathbf{r}}\right)\alpha\mathcal{F}(x,k_t)
+\end{equation}
+in small-$r$ limit (for $k_t r\ll1$ considering large-$k_t$ region is irrelevant.), 
+\begin{equation}
+\begin{split}
+\sigma(x,r)&=\frac{4\pi}{N_c}\int^{1/r^2}_0 dk^2_t\left(\frac{k_t^2r^2 \pi}{4}\right)\alpha\mathcal{F}(x,k_t^2)\\
+&=\frac{\pi^2}{N_c}\int^{1/r^2}_0 dk^2_t \alpha\mathcal{F}(x,k_t^2)
+\end{split}
+\end{equation}
+then in BGK,
+\begin{equation}
+%\begin{split}
+=\frac{\pi^2}{N_c}\alpha xg(x,1/r^2).
+%\end{split}
+\end{equation}
+But what exactly happened to $\alpha$? 
+Usually the relation is 
+\begin{equation}
+xg(x,Q^2)=\int^{Q^2}_0 d k^2_t \mathcal{F}(x,k_t^2)
+\end{equation}
+without $\alpha$. 
+if $\alpha=\alpha(\mu^2)$, the BGK derivation fails...
+Also, note, that the argument of $\
+alpha$ being $1/r$ may be a bit odd as it is not just $k^2_t$ in the $k_t$ formula.
 
@@
 \input{r-formula}
+
+\section{Log rise...}
+\begin{equation}
+\alpha \mathcal{F} =\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma
+\end{equation}
+in small $k$ limit,
+\begin{equation}
+\begin{split}
+\lim_{k\rightarrow0 } \alpha \mathcal{F} &=\frac{3}{8\pi^2}\int^\infty_0dr r \nabla^2_r \sigma\\
+&=\frac{3}{8\pi^2}\int^\infty_0dr r\left[\frac{\partial^2\sigma}{\partial r^2}+\frac{\partial\sigma}{\partial r}\right]\\
+&=\frac{3}{8\pi^2}\left[r\frac{\partial\sigma}{\partial r}-\int dr \frac{\partial\sigma}{\partial r} +\sigma \right]^\infty_0\\
+&=\frac{3}{8\pi^2}\left[r\frac{\partial\sigma}{\partial r}\right]^\infty_0=\frac{3}{8\pi^2}\left[\frac{\partial\sigma}{\partial \log(r)}\right]^\infty_0
+\end{split}
+\end{equation}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{./dipole1.png}
+\caption{Dipole cross sections. Left: GBW, Right: BGK.}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\textwidth]{./gluon1.png}
+\caption{Observe the new structure arizing from the DGLAP (larger-$k_t$ peak).
+When $x$ is small it becomes the dominant contributon.
+Also there is a narrow ridge around $x\sim1$.
+It is probably a saturation line, i.e.
+the line is not straight like in GBW case.
+{\color{green}Some change of variables may be helpfull...}   }
+\end{figure}
+
 \end{document}

### 2023-02-07 saturation-ver3/kt-formula-report1/kt-formula-report1.tex
large x problematic

@@
 
+\section{Computational strategies}
+\subsection{$\alpha\mathcal{F}$ and $\nabla^2_r \sigma$}
+\begin{equation}
+\begin{split}
+\alpha\mathcal{F}&=\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma(x,r)\\
+&=\frac{3}{8\pi^2}\int^\infty_0dr rJ_0(r k) \left(\frac{1}{r}\frac{\partial}{\partial r}\left(r\frac{\partial}{\partial r}\right)\right) \sigma(x,r)
+\end{split}
+\end{equation}
+Using integration by parts,
+\begin{equation}
+\begin{split}
+\alpha\mathcal{F}&=\frac{3}{8\pi^2}\int^\infty_0dr J_0(r k) \frac{\partial}{\partial r} \left(r\frac{\partial}{\partial r}\right) \sigma(x,r)\\
+&=\frac{3}{8\pi^2}\left[ J_0(r k)\left(r\frac{\partial}{\partial r}\right) \sigma(x,r) - \int dr \frac{\partial J_0(r k)}{\partial r} \left(r\frac{\partial}{\partial r}\right) \sigma(x,r)\right]^\infty_0\\
+&=\frac{3}{8\pi^2}\left[  \int dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)\right]^\infty_0,
+\end{split}
+\end{equation}
+assuming 
+\begin{equation}
+\lim_{r\rightarrow0,\infty}J_0(r k)\left(r\frac{\partial}{\partial r}\right) \sigma(x,r)=0.
+\end{equation}
+Hence, one has two ways to compute the gluon density;
+\begin{align}
+&\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma(x,r)\\
+&\frac{3}{8\pi^2}\int^\infty_0  dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)
+\end{align}
+Now, these integrals are in the form of\textbf{ Hankel transform}.
+
+as a by-product of interpolation, derivatives are obtainable in gsl\_cheb or gsl\_interp. However in any case second derivative may become a source of inaccuracy...
+
+Let us assume small $Q_s^2$, and for $r>>Q_s$, integrand is negligible, then
+\begin{equation}
+\begin{split}
+\frac{3}{8\pi^2}\int^{1/Q_s}_0  dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)\\
+\simeq \frac{3}{8\pi^2}\int^{1/Q_s}_0  dr  k J_1(r k) r^2 Q_s^2\\
+=\frac{3Q_s^2}{8\pi^2} \frac{J_2(k/Q_s)}{k Q_s^2}  
+\end{split}
+\end{equation}
+
 \end{document}

### 2023-02-07 saturation-ver3/Functions/control-default.h

@@ -42,7 +42,7 @@ typedef double PREC;
 	#define R_MIN 1.0e-6
 #endif
 #ifndef R_MAX
-	#define R_MAX 30
+	#define R_MAX 1e+3
 #endif
 
 

### 2023-02-07 saturation-ver3/Functions/plot-grid.cc

@@ -55,7 +55,7 @@ extern PREC INT_PREC;
 #ifndef MU02
 	#define MU02 1
 #endif
-int N_APPROX=N_CHEB_R;
+int N_APPROX=N_CHEB_R/2;
 
 double INT_PREC=1.0e-5;
 int main(int argc , char** argv){
@@ -101,7 +101,7 @@ int main(int argc , char** argv){
 	Gluon gluon;
 //#if GLUON_APPROX==1
 	printf("Gluon start\n");
-	gluon.init(2*N_APPROX,2*N_APPROX,N_APPROX,sigpar);
+	gluon.init(N_APPROX+50,N_APPROX+50,N_APPROX/2+25,sigpar);
 	printf("Initialized\n");
 	gluon.set_max(5.0e+4);
 //#else

### 2023-02-07 saturation-ver3/Run/fixa-bjorx/control.h

@@ -6,4 +6,5 @@
 #define PRINT_PROGRESS 1
 #define ALPHA_RUN 0
 #define MODX 0
-#define HANKEL 1
+#define HANKEL 0 
+#define IBP 1

### 2023-02-15 saturation-ver3/Plotting/surface.py
pthread at one place

@@ -130,7 +130,7 @@ def main():
                 ax[gpos].view_init(30, 25)
                 ax[gpos].set_ylabel('$\log_{10}(k^2\\;[\\mathrm{GeV^2}])$',rotation='vertical',loc='top')
             ax[gpos].set_xlabel('$\log_{10}x$',loc='right')
-        
+            ax[gpos].set_zlim3d(-0.001, 0.001)        
         #cs=ax[gpos].contour(np.array(X),np.array(Y),np.transpose(np.array(Z)), levels=10,colors="black",linewidths=0.5,linestyles=["solid","dashed"])
     #ax[len(grids)-1].set_xlabel('$x$',loc='right')
     #ax[0].set_ylabel('$k^2\\;[\\mathrm{GeV^2}]$',rotation='vertical',loc='top')

### 2023-02-17 saturation-ver3/kt-formula-report1/kt-formula-report1.tex
pthread at one place
plots to be modified

@@
 \usepackage[]{geometry}
+%\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{compare-gbw-500.png}
+\includegraphics[width=0.45\textwidth]{ibp1-200.png}
+\includegraphics[width=0.45\textwidth]{ibp1-750.png}
+\caption{IBP2,IBP1,IBP0, comparisom with analytic $\alpha\mathcal{F}$ of GBW. 500 points taken in $r$.
+Bottom: IBP1 with 200 and 750 points grid.\\
+All in the same scale.
+ }
+\end{figure}
+
+\begin{table}
+\begin{subtable}{\textwidth}
+\resizebox{\textwidth}{!}{\begin{tabular}{|c c|c|c|c|c|}
+\hline
+type & light quark mass $[\mathrm{GeV}]$&  $\sigma_0 \;[\mathrm{mb}]$ &  $x_0 (10^{-4})$ &  $\lambda$ &  $\chi^2/\mathrm{dof}$ 
+\\\hline
+$\mathrm{GBW}$& $m_l=0.14$ & 23.8 & 1.12 & 0.308 & 5.27 \\ \hline
+$\mathrm{GBW+Sud}$&$m_l=0.14$ & 23.0 & 1.32 & 0.287 & 3.37 \\ \hline
+\color{red}$\alpha(\mu)\mathcal{F}_\mathrm{GBW} $&$m_l=0$ & \color{red}56.1 & \color{red}2.64 & \color{red}0.32 &\color{red} 2.45\\ \hline
+\color{red}$\alpha\mathcal{F}_\mathrm{GBW} $&$m_l=0$ & \color{red}33.4 & \color{red}1.34 &\color{red}0.33 & \color{red}4.39\\ \hline
+$\mathrm{GBW}$& $m_l=0.0$ & 19.1 & 2.58 & 0.322 & 4.44 \\ \hline
+$\mathrm{GBW+Sud}$& $m_l=0.0$ & 18.6 & 3.11 & 0.299 & 2.66 \\ \hline
+\end{tabular} }
+        %\input{./Plots/GBWS-Fix-S.tex}
+        \vspace{2mm}
+    \end{subtable}
+
+    \begin{subtable}[H]{\textwidth}
+        \centering
+\resizebox{\textwidth}{!}{\begin{tabular}{|c c|c|c|c|c|c|c|}
+\hline
+type&light quark mass $[\mathrm{GeV}]$&  $\sigma_0\; [\mathrm{mb}]$ &  $A_{\mathrm{g}}$ &  $\lambda_{\mathrm{g}}$ &  $C$ &  $\mu_{0}^2\;[\mathrm{GeV^2}]$ &  $\chi^2/\mathrm{dof}$ 
+\\\hline
+$\mathrm{BGK}$& $m_l=0.14$ & 33.1 & 1.33 & 0.0553 & 0.420 & 1.76 & 1.62 \\ \hline
+$\mathrm{BGK+Sud}$& $m_l=0.14$& 30.7 & 6.28 & -0.380 & 0.677 & 3.09 & 1.27 \\ \hline
+\color{red}$\alpha\mathcal{F}_\mathrm{BGK}$& $m_l=0.0$ & \color{red}34.8& \color{red}1.09 & \color{red}0.210 & \color{red}0.215 & \color{red}1.06 &\color{red} 1.60 \\ \hline
+$\mathrm{BGK}$& $m_l=0.0$ & 23.3 & 1.18 & 0.0832 & 0.329 & 1.87 & 1.56 \\ \hline
+$\mathrm{BGK+Sud}$& $m_l=0.0$ & 22.2 & 8.67 & -0.500 & 0.670 & 3.83 & 1.21 \\ \hline
+\end{tabular}
+}
+       % \input{./Plots/BGKS-Fix-S.tex}
+    \end{subtable}
+    \caption{ }
+    \label{table:fullTable}
+\end{table}
+
+\begin{figure}
+\includegraphics[width=0.475\textwidth]{./dipole-GBW.png}
+\includegraphics[width=0.475\textwidth]{./dipole-BGK.png}
+\end{figure}
+\begin{figure}
+\includegraphics[width=0.475\textwidth]{./gluon-GBW.png}
+\includegraphics[width=0.475\textwidth]{./gluon-BGK.png}
+\end{figure}
+
 \end{document}

### 2023-02-17 saturation-ver3/Functions/plot-grid.cc

@@ -15,7 +15,7 @@
 	#define GLUON_APPROX 1
 #endif
 //#if GLUON_APPROX==1
-	#include"./interpolation.hh"
+	#include"./interpolation2.hh"
 #if HANKEL==1
 	typedef Hankel_aF Gluon ;
 #else

### 2023-02-24 saturation-ver3/Functions/main.cc
minor

@@ -133,8 +133,8 @@ int main(int argc, char** argv){
 #endif//USE_RESULT
 	ROOT::Minuit2::MnMachinePrecision prec;
 	//prec.SetPrecision(1.0e-8);
-	INT_PREC=5.0e-4;
-	N_APPROX=N_CHEB_R/2;
+	INT_PREC=1.0e-4;
+	N_APPROX=N_CHEB_R;
 	//prec.SetPrecision(INT_PREC);
 	int flag=0;
 	double goal=1;

### 2023-02-24 saturation-ver3/plot.py

@@ -94,10 +94,11 @@ def main():
         if (labels!=[] and labels[counter]!=""):
         	legs.append(leg[0])
         counter+=1
-    #if labels!=[]:
-    #    labels.remove("")
-    #    if len(legs)>0:
-    #        ax.legend(legs,labels)
+    print("LABELS ", labels);
+    if "" in labels:
+        labels.remove("")
+        if len(legs)>0:
+            ax.legend(legs,labels)
     ax.set(title=plottitle,  ylabel=axes[1],    xlabel=axes[0],  xscale= xs ,   yscale=ys )
     if(xlim[0]!=xlim[1]):
         ax.set_xlim(xlim[0],xlim[1])

### 2023-02-24 saturation-ver3/plots.sh

@@ -2,10 +2,11 @@
 
 SAT=/home/tomoki/Saturation-Model/saturation-ver3
 
-for i in  ./Run2/fixa-bjorx ./Run2/fixa-bjorx2 \
-	./Run2/runa-bjorx-4 ./Run2/runa-bjorx2-4 \
-	./Run2/fixa-bjorx-BGK ./Run2/fixa-bjorx-BGK2 \
-	./Run2/GBW ./Run2/GBW-Massive ./Run2/BGK ./Run2/BGK
+#for i in  ./Run2/fixa-bjorx ./Run2/fixa-bjorx2 \
+#	./Run2/runa-bjorx-4 ./Run2/runa-bjorx2-4 \
+#	./Run2/fixa-bjorx-BGK ./Run2/fixa-bjorx-BGK2 \
+#	./Run2/GBW ./Run2/GBW-Massive \
+for i in ./Run2/BGK
 do
 	echo ${i}
  	export DIR=${i}
@@ -44,57 +45,74 @@ done
 	-m ./Run2/BGK/dipole-grid.txt  ./Run2/fixa-bjorx-BGK/dipole-grid.txt #./Run2/fixa-bjorx-BGK2/dipole-grid.txt
 
 
+exit 0
 
-./plot.py -s "./kt-formula-report1/GBW-gluon.png" -y "linear" \
-	-c "b r r b r r b r r" -p "-. -. - -. -. - -. -. -" -l "GBW-r:GBW-kt:GBW-kt-run::::::" \
-	${SAT}/Run2/GBW/gluon-2-100.txt \
-	${SAT}/Run2/fixa-bjorx/gluon-2-100.txt \
-	${SAT}/Run2/runa-bjorx-4/gluon-2-100.txt \
-	${SAT}/Run2/GBW/gluon-6-100.txt \
-	${SAT}/Run2/fixa-bjorx/gluon-6-100.txt \
-	${SAT}/Run2/runa-bjorx-4/gluon-6-100.txt 
+#./plot.py -s "./kt-formula-report1/GBW-gluon.png" -y "linear" \
+#	-c "b r r b r r b r r" -p "-. -. - -. -. - -. -. -" -l "GBW-r:GBW-kt:GBW-kt-run::::::" \
+#	${SAT}/Run2/GBW/gluon-2-100.txt \
+#	${SAT}/Run2/fixa-bjorx/gluon-2-100.txt \
+#	${SAT}/Run2/runa-bjorx-4/gluon-2-100.txt \
[…]

### 2023-03-24 saturation-ver3/Documentation/Manual.tex
minor changes

\documentclass[12pt]{article}
\usepackage[a4paper,left=1in,right=1in]{geometry}
%\usepackage{merriweather}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\title{Saturation Model Fitter\\ (ver.~3)\\User's Guide}
\author{Tomoki Goda}

%\newenvironment{entry}[1]{\textbf{\large #1:}\vspace{1pt}\hrule\begin{center}}{\end{center}\vspace{2mm}}
\newenvironment{entry}[1]{\textbf{\large #1:  }}{\\\vspace{3mm}\\}

\begin{document}
	\maketitle
%\section{Intro.}

%\section{Functions}
\section{gluons.hh}
\subsection{\texttt{class} Collinear\_Gluon }\label{CollinearGluon}

\begin{entry}{Description}
computes $xg(x,Q^2)$.\\
$xg(x,Q_0^2)=A_g x^\lambda_g(1-x)^{5.6}$
\end{entry} 
\begin{entry}{Constructor}
	Collinear\_Gluon()
\end{entry} 
\begin{entry}{Main function}
	\textbf{operator}()($x$,$Q^2$,$A_g$,$\lambda_g$)
\end{entry} 
\begin{entry}{Dependence}
polygamma.h, clenshaw.hh
\end{entry}

\subsection{\texttt{class} Chebyshev\_Collinear\_Gluon}\label{ChebyshevCollinearGluon}
\begin{entry}{Description}
	Approximate $xg(x,Q^2)$ with 2D Chebyshev polynomials. 
\end{entry}
\begin{entry}{Constructor}
	Chebyshev\_Collinear\_Gluon()\\
	Global variable or Macro \texttt{N\_CHEB} is required to specify order of polynomials.
\end{entry}
\begin{entry}{Initialization}
	init($x_{\mathrm{min}}$, $x_{\mathrm{max}}$, $Q^2_{\mathrm{min}}$, $Q^2_{\mathrm{max}}$,$A_g$, $\lambda_g$ )\\
	Computes coefficients.\\
	set\_x($x$)\\
	Reduce 2D polynomial to 1D at specified $x$. 
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()($x$,$Q^2$)
	compute $xg(x,Q^2)$ from 2D polynomial or 1D if set\_x($x$) was run previously.(it can be reset by running set\_x($x$) with negative value. ) 
\end{entry}
\begin{entry}{Dependence}
	chebyseh.hh, Collinear\_Gluon~(\ref{CollinearGluon})
\end{entry}

\subsection{\texttt{class} Chebyshev1D\_Collinear\_Gluon}\label{Chebyshev1DCollinearGluon}
\begin{entry}{Description}
	Approximate $xg(x,Q^2)$ with 1D Chebyshev polynomials at fixed $x$. 
\end{entry}
\begin{entry}{Constructor}
	Chebyshev1D\_Collinear\_Gluon()\\
	Global variable or Macro \texttt{N\_CHEB} is required to specify order of polynomials.
\end{entry}
\begin{entry}{Initialization}
	init($x_{\mathrm{min}}$, $x_{\mathrm{max}}$, $Q^2_{\mathrm{min}}$, $Q^2_{\mathrm{max}}$,$A_g$, $\lambda_g$ )\\
	Computes coefficients.\\
	set\_x($x$)\\
	Record the value of $x$ and compute coefficients.
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()($x$,$Q^2$)\\
	compute $xg(x,Q^2)$ from 1D polynomial. If passed $x$ differs from the value at which approximation is done, it will print error.
\end{entry}
\begin{entry}{Dependence}
	chebyseh.hh, Collinear\_Gluon~(\ref{CollinearGluon})
\end{entry}
\subsubsection{\texttt{class} Interpolate\_Collinear\_Gluon}
No longer supported.

\section{r-formula.hh}
\subsection{Sigma}\label{Sigma}
\begin{entry}{Description}
	$\sigma_{\mathrm{dipole}}(x,r)$.
\end{entry}
\begin{entry}{Constructor}
	controlled by macro \texttt{MODEL}\\
	if MODEL == 1 (BGK)\\
		Sigma$<$cg$>$()\\
		where cg = is appropriate collinear gluon\\
		Collinear\_Gluon~(\ref{CollinearGluon}), Chebyshev\_Collinear\_Gluon~(\ref{ChebyshevCollinearGluon}),  Chebyshev1D\_Collinear\_Gluon~(\ref{Chebyshev1DCollinearGluon})
	else \\
		Sigma()\\
\end{entry}
\begin{entry}{Initialization}
	init(\textbf{const double *const }parameters)\\
	parameter array "parameters". see also Parameters.hh~(\ref{Parameters.hh}).\\

	set\_x(x)\\
	run cg.set\_x(x) for approx.ed collinear gluons (\texttt{SIGMA\_APPROX}$<$0).
	note, for \texttt{FREEZE\_QS2}$!=$0, set\_x($x$) will modify $x$ accordingly at this point and pass it to collinear gluon.
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()(x,r)\\
	computes $\sigma_{\mathrm{dipole}}(x,r)$.
\end{entry}
\section{Interpolation-dipole.hh}\label{Interpolationdipole}

\subsection{Laplacian\_Sigma}\label{LaplacianSigma}
\begin{entry}{Description}
	Approximates $\sigma_{\mathrm{dipole}}(x,r)$ at given $x$ with cubic spline. 
	return value is controlled by macros and most importantly returns $rJ_0(rk)\nabla^2_r \sigma$ or $rkJ_1(rk)\frac{\partial \sigma}{\partial r}$.
	Essentially a class to compute integrand for the Hankel transform;
	\begin{equation}
		\int^{r_{\mathrm{max}}}_{r_{\mathrm{min}}} dr r J_0(rk)\nabla^2_{r}\sigma_{\mathrm{dipole}}(x,r)
	\end{equation}
\end{entry}
\begin{entry}{Constructor}
	Laplacian\_Sigma$<$sigma$>$(sigma)
	where sigma is the dipole cross section (\ref{Sigma})
\end{entry}
\begin{entry}{Initialization}
	init(int N,const double * parameters, char mode)\\
	\texttt{N} is the number of points to be taken for the 1D grid. (for cubic spline, it should be around 500?)
	\texttt{parameters} is 1d array containing parameters for $\sigma$. \texttt{mode} is `l' or `s'.  (`l' stands for laplacian, and `s' for sigma (for when laplacian can be computed analytically )). \\
	set\_x($x$) will set $x$ in the components ($\sigma$, $xg$ etc.) and compute 1D grid of dipole cross section.
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()(\textbf{double} $\rho$, \textbf{std::vector$<$double$>$} arg)\\
	$\rho$ is $r$ or $\frac{r}{1+r}$, use macro \texttt{R\_CHANGE\_VAR}.
	arg = \{$k_t^2$,$x$\} 
\end{entry}
\begin{entry}{macro \texttt{IBP}}
	Use \texttt{IBP} = 0,1,2 to control which of the following integrand you want; 
	\begin{align}
		\int^{r_{\mathrm{max}}}_{r_{\mathrm{min}}} dr r J_0(rk)\nabla^2_{r}\sigma_{\mathrm{dipole}}(x,r)\\
		\left[ r J_0(rk)\frac{\partial\sigma_{\mathrm{dipole}}(x,r)}{\partial r}\right]^{r_{\mathrm{max}}}_{r_{\mathrm{min}}}
		+k\int^{r_{\mathrm{max}}}_{r_{\mathrm{min}}} dr r J_1(rk)\frac{\partial\sigma_{\mathrm{dipole}}(x,r)}{\partial r}\\
			\left[ r J_0(rk)\frac{\partial\sigma_{\mathrm{dipole}}(x,r)}{\partial r}+
			rk J_1(rk)\sigma_{\mathrm{dipole}}(x,r)
			 \right]^{r_{\mathrm{max}}}_{r_{\mathrm{min}}}
			-k^2\int^{r_{\mathrm{max}}}_{r_{\mathrm{min}}} dr r J_0(rk)\sigma_{\mathrm{dipole}}(x,r)
	\end{align}
	use constant(double $r$, std::vector$<$double$>$ arg ) for the first term, arg is the same but $r$ is $r_{\mathrm{max}}$ or $r_{\mathrm{min}}$ (it is $r$ not $\rho$!!). 
	also \texttt{NS}=1 will insert $\exp(-r^2/500)$ in the both first and second term, to suppress large $r$. 
	for \texttt{NS}=2 exists (not well maintained), which is  equivalent to inserting that exponent in the integral before IBP.
	\texttt{ADD\_END} will add or ignore $[...]^{r_{\mathrm{max}}}_{r_{\mathrm{min}}}$
\end{entry}
\subsection{\texttt{class} Gluon\_Integrand}\label{GluonIntegrand}
\begin{entry}{Description}
This usage is almost the same as Laplacian\_Sigma (\ref{LaplacianSigma}). 
This does not involve with interpolation at dipole cross section level. Recommended to use at leaset Chebyshev approximation of $xg(x,Q^2)$.
\end{entry}
\begin{entry}{Constructor}
 Gluon\_Integrand$<$sigma$>$(sigma)
	where sigma is the dipole cross section (\ref{Sigma})
\end{entry}
\begin{entry}{Initialization}
	init(const double* parameters, char mode)\\
	\texttt{parameters} is 1d array containing parameters for $\sigma$. \texttt{mode} is `l' or `s'.  (`l' stands for laplacian, and `s' for sigma (for when laplacian can be computed analytically )). \\
	set\_x($x$) will set $x$ in the components ($\sigma$, $xg$ etc.).
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()(const double $\rho$, const std::vector$<$double$>$ par) and 
	constant(const double $\rho$, const std::vector$<$double$>$ par)
	are same as Laplacian\_Sigma (\ref{LaplacianSigma}).
\end{entry}

\subsubsection{\texttt{class} Chebyshev\_Laplacian\_Sigma}
Under construction...

\section{dipole-gluon.hh}
\subsection{\texttt{class} Gluon\_GBW}
\begin{entry}{Description}
	Analytic form of GBW dipole gluon density.	
\end{entry}
\begin{entry}{Constructor}
	Gluon\_GBW()
\end{entry}
\begin{entry}{Initialization}
	init(cont double* parameters).
	parameters are the same as those for Sigma (\ref{Sigma}).
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()($x$,$k_t^2$,$\mu$) 
	compute $\alpha_s\mathcal{F}$. 
	use macro \texttt{ALPHA\_RUN}=1 to use $\alpha_s(\mu^2)$
\end{entry}
\subsection{\texttt{class} Dipole\_Gluon}\label{DipoleGluon}
\begin{entry}{Description}
	compute $\alpha_s\mathcal{F}$.
\end{entry}

\begin{entry}{Constructor}
	Dipole\_Gluon$<$integ$>$(integ).
	for integ  is appropriate integrand (Laplacian\_Sigma~\ref{LaplacianSigma}, Gluon\_Integrand~\ref{GluonIntegrand} etc)
\end{entry}

\begin{entry}{Initialization}
	init(double * parameters)\\
	set\_x(double $x$) 
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()($x$,$k_t^2$,$\mu$) 
	compute $\alpha_s\mathcal{F}$. 
	use macro \texttt{ALPHA\_RUN}=1 to use $\alpha_s(\mu^2)$
	note Threshold supression $(1-x)^7$ is not added here but already at the point of integrand (e.g. \ref{LaplacianSigma}). 
\end{entry}

\section{Interpolation-gluon.hh}
\subsection{\texttt{class} Approx\_aF}
\begin{entry}{Description}
	Produce grid of $\alpha_s\mathcal{F}(x,k_t^2,0)$.
\end{entry}
\begin{entry}{Constructor}
	Approx\_aF$<$gluon$>$(gluon). where gluon is appropriate gluon to approximated, e.g.~\ref{DipoleGluon}
\end{entry}
\begin{entry}{Initialization}
	init(int n1,int n2, double * parameters).
	n1 number of points for $x$
	n2 number of points for $k_t$.
	parameters to be passed down to $\sigma$.\\
	set\_max(double $k^2_{t,\mathrm{max}}$)	may be replaced in the future. 
	It will generate the grid for predefined limits $-8<\log_{10}(x)<0$, $10^{-6}<k_t^2$ and $k_t^2< k^2_{t,\mathrm{max}}$. 
	In reality the grid is a little wider than specified limits.
\end{entry}
\begin{entry}{Main function}
	\textbf{operator}()(double $x$,double $k^2$, double $\mu^2$)
	computes $\alpha_s\mathcal{F}$
\end{entry}

\end{document}

### 2023-04-07 saturation-ver3/kt-formula-report1/ww.tex
ww grid fine

\documentclass{article}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{ww.bib}

\newcommand{\fww}[0]{\mathcal{F}^{\mathrm{WW}}}
\newcommand{\fdp}[0]{\mathcal{F}^{\mathrm{dipole}}}
\newcommand{\sdp}[0]{\sigma_{\mathrm{dipole}}}
\newcommand{\sdpa}[0]{\sigma_{\mathrm{dipole\,Adj.}}}
\begin{document}
\section{Dijet process}
In order to investigate less inclusive processes, we will study the electron-dijet correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
Dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density\cite{}.
This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton. Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write  
\begin{equation}
\fww(x,k^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation} 	
with the adjoint dipole cross section
\begin{equation}
\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
\end{equation}
Resummation of the Sudakov logarithms is achieved by the formula~\cite{}
\begin{equation}
	\fww(x,k^2,\mu^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) e^{-S(r,\mu^2)} \sdpa(x,r),
\end{equation}
where, we use the Sudakov form factor~\cite{},
\begin{equation}
	S(r,\mu^2)=\frac{\alpha_s N_c}{4\pi}\ln^2\left(\frac{\mu^2r^2}{4e^{-2\gamma_E}}\right),
\end{equation}
in which $\gamma_E$ is the Euler-Mascheroni constant, and we use $\alpha_s=0.2$.

\appendix	
\section{Computation of gluon densities}
In order to obtain the WW gluon density, one needs to compute 
\begin{equation}
	\fww(x,k)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation} 	
where we use 
\begin{equation}
	\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
\end{equation}

The convergence of this integral may be slow due to high oscillation for large $k$.
For such integration, one can employ a method summarized in Ref.~\cite{LYNESS1985109}. 
Essentially, the integration is carried out between, anti-nodes of $J_0(rk)$. Then the total integral is written in the form of infinite sum
\begin{equation}
	I=\sum^\infty_{i=1} \int^{a_{i+1}}_{a_i} \frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation}
where we use $a_{i}=\frac{\pi}{k}(i+1/4)$.
This sum can be accelerated, with series transformation described in Ref.~\cite{doi:10.1080/00207167308803075,Weniger:1989rea,HOMEIER19951}.
The remarkable power of the Levin's transformation is shown in Tab.~\ref{tab:levin}.
This trick is also useful in the computation of dipole gluon density.

\begin{table}
	\begin{center}
	\begin{tabular}{|c||c|c|}
		\hline
		$n$&Levin&Sum\\\hline
		9&	-5.751e-9&	-0.0004998\\\hline
		12&	-1.5891e-9&	0.00025567\\\hline
		15&	-3.803e-11&	-0.00015069\\\hline
		18&	6.639e-13&	0.00009743\\\hline
		21&	2.6728e-13&	-0.00006722\\\hline
		24&	2.6744e-13&	0.00004866\\\hline
		27&	2.6744e-13&	-0.00003655\\\hline
	\end{tabular}
	\end{center}
	\caption{
		Computing $\int \frac{dr}{r}J_0(r k)(1-e^{-r^2})$, with $k=10$ adding up to $n$ th term.
		Levin-accelerated case reaches the true value of $\sim$2.674e-13 far more quickly, and shows superior stability.
	}
\label{tab:levin}
\end{table}
\printbibliography
\end{document}

### 2023-04-07 saturation-ver3/Functions/plot-ww.cc

@@ -61,25 +61,26 @@ int main(int argc , char** argv){
 		#if SIGMA_APPROX==-1||SIGMA_APPROX==0//if sigma is not in 1d grid
 			SIGMA sigma;
 			sigma.init(sigpar);
-			
+		/*	
 #if SUDAKOV>=1
 			Sudakov sudakov;
 			sudakov.init(sudpar);
 			DSIGMA dsigma(sigma,sudakov);
-#else
+#else*/
 			DSIGMA dsigma(sigma);
-#endif
+//#endif
 			dsigma.init(sigpar,'w');
  		#else //-2 and 1  
  			SIGMA sigma;
 			sigma.init(sigpar);
+/*
 #if SUDAKOV>=1
 			Sudakov sudakov;
 			sudakov.init(sudpar);
 			DSIGMA dsigma(sigma,sudakov);
-#else
+#else*/
 			DSIGMA dsigma(sigma);
-#endif
+//#endif
 			dsigma.init(N_APPROX+250,sigpar,'w');
 		#endif
 		

### 2023-04-07 saturation-ver3/grid.sh

@@ -1,0 +1,43 @@
+#! /usr/bin/env bash
+
+export DIR
+
+WW=/home/tomoki/Saturation-Model/saturation-ver3/RunWW
+PREV=/home/tomoki/Saturation-Model/saturation-ver3/Run2808
+RUN3=/home/tomoki/Saturation-Model/saturation-ver3/Run3
+
+DIR=${WW}/GBW
+make ww -silent
+${DIR}/ww -i ${RUN3}/GBW/result.txt -o ${DIR}/GBWr.dat
+
+DIR=${WW}/BGK
+make ww -silent
+${DIR}/ww -i ${RUN3}/BGK/result.txt -o ${DIR}/BGKr.dat
+
+DIR=${WW}/GBWS
+make ww -silent
+${DIR}/ww -i ${RUN3}/GBW/result.txt -o ${DIR}/GBWSr.dat
+
+DIR=${WW}/BGKS
+make ww -silent
+${DIR}/ww -i ${RUN3}/BGK/result.txt -o ${DIR}/BGKSr.dat
+
+###########################################
+
+
+DIR=${WW}/fixa-bjorx
+make ww -silent
+${DIR}/ww -i ${RUN3}/fixa-bjorx/result.txt -o ${DIR}/GBWkt.dat
+
+DIR=${WW}/fixa-bjorx-BGK
+make ww -silent
+${DIR}/ww -i ${RUN3}/fixa-bjorx-BGK/result.txt -o ${DIR}/BGKkt.dat
+
+DIR=${WW}/fixa-bjorx-Sud
+make ww -silent
+${DIR}/ww -i ${RUN3}/fixa-bjorx/result.txt -o ${DIR}/GBWSkt.dat
+
+DIR=${WW}/fixa-bjorx-BGK-Sud
+make ww -silent
+${DIR}/ww -i ${RUN3}/fixa-bjorx-BGK/result.txt -o ${DIR}/BGKSkt.dat
+

### 2023-04-12 saturation-ver3/kt-formula-report1/ww.tex
plots added

@@
-\documentclass{article}
-
-\usepackage[backend=bibtex]{biblatex}
+\documentclass[a4,12pt]{article}
+\usepackage[a4paper]{geometry}
+\usepackage{graphicx}
+\usepackage{pict2e}
+\usepackage{xcolor}
+\usepackage{subcaption}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+%\usepackage{epstopdf}
+\usepackage[backend=bibtex,style=ieee]{biblatex}
 \addbibresource{ww.bib}
@@
 \newcommand{\sdpa}[0]{\sigma_{\mathrm{dipole\,Adj.}}}
+\newcommand{\GeV}[0]{\mathrm{GeV}}
+\newcommand{\comment}[1]{\texttt{\color{red}#1}}
+
 \begin{document}
+	\begin{figure}[t]
+		\begin{subfigure}{0.5\textwidth}
+			\includegraphics[width=\textwidth]{gnuplot/GBWWW1} 
+		\end{subfigure}
+		\begin{subfigure}{0.5\textwidth}
+			\includegraphics[width=\textwidth]{gnuplot/BGKWW1} 
+		\end{subfigure}
+		\begin{subfigure}{0.5\textwidth}
+			\includegraphics[width=\textwidth]{gnuplot/GBWWW2} 
+		\end{subfigure}
+		\begin{subfigure}{0.5\textwidth}
+			\includegraphics[width=\textwidth]{gnuplot/BGKWW2} 
+		\end{subfigure}
+		\caption{\footnotesize Weizs\"acker-Williams gluon density at $x=10^{-3}$.
+Top row: comparison of the dipole-factorization fit and $k_t$-factorization fit results.
+Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
+}
+		\label{fig:ww}
+	\end{figure}
 \section{Dijet process}
 In order to investigate less inclusive processes, we will study the electron-dijet correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
-Dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density\cite{}.
-This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton. Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write  
+Dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
+This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm}.
+Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
 \begin{equation}
@@
 \sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
+\label{eq:ww}
 \end{equation}
-Resummation of the Sudakov logarithms is achieved by the formula~\cite{}
+Resummation of the Sudakov logarithms is achieved by the formula~\cite{Xiao:2017yya}
 \begin{equation}
 	\fww(x,k^2,\mu^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) e^{-S(r,\mu^2)} \sdpa(x,r),
+	\label{eq:ww-sud}
 \end{equation}
-where, we use the Sudakov form factor~\cite{},
+where, we use the Sudakov form factor~\cite{Mueller:2013wwa,Xiao:2017yya},
 \begin{equation}
@@
 
+The present study is carried out in the framework of the small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+The ITMD factorization is implemented in the program KATIE~\cite{vanHameren:2016kkz}, which we will use to compute the cross section.
+Important points of the formalism are the following.
+Firstly, it extends applicability of TMD to the large-$k_t$ region.
+Thus it recovers the $k_t$-factorization if saturation effects are neglected.
+Secondly, it is equivalent to CGC, except for lacking multipartonic interaction~(genuine twist)~\cite{Altinoluk:2019fui}.
+It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc} ), I assume it is $p_{1T}, p_{2T}$ that are relevant?}, ITMD is suitable for studying dijets.
+
+Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of jets and the final state electron in DIS ($e+p\rightarrow e+J_1+J_2+X$), where it was argued that this observable is sensitive to the soft emissions and the saturation effects.
+The kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
+\begin{align*}
+	E_e&=15\GeV& E_p&=135\GeV& Q^2&>1\GeV^2\\
+	0.1<&\nu<0.85&\Delta R_{\mathrm{Breit}}&<1&p^{\mathrm{Breit}}_{1,2\,T}&>3\GeV\\
+	&&-4<&y_{1,2\,\mathrm{lab}}<-1.&&
+\end{align*}
+
+Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
+The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale independent KS gluon~\cite{vanHameren:2021sqc}.
+Clearly, the GBW and BGK models falls much more quickly than the KS gluon density.
+In general, expected behaviour in the large-$k_t$ region is $\sim k_t^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while GBW behaves like $\sim e^{-k_t^2}$.
+As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_t$ region and suppresses in the large-$k_t$ region.
+In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more prominent in the case of the GBW and BGK models.
+The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (also see Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
+
+Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} corresponds to those of Fig.~4 in Ref.~\cite{vanHameren:2021sqc}. 
+In the top row of Fig.~\ref{fig:je-breit}, we clearly see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits.
+In the middle and the bottom row shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}.
+Fig.~\ref{fig:je-lab} shows the $e$-jets correlation in the lab frame.
+Here, the dofference between KS and GBW and BGK are more prominent.
+Unlike in the previous plots, the new fits in the $k-t$-factorization shows only limited improvement.
+The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e.
+The cross sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here, they are significantly increased).
+\comment{probably related to the high $k_t$ region of the gluon density?}\\
+\comment{regarding this differences between Breit and lab frames, what does "\dots since it (breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}
+
+\begin{figure}[p]
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotGBW1} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotBGK1} 
+	\end{subfigure}
+%	\caption{ }
+%\end{figure}
+%\begin{figure}[t]
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotGBW2}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotGBW3}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotBGK2}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{gnuplot/plotBGK3}
+	\end{subfigure}
+	\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the Breit frame.
+Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
+	\label{fig:je-breit}
+\end{figure}
+
+\begin{figure}[p]
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW1Lab} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK1Lab} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW2Lab}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW3Lab}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK2Lab}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK3Lab}
+	\end{subfigure}
+\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the lab frame.
+Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
+\label{fig:je-lab}
+\end{figure}
+
+Finally, Fig.~\ref{fig:jj-breit} shows the jet correlations in the Breit frame.
+Again, the GBW and BGK models show considerable deviation from the KS gluon.
+Similarly to the previous plots, the Sudakov factor affects the models differently from the KS in Ref.~\cite{vanHameren:2021sqc}.
+The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
+
+\begin{figure}[p]
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW1Jets} 
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK1Jets} 
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW2Jets}
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotGBW3Jets}
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK2Jets}
+	\end{subfigure}
+	\begin{subfigure}{0.48\textwidth}
+		\includegraphics[width=\textwidth]{gnuplot/plotBGK3Jets}
+	\end{subfigure}
+\caption{\footnotesize Azimuthal correlation of the jets in the Breit frame.
+Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
+}
+\label{fig:jj-breit}
+\end{figure}
+
 \appendix	
 \section{Computation of gluon densities}
-In order to obtain the WW gluon density, one needs to compute 
-\begin{equation}
-	\fww(x,k)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
-\end{equation} 	
-where we use 
-\begin{equation}
-	\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
-\end{equation}
-
-The convergence of this integral may be slow due to high oscillation for large $k$.
+In the evaluation Eq.~(\ref{eq:ww}) the convergence of this integral may be slow due to high oscillation for large $k$.
 For such integration, one can employ a method summarized in Ref.~\cite{LYNESS1985109}. 

### 2023-04-12 Grid-Interplation/KSgluon-example.cc

@@ -38,7 +38,7 @@ int main(int argc ,char** argv){
 	FILE* file=fopen(argv[3],"w");
 	
 	double x=1.0e-3;
-	double mu2=17*17;
+	double mu2=pow(atof(argv[4]),2);
 	double k2=0;
 	for(int i=0;i<=100;++i){
 		k2=exp(8*((double)i)/99);

### 2023-04-13 saturation-ver3/kt-formula-report1/ww.tex
document

@@
 Secondly, it is equivalent to CGC, except for lacking multipartonic interaction~(genuine twist)~\cite{Altinoluk:2019fui}.
-It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc} ), I assume it is $p_{1T}, p_{2T}$ that are relevant?}, ITMD is suitable for studying dijets.
+It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}.
+)  Also it was mentioned the cut on $p_T$ is selected for this.
+I assume it is $p_{1T}, p_{2T}$ that are relevant?}, ITMD is suitable for studying dijets.
 
@@
 Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
-The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale independent KS gluon~\cite{vanHameren:2021sqc}.
+The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc}.
 Clearly, the GBW and BGK models falls much more quickly than the KS gluon density.
@@
 As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_t$ region and suppresses in the large-$k_t$ region.
-In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more prominent in the case of the GBW and BGK models.
+In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more pronounced in the case of the GBW and BGK models.
 The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (also see Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
 
-Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} corresponds to those of Fig.~4 in Ref.~\cite{vanHameren:2021sqc}. 
+Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} corresponds to those of Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
 In the top row of Fig.~\ref{fig:je-breit}, we clearly see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits.
-In the middle and the bottom row shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}.
+In the middle and the bottom row, it shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by lowering the cross section.
 Fig.~\ref{fig:je-lab} shows the $e$-jets correlation in the lab frame.
-Here, the dofference between KS and GBW and BGK are more prominent.
-Unlike in the previous plots, the new fits in the $k-t$-factorization shows only limited improvement.
+Here, the difference between KS and GBW and BGK are more prominent.
+Unlike in the previous plots, the new fits in the $k_t$-factorization shows only limited improvement.
 The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e.
@@
 The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
+%The result seems natural as small $k_t$ corresponds to the back-to-back configuration of the jets, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons are much lower than the KS gluon.
 

### 2023-04-13 saturation-ver3/Functions/control-default.h
still problematic

@@ -42,9 +42,7 @@
 #ifndef R_MAX
 	#define R_MAX 1e+5
 #endif
-#ifndef R_MINMAX //for x dependent r max, this is as low as rmax gets. see dipole-gluon.hh
-	#define R_MINMAX 1.0e+2
-#endif
+
 
 #ifndef X_MIN 
 	#define X_MIN 1.0e-8
@@ -80,31 +78,7 @@
 	#define N_CHEB_R 250 
 #endif
 
-#ifndef STAR
-//star presctiption for r. 0 is Collins=Soper type, 1 is Golec-Biernat=Sapeta type
-	#define STAR 1
-#endif
 
-#ifndef R_FIX
-//treat r_max or mu02 as constant.
-	#define R_FIX 0
-#endif
-
-#ifndef INDEPENDENT_C
-//treat two C in model3 C/r independently
-	#define INDEPENDENT_C 1
-#endif
-
-#ifndef INDEPENDENT_RMAX
-//treat r_max or mu02 in model 3 independently
-	#define INDEPENDENT_RMAX 0
-#endif
-
-
-
-#ifndef LAPLACIAN
-	#define LAPLACIAN 0
-#endif
 #ifndef IBP
 	#define IBP 0
 #endif
@@ -119,9 +93,6 @@
 	#define PHI 0
 #endif
 
-#ifndef SCATTER
-	#define SCATTER 0
-#endif
 
 #ifndef MU02
 	#define MU02 1
@@ -131,9 +102,7 @@
 	#define GLUON_APPROX 1
 #endif
 
-#ifndef HANKEL
-	#define HANKEL 0
-#endif
+
 #ifndef FREEZE_QS2 
 	#define FREEZE_QS2 0
 #endif
@@ -141,9 +110,7 @@
 #ifndef ADD_END
 	#define ADD_END 0
 #endif
-#ifndef GBW_APPROX
-	#define GBW_APPROX 0
-#endif
+
 
 #ifndef R_CHANGE_VAR
 //use R=r/(1-r) for r integration. 

### 2023-04-13 saturation-ver3/Functions/fcn.h

@@ -156,6 +156,9 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 { 
 
 //////////////////////////////////////////////////////////////////////////////////////////
+#if SIGMA_APPROX==-2||SIGMA_APPROX==1
+printf("use with extra care\n");
+#endif
 #if R_FORMULA==1	
 	SIGMA sigma[3]={SIGMA() ,SIGMA() ,SIGMA() };
 		sigma[0].init(sigpar);
@@ -163,6 +166,7 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 		sigma[2].init(sigpar);	
 
 	#if SIGMA_APPROX==-2||SIGMA_APPROX==1 // AS GBW/BGK K   This require instance per thread
+		
 			INTEG dsigma[3]={DSIGMA(sigma[0]) ,DSIGMA(sigma[1]) ,DSIGMA(sigma[2]) };
 			dsigma[0].init(N_APPROX+250,sigpar,'s');
 			dsigma[1].init(N_APPROX+250,sigpar,'s');
@@ -175,6 +179,7 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 			};
 			F2_kt<Integrand_r<DSIGMA>> F2(integrands);
 	#elif SIGMA_APPROX==0||SIGMA_APPROX==-1
+		//printf("BGK r\n");
 		SIGMA (&dsigma)[3]=sigma;
 			Integrand_r<SIGMA> integrands[3]={
 				Integrand_r<SIGMA>(dsigma[0]) ,

### 2023-04-13 saturation-ver3/Functions/gluons.cc

@@ -1,10 +1,8 @@
 #include"gluons.hh"
-//#ifndef N_CHEB 
-
-//#endif
 ///////////////////////////////////////////////////////////////////////
 //
 ///////////////////////////////////////////////////////////////////////
+
 std::complex<double> Collinear_Gluon::gammatilde(const std::complex<double>& n)const{
 	std::complex<double> n1,n2,n3,l1,l2,t1,t2,t3,cx,value;
 	double m1,m2,rl;
@@ -62,8 +60,7 @@ double Collinear_Gluon::operator()(const double y,const std::vector<double>&par)
 //
 /////////////////////////////////////////////////////////////////////
 double Collinear_Gluon::operator()(const double x, const double QQ,const double A_g,const double l_g)const  {
-	static int flag_nan=0;
-	double normalization;
+	
 	double value;
 	const double bprim = 33.0/6.0-NF/3.0;
 	const std::vector<double> par={
@@ -71,7 +68,7 @@ double Collinear_Gluon::operator()(const double x, const double QQ,const double 
 		(1/bprim)*log(log(QQ/LQCD2)/log(Q0/LQCD2)),
 		l_g
 	};
-	normalization = A_g*exp(n_0* par[0] )*dgammafbeta;
+	const double normalization=A_g*exp(n_0* par[0] )*dgammafbeta;
 	value=dclenshaw<const Collinear_Gluon&,const std::vector<double>&>(cc,*this,par,0,150,1.0e-10,1.0e-15);  
 	value=normalization*value;
 	if(!std::isfinite(value)||value<0){
@@ -100,7 +97,7 @@ void Chebyshev1D_Collinear_Gluon::set_x(const double &x){
 	cheb_coeff<Chebyshev1D_Collinear_Gluon,const Collinear_Gluon&>(cheb[0],*this,xg);
 }
 
-double Chebyshev1D_Collinear_Gluon::operator()(const double x,const double Q2){
+double Chebyshev1D_Collinear_Gluon::operator()(const double x,const double Q2, double A_g,double l_g )const{
 	if(x!=*fixx){
 		printf("Chebyshev1D_Collinear_Gluon:: Error: x does not match. input=%.3e internal x= %.3e diff = %.3e\n",x,*fixx, x-*fixx);
 	}
[…]

### 2023-04-13 saturation-ver3/Functions/gluons.f

@@ -86,7 +86,7 @@ CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
       DOUBLE PRECISION PI,Q0
 c      COMMON /CONST/ N_F,BETA,N_0, EULERGAMMA
       DOUBLE PRECISION YG,TG,LAMBDA_G
-      PARAMETER( N_0= 0.5D0, N_F=3D0,
+      PARAMETER( N_0= 0.5D0, N_F=3D0, BETA =6.6D0,
      & EULERGAMMA =0.577215664901532860606512090082402431042D0,
      & LAMBDA2= 0.09D0, Q0=1D0,
      & PI =3.141592653589793238462643383279502884197D0)
@@ -105,11 +105,16 @@ C      YG= DLOG(1/X)
       PAR(2) = (1D0/BPRIM)*DLOG(DLOG(QQ/LAMBDA2)/DLOG(Q0/LAMBDA2))
 C      TG= (1/BPRIM)*DLOG(DLOG(QQ/LAMBDA2)/DLOG(Q0/LAMBDA2))
       NORMALIZATION = A_G*DEXP(N_0* PAR(1) )*DGAMMF(BETA)/PI
+C      PRINT *, "n_0= ",N_0, " PAR(1)= ", PAR(1)," DGAMMAF= ",
+C     &DGAMMF(BETA)
       XGPDF=DCLENSHAW(XGPDF_INTEGRAND,PAR,0d0,150d0,1.0D-12,1.0D-15)
+C      PRINT *, "x=", x," q2= ", QQ," Ag= ",A_G," lg= ",LAMBDA_G, 
+C     & " value= ",XGPDF," norm= ",NORMALIZATION 
       XGPDF=XGPDF*NORMALIZATION
       IF (ISNAN(XGPDF)) THEN
 c              WRITE(6,"(A5 E9.2 A5 E9.2)") " X= ",X," Q2= ", QQ
               xgpdf=0d0;
       ENDIF
+      
   100 RETURN
       END

### 2023-04-13 saturation-ver3/Functions/main.cc

@@ -58,14 +58,14 @@ int main(int argc, char** argv){
 	std::cout<<std::scientific<<std::endl;
 	
 	printf("********************Program Started********************.\n");
-	printf("MODEL     = %d, VARIANT      = %d,                N_CHEB_R     = %d\n",MODEL,VARIANT, N_CHEB_R);
+	printf("MODEL     = %d,               N_CHEB_R     = %d\n",MODEL,N_CHEB_R);
 	printf("R_FORMULA = %d, MU02         = %d\n",R_FORMULA, MU02);
 	printf("MODX      = %d, R_CHANGE_VAR = %d,             \t GLUON_APPROX = %d\n",MODX,R_CHANGE_VAR,GLUON_APPROX);
-	printf("ALPHA_RUN = %d, Hankel       = %d\n", ALPHA_RUN,  HANKEL);
+	printf("ALPHA_RUN = %d, \n", ALPHA_RUN);
 	printf("FREEZE_QS2= %d, ADD_END      = %d,             \t THRESHOLD    = %d\n",FREEZE_QS2,ADD_END,THRESHOLD);
-	printf("NS        = %d, IBP          = %d\n",NS,IBP);
+	printf("IBP          = %d\n",IBP);
 	printf("ADJOINT   = %d, WW           = %d\n",ADJOINT,WW);
-	printf("Directory = %s ,\t R  = [%.1e, %.1e, %.1e]\n",(char*)argv[1],R_MIN, R_MINMAX, R_MAX);
+	printf("Directory = %s ,\t R  = [%.1e, %.1e]\n",(char*)argv[1],R_MIN, R_MAX);
 	printf("SIGMA_APPROX = %d   N_CHEB   = %d              \t CHEB_D       = %d \n",SIGMA_APPROX,N_CHEB,CHEB_D);
 	printf("*******************************************************.\n");
 	

### 2023-04-13 saturation-ver3/Functions/r-formula.cc

@@ -1,6 +1,6 @@
 #include"r-formula.hh"
 //double Sigma::Qs2(const double x,const double r){
-double Sigma_GBW::Qs2(const double x,const double r){
+double Sigma_GBW::Qs2(const double x,const double r)const{
 	if(x>1){
 		printf("Sigma:: x is too large %.3e\n",x);
 		getchar();
@@ -11,7 +11,7 @@ double Sigma_GBW::Qs2(const double x,const double r){
 	}
 	return qs2;		
 }
-double Sigma_BGK::Qs2(const double x,const double r){
+double Sigma_BGK::Qs2(const double x,const double r)const{
 	if(x>1){
 		printf("Sigma:: x is too large %.3e\n",x);
 		getchar();
@@ -22,20 +22,13 @@ double Sigma_BGK::Qs2(const double x,const double r){
 	}
 	#endif
 	const double rrmax=pow(r,2)/C;
-	//const double mu2=(r>1.0e-5)?(mu02/((1.0-exp(-mu02*rrmax) ))):(1/rrmax) ;
-	const double mu2=C/pow(r,2)+mu02;
-	//const double mu2=mu02/((1.0-exp(-mu02*rrmax) ));
+	const double mu2=(r>1.0e-5)?(mu02/((1.0-exp(-mu02*rrmax) ))):(1/rrmax+mu02/2) ;
 	const double al=alpha(mu2);
-	#if SIGMA_APPROX>=0
+	//const double al=0.2;
 	const double qs2=4*PI*PI*al*xgpdf(x,mu2,A_g,lambda_g)/(3*sigma_0); 
-	//const double qs2=4*PI*PI*A_g*pow(x,-lambda_g)/(3*sigma_0); 
-	#elif SIGMA_APPROX<0
-	const double qs2=4*PI*PI*al*xgpdf(x,mu2)/(3*sigma_0); 
-	#endif
 	if(qs2<1.0e-50){
 		return 1.0e-50;
 	}
-	//printf("Qs2=%.2e\n",qs2);
 	return qs2;		
 }
 
@@ -54,42 +47,42 @@ void Sigma_BGK::set_x(const double &x){
 }
 
 //void Sigma::init(const double * const &sigpar){
-inline void Sigma_GBW::init(const double * const &sigpar){
-	par=sigpar;
[…]

### 2023-04-13 saturation-ver3/test-gluons.cc

@@ -1,71 +1,30 @@
-#define MODEL 0
-#include<cmath>
-#include "./Functions/complex.hh"
-//#include "cfortran.h"
-#include"./Functions/control-default.h"
-#include"./Functions/constants.h"
-//#include "./Functions/clenshaw.hh"
 #include<iostream>
-#include<pthread.h>
+#include"gluons.hh"
 
-//#include"./Functions/gluons.hh"
-
-
-//Collinear_Gluon xgpdf;
 extern "C" double xgpdf_(const double* x, const double* QQ,const double* A_g, const double* lambda_g );
-extern "C" double xgpdf_integrand_(const double* x, const double* QQ) ;
-void* compute(void* arg){
-	double *args=(double*)arg;
-	double j=1;
-	
-	//printf("%.3e %.3e %.3e %.3e \n",args[0],args[1],args[2],args[3] );
-	//getchar();
-	//args[4]=xgpdf(args[0],args[1],args[2],args[3] );
-	args[4]=xgpdf_(args,args+1,args+2,args+3);
-	//for(int i=0;i<30;i++){
-		//j=i;
-	//	args[4]=xgpdf_integrand_(&j,args) ;
-	//	(args[1]>2)?(printf("2\t\t")):(printf("1\t"));
-	//	printf("%.3e \n",args[4]);
-	//}
-	return NULL;	
-}
+
 
 int main(){
-	//pthread_t thread[3];
-	double args[5*200];
-	int i1;
-#pragma opm parallel
-{
-#pragma omp for
-	for(int j=0;j<200;j++){
-		args[5*j]=0.0001;//*(j+1);
-		args[5*j+1]=pow(10,2);
-		args[5*j+2]=1;
-		args[5*j+3]=0.01;
-		
-		//if(j>1) {pthread_join(thread[j-1],NULL); }
-		compute((void*)(args+5*j) );
-		printf(" %.3e \n", args[5*j+4]);
-		
-		
+	Collinear_Gluon xg;
+	Chebyshev1D_Collinear_Gluon cxg(30);
+	double x,mu2;
+	double val1,val2,val3;
+	const double Ag=1.1,lg=0.08;
+	cxg.init(1,2.0e+8,Ag,lg);
+	for(int j=0;j<50; ++j){
[…]

### 2023-04-14 New parameters for the Golec-Beiernat--Wusthoff and Bartels--Golec-Biernat--Kowlski saturation model in the k_t-facorization formula of F_2/draft.tex
restructuring

\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{times}
%\usepackage{merriweather}
%\usepackage{draftwatermark}
\usepackage[backend=bibtex, style=ieee]{biblatex}

\addbibresource{draft.bib}

\usetikzlibrary{decorations}
\usetikzlibrary{snakes}

%\newcommand{\comment}[1]{{\color{red}[\textbf{comment:} #1 ]}}

\pagenumbering{arabic}
\numberwithin{equation}{section}
\numberwithin{table}{section}
\numberwithin{figure}{section}

\newcommand{\fww}[0]{\mathcal{F}^{\mathrm{WW}}}
\newcommand{\fdp}[0]{\mathcal{F}^{\mathrm{dipole}}}
\newcommand{\sdp}[0]{\sigma_{\mathrm{dipole}}}
\newcommand{\sdpa}[0]{\sigma_{\mathrm{dipole\,Adj.}}}
\newcommand{\GeV}[0]{\mathrm{GeV}}
\newcommand{\comment}[1]{\texttt{\color{red}#1}}
\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\author{
T.~Goda,$^1$, K.~Kutak$^{1}$ and S.~Sapeta$^1$\\\,\\
$^1$ 
{\small\it The H.\ Niewodnicza\'nski Institute of Nuclear Physics PAN,}\\ 
{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\%\,\\
%$^2$ 
%{\small\it Physics Department, Brookhaven National Laboratory,}\\
%{\small\it Upton, NY 11973, USA}\\
}	 
\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_t$-facorization formula of $F_2$}

\date{\today}

\begin{document}

\maketitle

%--------------- preprint numbers ---------------------
\vspace{-25em}
\begin{flushright}
%  IFJPAN-IV-2022-16\\
\end{flushright}
\vspace{20em}
%-----------------------------------------------------------------

\begin{abstract}

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Introduction}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\comment{To be reduced... rewritten ... }
%{
%\color{gray}
%For decades Deep Inelastic Scattering (DIS) has played major role in the studies of particle physics. The structure of a proton is one of the key elements in the particle collider experiments. In the collinear factorization, one factorizes the total cross section in to the perturbatively calculable short-distance part and a process-independent long-distance part, called parton distribution functions~(PDFs). The energy scale dependence of the PDFs are described by the Dokshitzer--Gribov--Lipatov--Alterelli--Parisi~(DGLAP) evolution equations, which resums the large logarithms. While an inclusive process can be described well by the collinear PDFs, one needs transverse momentum dependent PDFs for less inclusive processes. The PDFs also denpends on so-called Bjorken scaling variable, $x$. While the $Q$ dependence of the PFDs are perturbatively calculable, one generally needs to extract $x$ dependence from experiments. In the limit of small-$x$, however, the Balitsky--Fadin--Kuraev--Lipatov (BFKL) equation predicts that, the gluon density rises like $\sim x^{-\lambda}$.   This rise eventually violates the Froissart bound, which limit the rise of the cross section to be $\sim\log^2(s)$.  
%This  taming of the rise is called saturation. The saturation phenomena becomes relevant when the gluon density inside the proton becomes so high that recombination of them can no longer be neglected.
%There has been much effort trying to understand this effect in both perturbative evolution equations and modeling.
%On the perturbative calculation side, notably, the  Balistki--Kovchegov~(BK) equation extends the BFKL equation by including a non-linear term to encapsulate the saturation. On the modeling side, among others, Golec-Biernat and W\"usthoff (GBW) proposed a simple model, whose key essence is encoded in the $x$ dependent saturation scale, $Q_s(x)$. The saturation scale can be thought of as a line which roughly separate the saturation region and the scaling region.  It is this GBW model, which we are primarily interested in this study.
%}
\comment{Bibliography will be properly made once the draft is complete. For only now I use biblatex.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{$k_t$-factorization formula}
\section{Introduction}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\resizebox{0.9\textwidth}{!}{
\begin{tikzpicture}
\draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
\draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
\draw(-0.5in , 0in)--(0.5in,0in)--(0.5in , -0.5in)--(-0.5in,-0.5in)--cycle ;

\filldraw(0.02in,0)--(-0.02in,-0.02in)--(-0.02in,0.02in)--cycle;
\filldraw(-0.02in,-0.5in)--(0.02in,-0.52in)--(0.02in, -0.48in)--cycle;

\filldraw(-0.5in,-0.23in)--(-0.52in,-0.27in)--(-0.48in,-0.27in)--cycle;
\filldraw(0.5in,-0.27in)--(0.52in,-0.23in)--(0.48in,-0.23in)--cycle;

\draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
\draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
\draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
\draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
\begin{tikzpicture}
\draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
\draw[snake=coil,segment aspect=0,segment length=0.1in](0.875in ,0.5in)--(0.5in,0.in);
\draw(-0.5in , 0in)--(0.5in,-0.5in)--(0.5in ,0in)--(-0.5in,-0.5in)--cycle ;

%\filldraw(0.02in,0)--(-0.02in,-0.02in)--(-0.02in,0.02in)--cycle;
%\filldraw(-0.02in,-0.5in)--(0.02in,-0.52in)--(0.02in, -0.48in)--cycle;

\filldraw(-0.5in,-0.23in)--(-0.52in,-0.27in)--(-0.48in,-0.27in)--cycle;
\filldraw(0.5in,-0.23in)--(0.52in,-0.27in)--(0.48in,-0.27in)--cycle;

%\draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
%\draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
\draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
\draw[snake=coil,segment aspect=1.5,segment length=0.1in](-0.5in , -1in)--(-0.5in,-0.5in);
\end{tikzpicture}
}
\caption{Kinematic variables of the gluon contribution to $F_2$. The momentum fraction of gluon is $x/z$ as it has to contribute via the quark box.
}
\label{fig:gluon-kinem}
\end{figure}

In the small-$x$ region of DIS, interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_t^2)$.   This appears in the $k_t$-factorization formula, which we will discuss later,  and plays role similar to that of collinear parton distribution function in the collinear factorization.
The dipole gluon density is also called unintegrated gluon density since it is related to the collinear (integrated) gluon density by
\begin{equation}
xg(x,Q^2)=\int^{Q^2}_0 dk_t^2 \mathcal{F}(x,k^2_t).
\end{equation}
%While the behaviour of $\mathcal{F}$ is described by evolution equations such as Balistky--Fadin--Kuraev-Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs}  and Ciafaloni--Catani--Fiorani--Marchesini (CCFM)~\cite{Ciafaloni:1987ur,Catani:1989sg,Catani:1989yc}. 
Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.  However, such rise violates the Froissart bound~\cite{Kovchegov:2012mbw}. The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth. The phenomenon described by this nonlinear term is called saturation.
Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity. A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}. The model was originally proposed in the position space version of the $k_t$-factorization formula, and the object which corresponds to the gluon density of the $k_t$-factorization is called dipole cross section.
In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
\begin{align}
\sigma_{\mathrm{dipole}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
&R^{-2}_0&=\frac{Q_0^{2}}{4}\left(\frac{x_0}{x}\right)^\lambda.
\end{align}
\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
The dipole cross section is related to the gluon density by the Fourier transform: 
\begin{equation}
\alpha_s\mathcal{F}(x,k_t^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
\label{eq:dipole-gluon}
\end{equation}
%An important feature of the GBW model is that it describes the phenomenon of saturation in a simple form. 
The essence of GBW model is encoded in the $x$-dependent saturation scale $Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and the scaling region.
A further development was made by Bartels, Golec-Biernat and Kowalski~(BGK)~\cite{Bartels:2002cj} which incorporates the DGLAP evolution by modifying the exponent to 
\begin{equation}
R_0^{-2}=\frac{\pi^2\alpha(\mu^2)xg(x,\mu^2)}{3\sigma_0},
\end{equation}
where
\begin{align}
\mu^2&=\frac{C}{r^2}+\mu_0^2 & &\mathrm{and} & xg(x,Q^2_0)&=A_g x^{-\lambda_g}(1-x)^{5.6},
\end{align}
thus improving the description of data at higher $Q^2$.\\
While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, the derivation of the dipole-factorization formula from the $k_t$-factorization involves with certain simplification and introduction of massive light quarks. The main goal of this paper is to investigate the GBW and BGK models in the $k_t$-factorization formula and to understand the dipole-factorization better.

Let us consider the inclusive DIS process $e p\rightarrow \gamma^* (q) p(p)\rightarrow X$. %where a proton and a photon interact, and their momenta are $p$ and $q$ respectively.
Additionally, let us introduce $q'\equiv q+x p$. 
Then one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
\begin{align}
    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_t.
\end{align}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize in the form~\cite{Kimber:2001uaa} 
\begin{align}
	\begin{split}
		F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
		\times\left[
		\left[\beta^2+(1-\beta)^2\right]
		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
		+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
		\right],&
		\label{eq:angle-unintegratedT}
	\end{split}\\
	\begin{split}
		F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
		\times\left[
		4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
		\right],&
		\label{eq:angle-unintegratedL}
	\end{split}
\end{align}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2},
	\label{eq:z}
\end{equation}
and
\begin{equation}
	\begin{split}
		D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2,\\
		D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
	\end{split}
\end{equation}
If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_t$, 
the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce} (i.e. dipole-factorizaton formula)
\begin{equation}
F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
\label{eq:dipole-factorization}
\end{equation}
where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the color dipole with the proton.\\

\comment{does that mean it was wrong to have massive quarks in the photon wave function?}
%Let us remind ourselves a few points about the dipole-factorization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Fits of saturation models in momentum space}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
With a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, Eqs.~(\ref{eq:angle-unintegratedT})~and~(\ref{eq:angle-unintegratedL}) can be integrated analytically over the angle $\phi$ to yield~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
\begin{multline}
F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_t^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_t^2)\Theta(1-x/z)\\
\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
\label{eq:angle-integrated}
\end{multline}
where %${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, 
\begin{equation}
\begin{split}
\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
\end{split}
\end{equation}
for
\begin{equation}
\begin{split}
N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_t^2,\\
N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_t^2, &\hspace{2cm}
N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_t^2.
\end{split}
\end{equation}
While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we will follow Ref.~\cite{Kwiecinski:1997ee} and use
\begin{equation}
\mu^2=k_t^2+{\kappa'}_t^2+m_f^2.
\end{equation}

The dipole cross section is used in Eq.~(\ref{eq:angle-integrated}) through Eq.~(\ref{eq:dipole-gluon}).
In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is a constant for the GBW model, and thus explicitly multiply by a running  coupling;
\begin{equation}
\alpha_s(\mu^2)\mathcal{F}(x,k_t^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_t^2)}{0.2},
\end{equation}
where 0.2 is an arbitrary normalization, and 
\begin{equation}
\alpha_s(\mu^2)=\frac{1}{\frac{11 C_A-2n_f}{12\pi}\log\left(\frac{\mu^2}{\Lambda_{\mathrm{QCD}}^2 }\right)},
\end{equation}
where $\Lambda_{\mathrm{QCD}}^2=0.09\;\mathrm{GeV^2}$.
Nevertheless, the effect of the normalization is absorbed by $\sigma_0$ and hence, bears no importance. \\
Since the lower limits of the integrations of $k_t$ and ${\kappa'}_t$ are 0, the scale $\mu^2$ has to be frozen. We do so by adding $\mu_0^2=4\;\mathrm{GeV^2}$ which seems to give reasonable result, thus making $\mu^2=k_t^2+{\kappa'}_t^2+m_f^2+\mu_0^2$. 
%\comment{something about large $x$ region should be mentoned. Particularly that of BGK.}
\comment{Unlike in the dipole-factorization formula Eq.~(\ref{eq:dipole-factorization}), the argument of $\mathcal{F}$ is $x/z$, not $x$, therefore, the gluon density enters the region of large-$x$ where the model is not expected to be valid.} Particularly the assumption that the parton density is dominated by gluons is no longer true.  While one may multiply the gluon density by a factor $(1-x/z)^\alpha$ in order to suppress the threshold region\cite{Timneanu:2001bk}, from a preliminary fit, it was observed that the effect is rather limited and for the case of the BGK model, the fit quality was deteriorated.\comment{Although small power may be possible to improve. Also recall, that Sudakov had effect of suppressing large-$x$.} 
We leave the detailed analysis of the threshold region for the future studies. \\
%, and we will not do anything in particular in this study to modify the large-$x$ region.
The GBW and BGK models were fitted to the $F_2$ data from HERA~\cite{Abt:2017nkc}. A numerical program was written with help of CERNLIB~\cite{Kolbig:1972zz}, GSL~\cite{GSL}, CUBA~\cite{Hahn:2004fe} and ROOT~\cite{Brun:1997pa} libraries to evaluate $F_2$. The data were selected to be in the range $0.045\leq Q^2\leq 650\;\mathrm{GeV^2}$, $x<0.01$.
As with the previous fit~\cite{Goda:2022wsc}, the $c$ and $b$ flavours were taken into account with the mass $1.3$ and $4.6\;\mathrm{GeV}$, respectively. As discussed earlier, we take the light quarks to be massless.
The fitting was performed using MnMigrad and MnSimplex of ROOT::Minuit2~\cite{James:2004xla}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Result}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The fit was performed for the following cases
\begin{itemize}
\item GBW model with the fixed coupling in $k_t$-factorization  ($k_t$-GBW),
\item GBW model with the running coupling in $k_t$-factorization (rc-$k_t$-GBW),
\item BGK model in $k_t$-factorization ($k_t$-BGK),
\end{itemize} 
and, as a reference, we provide the following results from Ref.~\cite{Goda:2022wsc};
\begin{itemize}
\item GBW model with massless light quarks in the dipole-factorization ($r$-GBW),
\item GBW model with massive light quarks in the dipole-factorizations ($r$-GBW-massive),
\item  BGK model in  the dipole-factorization ($r$-BGK).
\end{itemize}

The results of fits are summarized in Tab.~\ref{tab:table}. 
The fit quality of $k_t$-GBW is almost unchanged from $r$-GBW, while rc-$k_t$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects. \comment{What is the connection? Their result regarding the 1/x grad of $Q_s$ becoming smaller is clearly not present in our case. If we consider $\mathcal{F}$ with running coupling, it will be a bit bent in very small-x. besides, the analysis of \cite{Albacete:2004gw} extends to around $Y=\ln(x_0/x)\sim35$. for our case it may be just not low enough. (though around $Y=10$, $\alpha_0=0.2$ and running have sizable difference. ) }
Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_t$-GBW are almost identical to those of $r$-GBW. This can be seen also in Fig.~\ref{fig:GBW}. \\
Let us analyze the difference in $\sigma_0$. 
Recalling that the difference between the $k_t$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$. It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.). Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation.\comment{K.Kutak \& A. Stasto} In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.    
Since 
\begin{equation}
\left(1+\frac{4 m_f^2}{Q^2}\right)\leq\left(1+\frac{k_t^2}{Q^2}+\frac{{\kappa'}_t^2+m_f^2}{\beta(1-\beta)Q^2}\right),
\end{equation}
the $k_t$-factorization case receives more suppression. Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression. Thus, one would expect that the massive light quarks partially simulate the effect of $x/z$.
It is therefore, interesting to see that the parameters of $k_t$-GBW, are closer to those of $r$-GBW-massive than to the parameters of $r$-GBW.    
However, it seems that there is a compensating factor in rc-$k_t$-GBW. The compensating effect can be understood as follows. As it is visible in  Fig.~\ref{fig:GBW}, larger $x_0$ enhances the small-$r$ region which corresponds roughly to the large-$k_t$ of the dipole gluon density which also is visible. 
As the running coupling depends on $k_t^2$,  one can expect that the large-$k_t$ region gets suppressed.  Therefore, one can conclude that the change in $x_0$ is a direct consequence of the running coupling.\\
While the GBW model remains almost unaffected, the BGK model seems to show slightly more change. The difference is more prominent in the small-$x$ region (Fig.~\ref{fig:BGK}), particularly noticeable in the second peak of the gluon density.
The change is cleanly visible in the saturation scale of Fig.~\ref{fig:BGK}. \comment{Is there anything more to be said?}
The resulting $F_2$ of respective models are shown in Figs.~\ref{fig:GBW-Grid}~and~\ref{fig:BGK-Grid}.
While the $r$-GBW and $k_t$-GBW show little difference, rc-$k_t$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
As for the BGK model, the difference is too small to be seen in the top plots. However the bottom histogram shows some differences. While the small-$Q^2$ region is somewhat improved, as a whole, the changes cancel out.

\comment{notice the $x$-slope of $F_2$ in small-$Q^2$ is affected. Recalling that in $r$-formula that region was controlled by the mass of light-quarks. }
\comment{Also, running GBW is showing somewhat similar pattern with the Sudakov improvement.}

\begin{table}[t]
\begin{subtable}{\textwidth}
\center\footnotesize
\input{GBW-parameters.tex}
%\caption{}
\vspace{2mm}
\end{subtable}
\begin{subtable}{\textwidth}
\center\footnotesize
\input{BGK-parameters.tex}
%\caption{}
\vspace{2mm}
\end{subtable}
\caption{Fit parameters of respective models. The parameters of the dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}.
\comment{$\sigma_0\sim30$ is somewhat closer to the fit result of rcBK 1012.}
}
\label{tab:table}
\end{table}

\begin{figure}[t]
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/GBW-dipole.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/GBW-gluon.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/GBW-saturation.png}
\end{subfigure}
\caption{The dipole cross section and the dipole gluon density at
$x=10^{-2}, 10^{-6}$, and the saturation scale. 
Note, the dipole cross section and the gluon density are normalized by $\sigma_0^{-1}$.
\comment{The plots do not contain running coupling as the scale depends on $\kappa$ and $m_f$ etc. thus this should be thought of as normalized $\mathcal{F}$, rather than $\alpha\mathcal{F}$.}}
\label{fig:GBW}
\end{figure}

\begin{figure}[t]
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/BGK-dipole.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/BGK-gluon.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
\includegraphics[width=\textwidth]{./plots/BGK-saturation.png}
\end{subfigure}
\caption{The dipole cross section and the dipole gluon density at
$x=10^{-2}, 10^{-6}$, and the saturaton scale. 
Note, the dipole cross section and the gluon density are normalized by $\sigma_0^{-1}$}
\label{fig:BGK}
\end{figure}

\begin{figure}[p]
%\begin{subfigure}{\textwidth}
\includegraphics[width=0.49\textwidth]{./plots/Figure_1.png}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2.png}
\includegraphics[width=\textwidth]{./plots/Figure_3.png}
\vspace{2mm}
%\end{subfigure}
\caption{Comparison of GBW $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame.
 Improvement by the running coupling ($k_t$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_t$) shows only marginal improvement .  }
\label{fig:GBW-Grid}
\end{figure}
\begin{figure}[p]
%\begin{subfigure}{\textwidth}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-1.png}
\includegraphics[width=0.49\textwidth]{./plots/Figure_2-2.png}
\includegraphics[width=\textwidth]{./plots/Figure_2-3.png}
%\end{subfigure}
\caption{Comparison of BGK $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame. While the overall fit quality remain similar, the fit quality in each frame change noticeably. Particularly the $k_t$-formula case ($k_t$) shows better fit in the small-$Q^2$ region.}
\label{fig:BGK-Grid}
\end{figure}

%\begin{figure}[p]
%\center
%\includegraphics[width=0.9\textwidth]{../plots/dipole-GBW.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW-contour.png}
%\caption{from left: r-BGK, kt-BGK}
%\end{figure}
%\begin{figure}[p]
%\center
%\includegraphics[width=0.9\textwidth]{../plots/dipole-BGK.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK.png}\\
%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK-contour.png}
%\caption{from left: r-BGK, kt-BGK}
%\end{figure}

\section{Dijet process}
\begin{figure}[t]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{plots/GBWWW1} 
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{plots/BGKWW1} 
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{plots/GBWWW2} 
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{plots/BGKWW2} 
    \end{subfigure}
    \caption{\footnotesize Weizs\"acker-Williams gluon density at $x=10^{-3}$. Top row: comparison of the dipole-factorization fit and $k_t$-factorization fit results. Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$. Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}. }
    \label{fig:ww}
\end{figure}
In order to investigate less inclusive processes, we will study the electron-dijet correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
Dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm}. Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
\begin{equation}
\fww(x,k^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation} 	
with the adjoint dipole cross section
\begin{equation}
\sdpa(x,r)=\sigma_0\left( 1-\left(1-\frac{\sdp(x,r)}{\sigma_0}\right)^{C_A/C_F}\right).
\label{eq:ww}
\end{equation}
Resummation of the Sudakov logarithms is achieved by the formula~\cite{Xiao:2017yya}
\begin{equation}
	\fww(x,k^2,\mu^2)= \frac{C_F}{2\pi^3\alpha_s}\int^\infty_0\frac{dr}{r}J_0(r k) e^{-S(r,\mu^2)} \sdpa(x,r),
	\label{eq:ww-sud}
\end{equation}
where, we use the Sudakov form factor~\cite{Mueller:2013wwa,Xiao:2017yya},
\begin{equation}
	S(r,\mu^2)=\frac{\alpha_s N_c}{4\pi}\ln^2\left(\frac{\mu^2r^2}{4e^{-2\gamma_E}}\right),
\end{equation}
in which $\gamma_E$ is the Euler-Mascheroni constant, and we use $\alpha_s=0.2$.

The present study is carried out in the framework of the small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
The ITMD factorization is implemented in the program KATIE~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. Important points of the formalism are the following. Firstly, it extends applicability of TMD to the large-$k_t$ region. Thus it recovers the $k_t$-factorization if saturation effects are neglected. Secondly, it is equivalent to CGC, except for lacking multipartonic interaction~(genuine twist)~\cite{Altinoluk:2019fui}. It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with the above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}. )  Also it was mentioned the cut on $p_T$ is selected for this. I assume it is $p_{1T}, p_{2T}$ that are relevant?}, ITMD is suitable for studying dijets.

Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of jets and the final state electron in DIS ($e+p\rightarrow e+J_1+J_2+X$), where it was argued that this observable is sensitive to the soft emissions and the saturation effects. 
The kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
\begin{align*}
	E_e&=15\GeV& E_p&=135\GeV& Q^2&>1\GeV^2\\
	0.1<&\nu<0.85&\Delta R_{\mathrm{Breit}}&<1&p^{\mathrm{Breit}}_{1,2\,T}&>3\GeV\\
	&&-4<&y_{1,2\,\mathrm{lab}}<-1.&&
\end{align*}

Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc}. Clearly, the GBW and BGK models falls much more quickly than the KS gluon density. In general, expected behaviour in the large-$k_t$ region is $\sim k_t^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while GBW behaves like $\sim e^{-k_t^2}$.
As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_t$ region and suppresses in the large-$k_t$ region. In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more pronounced in the case of the GBW and BGK models. The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (also see Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).

Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} corresponds to those of Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
In the top row of Fig.~\ref{fig:je-breit}, we clearly see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits. In the middle and the bottom row, it shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by lowering the cross section.
Fig.~\ref{fig:je-lab} shows the $e$-jets correlation in the lab frame. Here, the difference between KS and GBW and BGK are more prominent. Unlike in the previous plots, the new fits in the $k_t$-factorization shows only limited improvement.
The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e. The cross sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here, they are significantly increased). \comment{probably related to the high $k_t$ region of the gluon density?}\\
\comment{regarding this differences between Breit and lab frames, what does "\dots since it (breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}

\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotGBW1} 
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotBGK1} 
	\end{subfigure}
%	\caption{ }
%\end{figure}
%\begin{figure}[t]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotGBW2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotGBW3}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotBGK2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\textwidth]{plots/plotBGK3}
	\end{subfigure}
	\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the Breit frame. Top: Comparison of dipole-factorization fit and $k_t$-factorization fit. Middle \& Bottom: Effect of the Sudakov form factor.   Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
	\label{fig:je-breit}
\end{figure}

\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW1Lab} 
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK1Lab} 
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW2Lab}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW3Lab}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK2Lab}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK3Lab}
	\end{subfigure}
\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the lab frame. Top: Comparison of dipole-factorization fit and $k_t$-factorization fit. Middle \& Bottom: Effect of the Sudakov form factor.  Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
\label{fig:je-lab}
\end{figure}

Finally, Fig.~\ref{fig:jj-breit} shows the jet correlations in the Breit frame. Again, the GBW and BGK models show considerable deviation from the KS gluon. Similarly to the previous plots, the Sudakov factor affects the models differently from the KS in Ref.~\cite{vanHameren:2021sqc}.
The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to small $k_t$ of the gluon, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in large-$k_t$ region.

\begin{figure}[p]
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW1Jets} 
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK1Jets} 
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW2Jets}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotGBW3Jets}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK2Jets}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=\textwidth]{plots/plotBGK3Jets}
	\end{subfigure}
\caption{\footnotesize Azimuthal correlation of the jets in the Breit frame. Top: Comparison of dipole-factorization fit and $k_t$-factorization fit. Middle \& Bottom: Effect of the Sudakov form factor. Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}. }
\label{fig:jj-breit}
\end{figure}

\section{Summary}
We have fitted the Golec-Biernat--W\"usthoff~(GBW)\cite{Golec-Biernat:1998zce} and Bartels--Golec-Biernat--Kowalski~(BGK)~\cite{Bartels:2002cj} models to the HERA data~\cite{Abt:2017nkc} in the context of the $k_t$-factorization of $F_2$.  The main difference between the $k_t$- and dipole-factorizations is an argument of the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the dipole-factorization. It was discussed that massive light quarks used in Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the fit result indicates such effect as expected. It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_t$-factorization formula. Only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_t$-factorization case. It was also observed that the explicit inclusion of the running coupling has significant effect in the fit quality particularly in the large-$Q^2$ region where the GBW model performs poorly.

\appendix	
\section{Computation of gluon densities}
In the evaluation Eq.~(\ref{eq:ww}) the convergence of this integral may be slow due to high oscillation for large $k$.
For such integration, one can employ a method summarized in Ref.~\cite{LYNESS1985109}. 
Essentially, the integration is carried out between, anti-nodes of $J_0(rk)$. Then the total integral is written in the form of infinite sum
\begin{equation}
	I=\sum^\infty_{i=1} \int^{a_{i+1}}_{a_i} \frac{dr}{r}J_0(r k) \sdpa(x,r),
\end{equation}
where we use $a_{i}=\frac{\pi}{k}(i+1/4)$.
This sum can be accelerated, with series transformation described in Ref.~\cite{doi:10.1080/00207167308803075,Weniger:1989rea,HOMEIER19951}.
The remarkable power of the Levin's transformation is shown in Tab.~\ref{tab:levin}.
This trick is also useful in the computation of dipole gluon density.

\begin{table}
	\begin{center}
		\begin{tabular}{|c||c|c|}
			\hline
			$n$&Levin&Sum\\\hline
			9&	-5.751e-9&	-0.0004998\\\hline
			12&	-1.5891e-9&	0.00025567\\\hline
			15&	-3.803e-11&	-0.00015069\\\hline
			18&	6.639e-13&	0.00009743\\\hline
			21&	2.6728e-13&	-0.00006722\\\hline
			24&	2.6744e-13&	0.00004866\\\hline
			27&	2.6744e-13&	-0.00003655\\\hline
		\end{tabular}
	\end{center}
	\caption{
		Computing $\int \frac{dr}{r}J_0(r k)(1-e^{-r^2})$, with $k=10$ adding up to $n$ th term.
		Levin-accelerated case reaches the true value of $\sim$2.674e-13 far more quickly, and shows superior stability.
	}
	\label{tab:levin}
 \end{table}

\section{Derivation of dipole-factorization}
For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize in the form~\cite{Kimber:2001uaa} 
\begin{align}
	\begin{split}
		F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
		\times\left[
		\left[\beta^2+(1-\beta)^2\right]
		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
		+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
		\right],&
		\label{eq:angle-unintegratedT}
	\end{split}\\
	\begin{split}
		F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
		\times\left[
		4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
		\right],&
		\label{eq:angle-unintegratedL}
	\end{split}
\end{align}
where
\begin{equation}
	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2},
	\label{eq:z}
\end{equation}
and
\begin{equation}
	\begin{split}
		D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2,\\
		D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
	\end{split}
\end{equation}
In the remaining part of this section, let us revisit the derivation of the dipole-factorization formula in Ref.~\cite{Bartels:2002cj}, and show that the difference boils down to replacing $x/z$ with $\tilde{x}\equiv x\left(1+4m_f^2/Q^2\right)$ of Ref.~\cite{Golec-Biernat:1998zce}.

%As demonstrated below, this factorization can be transformed into the position space factorization with a new object, namely, the dipole cross section~\cite{Golec-Biernat:1998zce, Bartels:2002cj}.
%In short, the formula of Ref.~\cite{Golec-Biernat:1998zce} can essentially be obtained by replacing $x/z$ with $\tilde{x}$ of Ref.~\cite{Golec-Biernat:1998zce} and assuming fixed coupling.\\
Using the identities \cite{Bartels:2002cj}
\begin{align}
	i N_1\int\frac{d^2\mathbf{r}}{2\pi} \left( \frac{\mathbf{r}}{r}\right) e^{i r k \cos\theta}K_1(N_1 r)&=- \frac{\mathbf{k}}{k^2+N_1^2},\\
	i \int\frac{d^2\mathbf{r}}{2\pi}e^{i r k \cos\theta}K_1(N_1 r)&=- \frac{1}{k^2+N_1^2},
\end{align}
one can write
\begin{align}
	\begin{split}
		\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2&\\
		=\int\frac{d^2\mathbf{r}}{2\pi}&\int\frac{d^2\mathbf{r}'}{2\pi}
		e^{i \boldsymbol{\kappa}_t\cdot(\mathbf{r}-\mathbf{r}')}
		\left(1 -e^{-i\mathbf{k}\cdot \mathbf{r}\phantom{'}}
		\right)
		\left(1 -e^{i\mathbf{k}\cdot \mathbf{r}'}
		\right)
		K_0(N_1 r)K_0(N_1 r'),
	\end{split}\\
	\begin{split}
		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2&\\
		=\int\frac{d^2\mathbf{r}}{2\pi}\int\frac{d^2\mathbf{r}'}{2\pi}&
		\left(\frac{\mathbf{r}\cdot\mathbf{r}'}{r r'}\right)
		e^{i \boldsymbol{\kappa}_t\cdot(\mathbf{r}-\mathbf{r}')}
		\left(1 -e^{-i\mathbf{k}\cdot \mathbf{r}\phantom{'}}
		\right)
		\left(1 -e^{i\mathbf{k}\cdot \mathbf{r}'}
		\right)
		K_1(N_1 r)K_1(N_1 r').
	\end{split}
\end{align}
Now, if one assumes that \underline{$x/z$ and $\mu$ have no dependence on $\kappa_t$}, one can integrate over $\boldsymbol{\kappa}_t$ to yield a delta function $(2\pi)^2 \delta^2(\mathbf{r}-\mathbf{r}')$. Notice that, this means that the dipole does not change its size $r$ during the interaction~\cite{Bartels:2002cj}.\\
One then obtains
\begin{align}
	\int \frac{d^2\boldsymbol{\kappa}_t}{2\pi}\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
	&=\int\frac{d^2\mathbf{r}}{2\pi}
	\left |1 -e^{i\mathbf{k}\cdot \mathbf{r}}
	\right|^2
	K_0^2(N_1 r),
	\\
	\int \frac{d^2\boldsymbol{\kappa}_t}{2\pi}\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2&
	=\int\frac{d^2\mathbf{r}}{2\pi}
	\left|1 -e^{i\mathbf{k}\cdot \mathbf{r}}
	\right|^2
	K_1^2(N_1 r).
\end{align}
Inserting the above back to Eqs.~(\ref{eq:angle-unintegratedT})~and~(\ref{eq:angle-unintegratedL}) and using 
\begin{equation}
	\sigma(x/z,r)=\frac{2\pi}{3}\int\frac{d^2\mathbf{k}}{k^2}\alpha(\mu^2)\mathcal{F}(x/z,k^2)\left|1-e^{i \mathbf{k}\cdot\mathbf{r}}\right|^2,
\end{equation}
where \underline{$z$ and $\mu$ are assumed to be independent of $k_t$},
one finally arrives at the dipole factorization formula of Ref.~\cite{Golec-Biernat:1998zce}
\begin{align}
	\begin{split}
		F_{2T}(x,Q^2)=6\sum e^2_f\frac{Q^2}{4\pi^2}\int^1_0 d\beta\int\frac{d^2\mathbf{r}}{(2\pi)^2}
		\sigma(x/z,r)
		&\Theta(1-x/z)\\
		\Big[
		\left[\beta^2+(1-\beta)^2\right]
		K_0^2&(N_1 r)
		+m_f^2
		K_1^2(N_1 r)
		\Big],
	\end{split}\\
	\begin{split}
		F_{2L}(x,Q^2)=6\sum e^2_f\frac{Q^2}{4\pi^2}\int^1_0 d\beta \int\frac{d^2\mathbf{r}}{(2\pi)^2}
		\sigma(x/z,r)
		&\Theta(1-x/z)\\
		\Big[
		4Q^2&\beta^2 (1-\beta)^2
		K_1^2(N_1 r)
		\Big].
	\end{split}
\end{align}
\comment{Factor of $(2\pi)^2$ different from the GBW.}
It is now straightforward to identify that the formula of Ref.~\cite{Golec-Biernat:1998zce} is obtained for the case where $ 1/z\rightarrow\left(1+4 m_f^2/Q^2\right)$.
Comparing with Eq.~(\ref{eq:z}), this is the minimum value of $1/z$ where $k_t={\kappa'}=0,\;\beta=1/2$. This assumption motivates one to introduce massive light quarks to replace non-zero $k_t$ and $\kappa'_2$.
\section*{Acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
%\bibliography{draft}
\printbibliography

%\begin{thebibliography}{10}
%\bibliographystyle{unsrt}

%\input{./draft-references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% !!! DO NOT DELETE !!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\cite{GSL}
%\bibitem{GSL}
%M.~Galassi, J.~Davies, J.~Theiler, B.~Gough, G.~Jungman,
%"GNU Scientific Library - Reference Manual, Third Edition, for GSL Version 1.12 (3. ed.)",
%(2009),
%isbn:~978-0-9546120-7-8
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{thebibliography}
\end{document}

### 2023-04-14 Run-kt/fixa-bjorx/control.h

@@ -1,0 +1,10 @@
+#define MASS_L2 0.0
+#define MASS_S2 0.0
+#define Q2_MAX 650.0
+#define MODEL 0 
+#define PRINT_PROGRESS 1
+#define ALPHA_RUN 0
+#define MODX 0
+#define USE_RESULT 1 
+#define IBP 1
+#define GLUON_APPROX 1

### 2023-04-14 RunWW/GBWS/control.h

@@ -1,0 +1,18 @@
+#define MASS_L2 0.0
+#define MASS_S2 0.0
+#define Q2_MAX 650.0
+#define MODEL 0
+
+#define GLUON_APPROX 1 
+#define N_CHEB_R 100
+#define PRINT_PROGRESS 1
+#define ALPHA_RUN 0
+#define SIGMA_APPROX -1
+#define N_CHEB 30
+#define CHEB_D 1
+
+#define X_MIN 1.0e-8
+#define X_MAX 2.5e-1
+#define KT2_MIN 1.0e-2
+#define WW 1
+#define SUDAKOV 1

### 2023-04-14 RunWW/fixa-bjorx-Sud/control.h

@@ -1,0 +1,19 @@
+#define MASS_L2 0.0
+#define MASS_S2 0.0
+#define Q2_MAX 650.0
+#define MODEL 0
+
+#define GLUON_APPROX 1 
+#define N_CHEB_R 100
+#define PRINT_PROGRESS 1
+#define ALPHA_RUN 0
+#define SIGMA_APPROX -1
+#define N_CHEB 30
+#define CHEB_D 1
+
+#define X_MIN 1.0e-8
+#define X_MAX 2.5e-1
+#define KT2_MIN 1.0e-2
+#define WW 1
+#define SUDAKOV 1
+

### 2023-04-14 RunWW/fixa-bjorx/control.h

@@ -1,0 +1,19 @@
+#define MASS_L2 0.0
+#define MASS_S2 0.0
+#define Q2_MAX 650.0
+#define MODEL 0
+
+#define GLUON_APPROX 1 
+#define N_CHEB_R 100
+#define PRINT_PROGRESS 1
+#define ALPHA_RUN 0
+#define SIGMA_APPROX -1
+#define N_CHEB 30
+#define CHEB_D 1
+
+#define X_MIN 1.0e-8
+#define X_MAX 2.5e-1
+#define KT2_MIN 1.0e-2
+#define WW 1
+#define SUDAKOV 0
+

### 2023-04-14 saturation-ver3/test-gluons.cc

@@ -1,31 +1,0 @@
-#include<iostream>
-#include"gluons.hh"
-
-extern "C" double xgpdf_(const double* x, const double* QQ,const double* A_g, const double* lambda_g );
-
-
-int main(){
-	Collinear_Gluon xg;
-	Chebyshev1D_Collinear_Gluon cxg;
-	cxg.allocate(30);
-	double x,mu2;
-	double val1,val2,val3;
-	const double Ag=1.1,lg=0.08;
-	cxg.init(1,2.0e+8,Ag,lg);
-	for(int j=0;j<50; ++j){
-		x=1.0e-6*pow(1.0e+6,((double)j)/49);
-		cxg.set_x(x);
-	for(int i=0;i<50;++i){	
-		mu2=2*pow(1.0e+8/2,((double)i)/49);
-		val1=xgpdf_(&x,&mu2,&Ag,&lg);
-		val2=xg(x,mu2,Ag,lg);
-		val3=cxg(x,mu2,Ag,lg);
-		if(fabs((val1-val2)/(val1+val2))>1.0e-6||fabs((val1-val3)/(val1+val3))>1.0e-6){
-			printf("FORTRAN=%.2e\tdiff=%.2e,\t%.2e\n",val1,val1-val2,val1-val3);
-		}
-	}
-	}
-		
-		
-	return 0;
-}

### 2023-04-14 saturation-ver3/test-integral.cc

@@ -1,49 +1,0 @@
-#include<iostream>
-#include<fstream>
-#include<vector>
-#include<string>
-#include<cmath>
-#include"./Functions/clenshaw.hh"
-//#define PI 3.14159265358979323846264338327950288419716939937510
-
-int k=100;
-
-class Integrand{
-	public:
-		/*double operator()(double r,void*){
-			return(r*exp(-r));
-		}*/
-		double operator()(double r,void*p){
-			double *i=(double*)p;
-			return(i[1]*cos( r * i[0])+pow(i[1],2)*sin(r*i[0]*2));
-			//return( std::cyl_bessel_j(1,k*r) );
-		}
-			
-};
-
-int main (){
-	Integrand integrand;
-	CCIntegral cc=CCprepare(64,"name",1,5);
-	double par[]={50,1000};
-	double res;
-
-	res =dclenshaw<Integrand,void*>(cc,integrand,(void*)par,0,2*PI,1.0e-14,1.0e-15);
-	printf("1:  %.3e\n",res);
-
-
-	double min=0 ,max=2*PI;
-	double sum=0;
-	double scale=5*(max-min)/par[0];
-	for (int i=0;i<par[0];i++){	
-		max+=scale;
-
-		res =dclenshaw<Integrand,void*>(cc,integrand,(void*)par,min,max,1.0e-14,1.0e-15);
-		printf("2.%d:%.3e \n",i,res);
-		min=max;
-		sum+=res;
-	}
-
-	printf("2: %.3e\n",res);
-	
-	return 0;
-}

### 2023-04-14 saturation-ver3/testkahn.cc

@@ -1,30 +1,0 @@
-#include<iostream>
-#include<cmath>
-#include"./Functions/Kahn.hh"
-
-int main(){
-	int N=7;
-	Kahn sum=Kahn_init(2);
-	//double arr[N]={1.0e+20,1.03e-35,1,-1.0e-25,-1.01e+20,-1,1.0e+18};
-	double arr[N]={1.0e+20,1.03e-35,1,-1.0e-25,-1.0e+20,-1,1.0e-20};
-	for(int i=0;i<N;i++){
-		sum+=arr[i];		
-		Kahn_show(sum);
-	}
-	Kahn_show(sum);
-	std::cout<<"total= "<<Kahn_total(sum)<<std::endl;
-	for(int i=0;i<N;i++){
-		sum+=arr[N-1-i];		
-		Kahn_show(sum);
-	}
-	Kahn_show(sum);
-	std::cout<<"total= "<<Kahn_total(sum)<<std::endl;
-	for(int i=0;i<N;i++){
-		sum+=-arr[i];		
-		Kahn_show(sum);
-	}
-	Kahn_show(sum);
-	std::cout<<"total= "<<Kahn_total(sum)<<std::endl;
-
-	return 0;
-}

### 2023-04-17 saturation-ver3/Functions/dipole-gluon.cc
table updated

@@ -17,8 +17,8 @@ void Gluon_GBW::init(const double *par){
 	#else
 		thresh_power=THRESHOLD;
 	#endif
-	}
-	double Gluon_GBW::operator()(const double  x,const double k2,double mu2){
+}
+double Gluon_GBW::operator()(const double  x,const double k2,double mu2){
 	if(x_0<1.0e-5||x_0>1.0e-3){
 		return 0;
 	}

### 2023-04-18 New parameters for the Golec-Beiernat--Wusthoff and Bartels--Golec-Biernat--Kowlski saturation model in the k_t-facorization formula of F_2/draft.tex
draft

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 \usepackage[english]{babel}
@@
 }	 
-\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_t$-facorization formula of $F_2$}
-
+%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_t$-facorization formula of $F_2$}
+\title{Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models}
 \date{\today}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\comment{To be reduced... rewritten ... }
-%{
-%\color{gray}
-%For decades Deep Inelastic Scattering (DIS) has played major role in the studies of particle physics.
-The structure of a proton is one of the key elements in the particle collider experiments.
-In the collinear factorization, one factorizes the total cross section in to the perturbatively calculable short-distance part and a process-independent long-distance part, called parton distribution functions~(PDFs).
-The energy scale dependence of the PDFs are described by the Dokshitzer--Gribov--Lipatov--Alterelli--Parisi~(DGLAP) evolution equations, which resums the large logarithms.
-While an inclusive process can be described well by the collinear PDFs, one needs transverse momentum dependent PDFs for less inclusive processes.
-The PDFs also denpends on so-called Bjorken scaling variable, $x$.
-While the $Q$ dependence of the PFDs are perturbatively calculable, one generally needs to extract $x$ dependence from experiments.
-In the limit of small-$x$, however, the Balitsky--Fadin--Kuraev--Lipatov (BFKL) equation predicts that, the gluon density rises like $\sim x^{-\lambda}$.
-This rise eventually violates the Froissart bound, which limit the rise of the cross section to be $\sim\log^2(s)$.
-%This  taming of the rise is called saturation.
-The saturation phenomena becomes relevant when the gluon density inside the proton becomes so high that recombination of them can no longer be neglected.
-%There has been much effort trying to understand this effect in both perturbative evolution equations and modeling.
-%On the perturbative calculation side, notably, the  Balistki--Kovchegov~(BK) equation extends the BFKL equation by including a non-linear term to encapsulate the saturation.
-On the modeling side, among others, Golec-Biernat and W\"usthoff (GBW) proposed a simple model, whose key essence is encoded in the $x$ dependent saturation scale, $Q_s(x)$.
-The saturation scale can be thought of as a line which roughly separate the saturation region and the scaling region.
-It is this GBW model, which we are primarily interested in this study.
-%}
 \comment{Bibliography will be properly made once the draft is complete. For only now I use biblatex.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{$k_t$-factorization formula}
+
 \section{Introduction}
@@
 \centering
-\resizebox{0.9\textwidth}{!}{
+\resizebox{0.75\textwidth}{0.25\textwidth}{
 \begin{tikzpicture}
@@
 
-%\filldraw(0.02in,0)--(-0.02in,-0.02in)--(-0.02in,0.02in)--cycle;
-%\filldraw(-0.02in,-0.5in)--(0.02in,-0.52in)--(0.02in, -0.48in)--cycle;
-
 \filldraw(-0.5in,-0.23in)--(-0.52in,-0.27in)--(-0.48in,-0.27in)--cycle;
@@
 
-%\draw(-0.5in , -0.25in)node[left,scale=0.02in]{$x$, $\kappa$};
-%\draw(-0.5in , -0.75in)node[left,scale=0.02in]{$x/z$, $k$};
 \draw[ snake=coil,segment aspect=1.5,segment length=0.1in](0.5in , -1in)--(0.5in,-0.5in);
@@
 \end{figure}
+%Factorization has played central role in QCD, where one expresses a cross section in terms of factors, each depends on a different scale.
+Parton Distribution Functions (PDF) are examples of such objects which appear in factorization.
+The PDFs describe the structure of hadrons, and they are process independent.
+As PDFs are not perturbatively calculable objects, they have to be obtained from experiments.
+%Deeply Inelastic Scattering (DIS) is one of such experiments which can probe the structure of proton.
+Process independence means that the PDFs obtained in DIS can be used in other experiments such as proton-proton collision.
 
@@
 As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
-An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_t^2)$.
+An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_t^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF).
 This appears in the $k_t$-factorization formula, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
-The dipole gluon density is also called unintegrated gluon density since it is related to the collinear (integrated) gluon density by
+The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
 \begin{equation}
@@
 \end{equation}
-%While the behaviour of $\mathcal{F}$ is described by evolution equations such as Balistky--Fadin--Kuraev-Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs}  and Ciafaloni--Catani--Fiorani--Marchesini (CCFM)~\cite{Ciafaloni:1987ur,Catani:1989sg,Catani:1989yc}.
 Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.
@@
 \end{align}
-\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
+%\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
 The dipole cross section is related to the gluon density by the Fourier transform: 
@@
 While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, the derivation of the dipole-factorization formula from the $k_t$-factorization involves with certain simplification and introduction of massive light quarks.
-The main goal of this paper is to investigate the GBW and BGK models in the $k_t$-factorization formula and to understand the dipole-factorization better.
+In the rest of this section, differences of the $k_t$-factorization and the dipole-factorization are outlined.
+In Sec.~\ref{Results}, results of the new fit to HERA data are presented and discussed.
+In Sec.~\ref{Dijet process at EIC}, we apply the results to compute corss section for dijet processes in DIS at Electron-Ion Collider (EIC) and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
 
@@
 \end{align}
-For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize in the form~\cite{Kimber:2001uaa} 
-\begin{align}
-	\begin{split}
-		F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
-		\times\left[
-		\left[\beta^2+(1-\beta)^2\right]
-		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
-		+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
-		\right],&
-		\label{eq:angle-unintegratedT}
-	\end{split}\\
-	\begin{split}
-		F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
-		\times\left[
-		4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
-		\right],&
-		\label{eq:angle-unintegratedL}
-	\end{split}
-\end{align}
+For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
+\begin{multline}
+	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_t^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_t^2)\Theta(1-x/z)\\
+	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
+	+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
+	\label{eq:angle-integrated}
+\end{multline}
 where
 \begin{equation}
-	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2},
+	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
 	\label{eq:z}
 \end{equation}
-and
-\begin{equation}
-	\begin{split}
-		D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2,\\
-		D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
-	\end{split}
-\end{equation}
+(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
+%and
+%\begin{equation}
+%	\begin{split}
+%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
+%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
+%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
+%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
+%	\end{split}
+%\end{equation}
+%for
+%\begin{equation}
+%	\begin{split}
+%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
+%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_t^2,\\
+%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_t^2, &\hspace{2cm}
+%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_t^2.
+%	\end{split}
+%\end{equation}
+Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_t$-factorizaton formula.
+
 If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_t$, 
@@
 \end{equation}
-where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the color dipole with the proton.\\
+where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole with the proton.\\
 
-\comment{does that mean it was wrong to have massive quarks in the photon wave function?}
-%Let us remind ourselves a few points about the dipole-factorization.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\section{Fits of saturation models in momentum space}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-With a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, Eqs.~(\ref{eq:angle-unintegratedT})~and~(\ref{eq:angle-unintegratedL}) can be integrated analytically over the angle $\phi$ to yield~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
-\begin{multline}
-F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_t^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_t^2)\Theta(1-x/z)\\
-\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
-+\left(m_f^2+4Q^2\beta^2(1-\beta)^2\right)\left(\frac{I_3}{2\pi}-\frac{I_4}{2\pi}\right)\right],
-\label{eq:angle-integrated}
-\end{multline}
-where %${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, 
-\begin{equation}
-\begin{split}
-\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
-\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
-\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
-\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
-\end{split}
-\end{equation}
-for
-\begin{equation}
-\begin{split}
-N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
-N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_t^2,\\
-N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_t^2, &\hspace{2cm}
-N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_t^2.
-\end{split}
-\end{equation}
-While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we will follow Ref.~\cite{Kwiecinski:1997ee} and use
-\begin{equation}
-\mu^2=k_t^2+{\kappa'}_t^2+m_f^2.
-\end{equation}
-
-The dipole cross section is used in Eq.~(\ref{eq:angle-integrated}) through Eq.~(\ref{eq:dipole-gluon}).
-In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is a constant for the GBW model, and thus explicitly multiply by a running  coupling;
+The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}).
+In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}) numerically.
+In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
 \begin{equation}
@@
 \end{equation}
-where 0.2 is an arbitrary normalization, and 
+where %0.2 is an arbitrary normalization, and 
 \begin{equation}
@@
 \end{equation}
-where $\Lambda_{\mathrm{QCD}}^2=0.09\;\mathrm{GeV^2}$.
-Nevertheless, the effect of the normalization is absorbed by $\sigma_0$ and hence, bears no importance. \\
-Since the lower limits of the integrations of $k_t$ and ${\kappa'}_t$ are 0, the scale $\mu^2$ has to be frozen.
-We do so by adding $\mu_0^2=4\;\mathrm{GeV^2}$ which seems to give reasonable result, thus making $\mu^2=k_t^2+{\kappa'}_t^2+m_f^2+\mu_0^2$.
-%\comment{something about large $x$ region should be mentoned. Particularly that of BGK.}
-\comment{Unlike in the dipole-factorization formula Eq.~(\ref{eq:dipole-factorization}), the argument of $\mathcal{F}$ is $x/z$, not $x$, therefore, the gluon density enters the region of large-$x$ where the model is not expected to be valid.} Particularly the assumption that the parton density is dominated by gluons is no longer true.
-While one may multiply the gluon density by a factor $(1-x/z)^\alpha$ in order to suppress the threshold region\cite{Timneanu:2001bk}, from a preliminary fit, it was observed that the effect is rather limited and for the case of the BGK model, the fit quality was deteriorated.\comment{Although small power may be possible to improve.
-Also recall, that Sudakov had effect of suppressing large-$x$.}
-We leave the detailed analysis of the threshold region for the future studies. \\
-%, and we will not do anything in particular in this study to modify the large-$x$ region.
+and  $\Lambda_{\mathrm{QCD}}^2=0.09\;\GeV^2$.
+The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
+While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we follow Ref.~\cite{Kwiecinski:1997ee} and use
+\begin{equation}
+	\mu^2=k_t^2+{\kappa'}_t^2+m_f^2+\mu^2_0,
+\end{equation}
+where we add $\mu^2_0=4\;\GeV^2$ in order to freeze the coupling at low scales.
+
 The GBW and BGK models were fitted to the $F_2$ data from HERA~\cite{Abt:2017nkc}.
@@
 %
-\section{Result}
+\section{Results}
+\label{Results}
 %
@@
 It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.).
-Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation.\comment{K.Kutak \& A.
-Stasto} In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.
+Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation.
+In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.
 Since 
@@
 \begin{figure}[t]
-\begin{subfigure}{0.32\textwidth}
+	\centering
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/GBW-dipole.png}
 \end{subfigure}
-\begin{subfigure}{0.32\textwidth}
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/GBW-gluon.png}
 \end{subfigure}
-\begin{subfigure}{0.32\textwidth}
+
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/GBW-saturation.png}
@@
 \begin{figure}[t]
-\begin{subfigure}{0.32\textwidth}
+	\centering
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/BGK-dipole.png}
 \end{subfigure}
-\begin{subfigure}{0.32\textwidth}
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/BGK-gluon.png}
 \end{subfigure}
-\begin{subfigure}{0.32\textwidth}
+
+\begin{subfigure}{0.47\textwidth}
 \includegraphics[width=\textwidth]{./plots/BGK-saturation.png}
@@
 
-\section{Dijet process}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\section{Dijet process at EIC}
+\label{Dijet process at EIC}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}[t]
@@
 In order to investigate less inclusive processes, we will study the electron-dijet correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
-Dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
+The dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
 This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm}.
@@
 The present study is carried out in the framework of the small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
-The ITMD factorization is implemented in the program KATIE~\cite{vanHameren:2016kkz}, which we will use to compute the cross section.
+The ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section.
 Important points of the formalism are the following.
 Firstly, it extends applicability of TMD to the large-$k_t$ region.
-Thus it recovers the $k_t$-factorization if saturation effects are neglected.
-Secondly, it is equivalent to CGC, except for lacking multipartonic interaction~(genuine twist)~\cite{Altinoluk:2019fui}.
+Thus it recovers the $k_t$-factorization if saturation effects are neglected\comment{what does this mean exactly?
+why are we using saturation model?}.
+Secondly, it is equivalent to CGC, where $(Q_s/k_t)^n$ and $(k_t/P_t)^n$ are resummed, except for lacking multipartonic interaction~(genuine twist)~\cite{vanHameren:2016kkz,Altinoluk:2019fui}.
 It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with the above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}.
@@
 As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_t$ region and suppresses in the large-$k_t$ region.
+In other words it broadens the distribution.
 In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more pronounced in the case of the GBW and BGK models.
-The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (also see Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
+The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (\textit{cf.} Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
 
-Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} corresponds to those of Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
-In the top row of Fig.~\ref{fig:je-breit}, we clearly see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits.
+Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} correspond to Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
+In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits.
+However the overall normalization of the gluon density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
 In the middle and the bottom row, it shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by lowering the cross section.
@@
 Here, the difference between KS and GBW and BGK are more prominent.
-Unlike in the previous plots, the new fits in the $k_t$-factorization shows only limited improvement.
+%Unlike in the previous plots, the new fits in the $k_t$-factorization shows only limited improvement.
 The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e.
 The cross sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here, they are significantly increased).
-\comment{probably related to the high $k_t$ region of the gluon density?}\\
+\\
 \comment{regarding this differences between Breit and lab frames, what does "\dots since it (breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}
@@
 	\end{subfigure}
+
 	\begin{subfigure}{0.5\textwidth}
@@
 Again, the GBW and BGK models show considerable deviation from the KS gluon.
-Similarly to the previous plots, the Sudakov factor affects the models differently from the KS in Ref.~\cite{vanHameren:2021sqc}.
+Similarly to the previous plots, the Sudakov factor affects the models differently from the KS gluon in Ref.~\cite{vanHameren:2021sqc}.
 The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
-The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to small $k_t$ of the gluon, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in large-$k_t$ region.
+The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to the small-$k_t$ region of gluon densities, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in the large-$k_t$ region.
+That is to say that the enhancement in the small-$\Delta\phi$ region is a direct consequence of the broadening by the Sudakov factor.
 
 \begin{figure}[p]
-	\begin{subfigure}{0.48\textwidth}
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotGBW1Jets} 
 	\end{subfigure}
-	\begin{subfigure}{0.48\textwidth}
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotBGK1Jets} 
 	\end{subfigure}
-	\begin{subfigure}{0.48\textwidth}
+
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotGBW2Jets}
 	\end{subfigure}
-	\begin{subfigure}{0.48\textwidth}
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotGBW3Jets}
 	\end{subfigure}
-	\begin{subfigure}{0.48\textwidth}
+
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotBGK2Jets}
 	\end{subfigure}
-	\begin{subfigure}{0.48\textwidth}
+	\begin{subfigure}{0.5\textwidth}
 		\includegraphics[width=\textwidth]{plots/plotBGK3Jets}
@@
 It was discussed that massive light quarks used in Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the fit result indicates such effect as expected.
-It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_t$-factorization formula.
+It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_t$-factorization formula well.
 Only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_t$-factorization case.
 It was also observed that the explicit inclusion of the running coupling has significant effect in the fit quality particularly in the large-$Q^2$ region where the GBW model performs poorly.
+We have applied the new result for the prediction of the dijet process in DIS at EIC.
+Additionally, effects of the Sudakov form factor was investigated.
+Results of the $e$-jets correlation in the Breit frame agree qualitatively to that of Ref.~\cite{vanHameren:2021sqc}.
+Other results, namely the $e$-jets in the lab frame and the jet-jet correlation in the Breit frame, show considerable effects of the Sudakov form factor which broaden the gluon density.
 
-\appendix	
-\section{Computation of gluon densities}
-In the evaluation Eq.~(\ref{eq:ww}) the convergence of this integral may be slow due to high oscillation for large $k$.
-For such integration, one can employ a method summarized in Ref.~\cite{LYNESS1985109}. 
-Essentially, the integration is carried out between, anti-nodes of $J_0(rk)$. Then the total integral is written in the form of infinite sum
-\begin{equation}
-	I=\sum^\infty_{i=1} \int^{a_{i+1}}_{a_i} \frac{dr}{r}J_0(r k) \sdpa(x,r),
-\end{equation}
-where we use $a_{i}=\frac{\pi}{k}(i+1/4)$.
-This sum can be accelerated, with series transformation described in Ref.~\cite{doi:10.1080/00207167308803075,Weniger:1989rea,HOMEIER19951}.
-The remarkable power of the Levin's transformation is shown in Tab.~\ref{tab:levin}.
-This trick is also useful in the computation of dipole gluon density.
-
-\begin{table}
-	\begin{center}
-		\begin{tabular}{|c||c|c|}
-			\hline
-			$n$&Levin&Sum\\\hline
-			9&	-5.751e-9&	-0.0004998\\\hline
-			12&	-1.5891e-9&	0.00025567\\\hline
-			15&	-3.803e-11&	-0.00015069\\\hline
-			18&	6.639e-13&	0.00009743\\\hline
-			21&	2.6728e-13&	-0.00006722\\\hline
-			24&	2.6744e-13&	0.00004866\\\hline
-			27&	2.6744e-13&	-0.00003655\\\hline
-		\end{tabular}
-	\end{center}
-	\caption{
-		Computing $\int \frac{dr}{r}J_0(r k)(1-e^{-r^2})$, with $k=10$ adding up to $n$ th term.
-		Levin-accelerated case reaches the true value of $\sim$2.674e-13 far more quickly, and shows superior stability.
-	}
-	\label{tab:levin}
- \end{table}
-
-\section{Derivation of dipole-factorization}
-For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize in the form~\cite{Kimber:2001uaa} 
-\begin{align}
-	\begin{split}
-		F_{2T}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
-		\times\left[
-		\left[\beta^2+(1-\beta)^2\right]
-		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2
-		+m_f^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
-		\right],&
-		\label{eq:angle-unintegratedT}
-	\end{split}\\
-	\begin{split}
-		F_{2L}(x,Q^2)=\sum e^2_f\frac{Q^2}{4\pi}\int\frac{d k_t^2}{k_t^2}\int^1_0 d\beta\int d \kappa_t ^2 \frac{d\phi}{2\pi}\alpha_s(\mu^2)\mathcal{F}(x/z,k^2_t,\mu^2)\Theta(1-x/z)&\\
-		\times\left[
-		4Q^2\beta^2 (1-\beta)^2\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
-		\right],&
-		\label{eq:angle-unintegratedL}
-	\end{split}
-\end{align}
-where
-\begin{equation}
-	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2},
-	\label{eq:z}
-\end{equation}
-and
-\begin{equation}
-	\begin{split}
-		D_1&=\kappa_t^2+\beta(1-\beta)Q^2+m_f^2,\\
-		D_2&=(\boldsymbol{\kappa}_t-\mathbf{k}_t)^2+\beta(1-\beta)Q^2+m_f^2.
-	\end{split}
-\end{equation}
-In the remaining part of this section, let us revisit the derivation of the dipole-factorization formula in Ref.~\cite{Bartels:2002cj}, and show that the difference boils down to replacing $x/z$ with $\tilde{x}\equiv x\left(1+4m_f^2/Q^2\right)$ of Ref.~\cite{Golec-Biernat:1998zce}.
-
-%As demonstrated below, this factorization can be transformed into the position space factorization with a new object, namely, the dipole cross section~\cite{Golec-Biernat:1998zce, Bartels:2002cj}.
-%In short, the formula of Ref.~\cite{Golec-Biernat:1998zce} can essentially be obtained by replacing $x/z$ with $\tilde{x}$ of Ref.~\cite{Golec-Biernat:1998zce} and assuming fixed coupling.\\
-Using the identities \cite{Bartels:2002cj}
-\begin{align}
-	i N_1\int\frac{d^2\mathbf{r}}{2\pi} \left( \frac{\mathbf{r}}{r}\right) e^{i r k \cos\theta}K_1(N_1 r)&=- \frac{\mathbf{k}}{k^2+N_1^2},\\
-	i \int\frac{d^2\mathbf{r}}{2\pi}e^{i r k \cos\theta}K_1(N_1 r)&=- \frac{1}{k^2+N_1^2},
-\end{align}
-one can write
-\begin{align}
-	\begin{split}
-		\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2&\\
-		=\int\frac{d^2\mathbf{r}}{2\pi}&\int\frac{d^2\mathbf{r}'}{2\pi}
-		e^{i \boldsymbol{\kappa}_t\cdot(\mathbf{r}-\mathbf{r}')}
-		\left(1 -e^{-i\mathbf{k}\cdot \mathbf{r}\phantom{'}}
-		\right)
-		\left(1 -e^{i\mathbf{k}\cdot \mathbf{r}'}
-		\right)
-		K_0(N_1 r)K_0(N_1 r'),
-	\end{split}\\
-	\begin{split}
-		\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2&\\
-		=\int\frac{d^2\mathbf{r}}{2\pi}\int\frac{d^2\mathbf{r}'}{2\pi}&
-		\left(\frac{\mathbf{r}\cdot\mathbf{r}'}{r r'}\right)
-		e^{i \boldsymbol{\kappa}_t\cdot(\mathbf{r}-\mathbf{r}')}
-		\left(1 -e^{-i\mathbf{k}\cdot \mathbf{r}\phantom{'}}
-		\right)
-		\left(1 -e^{i\mathbf{k}\cdot \mathbf{r}'}
-		\right)
-		K_1(N_1 r)K_1(N_1 r').
-	\end{split}
-\end{align}
-Now, if one assumes that \underline{$x/z$ and $\mu$ have no dependence on $\kappa_t$}, one can integrate over $\boldsymbol{\kappa}_t$ to yield a delta function $(2\pi)^2 \delta^2(\mathbf{r}-\mathbf{r}')$.
-Notice that, this means that the dipole does not change its size $r$ during the interaction~\cite{Bartels:2002cj}.\\
-One then obtains
-\begin{align}
-	\int \frac{d^2\boldsymbol{\kappa}_t}{2\pi}\left(\frac{1}{D_1}-\frac{1}{D_2}\right)^2
-	&=\int\frac{d^2\mathbf{r}}{2\pi}
-	\left |1 -e^{i\mathbf{k}\cdot \mathbf{r}}
-	\right|^2
-	K_0^2(N_1 r),
-	\\
-	\int \frac{d^2\boldsymbol{\kappa}_t}{2\pi}\left(\frac{\boldsymbol{\kappa}_t}{D_1}-\frac{\boldsymbol{\kappa}_t-\mathbf{k}_t}{D_2}\right)^2&
-	=\int\frac{d^2\mathbf{r}}{2\pi}
-	\left|1 -e^{i\mathbf{k}\cdot \mathbf{r}}
-	\right|^2
-	K_1^2(N_1 r).
-\end{align}
-Inserting the above back to Eqs.~(\ref{eq:angle-unintegratedT})~and~(\ref{eq:angle-unintegratedL}) and using 
-\begin{equation}
-	\sigma(x/z,r)=\frac{2\pi}{3}\int\frac{d^2\mathbf{k}}{k^2}\alpha(\mu^2)\mathcal{F}(x/z,k^2)\left|1-e^{i \mathbf{k}\cdot\mathbf{r}}\right|^2,
-\end{equation}
-where \underline{$z$ and $\mu$ are assumed to be independent of $k_t$},
-one finally arrives at the dipole factorization formula of Ref.~\cite{Golec-Biernat:1998zce}
-\begin{align}
-	\begin{split}
-		F_{2T}(x,Q^2)=6\sum e^2_f\frac{Q^2}{4\pi^2}\int^1_0 d\beta\int\frac{d^2\mathbf{r}}{(2\pi)^2}
-		\sigma(x/z,r)
-		&\Theta(1-x/z)\\
-		\Big[
-		\left[\beta^2+(1-\beta)^2\right]
-		K_0^2&(N_1 r)
-		+m_f^2
-		K_1^2(N_1 r)
-		\Big],
-	\end{split}\\
-	\begin{split}
-		F_{2L}(x,Q^2)=6\sum e^2_f\frac{Q^2}{4\pi^2}\int^1_0 d\beta \int\frac{d^2\mathbf{r}}{(2\pi)^2}
-		\sigma(x/z,r)
-		&\Theta(1-x/z)\\
-		\Big[
-		4Q^2&\beta^2 (1-\beta)^2
-		K_1^2(N_1 r)
-		\Big].
-	\end{split}
-\end{align}
-\comment{Factor of $(2\pi)^2$ different from the GBW.}
-It is now straightforward to identify that the formula of Ref.~\cite{Golec-Biernat:1998zce} is obtained for the case where $ 1/z\rightarrow\left(1+4 m_f^2/Q^2\right)$.
-Comparing with Eq.~(\ref{eq:z}), this is the minimum value of $1/z$ where $k_t={\kappa'}=0,\;\beta=1/2$.
-This assumption motivates one to introduce massive light quarks to replace non-zero $k_t$ and $\kappa'_2$.
-\section*{Acknowledgement}
+\section*{Acknowledment}
 

### 2023-04-20 saturation-ver3/Functions/interpolation-gluon.cc
fit strategy

@@ -23,8 +23,8 @@ void Approx_aF::alloc(int x_npts,int kt2_npts){
 		aF_array=(double*)malloc(x_npts*kt2_npts*sizeof(double));
 		x_accel_ptr = gsl_interp_accel_alloc ();
 		kt2_accel_ptr = gsl_interp_accel_alloc ();
-		//spline_ptr = gsl_spline2d_alloc(gsl_interp2d_bicubic,kt2_npts, x_npts);
-		spline_ptr = gsl_spline2d_alloc(gsl_interp2d_bilinear,kt2_npts, x_npts);
+		spline_ptr = gsl_spline2d_alloc(gsl_interp2d_bicubic,kt2_npts, x_npts);
+		//spline_ptr = gsl_spline2d_alloc(gsl_interp2d_bilinear,kt2_npts, x_npts);
 		alloc_flag=1;
 	}else{
 		printf("Approx_aF cannot allocate\n");

### 2023-04-20 saturation-ver3/Functions/main.cc

@@ -157,7 +157,26 @@ int main(int argc, char** argv){
 		printf("*****************************\n");
 		printf("*** Simplex: eps=%.1e  N_APPROX=%d***\n",(double)INT_PREC,N_APPROX);
 		printf("*****************************\n");
-		min=simplex1(100,pow(10,1-i));
+		//min=simplex1(100,pow(10,1-i));
+		for(int i=0;i<N_PAR-skip;++i){
+			min=simplex1(50,25);
+			simplex1.Fix(i);
+#if MODEL==1
+			for(int j=0;j<N_PAR-skip;++j){
+				if(i==j){
+					continue;
+				}
+				simplex1.Fix(j);
+				min=simplex1(100,pow(10,1-i));
+				std::cout<<"Parameters "<<min.UserState()<<std::endl;
+				simplex1.Release(j);
+			}
+#endif
+			min=simplex1(50,25);
+			std::cout<<"Parameters "<<min.UserState()<<std::endl;
+			simplex1.Release(i);
+		}
+		min=simplex1(50,25);
 		INT_PREC/=2;
 		N_APPROX=(int)(N_APPROX*2);
 		save_res(((std::string)argv[1])+"/result.txt",&min,&theFCN,N_PAR-skip);
@@ -167,41 +186,39 @@ int main(int argc, char** argv){
 	INT_PREC=2.5e-4;
 	N_APPROX=(2*N_CHEB_R)/3;
 	//prec.SetPrecision(INT_PREC);
-	
 	printf("***************************\n");
 	printf("*** First: eps=%.1e  N_APROX=%d***\n",(double)INT_PREC,N_APPROX);
 	printf("***************************\n");
-	
-	{	
-	  ROOT::Minuit2::MnMigrad migrad(theFCN,min.UserParameters(),0);
-	  for(int i=0;i<(N_PAR-skip);i++ ){
+{	
+	ROOT::Minuit2::MnMigrad migrad(theFCN,min.UserParameters(),0);
+	for(int i=0;i<(N_PAR-skip);i++ ){
 		migrad.RemoveLimits(i);
-	  }
-#if MODEL==1
+	}
+	min=migrad(20,25);
+}
+	std::cout<<"Parameters "<<min.UserState()<<std::endl;
+	goal=25;
+	for(int k=0;k<5;k++){
+		ROOT::Minuit2::MnMigrad migrad(theFCN,min.UserParameters(),0);
 		for(int i=0;i<N_PAR-skip;++i){
 			migrad.Fix(i);
[…]

### 2023-04-20 Paper/draft.tex

--- 2023-04-18 New parameters for the Golec-Beiernat--Wusthoff and Bartels--Golec-Biernat--Kowlski saturation model in the k_t-facorization formula of F_2/draft.tex
@@
 %\usepackage{draftwatermark}
-\usepackage[backend=bibtex, style=ieee]{biblatex}
+\usepackage[backend=biber, style=ieee]{biblatex}
 
@@
 }	 
-%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_t$-facorization formula of $F_2$}
+%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_T$-facorization formula of $F_2$}
 \title{Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models}
@@
 \begin{abstract}
-
+  We investigate effects of exact gluon kinematics on the parameters of the Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models.
+The resulting parameters show sizable difference, particularly in the normalization $\sigma_0$.
+The resulting models are applied for the dijet process in DIS to investigate effects of the Sudakov form factor.
+  The result qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming from the large-$k_T$ behaviour of the models.
 \end{abstract}
@@
 As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
-An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_t^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF).
-This appears in the $k_t$-factorization formula, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
+An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}.
+This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
 The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
 \begin{equation}
-xg(x,Q^2)=\int^{Q^2}_0 dk_t^2 \mathcal{F}(x,k^2_t).
+xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
 \end{equation}
 Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.
-However, such rise violates the Froissart bound~\cite{Kovchegov:2012mbw}.
+However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}.
 The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
@@
 Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.
-A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}.
-The model was originally proposed in the position space version of the $k_t$-factorization formula, and the object which corresponds to the gluon density of the $k_t$-factorization is called dipole cross section.
+A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}~(also \cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}).
+The model was originally proposed in the position space version of the $k_T$-factorization formula, and the object which corresponds to the gluon density of the $k_T$-factorization is called dipole cross section.
 In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
 \begin{align}
-\sigma_{\mathrm{dipole}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
+\sigma_{\mathrm{GBW}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
 &R^{-2}_0&=\frac{Q_0^{2}}{4}\left(\frac{x_0}{x}\right)^\lambda.
@@
 \begin{equation}
-\alpha_s\mathcal{F}(x,k_t^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
+\alpha_s\mathcal{F}(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
 \label{eq:dipole-gluon}
@@
 thus improving the description of data at higher $Q^2$.\\
-While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, the derivation of the dipole-factorization formula from the $k_t$-factorization involves with certain simplification and introduction of massive light quarks.
-In the rest of this section, differences of the $k_t$-factorization and the dipole-factorization are outlined.
-In Sec.~\ref{Results}, results of the new fit to HERA data are presented and discussed.
-In Sec.~\ref{Dijet process at EIC}, we apply the results to compute corss section for dijet processes in DIS at Electron-Ion Collider (EIC) and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
+While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, derivation of the dipole-factorization formula from the $k_T$-factorization involves with certain simplification and introduction of massive light quarks.
+In the rest of this section, differences of the $k_T$-factorization and the dipole-factorization are outlined.
+In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed.
+In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at Electron-Ion Collider (EIC) and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
 
@@
 \begin{align}
-    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_t.
+    \kappa&=\alpha p-\beta q'+\kappa_t&&\mathrm{and}& k&=a p- bq'+k_T.
 \end{align}
@@
 \begin{multline}
-	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_t^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_t^2)\Theta(1-x/z)\\
+	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
 	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
@@
 %		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
-%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_t^2,\\
-%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_t^2, &\hspace{2cm}
-%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_t^2.
+%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
+%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
+%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
 %	\end{split}
 %\end{equation}
-Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_t$-factorizaton formula.
+%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
 
-If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_t$, 
+If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
 the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce} (i.e. dipole-factorizaton formula)
@@
 \end{equation}
-where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole with the proton.\\
+where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\
 
 The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}).
-In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}) numerically.
+In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
 In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
 \begin{equation}
-\alpha_s(\mu^2)\mathcal{F}(x,k_t^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_t^2)}{0.2},
+\alpha_s(\mu^2)\mathcal{F}(x,k_T^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_T^2)}{0.2},
 \end{equation}
@@
 The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
+(For a more detailed analysis of UGD from the BGK model see.
+Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
+Their treatment is also different from the original BGK paper~\cite{Bartels:2002cj}.
+As a consequence their gluon density is positive in the large $k_T$-region and the overall large-$k_T$ behaviour is significantly different.}
+)
 While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we follow Ref.~\cite{Kwiecinski:1997ee} and use
 \begin{equation}
-	\mu^2=k_t^2+{\kappa'}_t^2+m_f^2+\mu^2_0,
+	\mu^2=k_T^2+{\kappa'}_t^2+m_f^2+\mu^2_0,
 \end{equation}
@@
 \begin{itemize}
-\item GBW model with the fixed coupling in $k_t$-factorization  ($k_t$-GBW),
-\item GBW model with the running coupling in $k_t$-factorization (rc-$k_t$-GBW),
-\item BGK model in $k_t$-factorization ($k_t$-BGK),
+\item GBW model with the fixed coupling in $k_T$-factorization  ($k_T$-GBW),
+\item GBW model with the running coupling in $k_T$-factorization (rc-$k_T$-GBW),
+\item BGK model in $k_T$-factorization ($k_T$-BGK),
 \end{itemize} 
@@
 The results of fits are summarized in Tab.~\ref{tab:table}. 
-The fit quality of $k_t$-GBW is almost unchanged from $r$-GBW, while rc-$k_t$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
+The fit quality of $k_T$-GBW is almost unchanged from $r$-GBW, while rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
 It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
-\comment{What is the connection?
+% \comment{What is the connection?
 Their result regarding the 1/x grad of $Q_s$ becoming smaller is clearly not present in our case.
@@
 ) }
-Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_t$-GBW are almost identical to those of $r$-GBW.
+Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW.
 This can be seen also in Fig.~\ref{fig:GBW}.
@@
 Let us analyze the difference in $\sigma_0$. 
-Recalling that the difference between the $k_t$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$.
+Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$.
 It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.).
@@
 \begin{equation}
-\left(1+\frac{4 m_f^2}{Q^2}\right)\leq\left(1+\frac{k_t^2}{Q^2}+\frac{{\kappa'}_t^2+m_f^2}{\beta(1-\beta)Q^2}\right),
+\left(1+\frac{4 m_f^2}{Q^2}\right)\leq\left(1+\frac{k_T^2}{Q^2}+\frac{{\kappa'}_t^2+m_f^2}{\beta(1-\beta)Q^2}\right),
 \end{equation}
-the $k_t$-factorization case receives more suppression.
+the $k_T$-factorization case receives more suppression.
 Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression.
 Thus, one would expect that the massive light quarks partially simulate the effect of $x/z$.
-It is therefore, interesting to see that the parameters of $k_t$-GBW, are closer to those of $r$-GBW-massive than to the parameters of $r$-GBW.    
-However, it seems that there is a compensating factor in rc-$k_t$-GBW. 
+It is therefore, interesting to see that the parameters of $k_T$-GBW, are closer to those of $r$-GBW-massive than to the parameters of $r$-GBW.    
+However, it seems that there is a compensating factor in rc-$k_T$-GBW. 
 The compensating effect can be understood as follows.
-As it is visible in  Fig.~\ref{fig:GBW}, larger $x_0$ enhances the small-$r$ region which corresponds roughly to the large-$k_t$ of the dipole gluon density which also is visible.
-As the running coupling depends on $k_t^2$,  one can expect that the large-$k_t$ region gets suppressed.
+As it is visible in  Fig.~\ref{fig:GBW}, larger $x_0$ enhances the small-$r$ region which corresponds roughly to the large-$k_T$ of the dipole gluon density which also is visible.
+As the running coupling depends on $k_T^2$,  one can expect that the large-$k_T$ region gets suppressed.
 Therefore, one can conclude that the change in $x_0$ is a direct consequence of the running coupling.\\
@@
 The difference is more prominent in the small-$x$ region (Fig.~\ref{fig:BGK}), particularly noticeable in the second peak of the gluon density.
-The change is cleanly visible in the saturation scale of Fig.~\ref{fig:BGK}. \comment{Is there anything more to be said?}
+The change is cleanly visible in the saturation scale of Fig.~\ref{fig:BGK}. 
 The resulting $F_2$ of respective models are shown in Figs.~\ref{fig:GBW-Grid}~and~\ref{fig:BGK-Grid}.
-While the $r$-GBW and $k_t$-GBW show little difference, rc-$k_t$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
+While the $r$-GBW and $k_T$-GBW show little difference, rc-$k_T$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
 As for the BGK model, the difference is too small to be seen in the top plots.
@@
 While the small-$Q^2$ region is somewhat improved, as a whole, the changes cancel out.
-
-\comment{notice the $x$-slope of $F_2$ in small-$Q^2$ is affected. Recalling that in $r$-formula that region was controlled by the mass of light-quarks. }
-\comment{Also, running GBW is showing somewhat similar pattern with the Sudakov improvement.}
 
@@
 \end{subtable}
-\caption{Fit parameters of respective models. The parameters of the dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}.
-\comment{$\sigma_0\sim30$ is somewhat closer to the fit result of rcBK 1012.}
-}
+\caption{Fit parameters of respective models. The parameters of the dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}}.
 \label{tab:table}
@@
 Note, the dipole cross section and the gluon density are normalized by $\sigma_0^{-1}$.
-\comment{The plots do not contain running coupling as the scale depends on $\kappa$ and $m_f$ etc. thus this should be thought of as normalized $\mathcal{F}$, rather than $\alpha\mathcal{F}$.}}
+%\comment{The plots do not contain running coupling as the scale depends on $\kappa$ and $m_f$ etc. thus this should be thought of as normalized $\mathcal{F}$, rather than $\alpha\mathcal{F}$.}
+}
 \label{fig:GBW}
@@
 \caption{Comparison of GBW $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame.
- Improvement by the running coupling ($k_t$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_t$) shows only marginal improvement .  }
+ Improvement by the running coupling ($k_T$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_T$) shows only marginal improvement .  }
 \label{fig:GBW-Grid}
@@
 While the overall fit quality remain similar, the fit quality in each frame change noticeably.
-Particularly the $k_t$-formula case ($k_t$) shows better fit in the small-$Q^2$ region.}
+Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
 \label{fig:BGK-Grid}
@@
     \caption{\footnotesize Weizs\"acker-Williams gluon density at $x=10^{-3}$.
-Top row: comparison of the dipole-factorization fit and $k_t$-factorization fit results.
+Top row: comparison of the dipole-factorization fit and $k_T$-factorization fit results.
 Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.
@@
 \end{figure}
-In order to investigate less inclusive processes, we will study the electron-dijet correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
+In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
 The dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
-This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm}.
+This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm,Dominguez:2011wm}.
 Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
@@
 \end{equation}
-Resummation of the Sudakov logarithms is achieved by the formula~\cite{Xiao:2017yya}
+Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2013wwa,Xiao:2017yya}
 \begin{equation}
@@
 
-The present study is carried out in the framework of the small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
-The ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section.
-Important points of the formalism are the following.
-Firstly, it extends applicability of TMD to the large-$k_t$ region.
-Thus it recovers the $k_t$-factorization if saturation effects are neglected\comment{what does this mean exactly?
-why are we using saturation model?}.
-Secondly, it is equivalent to CGC, where $(Q_s/k_t)^n$ and $(k_t/P_t)^n$ are resummed, except for lacking multipartonic interaction~(genuine twist)~\cite{vanHameren:2016kkz,Altinoluk:2019fui}.
-It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with the above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}.
+The present study is carried out in the framework of small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
+ITMD is an generalization of TMD where the momentum imbalance is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$, where $P_t\sim p_{1T},p_{2T}$ of jets~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
+
+%It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with the above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}.
 )  Also it was mentioned the cut on $p_T$ is selected for this.
@@
 Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of jets and the final state electron in DIS ($e+p\rightarrow e+J_1+J_2+X$), where it was argued that this observable is sensitive to the soft emissions and the saturation effects.
+However, in this study, we will not test the saturation effect, and focus only on the proton case.
 The kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
@@
 Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
-The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc}.
+The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr}.
 Clearly, the GBW and BGK models falls much more quickly than the KS gluon density.
-In general, expected behaviour in the large-$k_t$ region is $\sim k_t^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while GBW behaves like $\sim e^{-k_t^2}$.
-As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_t$ region and suppresses in the large-$k_t$ region.
-In other words it broadens the distribution.
-In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov is significantly more pronounced in the case of the GBW and BGK models.
+In general, expected behaviour in the large-$k_T$ region is $\sim k_T^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while $\sigma_{\mathrm{GBW}}$ behaves like $\sim e^{-k_T^2}$.
+As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_T$ region and suppresses in the large-$k_T$ region.
+In other words, it broadens the distribution.
+In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov factor is significantly more pronounced in the case of the GBW and BGK models.
 The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (\textit{cf.} Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
@@
 Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} correspond to Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
-In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_t$-factorization fits.
+In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_T$-factorization fits.
 However the overall normalization of the gluon density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
+Nevertheless, it shows clearly the effect of the parameter $\sigma_0$.
 In the middle and the bottom row, it shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by lowering the cross section.
@@
 Here, the difference between KS and GBW and BGK are more prominent.
-%Unlike in the previous plots, the new fits in the $k_t$-factorization shows only limited improvement.
+%Unlike in the previous plots, the new fits in the $k_T$-factorization shows only limited improvement.
 The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e.
@@
 \\
-\comment{regarding this differences between Breit and lab frames, what does "\dots since it (breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}
+%\comment{regarding this differences between Breit and lab frames, what does "\dots since it (Breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}
 
@@
 	\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the Breit frame.
-Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
@@
 \caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the lab frame.
-Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
@@
 
-Finally, Fig.~\ref{fig:jj-breit} shows the jet correlations in the Breit frame.
+Finally, Fig.~\ref{fig:jj-breit} shows the jet-jet correlations in the Breit frame.
 Again, the GBW and BGK models show considerable deviation from the KS gluon.
@@
 The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
-The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to the small-$k_t$ region of gluon densities, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in the large-$k_t$ region.
+The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to the small-$k_T$ region of gluon densities, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in the large-$k_T$ region.
 That is to say that the enhancement in the small-$\Delta\phi$ region is a direct consequence of the broadening by the Sudakov factor.
@@
 \caption{\footnotesize Azimuthal correlation of the jets in the Breit frame.
-Top: Comparison of dipole-factorization fit and $k_t$-factorization fit.
+Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
@@
 \section{Summary}
-We have fitted the Golec-Biernat--W\"usthoff~(GBW)\cite{Golec-Biernat:1998zce} and Bartels--Golec-Biernat--Kowalski~(BGK)~\cite{Bartels:2002cj} models to the HERA data~\cite{Abt:2017nkc} in the context of the $k_t$-factorization of $F_2$.
-The main difference between the $k_t$- and dipole-factorizations is an argument of the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the dipole-factorization.
+We have fitted the Golec-Biernat--W\"usthoff~(GBW)\cite{Golec-Biernat:1998zce} and Bartels--Golec-Biernat--Kowalski~(BGK)~\cite{Bartels:2002cj} models to HERA data~\cite{Abt:2017nkc} in the context of the $k_T$-factorization of $F_2$.
+The main difference between the $k_T$- and dipole-factorizations is an argument of the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the dipole-factorization.
 It was discussed that massive light quarks used in Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the fit result indicates such effect as expected.
-It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_t$-factorization formula well.
-Only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_t$-factorization case.
+It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_T$-factorization formula well.
+Only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_T$-factorization case.
 It was also observed that the explicit inclusion of the running coupling has significant effect in the fit quality particularly in the large-$Q^2$ region where the GBW model performs poorly.
 We have applied the new result for the prediction of the dijet process in DIS at EIC.
-Additionally, effects of the Sudakov form factor was investigated.
+Additionally, effects of the Sudakov form factor were investigated.
 Results of the $e$-jets correlation in the Breit frame agree qualitatively to that of Ref.~\cite{vanHameren:2021sqc}.
@@
 
-\section*{Acknowledment}
+\section*{Acknowledgment}
 

### 2023-04-20 saturation-ver3/Functions/dipole-gluon.cc
paper

@@ -64,7 +64,6 @@ void Dipole_Gluon::set_x(const double &x){
 }
 
 double Dipole_Gluon::operator()(const double x,const double kt2,const double mu2){
-	
 	Kahn accum=Kahn_init(3);
 	const std::vector<double> par{kt2,x,mu2};
 	double rmax=R_MAX,rmin=R_MIN;
@@ -81,11 +80,7 @@ double Dipole_Gluon::operator()(const double x,const double kt2,const double mu2
 		sectors=SECTOR_MAX;
 	}
 
-	//#if IBP==1&&WW!=1
-	//double imax=3*PI/(sqrt(kt2)*4); //forJ1 integral, this is efficient
-	//#else
 	double imax=PI/(sqrt(kt2)*4); //forJ0 integral, this is efficient
-	//#endif						      
 				  
 	int flag=0,pass=5,accel_len=6,accel_min=3;
 	//flag=0 untested
@@ -108,11 +103,7 @@ double Dipole_Gluon::operator()(const double x,const double kt2,const double mu2
 			}
 		};
 		
-	#if R_CHANGE_VAR==1
-		val=dclenshaw<INTEG ,const std::vector<double>&>(cc,*integrand,par,imin/(1+imin),imax/(1+imax),pow(INT_PREC,2),10e-14);
-	#elif R_CHANGE_VAR==0
 		val=dclenshaw<INTEG ,const std::vector<double>&>(cc,*integrand,par,imin,imax,pow(INT_PREC,2),10e-14);
-	#endif
 		
 		imin=imax;
 		if(val==0.0||sum+val==sum){
@@ -156,7 +147,7 @@ double Dipole_Gluon::operator()(const double x,const double kt2,const double mu2
 		val1=lev.accel(sectors-accel_len,accel_len);
 		val2=lev.accel(sectors-1-accel_len,accel_len);
 		if(fabs(2*(val1-val2)/(val1+val2))>INT_PREC/2&&fabs(val2-val1)>2*pow(INT_PREC/5,2) ){
-			printf("3: sum=%.3e \t lev=%.1e %.1e\t diff= %.2e\t %d rmax= %.1e x=%.1e kt2=%.1e last term=%.1e, INT_PREC=%.1e\n",
[…]

### 2023-04-20 Paper/draft.tex

@@
 The phenomenon described by this nonlinear term is called saturation.
+The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
 Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.
@@
 In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed.
-In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at Electron-Ion Collider (EIC) and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
+In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
 
@@
 Additionally, let us introduce $q'\equiv q+x p$. 
-Then one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
+Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
 \begin{align}
@@
 %Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
-
+One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
 If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
-the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce} (i.e. dipole-factorizaton formula)
+the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
 \begin{equation}
@@
 \end{equation}
-where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes a splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\
+where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\
 

### 2023-04-21 dijet/plot1.sh
plots seem ok

@@ -1,0 +1,16 @@
+#! /usr/bin/env bash
+
+for i in GBW GBWr GBWS GBWSr BGK  BGKr BGKS BGKSr KS
+do
+	rm ${i} -r
+	./run.sh prepare input${i} ${i}
+done
+for i in GBW GBWr GBWS GBWSr BGK  BGKr BGKS BGKSr KS
+do
+	cd ${i}
+	./optimize.sh
+	cd ..
+done
+
+
+

### 2023-04-21 Paper/draft.tex
plots seem ok
plots to be re-done

@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
+\usepackage[a4paper,left=0.99in, right=0.99in,top=1.2in, bottom=1.2in]{geometry}
+
 \usepackage[english]{babel}
 \usepackage[a4paper]{geometry}
+\usepackage{multicol}
 \usepackage{graphicx}
@@
 \usepackage{hyperref}
+\usepackage{cite}
 %\usepackage{times}
@@
 %\usepackage{draftwatermark}
-\usepackage[backend=biber, style=ieee]{biblatex}
+%\usepackage[backend=biber, style=ieee]{biblatex}
 
-\addbibresource{draft.bib}
+%\addbibresource{draft.bib}
 
@@
 {\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\%\,\\
-%$^2$ 
-%{\small\it Physics Department, Brookhaven National Laboratory,}\\
-%{\small\it Upton, NY 11973, USA}\\
 }	 
@@
 \begin{flushright}
-%  IFJPAN-IV-2022-16\\
+  IFJPAN-IV-2023-XX\\
 \end{flushright}
 \vspace{20em}
-%-----------------------------------------------------------------
+%------------------------------------------------------
 
 \begin{abstract}
-  We investigate effects of exact gluon kinematics on the parameters of the Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models.
-The resulting parameters show sizable difference, particularly in the normalization $\sigma_0$.
-The resulting models are applied for the dijet process in DIS to investigate effects of the Sudakov form factor.
-  The result qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming from the large-$k_T$ behaviour of the models.
+We investigate effects of exact gluon kinematics on the parameters of the
+Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models. The
+resulting parameters show sizable difference, particularly in the normalization
+$\sigma_0$. The resulting models are applied for the dijet process in DIS to
+investigate effects of the Sudakov form factor.  The result qualitatively agrees
+with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming
+from the large-$k_T$ behaviour of the models.
 \end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{Introduction}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\comment{Bibliography will be properly made once the draft is complete. For only now I use biblatex.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}[t]
 \centering
-\resizebox{0.75\textwidth}{0.25\textwidth}{
+\resizebox{0.6\textwidth}{0.2\textwidth}{
 \begin{tikzpicture}
@@
   \end{tikzpicture}
+  \hspace{60pt}
   \begin{tikzpicture}
@@
 
-In the small-$x$ region of DIS, interactions are dominated by gluons\cite{Kovchegov:2012mbw}.
+In the small-$x$ region of deep intelastic scattering (DIS) process   
+%
+\begin{equation}
+  %\label{eq:}
+  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
+\end{equation}
+%
+where are $p$ and $q$ are, respectively, the momenta of the photon and the
+proton, the interactions are dominated by gluons\cite{Kovchegov:2012mbw}.
 As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
@@
 Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.
+
+\comment{Some more general talk like in the previous paper}
+
+\comment{EIC}
+
+In the next section, differences of the $k_T$-factorization and the dipole-factorization are outlined.
+In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed.
+In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The framework}
+
 A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}~(also \cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}).
@@
 While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, derivation of the dipole-factorization formula from the $k_T$-factorization involves with certain simplification and introduction of massive light quarks.
-In the rest of this section, differences of the $k_T$-factorization and the dipole-factorization are outlined.
-In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed.
-In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
 
-Let us consider the inclusive DIS process $e p\rightarrow \gamma^* (q) p(p)\rightarrow X$. %where a proton and a photon interact, and their momenta are $p$ and $q$ respectively.
 Additionally, let us introduce $q'\equiv q+x p$. 
@@
 In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
+%
 \begin{equation}
@@
 where %0.2 is an arbitrary normalization, and 
+%
+\comment{Question: alphas=0.2}
+
 \begin{equation}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Fits to $F_2$ data}
+\label{Results}
+
 The GBW and BGK models were fitted to the $F_2$ data from HERA~\cite{Abt:2017nkc}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\section{Results}
-\label{Results}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The fit was performed for the following cases
+The fits were performed for the following cases
 \begin{itemize}
@@
 
+%-----------------------------------------------------------------------------
+\begin{table}[t]
+\begin{subtable}{\textwidth}
+\center\footnotesize
+\input{GBW-parameters.tex}
+%\caption{}
+\vspace{2mm}
+\end{subtable}
+\begin{subtable}{\textwidth}
+\center\footnotesize
+\input{BGK-parameters.tex}
+%\caption{}
+\vspace{2mm}
+\end{subtable}
+\caption{Fit parameters of respective models. The parameters of the
+dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}.}
+\label{tab:table}
+\end{table}
+%-----------------------------------------------------------------------------
+
 The results of fits are summarized in Tab.~\ref{tab:table}. 
-The fit quality of $k_T$-GBW is almost unchanged from $r$-GBW, while rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
+The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
 It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
@@
 Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW. 
-This can be seen also in Fig.~\ref{fig:GBW}.
-\\
+\comment{Describet what's in the figuers...}
+
+\begin{figure}[p]
+  \begin{multicols}{2}
+    \includegraphics[width=0.47\textwidth]{./plots/GBW-dipole.png}
+    \includegraphics[width=0.47\textwidth]{./plots/GBW-gluon.png}
+    \includegraphics[width=0.47\textwidth]{./plots/GBW-saturation.png}\par
+    \includegraphics[width=0.47\textwidth]{./plots/BGK-dipole.png}
+    \includegraphics[width=0.47\textwidth]{./plots/BGK-gluon.png}
+    \includegraphics[width=0.47\textwidth]{./plots/BGK-saturation.png}
+  \end{multicols}
+  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},
+  10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
+  models Note, the dipole cross section and the gluon density are normalized by
+  $\sigma_0^{-1}$. \comment{Larger y and x labels}} 
+\end{figure}
+
+\begin{figure}[p]
+%\begin{subfigure}{\textwidth}
+\includegraphics[width=0.49\textwidth]{./plots/Figure_1.png}
+\includegraphics[width=0.49\textwidth]{./plots/Figure_2.png}
+\includegraphics[width=\textwidth]{./plots/Figure_3.png}
+%\end{subfigure}
+\caption{Comparison of GBW $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame.
+ Improvement by the running coupling ($k_T$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_T$) shows only marginal improvement .  }
+\label{fig:GBW-Grid}
+\end{figure}
+
+\begin{figure}[p]
+%\begin{subfigure}{\textwidth}
+\includegraphics[width=0.49\textwidth]{./plots/Figure_2-1.png}
+\includegraphics[width=0.49\textwidth]{./plots/Figure_2-2.png}
+\includegraphics[width=\textwidth]{./plots/Figure_2-3.png}
+%\end{subfigure}
+\caption{Comparison of BGK $F_2$ with HERA data.
+The histogram shows the $\chi^2$ value per data point in each frame.
+While the overall fit quality remain similar, the fit quality in each frame change noticeably.
+Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
+\label{fig:BGK-Grid}
+\end{figure}
+
 Let us analyze the difference in $\sigma_0$. 
@@
 Since 
+%
 \begin{equation}
@@
 \end{equation}
+%
 the $k_T$-factorization case receives more suppression.
@@
 The resulting $F_2$ of respective models are shown in Figs.~\ref{fig:GBW-Grid}~and~\ref{fig:BGK-Grid}.
+
 While the $r$-GBW and $k_T$-GBW show little difference, rc-$k_T$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
@@
 While the small-$Q^2$ region is somewhat improved, as a whole, the changes cancel out.
-
-\begin{table}[t]
-\begin{subtable}{\textwidth}
-\center\footnotesize
-\input{GBW-parameters.tex}
-%\caption{}
-\vspace{2mm}
-\end{subtable}
-\begin{subtable}{\textwidth}
-\center\footnotesize
-\input{BGK-parameters.tex}
-%\caption{}
-\vspace{2mm}
-\end{subtable}
-\caption{Fit parameters of respective models. The parameters of the dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}}.
-\label{tab:table}
-\end{table}
-
-\begin{figure}[t]
-	\centering
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/GBW-dipole.png}
-\end{subfigure}
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/GBW-gluon.png}
-\end{subfigure}
-
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/GBW-saturation.png}
-\end{subfigure}
-\caption{The dipole cross section and the dipole gluon density at
-$x=10^{-2}, 10^{-6}$, and the saturation scale. 
-Note, the dipole cross section and the gluon density are normalized by $\sigma_0^{-1}$.
-%\comment{The plots do not contain running coupling as the scale depends on $\kappa$ and $m_f$ etc. thus this should be thought of as normalized $\mathcal{F}$, rather than $\alpha\mathcal{F}$.}
-}
-\label{fig:GBW}
-\end{figure}
-
-\begin{figure}[t]
-	\centering
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/BGK-dipole.png}
-\end{subfigure}
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/BGK-gluon.png}
-\end{subfigure}
-
-\begin{subfigure}{0.47\textwidth}
-\includegraphics[width=\textwidth]{./plots/BGK-saturation.png}
-\end{subfigure}
-\caption{The dipole cross section and the dipole gluon density at
-$x=10^{-2}, 10^{-6}$, and the saturaton scale. 
-Note, the dipole cross section and the gluon density are normalized by $\sigma_0^{-1}$}
-\label{fig:BGK}
-\end{figure}
-
-\begin{figure}[p]
-%\begin{subfigure}{\textwidth}
-\includegraphics[width=0.49\textwidth]{./plots/Figure_1.png}
-\includegraphics[width=0.49\textwidth]{./plots/Figure_2.png}
-\includegraphics[width=\textwidth]{./plots/Figure_3.png}
-\vspace{2mm}
-%\end{subfigure}
-\caption{Comparison of GBW $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame.
- Improvement by the running coupling ($k_T$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_T$) shows only marginal improvement .  }
-\label{fig:GBW-Grid}
-\end{figure}
-\begin{figure}[p]
-%\begin{subfigure}{\textwidth}
-\includegraphics[width=0.49\textwidth]{./plots/Figure_2-1.png}
-\includegraphics[width=0.49\textwidth]{./plots/Figure_2-2.png}
-\includegraphics[width=\textwidth]{./plots/Figure_2-3.png}
-%\end{subfigure}
-\caption{Comparison of BGK $F_2$ with HERA data.
-The histogram shows the $\chi^2$ value per data point in each frame.
-While the overall fit quality remain similar, the fit quality in each frame change noticeably.
-Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
-\label{fig:BGK-Grid}
-\end{figure}
 
@@
 \end{figure}
+
 In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}.
+
+\comment{process}
+
+\comment{factorization formula for dijets in DIS involving WW gluon}
+
+\comment{mention why Sudakov is important for dijet production}
+
 The dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
@@
 
+\comment{Question: normalization}
 Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
@@
 
+\comment{Question: rcBK}
+
+\comment{Question: what about pieces of derivation removed from the main part?}
+
 \section{Summary}
-We have fitted the Golec-Biernat--W\"usthoff~(GBW)\cite{Golec-Biernat:1998zce} and Bartels--Golec-Biernat--Kowalski~(BGK)~\cite{Bartels:2002cj} models to HERA data~\cite{Abt:2017nkc} in the context of the $k_T$-factorization of $F_2$.
-The main difference between the $k_T$- and dipole-factorizations is an argument of the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the dipole-factorization.
-It was discussed that massive light quarks used in Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the fit result indicates such effect as expected.
-It is quite remarkable that with such simplicity, the dipole-factorization can reproduce the result of the $k_T$-factorization formula well.
-Only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_T$-factorization case.
+We have fitted the GBW\cite{Golec-Biernat:1998zce}
+and BGK~\cite{Bartels:2002cj} models to HERA
+data~\cite{Abt:2017nkc} in the context of the $k_T$-factorization of $F_2$.  The
+main difference between the $k_T$- and dipole-factorizations is an argument of
+the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the
+dipole-factorization. It was discussed that massive light quarks used in
+Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the
+fit result indicates such effect as expected. It is quite remarkable that with
+such simplicity, the dipole-factorization can reproduce the result of the
+$k_T$-factorization formula well.
+The only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_T$-factorization case.
 It was also observed that the explicit inclusion of the running coupling has significant effect in the fit quality particularly in the large-$Q^2$ region where the GBW model performs poorly.
+
 We have applied the new result for the prediction of the dijet process in DIS at EIC.
@@
 \section*{Acknowledgment}
+\comment{Add what we had in the previous paper}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-%\bibliography{draft}
-\printbibliography
+%\clearpage
+%\printbibliography
+
+\newpage
+\bibliographystyle{unsrt}
+\bibliography{draft}
 
 %\begin{thebibliography}{10}
+%\bibliography{draft}
 %\bibliographystyle{unsrt}

### 2023-04-21 saturation-ver3/Functions/plot/plot-sigma.cc
plots

@@ -1,0 +1,110 @@
+#include<iostream>
+#include<fstream>
+#include<cuba.h>
+#include<cmath>
+#include <vector>
+#include <string>
+#include"control.h"
+#include"control-default.h"
+#include"constants.h"
+#include"Parameters.hh"
+
+#include<chrono>
+#include <gsl/gsl_errno.h> 
+#include <gsl/gsl_spline.h>
+#include <gsl/gsl_interp2d.h>
+#include <gsl/gsl_spline2d.h>
+#include <gsl/gsl_sf.h>
+#include<pthread.h>
+#include<cuba.h>
+
+extern double  INT_PREC;
+#include"clenshaw.hh"
+#include"gauss.hh"
+
+#include"kt-formula.hh"
+#include"options.h"
+
+int N_APPROX=N_CHEB_R;
+
+double INT_PREC=1.0e-5;
+
+
+int main(int argc , char** argv){
+	options opt=read_options(argc, argv);
+	std::vector<double> param(10,0);
+
+	char infilenames[500];
+	char filenames[500];
+	if(opt.path==""){
+		opt.path=getenv("DIR");
+	}
+	if(opt.input_file_name!="result.txt"){	
+		sprintf(infilenames,"%s",opt.input_file_name.c_str());
+	}else{
+		sprintf(infilenames,"%s/%s",opt.path.c_str(),opt.input_file_name.c_str());
+	}
+	
+	printf("%s\n",infilenames);
+	FILE* infile=fopen(infilenames,"r");
+	read_parameters(infile,param);
+	fclose(infile);
+	double sigpar[10]={0},sudpar[10]={0};
+	parameter(param,sigpar,sudpar);
+////////////////////////////////////////////////////////////////////////////	
+			SIGMA sigma;
+			sigma.init(sigpar);
+        
+		if(opt.output_file_name!="out.txt"){
+            sprintf(filenames,"%s",opt.output_file_name.c_str());
+        }else{
+		    sprintf(filenames,"%s/sigma.txt",opt.path.c_str());
+		}
+		printf("%s\n",infilenames);
+  		//FILE *outfile=fopen(filenames,"w");
+//#if SUDAKOV>=1
+		FILE *outfile=fopen(filenames,"w");
+		//fclose(outfile);
+		double val=0,x=0;
+		double r;
[…]

### 2023-04-21 saturation-ver3/Functions/plot/plot-ww.cc

@@ -1,0 +1,151 @@
+#include<iostream>
+#include<fstream>
+#include<cuba.h>
+#include<cmath>
+#include <vector>
+#include <string>
+#include"control.h"
+#include"control-default.h"
+#include"constants.h"
+#include"Parameters.hh"
+
+#include<chrono>
+#include <gsl/gsl_errno.h> 
+#include <gsl/gsl_spline.h>
+#include <gsl/gsl_interp2d.h>
+#include <gsl/gsl_spline2d.h>
+#include <gsl/gsl_sf.h>
+#include<pthread.h>
+#include<cuba.h>
+
+extern double  INT_PREC;
+#include"clenshaw.hh"
+#include"gauss.hh"
+
+
+#include"kt-formula.hh"
+#include"options.h"
+
+
+int N_APPROX=N_CHEB_R;
+
+double INT_PREC=1.0e-5;
+
+int main(int argc , char** argv){
+	options opt=read_options(argc, argv);
+	std::vector<double> param(10,0);
+
+	char infilenames[500];
+	char filenames[500];
+	if(opt.path==""){
+		opt.path=getenv("DIR");
+	}
+	if(opt.input_file_name!="result.txt"){	
+		sprintf(infilenames,"%s",opt.input_file_name.c_str());
+	}else{
+		sprintf(infilenames,"%s/%s",opt.path.c_str(),opt.input_file_name.c_str());
+	}
+	
+	printf("reading %s\n",infilenames);
+	FILE* infile=fopen(infilenames,"r");
+	read_parameters(infile,param);
+	fclose(infile);
+	double sigpar[10]={0},sudpar[10]={0};
+	parameter(param,sigpar,sudpar);
+	
+	const double kt2max=1.0e+6;
+////////////////////////////////////////////////////////////////////////////	
+	#if GLUON_APPROX==1
+		#if SIGMA_APPROX==-1||SIGMA_APPROX==0//if sigma is not in 1d grid
+			SIGMA sigma;
+			sigma.init(sigpar);
+			INTEG dsigma(sigma);
+			dsigma.init(sigpar,'w');
+		#endif
+		
+		GLUON dipole_gluon(dsigma);
+		dipole_gluon.init(sigpar);
+	#else //only GBW K
+		GLUON dipole_gluon;
[…]

### 2023-04-23 Paper/draft.tex
plots udated

@@
 \usepackage{cite}
+\usepackage{ulem}
 %\usepackage{times}
@@
   \begin{multicols}{2}
-    \includegraphics[width=0.47\textwidth]{./plots/GBW-dipole.png}
-    \includegraphics[width=0.47\textwidth]{./plots/GBW-gluon.png}
-    \includegraphics[width=0.47\textwidth]{./plots/GBW-saturation.png}\par
-    \includegraphics[width=0.47\textwidth]{./plots/BGK-dipole.png}
-    \includegraphics[width=0.47\textwidth]{./plots/BGK-gluon.png}
-    \includegraphics[width=0.47\textwidth]{./plots/BGK-saturation.png}
+    \includegraphics[width=0.49\textwidth]{./plots/GBW-dipole.pdf}
+    \includegraphics[width=0.49\textwidth]{./plots/GBW-gluon.pdf}
+    \includegraphics[width=0.49\textwidth]{./plots/GBW-saturation.pdf}\par
+    \includegraphics[width=0.49\textwidth]{./plots/BGK-dipole.pdf}
+    \includegraphics[width=0.49\textwidth]{./plots/BGK-gluon.pdf}
+    \includegraphics[width=0.49\textwidth]{./plots/BGK-saturation.pdf}
   \end{multicols}
-  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},
+  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},\;
   10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
   models Note, the dipole cross section and the gluon density are normalized by
-  $\sigma_0^{-1}$. \comment{Larger y and x labels}} 
+  $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
 \end{figure}

### 2023-04-23 saturation-ver3/Functions/plot/plot-from-grid.cc

@@ -58,14 +58,14 @@ int main(int c , char** argv){
 			}
 			//printf("x: %.3e\n",x_array[j]);
 		}
-		printf("grid shape %d %d\n",x_npts,k2_npts);
+		printf("Gluon grid shape %d %d\n",x_npts,k2_npts);
 		spline_ptr = gsl_spline2d_alloc(gsl_interp2d_bicubic,k2_npts, x_npts);
 		gsl_spline2d_init (spline_ptr,k2_array, x_array, sigma_array, k2_npts, x_npts);
 		fclose(file);
-		
+		printf("GLUON\n");	
 		int xplot[2]={2,6};
 		for(int j=0;j<2;++j){
-			sprintf(filename,"%s/%s%d.txt",argv[2],"gluon-",xplot[j]);
+			sprintf(filename,"%s/%s%d.txt",argv[3],"gluon-",xplot[j]);
 			file=fopen(filename,"w");
 			x=pow(10,-xplot[j]);
 			for(int i=0;i<100;++i){
@@ -77,6 +77,7 @@ int main(int c , char** argv){
 		fclose(file);
 ///////////////////////////////////////////
 //
+		printf("SATURATION\n");
 //
 //
 //////////////////////////////////////////
@@ -85,7 +86,7 @@ int main(int c , char** argv){
 		int flag=0;
 		int counter=0;
 		double grad=0;
-		sprintf(filename,"%s/%s.txt",argv[2],"saturation");
+		sprintf(filename,"%s/%s.txt",argv[3],"saturation");
 		file=fopen(filename,"w");
 		for(int i=0;i<25;++i){
 			k2=0.01;
@@ -115,6 +116,64 @@ int main(int c , char** argv){
 		}
 		
 		fclose(file);
+/////////////////////////////////////////////////////////
+//
+		printf("SIGMA\n");
+//
+/////////////////////////////////////////////////////////		
+		
+		file=fopen(argv[2],"r");
+		
+		xprev=0.0;
+		double r;
+		for(int j=0;j<x_npts;++j){
+			for(int i=0;i<k2_npts;++i){
+				fscanf(file,"%lf %lf %lf",&x,&r,&val);
+				//printf("%lf %lf %lf %d\n",x,k2,val,feof(file));
+				if(i==0){
+					x_array[j]=exp(x);
+				}
+				if(j==0&&i==0){
[…]

### 2023-04-23 saturation-ver3/Functions/plot/plot-sigma.cc

@@ -72,22 +72,27 @@ int main(int argc , char** argv){
 			x=X_MIN*pow(X_MAX/X_MIN,((double)k)/99);
 			sigma.set_x(x);
 			
-#pragma omp parallel private(r)
+//#pragma omp parallel private(r)
 {
 			//double k2,mu2=0;
-#pragma omp for schedule(dynamic)
+//#pragma omp for schedule(dynamic)
 			for(int j=0;j<100;++j){
 				r=R_MIN*pow(R_MAX/R_MIN,((double)j)/99);
 				printf("r= %.2e\n",r);
 				arr[j]=sigma(x,r);
+				
 				printf("\033[1A\033[2K\r");
+				if(arr[j]<0){
+					printf("%.2e %.2e %.2e\n",x,r,arr[j]);
+				}
 
 			}
 }
 			for(int j=0;j<100;++j){
 				r=R_MIN*pow(R_MAX/R_MIN,((double)j)/99);
 				val=arr[j];
-				fprintf(outfile ,"%.10e\t%.10e\t%.10e\n",log(x),log(r),val );
+				fprintf(outfile ,"%.10e\t%.10e\t%.10e\n",log(x),log(r),val/sigpar[0] );
+				
 			}
 			printf("\033[1A\033[2K\r");
 			//gluon.set_max(kt2max,mu2);	

### 2023-04-23 saturation-ver3/Functions/r-formula.cc

@@ -104,10 +104,6 @@ double Sigma::operator()(const double x, const double r) {//,const double Q2,con
 	#if ADJOINT==1
 	qs2*=9.0/4.0;
 	#endif
-
-	#if IBP==2&&R_FORMULA==0
-	double val=-sigma_0*exp(-pow(r,2)*qs2/4);
-	#else
 //	#if LAPLACIAN==0
 	double val;
 	val=pow(r,2)*qs2/4;
@@ -123,11 +119,31 @@ double Sigma::operator()(const double x, const double r) {//,const double Q2,con
 		printf("dp negative\n");
 		val=0;
 	}
-//	#elif LAPLACIAN==1
-//	double val=pow(r,2)*qs2/4;
-//	val=sigma_0*qs2*(1-val)*exp(-val);
-//	#endif//LAPLACIAN
-	#endif//IBP==2
+
+
+	#if THRESHOLD!=0 
+	//double thresh_power=THRESHOLD;
+	val*=pow(1-x1,thresh_power);
+	#endif
+	if(!std::isfinite(val)){
+		return(0);
+	}
+	return val;
+}
+double Sigma:: S(const double x, const double r) {//,const double Q2,const double*sigpar)const {
+	#if FREEZE_QS2==1 ////Beware this transformation is also required in set_x()!!!!
+	double x1=0.5*x/(0.5*(1-x)+x);
+	#elif FREEZE_QS2==2
+	double x1=((x>0.5)?0.5:x);
+	#elif FREEZE_QS2==0
+	double x1=x;
+	#endif///////////////////////////////////////////////////////////////////////////
+	
+	double qs2=Qs2(x1,r);
+	#if ADJOINT==1
+	qs2*=9.0/4.0;
+	#endif
+	double val=sigma_0*exp(-pow(r,2)*qs2/4);
 	#if THRESHOLD!=0 
 	//double thresh_power=THRESHOLD;
 	val*=pow(1-x1,thresh_power);

### 2023-04-24 Paper/draft.tex
domument update

@@
 We investigate effects of exact gluon kinematics on the parameters of the
-Golec-Biernat--W\"sthoff, and Bartels--Golec-Biernat--Kowalski models. The
+Golec-Biernat--W\"usthoff, and Bartels--Golec-Biernat--Kowalski models. The
 resulting parameters show sizable difference, particularly in the normalization
@@
 \end{figure}
-%Factorization has played central role in QCD, where one expresses a cross section in terms of factors, each depends on a different scale.
-Parton Distribution Functions (PDF) are examples of such objects which appear in factorization.
-The PDFs describe the structure of hadrons, and they are process independent.
-As PDFs are not perturbatively calculable objects, they have to be obtained from experiments.
-%Deeply Inelastic Scattering (DIS) is one of such experiments which can probe the structure of proton.
-Process independence means that the PDFs obtained in DIS can be used in other experiments such as proton-proton collision.
-
-In the small-$x$ region of deep intelastic scattering (DIS) process   
-%
+Factorization has played central role in QCD, where long-distance effects can be isolated into an object called parton distribution functions (PDFs)~\cite{roberts_1990,collins_2011}. 
+The PDFs are not perturbatively calculable but they are process independent~\cite{collins_2011}.
+That is to say, that one needs to measure them in experiments, but the PDFs obtained one experiment can be used as input in another.
+A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}.
+The election-ion collider (EIC)~\cite{NAP25171}, which is currently under construction, will be the next generation of the DIS experiments and expected to uncover more details about the structure.  
+As one increases the center of mass energy at a fixed value of the photon virtuality, $Q$, one is probing the region of the small Bjorken scaling variable, $x$.
+In the small-$x$ region of DIS process   
 \begin{equation}
@@
 
-\comment{Some more general talk like in the previous paper}
+\sout{\comment{Some more general talk like in the previous paper}}
 
-\comment{EIC}
+\sout{\comment{EIC}}
 
@@
 \begin{equation}
-F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(x,\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(x,r\right),
+F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(\tilde{x},\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(\tilde{x},r\right),
 \label{eq:dipole-factorization}
 \end{equation}
-where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.\\
+where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.
+In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
+\\
 
@@
 It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
-% \comment{What is the connection?
-Their result regarding the 1/x grad of $Q_s$ becoming smaller is clearly not present in our case.
-If we consider $\mathcal{F}$ with running coupling, it will be a bit bent in very small-x.
-besides, the analysis of \cite{Albacete:2004gw} extends to around $Y=\ln(x_0/x)\sim35$.
-for our case it may be just not low enough.
-(though around $Y=10$, $\alpha_0=0.2$ and running have sizable difference.
-) }
+
 Another notable point is that, except for the normalization $\sigma_0$, the parameters are very similar, particularly those of rc-$k_T$-GBW are almost identical to those of $r$-GBW. 
-\comment{Describet what's in the figuers...}
+While the GBW model remains almost unaffected, the BGK model seems to show slightly more change. The difference in $\sigma_0$ is similar to that of GBW model, and other parameters changed moderately.
+\sout{\comment{Describet what's in the figuers...} }
+In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole gluon density and the saturation scale are shown for the GBW and BGK models are shown.
+The dipole cross section and the gluon density are both normalized by $\sigma_0$ in order to see the effects  of other parameters better,
+and the saturation scale is defined as a ridge of the dipole gluon density on the $(x,k_T^2)$ plane.\\
+One can see, in the plots on the left side, the effects of the changes (or rather no changes) in the parameters of the GBW model.
+The difference between the rc-$k_T$-GBW and $r$-GBW are negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.\\
+On th right side of Fig.~\ref{fig:GBW-BGK}, the same plots for the BGK model are shown.
+Unlike in the GBW model, the connection between the differences shown in the plots and the differences in the parameters are not clear.
+Nevertheless, the difference is more prominent in the small-$x$ region.
+Comparisons of the results with the $F_2$ data are shown in Figs.~\ref{fig:GBW-Grid} and~\ref{fig:BGK-Grid}.
+In Fig.~\ref{fig:GBW-Grid}, the difference between $r$-GBW and $k_T$-GBW are not visible, while rc-$k_T$-GBW shows sizable difference from the others, particularly in the large-$Q^2$ region. 
+Recalling that the parameters of rc-$k_T$-GBW and $r$-GBW are very similar, the difference in $F_2$ is almost entirely due to the coupling constant.
+The improvement in the fit quality is depicted as a histogram of the $\chi^2$-vale per number of points at the bottom of Fig.~\ref{fig:GBW-Grid}.
+Here, the improvement in the large-$Q^2$ region is very clear.
+In Fig.~\ref{fig:BGK-Grid}, the difference between $r$-BGK and $k_T$-BGK are hardly visible.
+In the histogram at the bottom, one can see some differences, but they cancel out mostly, making little improvement overall.
 
 \begin{figure}[p]
+
   \begin{multicols}{2}
-    \includegraphics[width=0.49\textwidth]{./plots/GBW-dipole.pdf}
-    \includegraphics[width=0.49\textwidth]{./plots/GBW-gluon.pdf}
-    \includegraphics[width=0.49\textwidth]{./plots/GBW-saturation.pdf}\par
-    \includegraphics[width=0.49\textwidth]{./plots/BGK-dipole.pdf}
-    \includegraphics[width=0.49\textwidth]{./plots/BGK-gluon.pdf}
-    \includegraphics[width=0.49\textwidth]{./plots/BGK-saturation.pdf}
+  \begin{subfigure}{0.5\textwidth}
+    \includegraphics[width=\textwidth]{./plots/GBW-dipole.pdf}
+    \includegraphics[width=\textwidth]{./plots/GBW-gluon.pdf}
+    \includegraphics[width=\textwidth]{./plots/GBW-saturation.pdf}
+    \caption{GBW}
+    \label{fig:GBW}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+    \includegraphics[width=\textwidth]{./plots/BGK-dipole.pdf}
+    \includegraphics[width=\textwidth]{./plots/BGK-gluon.pdf}
+    \includegraphics[width=\textwidth]{./plots/BGK-saturation.pdf}
+    \caption{BGK}
+    \label{fig:BGK}
+\end{subfigure}
   \end{multicols}
@@
   10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
-  models Note, the dipole cross section and the gluon density are normalized by
+  models. Note, the dipole cross section and the gluon density are normalized by
   $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
+\label{fig:GBW-BGK}
 \end{figure}
@@
 \end{figure}
-
-Let us analyze the difference in $\sigma_0$. 
+For the rest of this section, let us have a closer look at $\sigma_0$. 
 Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$.
@@
 Since 
-%
 \begin{equation}
@@
 \end{equation}
-%
-the $k_T$-factorization case receives more suppression.
-Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression.
-Thus, one would expect that the massive light quarks partially simulate the effect of $x/z$.
-It is therefore, interesting to see that the parameters of $k_T$-GBW, are closer to those of $r$-GBW-massive than to the parameters of $r$-GBW.    
-However, it seems that there is a compensating factor in rc-$k_T$-GBW. 
-The compensating effect can be understood as follows.
-As it is visible in  Fig.~\ref{fig:GBW}, larger $x_0$ enhances the small-$r$ region which corresponds roughly to the large-$k_T$ of the dipole gluon density which also is visible.
-As the running coupling depends on $k_T^2$,  one can expect that the large-$k_T$ region gets suppressed.
-Therefore, one can conclude that the change in $x_0$ is a direct consequence of the running coupling.\\
-While the GBW model remains almost unaffected, the BGK model seems to show slightly more change.
-The difference is more prominent in the small-$x$ region (Fig.~\ref{fig:BGK}), particularly noticeable in the second peak of the gluon density.
-The change is cleanly visible in the saturation scale of Fig.~\ref{fig:BGK}. 
-The resulting $F_2$ of respective models are shown in Figs.~\ref{fig:GBW-Grid}~and~\ref{fig:BGK-Grid}.
-
-While the $r$-GBW and $k_T$-GBW show little difference, rc-$k_T$-GBW clearly shows better fit quality in the high-$Q^2$ region. This is clearly shown in the histogram at the bottom. 
-As for the BGK model, the difference is too small to be seen in the top plots.
-However the bottom histogram shows some differences.
-While the small-$Q^2$ region is somewhat improved, as a whole, the changes cancel out.
-
-%\begin{figure}[p]
-%\center
-%\includegraphics[width=0.9\textwidth]{../plots/dipole-GBW.png}\\
-%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW.png}\\
-%\includegraphics[width=0.9\textwidth]{../plots/gluon-GBW-contour.png}
-%\caption{from left: r-BGK, kt-BGK}
-%\end{figure}
-%\begin{figure}[p]
-%\center
-%\includegraphics[width=0.9\textwidth]{../plots/dipole-BGK.png}\\
-%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK.png}\\
-%\includegraphics[width=0.9\textwidth]{../plots/gluon-BGK-contour.png}
-%\caption{from left: r-BGK, kt-BGK}
-%\end{figure}
-
+the $k_T$-factorization case receives more suppression. Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression. 
+Therefore, one can understand the change in $\sigma_0$ as a direct consequence of the key difference between the $k_t$-factorization and the dipole-factorization.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
+At the leading order, the dijet DIS in small-$x$ limit is dominated by $q\overline{q}$ jets~\cite{}.
+This process is therefore closely related to the dipole picture we discussed earlier (see.
+Ref.~\cite{Dominguez:2011wm}).
+In the Breit frame where the photon momentum is $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance $p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon momentum $k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.
+This makes dijets an interesting observable.
+For the region where $p_T\ll P_T\sim p_{1T},\,p_{2T}$, one may use power counting to take leading order in $p_T/P_T$, which leads to the transverse-momentum-dependent~(TMD) factorization .
 
-\comment{process}
+\sout{\comment{process}}
 
-\comment{factorization formula for dijets in DIS involving WW gluon}
+\sout{\comment{factorization formula for dijets in DIS involving WW gluon}}
 
-\comment{mention why Sudakov is important for dijet production}
+\sout{\comment{mention why Sudakov is important for dijet production}}
 
-The dijet process is known to probe a type of unintegrated gluon density, called Weizs\"acker-Williams gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
-This UGD, $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton~\cite{Dominguez:2010xd,Dominguez:2011wm,Dominguez:2011wm}.
+In the large-$N_c$ limit of the TMD factorization, there are two types of gluon densities, namely the dipole gluon density and the Weizs\"acker-Williams (WW) gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,vanHameren:2016ftb,Xiao:2017ggh}.
+It was shown in Ref.~\cite{Dominguez:2011wm}, that the dijet process in DIS can directly probe the WW gluon,$\fww(x,k^2)$, where the differential cross section factorizes as
+\begin{equation}
+	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
+\end{equation}
+with the hard function $H_{\gamma^*g\rightarrow q\overline{q}}$ describing interactions of an off-shell photon with an on-shell gluon to a $q\overline{q}$ pair.
+$\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton, while $\fdp(x,k_T^2)$ does not have such an interpretation~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
+
 Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
@@
 \end{equation}
-Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2013wwa,Xiao:2017yya}
+
+For the region where TMD factorization is applicable, $Q_s\sim k_T\ll P_T\sim Q$, one needs to resum the large Sudakov logarithms $\log(k_T/Q)$, as well as $\log(1/x)$~\cite{Dominguez:2011wm}. 
+It was shown in Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent resummation such logarithms are possible owing to the separation of corresponding regions.  
+Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya}
 \begin{equation}
@@
 ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
-ITMD is an generalization of TMD where the momentum imbalance is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
-That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$, where $P_t\sim p_{1T},p_{2T}$ of jets~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
+ITMD is an generalization of TMD where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
 
@@
 \comment{Add what we had in the previous paper}
+We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren \comment{appropriate phrase }.
+The project is partially supported by
+the European Union’s Horizon 2020 research and innovation program under grant agreement No. 824093.
+TG and SS are partially supported by the Polish National Science Centre grant no. 2017/27/B/ST2/02004.
+KK acknowledges the support of The Kosciuszko Foundation for the Academic year 22/23 for the
+project ”Entropy of dense system of quarks and gluons”. Furthermore, KK  acknowledges the hospitality of the Nuclear Theory group at the BNL, where part of the  project was realized.
 

### 2023-04-25 Paper/draft.tex
document update

@@
 The PDFs are not perturbatively calculable but they are process independent~\cite{collins_2011}.
-That is to say, that one needs to measure them in experiments, but the PDFs obtained one experiment can be used as input in another.
+That is to say, that one needs to measure them in experiments, but the PDFs obtained in one experiment can be used as input in another.
 A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}.
@@
 
-Additionally, let us introduce $q'\equiv q+x p$. 
+Now let us introduce $q'\equiv q+x p$. 
 Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
@@
 where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.
-In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
+In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ was used, even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
 \\
@@
 In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
-In order to account for the running coupling, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
+Comparing, the GBW and BGK models, one identifies that, the GBW model is effectively the BGK model with $\alpha_s(\mu^2)xg(x,\mu^2)\rightarrow \alpha_s(Q_0^2)xg(x,Q_0^2)$.
+For this reason, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
 %
@@
 The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
-(For a more detailed analysis of UGD from the BGK model see.
+(For a more detailed analysis of the dipole gluon density from the BGK model see.
 Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
@@
 \sout{\comment{Describet what's in the figuers...} }
-In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole gluon density and the saturation scale are shown for the GBW and BGK models are shown.
+In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole gluon density and the saturation scale for the GBW and BGK models are shown.
 The dipole cross section and the gluon density are both normalized by $\sigma_0$ in order to see the effects  of other parameters better,
@@
 For the rest of this section, let us have a closer look at $\sigma_0$. 
-Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as modified $x$.
+Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as $\tilde{x}$.
 It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.).
@@
 Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.
-Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
 }
@@
 
-In order to investigate less inclusive processes, we will study the electron-dijet correlation at the electron-ion collider(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}. 
+In order to study the $k_T$-dependence better we investigate less inclusive processes.
+To this end, we will apply the obtained dipole cross section to the electron-dijet correlation at the electron-ion collider~(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}.
 At the leading order, the dijet DIS in small-$x$ limit is dominated by $q\overline{q}$ jets~\cite{}.
@@
 Ref.~\cite{Dominguez:2011wm}).
-In the Breit frame where the photon momentum is $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance $p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon momentum $k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.
+In the Breit frame where the photon momentum is $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance $p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon transverse momentum $k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.
 This makes dijets an interesting observable.
@@
 	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
+	\label{eq:TMD}
 \end{equation}
-with the hard function $H_{\gamma^*g\rightarrow q\overline{q}}$ describing interactions of an off-shell photon with an on-shell gluon to a $q\overline{q}$ pair.
+with the hard function $H_{\gamma^*g\rightarrow q\overline{q}}$ describing interactions of an off-shell photon with an on-shell gluon producing a $q\overline{q}$ pair.
 $\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton, while $\fdp(x,k_T^2)$ does not have such an interpretation~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
@@
 For the region where TMD factorization is applicable, $Q_s\sim k_T\ll P_T\sim Q$, one needs to resum the large Sudakov logarithms $\log(k_T/Q)$, as well as $\log(1/x)$~\cite{Dominguez:2011wm}. 
-It was shown in Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent resummation such logarithms are possible owing to the separation of corresponding regions.  
+It was shown in Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent resummation of such logarithms are possible owing to the separation of corresponding regions.  
 Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya}
@@
 ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
-ITMD is an generalization of TMD where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+ITMD is an generalization of TMD, where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
 That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
+In other words, the hard function in Eq.~(\ref{eq:TMD}) no longer has the on-shell gluon, but instead has an off-shell gluon $g^*$, thus rendering the $k_T$ dependence in the hard function as well~\cite{Kotko:2015ura}.
 
@@
 Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of jets and the final state electron in DIS ($e+p\rightarrow e+J_1+J_2+X$), where it was argued that this observable is sensitive to the soft emissions and the saturation effects.
-However, in this study, we will not test the saturation effect, and focus only on the proton case.
+However, in this study, we will not test the saturation effect~(\textit{i.e.}, $A$ dependence), and focus only on the proton case.
 The kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
@@
 Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
-The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr}.
-Clearly, the GBW and BGK models falls much more quickly than the KS gluon density.
+The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr} and running-coupling BK~(rcBK) gluon density~\cite{}.
+Clearly, the GBW and BGK models falls much more quickly than the KS and rcBK gluon density.
 In general, expected behaviour in the large-$k_T$ region is $\sim k_T^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while $\sigma_{\mathrm{GBW}}$ behaves like $\sim e^{-k_T^2}$.
@@
 In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov factor is significantly more pronounced in the case of the GBW and BGK models.
-The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS gluon (\textit{cf.} Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
+The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS and rcBK gluons (\textit{cf.} Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
 
 Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} correspond to Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
-In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS for the new $k_T$-factorization fits.
+In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS and rcBK for the new $k_T$-factorization fits.
 However the overall normalization of the gluon density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
@@
 Fig.~\ref{fig:je-lab} shows the $e$-jets correlation in the lab frame.
-Here, the difference between KS and GBW and BGK are more prominent.
+Here, the difference between KS and GBW and BGK are more prominent, while rcBK shows similar pattern to the GBW and BGK models.
 %Unlike in the previous plots, the new fits in the $k_T$-factorization shows only limited improvement.
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
 	\label{fig:je-breit}
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
 \label{fig:je-lab}
@@
 Again, the GBW and BGK models show considerable deviation from the KS gluon.
-Similarly to the previous plots, the Sudakov factor affects the models differently from the KS gluon in Ref.~\cite{vanHameren:2021sqc}.
+The difference from the previous plot is the disagreement of the GBW/BGK models and the rcBK in the small-$\delta\phi$ region.
+Similarly to the previous plots, the Sudakov factor affects the models somewhat differently from the KS gluon in Ref.~\cite{vanHameren:2021sqc}.
 The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
 }
@@
 
-\comment{Question: what about pieces of derivation removed from the main part?}
+\sout{\comment{Question: what about pieces of derivation removed from the main part?}}
 
@@
 \section*{Acknowledgment}
-\comment{Add what we had in the previous paper}
-We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren \comment{appropriate phrase }.
+\sout{\comment{Add what we had in the previous paper}}
+We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren for the clarification of details of Ref.~\cite{vanHameren:2021sqc} and the use of the KaTie package.
 The project is partially supported by

### 2023-04-25 Paper/draft.tex
git overleaf merged

--- 2023-04-24 Paper/draft.tex
@@
 As one increases the center of mass energy at a fixed value of the photon virtuality, $Q$, one is probing the region of the small Bjorken scaling variable, $x$.
-In the small-$x$ region of DIS process   
-\begin{equation}
+In the small-$x$ region of DIS % process   
+%\begin{equation}
   %\label{eq:}
-  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
-\end{equation}
+%  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
+%\end{equation}
 %
-where are $p$ and $q$ are, respectively, the momenta of the photon and the
-proton, the interactions are dominated by gluons\cite{Kovchegov:2012mbw}.
-As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
+%where are $p$ and $q$ are, respectively, the momenta of the photon and the
+%proton, the
+interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
 An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}.
 This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
-The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by
+The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by{\color{red} Do we need this?
+This relation is only true in DLL limit.}
 \begin{equation}
@@
 However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}.
-The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
+In \cite{Gribov:1983ivg} it has been recognized that gluon recombination can tame the growth of gluons \cite{Gribov:1983ivg}.
+The interplay of linear and nonlinear term leads to gluon saturation.
+% The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
 The phenomenon described by this nonlinear term is called saturation.
@@
 (see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
+{\color{red} We need an appendix with expressions for $I_i$}
 %and

### 2023-04-25 Paper/draft.tex
document merged with overleaf

@@
 The PDFs are not perturbatively calculable but they are process independent~\cite{collins_2011}.
-That is to say, that one needs to measure them in experiments, but the PDFs obtained in one experiment can be used as input in another.
+That is to say, that one needs to measure them in experiments, but the PDFs obtained one experiment can be used as input in another.
 A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}.
@@
 This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
-The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by{\color{red} Do we need this?
+%The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by{\color{red} Do we need this?
 This relation is only true in DLL limit.}
-\begin{equation}
-xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
-\end{equation}
+%\begin{equation}
+%xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
+%\end{equation}}
 Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.
@@
 The interplay of linear and nonlinear term leads to gluon saturation.
-% The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
+\comment{a line mentioning BK is removed.
+Is there a particular reason not to mention BK or simply GLR replaced?
+}% The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
 The phenomenon described by this nonlinear term is called saturation.
@@
 
-Now let us introduce $q'\equiv q+x p$. 
+Now, let us introduce $q'\equiv q+x p$. 
 Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
@@
 (see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
-{\color{red} We need an appendix with expressions for $I_i$}
+\sout{{\color{red} We need an appendix with expressions for $I_i$}}
 %and
-%\begin{equation}
-%	\begin{split}
-%		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
-%		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
-%		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
-%		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
-%	\end{split}
-%\end{equation}
-%for
-%\begin{equation}
-%	\begin{split}
-%		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
-%		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
-%		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
-%		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
-%	\end{split}
-%\end{equation}
+
 %Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
@@
 where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.
-In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ was used, even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
+In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
 \\
@@
 The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
-(For a more detailed analysis of the dipole gluon density from the BGK model see.
+(For a more detailed analysis of dipole gluon density from the BGK model see.
 Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
@@
 Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
 }
@@
 	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
-	\label{eq:TMD}
 \end{equation}
@@
 ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
-ITMD is an generalization of TMD, where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
+ITMD is an generalization of TMD where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
 That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
 	\label{fig:je-breit}
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.}
 \label{fig:je-lab}
@@
 Again, the GBW and BGK models show considerable deviation from the KS gluon.
-The difference from the previous plot is the disagreement of the GBW/BGK models and the rcBK in the small-$\delta\phi$ region.
+The difference from the previous plot is the disagreement of the GBW/BGK models and the rcBK in the small-$\Delta\phi$ region.
 Similarly to the previous plots, the Sudakov factor affects the models somewhat differently from the KS gluon in Ref.~\cite{vanHameren:2021sqc}.
@@
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
+Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
 }
@@
 
-\sout{\comment{Question: what about pieces of derivation removed from the main part?}}
+\comment{Question: what about pieces of derivation removed from the main part?}
 
@@
 
+\appendix
+\section{$I_i$ in Eq.~(\ref{eq:angle-integrated})}
+$I_1,\, I_2,\,  I_3,\,  I_4$ in Eq.~(\ref{eq:angle-integrated}) are defined in Ref.~\cite{Kimber:2001uaa} as
+\begin{equation}
+	\begin{split}
+		\frac{I_1}{2\pi}=\frac{N_1N_2+N_3^2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}}, &\hspace{1cm}
+		\frac{I_2}{2\pi}=\frac{N_3-(1-2\beta)N_1}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},\\
+		\frac{I_3}{2\pi}=\frac{N_1+N_2}{\left( N^2_1+2N_1N_2+N_3^2\right)^{3/2}},&\hspace{1cm}
+		\frac{I_2}{2\pi}=\frac{(1-\beta)}{(N_1+N_4)\sqrt{ N^2_1+2N_1N_2+N_3^2}},
+	\end{split}
+\end{equation}
+for
+\begin{equation}
+	\begin{split}
+		N_1\equiv\beta(1-\beta)Q^2+m_f^2, &\hspace{2cm}
+		N_2\equiv{\kappa'}_t^2+(1-\beta)^2k_T^2,\\
+		N_3\equiv{\kappa'}_t^2-(1-\beta)^2k_T^2, &\hspace{2cm}
+		N_4\equiv{\kappa'}_t^2+\beta(1-\beta)k_T^2.
+	\end{split}
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-04-25 Paper/draft.tex
merged again

@@
 A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}.
-The election-ion collider (EIC)~\cite{NAP25171}, which is currently under construction, will be the next generation of the DIS experiments and expected to uncover more details about the structure.  
+The election-ion collider (EIC)~\cite{NAP25171}, which is currently under construction, will be the next generation of the DIS experiments and expected to uncover more details about the hadron structure.
 As one increases the center of mass energy at a fixed value of the photon virtuality, $Q$, one is probing the region of the small Bjorken scaling variable, $x$.
-In the small-$x$ region of DIS % process   
-%\begin{equation}
-  %\label{eq:}
-%  e\, p\rightarrow \gamma^* (q)\, p(p)\rightarrow X\,,
-%\end{equation}
-%
-%where are $p$ and $q$ are, respectively, the momenta of the photon and the
-%proton, the
-interactions are dominated by gluons\cite{Kovchegov:2012mbw}. As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}. 
-An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}.
-This appears in the $k_T$-factorization formula~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
-%The dipole gluon density is also called unintegrated gluon density~(UGD) since it is related to the collinear (integrated) gluon density by{\color{red} Do we need this?
-This relation is only true in DLL limit.}
-%\begin{equation}
-%xg(x,Q^2)=\int^{Q^2}_0 dk_T^2 \mathcal{F}(x,k^2_t).
-%\end{equation}}
+In the small-$x$ region of DIS, % process   
+interactions are dominated by gluons\cite{roberts_1990,collins_2011, Kovchegov:2012mbw}.
+As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
+An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Bomhof:2006dp,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}.
+This appears in the $k_T$-factorization formula~\cite{Catani:1990eg,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
 Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.
-However, such rise violates unitarity and the Froissart bound~\cite{Kovchegov:2012mbw,Barone:1993sy}.
+However, such rise violates unitarity and the Froissart bound~\cite{roberts_1990,collins_2011,Kovchegov:2012mbw,Barone:1993sy}.
 In \cite{Gribov:1983ivg} it has been recognized that gluon recombination can tame the growth of gluons \cite{Gribov:1983ivg}.
-The interplay of linear and nonlinear term leads to gluon saturation.
+The interplay of linear and nonlinear term leads to an phenomenon called gluon saturation.
 \comment{a line mentioning BK is removed.
-Is there a particular reason not to mention BK or simply GLR replaced?
-}% The work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination, by including nonlinear term in the evolution, thus taming the growth.
-The phenomenon described by this nonlinear term is called saturation.
+Is there a particular reason not to mention BK or simply GLR replaced them?
+}%
+{\color{gray}Similarly, the work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination in the evolution in the dipole formalism, thus successfully incorporating the saturation.}
  The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
@@
 
-\sout{\comment{Some more general talk like in the previous paper}}
-
-\sout{\comment{EIC}}
+\sout{\comment{Some more general talk like in the previous paper}\\ }
+\sout{\comment{EIC} }
 
@@
 (see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
-\sout{{\color{red} We need an appendix with expressions for $I_i$}}
+\sout{\color{red} We need an appendix with expressions for $I_i$}
 %and
@@
 where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.
-In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
+In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ was used even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
 \\
@@
 \center\footnotesize
-\input{GBW-parameters.tex}
+\begin{tabular}{|c|c|c|c|c|}
+	\hline - & $\sigma_0 $ [mb] & $x_0 \left(10^{-4}\right)$ & $\lambda$ & $\chi^2/\mathrm{dof}$ \\\hline 
+	{\footnotesize $r$-GBW} & 1.907e+01& 2.582e+00& 3.219e-01& 4.438e+00\\\hline 
+	{\footnotesize $r$-GBW-massive} & 2.384e+01& 1.117e+00& 3.082e-01& 5.274e+00\\\hline 
+	{\footnotesize $k_t$-GBW} & 3.344e+01& 1.333e+00& 3.258e-01& 4.396e+00\\\hline 
+	{\footnotesize rc-$k_t$-GBW} & 1.520e+01& 2.648e+00& 3.211e-01& 2.447e+00\\\hline 
+\end{tabular}
 %\caption{}
@@
 \center\footnotesize
-\input{BGK-parameters.tex}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+	\hline - & $\sigma_0 $ [mb] & $A_g$ & $\lambda_g$ & $C$ & $\mu_0^2 \left[\mathrm{GeV^2}\right]$ & $\chi^2/\mathrm{dof}$ \\\hline 
+	{\footnotesize $r$-BGK} & 2.326e+01& 1.181e+00& 8.317e-02& 3.294e-01& 1.873e+00& 1.556e+00\\\hline 
+	{\footnotesize $k_t$-BGK} & 3.470e+01& 1.048e+00& 2.205e-01&2.391e-01& 9.954e-01&  1.527e+00\\\hline 
+\end{tabular}
 %\caption{}
@@
 Top row: comparison of the dipole-factorization fit and $k_T$-factorization fit results.
-Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.
-Green dashed line is the KS gluon~\cite{vanHameren:2021sqc}.
+Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
 }
@@
 	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
+        \label{eq:TMD}
 \end{equation}
@@
 \section*{Acknowledgment}
-\sout{\comment{Add what we had in the previous paper}}
+\comment{Add what we had in the previous paper}
 We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren for the clarification of details of Ref.~\cite{vanHameren:2021sqc} and the use of the KaTie package.
@@
 KK acknowledges the support of The Kosciuszko Foundation for the Academic year 22/23 for the
-project ”Entropy of dense system of quarks and gluons”. Furthermore, KK  acknowledges the hospitality of the Nuclear Theory group at the BNL, where part of the  project was realized.
+project ”Entropy of dense system of quarks and gluons”.% Furthermore, KK  acknowledges the hospitality of the Nuclear Theory group at the BNL, where part of the  project was realized.
 
@@
 \bibliographystyle{unsrt}
+%\bibliographystyle{apalike}
 \bibliography{draft}

### 2023-05-04 saturation-ver3/Functions/control-default.h
main changed

@@ -153,9 +153,10 @@
 //////////////////////////////////////////////////////////////////
 //N_PAR is number of fit parameters
 #if MODEL ==0 
-	#define N_PAR 5
+	#define N_PAR 4
 #elif MODEL==1
-	#define N_PAR 7
+	#define N_PAR 6
+	
 #elif (MODEL==2||MODEL==22)
 	#if SUDAKOV==0
 		#define N_PAR 3

### 2023-05-04 saturation-ver3/Functions/dipole-gluon.cc

@@ -6,16 +6,7 @@ void Gluon_GBW::init(const double *par){
 		sigma_0 = par[count++];
 		lambda	= par[count++];
 		x_0	=par[count++];
-	#if MU02==0
-		mu02 = par[count++];
-	#else 
-		mu02 = MU02;
-	#endif
-	#if THRESHOLD==-1
-		thresh_power=par[count++];
-	#else
-		thresh_power=THRESHOLD;
-	#endif
+	
 }
 double Gluon_GBW::operator()(const double  x,const double k2,double mu2){
 	if(x_0<1.0e-5||x_0>1.0e-3){
@@ -25,9 +16,7 @@ double Gluon_GBW::operator()(const double  x,const double k2,double mu2){
 		return 0;
 	}
 	double Qs2=pow(x_0/x,lambda);
-	#if THRESHOLD==-2
-	Qs2*=pow(1-x,5);
-	#endif		
+		
 	#if WW==1
 	Qs2*=9.0/4.0;
 	gsl_sf_result result;
@@ -41,15 +30,7 @@ double Gluon_GBW::operator()(const double  x,const double k2,double mu2){
 	if(std::isnan(val)==1){
 		return(0);
 	}
-	#if ALPHA_RUN==1
-	val*=alpha(mu2+mu02)/0.2;
-	//val*=alpha((mu2>mu02)?(mu2):(mu02))/0.2;
-	//printf("%.2e %.2e\n",mu2,alpha(mu2));
-	#endif
-	#if THRESHOLD>0||THRESHOLD==-1 
-	//double thresh_power=THRESHOLD;
-	val*=pow(1-x,thresh_power);
-	#endif
+	
 	return (sigma_0*val) ;
 }
 //////////////////////////////////////////////////////////////////////

### 2023-05-04 saturation-ver3/Functions/fcn.h

@@ -7,6 +7,7 @@
 #include"Minuit2/MnEigen.h"
 #include"Minuit2/FCNBase.h"
 #include"Minuit2/MnMachinePrecision.h"
+#include"Minuit2/MnGlobalCorrelationCoeff.h"
 
 //#include"/home/tomoki/Numerics/clenshaw-curtis-gauss-legendre.hh"
 //#include"./clenshaw-curtis.hh"

### 2023-05-04 saturation-ver3/Functions/interpolation-gluon.cc

@@ -147,13 +147,8 @@ void Approx_aF::init(const int npts1, const int npts2, const double * const &par
 	alloc(x_npts,kt2_npts);
 	
 	sigma_0=par[0];
-#if ALPHA_RUN==1
-#if MU02==0
-	mu02 = par[3];
-#else 
-	mu02 = MU02;
-#endif
-#endif
+
+
 }
 
 double Approx_aF::operator()(const double x,const double kt2,const double mu2)const{
@@ -168,8 +163,6 @@ double Approx_aF::operator()(const double x,const double kt2,const double mu2)co
 	if(x<X_MIN){printf("Approx_aF:: x too small xmin= %.1e x= %.1e diff=%.1e\n",1.0e-8,x,x-1.0e-8);}			
 	double val = 0;
 	val=gsl_spline2d_eval(spline_ptr,kt2, x,kt2_accel_ptr, x_accel_ptr);
-#if ALPHA_RUN==1
-	val*=alpha(mu2+mu02)/0.2;
-#endif
+
 	return(val);
 }

### 2023-05-04 saturation-ver3/Functions/main.cc

@@ -46,6 +46,12 @@ int save_res(std::string name, const ROOT::Minuit2::FunctionMinimum *min,const K
 	return 0;
 }
 
+
+//////////////////////////////////////////////////////////
+//
+// MAIN 
+//
+////////////////////////////////////////////////////////////
 int main(int argc, char** argv){
 	
 #if SCATTER==1
@@ -91,6 +97,9 @@ int main(int argc, char** argv){
 	int skip=0;
 #if USE_RESULT==0
 //	for(unsigned i=0;(i-skip)<N_PAR;i++){
+////////////////////////////////////////////
+// Set up the parameters
+////////////////////////////////////////////
 	for(unsigned i=0;i<N_PAR;i++){
 #if (ALPHA_RUN==0||MU02!=0)
 		if(par_name[i]=="mu02"){
@@ -99,13 +108,7 @@ int main(int argc, char** argv){
 			continue;
 		}
 #endif
-#if (THRESHOLD!=-1)
-		if(par_name[i]=="thresh"){
-			skip++;
-			//std::cout<<"Skip "<< par_name[i]<<" = "<< MU02<<std::endl;;
-			continue;
-		}
-#endif
+
 		std::cout<<par_name[i]<<" = "<<par_start[i]<<std::endl;
 		//std::cout<<N_PAR<<"  "<<skip <<" : parameter position="<<i<<std::endl;
 		upar.Add(par_name[i], par_start[i],par_error[i]);
@@ -130,13 +133,14 @@ int main(int argc, char** argv){
 		ival=double_round(ival,USE_RESULT);
 #endif
 		printf("%s %le %le \n",name,ival,ierr*10);
-		//upar.Add(name, ival,(fabs(ierr)<fabs(ival/100))?(ival/50):(ierr*10));
-		//upar.Add(name, ival,(fabs(ierr)<1.0e-5)?(ival/50):(ierr*10));
-		//upar.Add(name, ival, ival/50);
 		upar.Add(name, ival, ival*5*pow(10,-USE_RESULT));
 	}printf("\n");
 	fclose(resinputfile);
 #endif//USE_RESULT
+
+//////////////////////////////////////////////////////////
+// Start fitting
+//////////////////////////////////////////////////////////
 	ROOT::Minuit2::MnMachinePrecision prec;
 	
 	INT_PREC=5.0e-4 ;
[…]

### 2023-05-04 saturation-ver3/Functions/r-formula.cc

@@ -32,16 +32,33 @@ double Sigma_BGK::Qs2(const double x,const double r)const{
 	return qs2;		
 }
 
+inline double Sigma::freeze_x(const double x){
+	double x2;
+#if FREEZE_QS2==1
+		x2=xmax*x/(xmax*(1-x)+x);
+#elif  FREEZE_QS2==2
+		x2=((x>xmax)?xmax:x);
+#else
+		x2=x;
+#endif
+/*
+	switch(FREEZE_QS2){
+	case 1:
+		x2=0.5*x/(0.5*(1-x)+x);
+		break;
+	case 2:
+		x2=((x>0.5)?0.5:x);
+		break;
+	default:
+		x2=x;
+	}
+*/
+	return x2;
+}
 //void Sigma::set_x(const double &x){
 void Sigma_BGK::set_x(const double &x){
 #if SIGMA_APPROX<0
-	#if FREEZE_QS2==1
-	x2=0.5*x/(0.5*(1-x)+x);
-	#elif FREEZE_QS2==2
-	x2=((x>0.5)?0.5:x);
-	#elif FREEZE_QS2==0
-	x2=x;
-	#endif
+	x2=freeze_x(x);
 	xgpdf.set_x(x2);
 #endif
 }
@@ -56,12 +73,6 @@ void Sigma_GBW::init(const double * const &sigpar){
 	#if MU02==0
 	i++;//mu102=sigpar[i++];
 	#endif
-	#if THRESHOLD==-1
-	this->thresh_power=sigpar[i++];
-	#else
-	this->thresh_power=THRESHOLD;
-	#endif
-	//sigpar=par;
 }
 void Sigma_BGK::init(const double * const &sigpar){
 	this->par=sigpar;
@@ -79,12 +90,6 @@ void Sigma_BGK::init(const double * const &sigpar){
 	this->xgpdf.init(mu02*0.5 , 2*(C/pow(R_MIN,2)+mu02),A_g,lambda_g);
 	#endif
 
-	#if THRESHOLD==-1
-	this->thresh_power=sigpar[i++];
-	#else
-	this->thresh_power=THRESHOLD;
-	#endif
-	//sigpar=par;
 }
 
 //inline double operator()(const double r)const {
@@ -92,13 +97,8 @@ void Sigma_BGK::init(const double * const &sigpar){
 //}
 //double Sigma::operator()(const double x, const double r) {//,const double Q2,const double*sigpar)const {
[…]

### 2023-05-04 saturation-ver3/Functions/r-formula.cc
r-f

@@ -6,8 +6,8 @@ double Sigma_GBW::Qs2(const double x,const double r)const{
 		getchar();
 	}
 	const double qs2=pow(x_0/x,lambda);//*pow(1-x,5.6); 
-	if(qs2<1.0e-25){
-		return 1.0e-25;
+	if(qs2<1.0e-50){
+		return 1.0e-50;
 	}
 	return qs2;		
 }
@@ -22,7 +22,8 @@ double Sigma_BGK::Qs2(const double x,const double r)const{
 	}
 	#endif
 	const double rrmax=pow(r,2)/C;
-	const double mu2=(r>1.0e-5)?(mu02/((1.0-exp(-mu02*rrmax) ))):(1/rrmax+mu02/2) ;
+	const double mu2=(rrmax>1.0e-6)?(mu02/((1.0-exp(-mu02*rrmax) ))):(1/rrmax+mu02/2+pow(mu02,2)*rrmax/12) ;
+	//const double mu2=mu02/(1.0-exp(-mu02*rrmax)) ;
 	const double al=alpha(mu2);
 	//const double al=0.2;
 	const double qs2=4*PI*PI*al*xgpdf(x,mu2,A_g,lambda_g)/(3*sigma_0); 
@@ -109,13 +110,19 @@ double Sigma::operator()(const double x, const double r) {//,const double Q2,con
 	double val=-sigma_0*exp(-pow(r,2)*qs2/4);
 	#else
 //	#if LAPLACIAN==0
-	double val;
-	val=pow(r,2)*qs2/4;
-	if(val<1.0e-4){
-		val*=(1-val/2+pow(val,2)/6-pow(val,3)/24);
+	double val,ex;
+	ex=pow(r,2)*qs2/4;
+	if(ex<5.0e-3){
+		//val*=(1-val/2+pow(val,2)/6-pow(val,3)/24);
+		val=ex*(1-ex*(1-ex*(1-ex*(1-ex/5)/4)/3)/2);
+		if(val>2.0e-3){
+			if(fabs((1-exp(-ex))-val)>1.0e-15){
+				printf("sigma discontinuous, %.2e %.2e \t %.3e\n",1-exp(-ex),val,val-(1-exp(-ex)));	
+			}
+		}
 //		//printf("%.4e %.4e %.4e\n",r,(1-exp(-val))/pow(r,2),val/pow(r,2));
 	}else{
-		val=(1-exp(-val));
+		val=(1-exp(-ex));
 	}
 	val*=sigma_0;
 

### 2023-05-04 saturation-ver3/Functions/control-default.h
r-f

@@ -139,7 +139,7 @@
 #endif
 
 #ifndef N_CHEB//variants of models. see r-formula.h
-	#define N_CHEB 25
+	#define N_CHEB 30
 #endif
 #ifndef CHEB_D//variants of models. see r-formula.h
 	#define CHEB_D 1

### 2023-05-08 Paper/draft.tex
documet update

@@
 \usepackage{amssymb}
-\usepackage{breqn}
-\usepackage[]{fancyhdr}
+%\usepackage{breqn}
+%\usepackage[]{fancyhdr}
 \usepackage{tikz}
@@
 \usepackage{cite}
-\usepackage{ulem}
-%\usepackage{times}
-%\usepackage{merriweather}
-%\usepackage{draftwatermark}
-%\usepackage[backend=biber, style=ieee]{biblatex}
-
-%\addbibresource{draft.bib}
+%\usepackage{ulem}
 
@@
 
-%\newcommand{\comment}[1]{{\color{red}[\textbf{comment:} #1 ]}}
+%-----------------------------------------------------------------------------
+%\pagenumbering{arabic}
+%\numberwithin{equation}{section}
 
-\pagenumbering{arabic}
-\numberwithin{equation}{section}
-\numberwithin{table}{section}
-\numberwithin{figure}{section}
-
+%-----------------------------------------------------------------------------
 \newcommand{\fww}[0]{\mathcal{F}^{\mathrm{WW}}}
@@
 \newcommand{\comment}[1]{\texttt{\color{red}#1}}
+\newcommand{\commentPending}[1]{\texttt{\color{red!25}#1}}
 \newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
+
+%-----------------------------------------------------------------------------
 \author{
@@
 {\small\it The H.\ Niewodnicza\'nski Institute of Nuclear Physics PAN,}\\ 
-{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\%\,\\
+{\small\it Radzikowskiego 152, 31-342 Krak\'ow, Poland}\\
 }
-%\title{ New parameters for the Golec-Beiernat--W\"usthoff and Bartels--Golec-Biernat--Kowlski saturation models in the $k_T$-facorization formula of $F_2$}
-\title{Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models}
-\date{\today}
 
+\title{Effects of gluon kinematics and the Sudakov form factor\\ on the dipole amplitude}
+
+\date{}
+
+%-----------------------------------------------------------------------------
 \begin{document}
@@
 %--------------- preprint numbers ---------------------
-\vspace{-25em}
+\vspace{-22em}
 \begin{flushright}
-  IFJPAN-IV-2023-XX\\
+  IFJPAN-IV-2023-XX
 \end{flushright}
-\vspace{20em}
+\vspace{17.5em}
 %------------------------------------------------------
@@
 We investigate effects of exact gluon kinematics on the parameters of the
-Golec-Biernat--W\"usthoff, and Bartels--Golec-Biernat--Kowalski models. The
-resulting parameters show sizable difference, particularly in the normalization
-$\sigma_0$. The resulting models are applied for the dijet process in DIS to
-investigate effects of the Sudakov form factor.  The result qualitatively agrees
-with that of Ref.~\cite{vanHameren:2021sqc}, except for the difference stemming
-from the large-$k_T$ behaviour of the models.
+Golec-Biernat--W\"usthoff, and Bartels--Golec-Biernat--Kowalski saturation
+models. The resulting parameters show some differences, particularly, the
+normalization of the dipole cross section $\sigma_0$. The refitted models are
+used for the dijet production process in DIS to investigate effects of the
+Sudakov form factor at Electron Ion Collider energies.  
 \end{abstract}
@@
 \section{Introduction}
+
+\comment{preprint number (SS)}\\
 
@@
 \end{figure}
-Factorization has played central role in QCD, where long-distance effects can be isolated into an object called parton distribution functions (PDFs)~\cite{roberts_1990,collins_2011}. 
-The PDFs are not perturbatively calculable but they are process independent~\cite{collins_2011}.
-That is to say, that one needs to measure them in experiments, but the PDFs obtained one experiment can be used as input in another.
-A type of experiments called deep inelastic scattering~(DIS), has been one of experiments which largely contributed to the study of the structure of the proton~\cite{roberts_1990,collins_2011}.
-The election-ion collider (EIC)~\cite{NAP25171}, which is currently under construction, will be the next generation of the DIS experiments and expected to uncover more details about the hadron structure.
-As one increases the center of mass energy at a fixed value of the photon virtuality, $Q$, one is probing the region of the small Bjorken scaling variable, $x$.
-In the small-$x$ region of DIS, % process   
-interactions are dominated by gluons\cite{roberts_1990,collins_2011, Kovchegov:2012mbw}.
-As a photon does not interact directly with a gluon, it interact through a box of quarks as depicted in Fig.~\ref{fig:gluon-kinem}.
-An object, which is central to the description of this process is called dipole gluon density, $\mathcal{F}(x,k_T^2)$, which is a type of transverse momentum dependent PDFs (TMD PDF)~\cite{Bomhof:2006dp,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}.
-This appears in the $k_T$-factorization formula~\cite{Catani:1990eg,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}, which we will discuss later, and plays role similar to that of collinear parton distribution function in the collinear factorization.
-Much effort has been made to study this object, notably the work of Balistky, Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross sections with $1/x$.
-However, such rise violates unitarity and the Froissart bound~\cite{roberts_1990,collins_2011,Kovchegov:2012mbw,Barone:1993sy}.
-In \cite{Gribov:1983ivg} it has been recognized that gluon recombination can tame the growth of gluons \cite{Gribov:1983ivg}.
-The interplay of linear and nonlinear term leads to an phenomenon called gluon saturation.
-\comment{a line mentioning BK is removed.
-Is there a particular reason not to mention BK or simply GLR replaced them?
-}%
-{\color{gray}Similarly, the work of Balitsky and Kovchegov (BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} incorporated the gluon recombination in the evolution in the dipole formalism, thus successfully incorporating the saturation.}
- The meaning of the Froissart bound is that, asymptotically, the cross section can not grow faster than the size of black-disk (proton with high gluon density) which expands like $\ln(s)$~\cite{Badelek:1992gs}.
-Despite the success of such evolution equations, there are several popular phenomenological models owing to their simplicity.
 
-\sout{\comment{Some more general talk like in the previous paper}\\ }
-\sout{\comment{EIC} }
+Factorization of scales plays central role in {\it Quantum Chromodynamics}
+(QCD). In particular, within collinear factorization approach, long-distance
+effects can be isolated into objects called {\it collinear parton distribution
+functions}~(PDFs)~\cite{Roberts:1990ww,Collins:2011zzd}.  The collinear PDFs are not
+fully perturbatively calculable but they obey perturbative evolution equations
+and are process independent~\cite{Collins:2011zzd}. That is to say that one needs
+to measure them in experiments, but the PDFs obtained in one experiment can be
+used as input in another.
 
-In the next section, differences of the $k_T$-factorization and the dipole-factorization are outlined.
-In Sec.~\ref{Results}, results of the new fit to HERA data in the $k_T$-factorization formula are presented and discussed.
-In Sec.~\ref{Dijet process at EIC}, we apply the results to compute cross section for the dijet process in DIS at the Electron-Ion Collider (EIC)~\cite{NAP25171} and make comparisons with Ref.~\cite{vanHameren:2021sqc}.\\
+One of the main type of processes that is suited particularly well to the studies
+of proton structure is the {\it deep inelastic
+scattering}~(DIS)~\cite{Roberts:1990ww,Collins:2011zzd}. The data from HERA has
+enabled us to answer many questions in that domain and largely improved our
+picture of interior of a proton. 
+It is therefore very exiting that the next generation of a DIS machines,
+the election-ion collider~(EIC)~\cite{NAP25171} is making its way and will soon
+allow us to uncover more details about the hadron structure.
+
+With an increase of the of the center of mass energy at fixed value of the
+photon virtuality, $Q$, one shall probe  the region of the small Bjorken scaling
+variable, $x$.  
+In that region, dominated by gluons\cite{Roberts:1990ww,Collins:2011zzd,
+Kovchegov:2012mbw}, the appropriate theoretical formalism to use is the Color
+Glass Condensate~\cite{McLerran:1993ni, Ayala:1995kg, Kovchegov:1996ty,Jalilian-Marian:1996mkd,Iancu:2000hn,Iancu:2001ad,Ferreiro:2001qy,Iancu:2002xk} or, if the density of gluons is still moderate, the
+High Energy Factorization also called $k_T$-factorization~\cite{Catani:1990xk,Catani:1990eg,Collins:1991ty,Catani:1993ww,Catani:1993rn,Catani:1994sq}.
+
+In the above frameworks, the interaction of the photon with gluons happens
+through a box of quarks, as depicted in Fig.~\ref{fig:gluon-kinem}. An object,
+which is central to the description of this process is called the dipole gluon
+density, $\fdp(x,k_T^2)$, which is a type of {\it transverse momentum
+dependent} PDFs (TMD
+PDFs)~\cite{Bomhof:2006dp,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. 
+%
+It appears in the $k_T$-factorization
+formula~\cite{Catani:1990eg,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya},
+which we shall discuss in the next section, and plays a role similar to that of
+the collinear parton distribution function in the collinear factorization.
+
+Much effort has been made
+to study this object, notably the work of Balitsky, Fadin, Kuraev and Lipatov
+(BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross
+sections with $1/x$.  However, such rise violates unitarity and the Froissart
+bound~\cite{Roberts:1990ww,Collins:2011zzd,Kovchegov:2012mbw,Barone:1993sy}. In
+\cite{Gribov:1983ivg} it has been recognized that gluon recombination can tame
+the growth of gluons \cite{Gribov:1983ivg}. The interplay of linear and
+nonlinear terms leads to a phenomenon called {\it gluon saturation} and
+corresponding evolution equations are known as
+Balitsky-Kovchegov~(BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} equation or
+JIMWLK\cite{Kovner:1999bj,Kovner:2000pt,Iancu:2000hn,JalilianMarian:1997dw,JalilianMarian:1997gr,JalilianMarian:1997jx} equation.
+
+Due to its clear picture, one often uses a position space counter part of the gluon density, called {\it dipole cross section}.
+Despite the success of the aforementioned evolution equations, there exists a number of phenomenological models of the dipole cross section, which are popular due to to their simplicity.
+\commentPending{More about saturation models}
+A notable example of a dipole saturation model is the one proposed by
+Golec-Biernat and Wu\"sthoff (GBW)~\cite{Golec-Biernat:1998zce} and the one proposed by
+Bartels, Golec-Biernat and Kowalski (BGK)~\cite{Bartels:2002cj}.
+We will use these two models in this study.
+There are other models, with different considerations, such as impact parameter dependence~({\it cf.}
+\cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}).
+
+\commentPending{Section about what we did: fits of saturation models with exact
+kinematics, use of those results + Sudakov for EIC predictions.}
+
+In the present study, we fit the GBW~\cite{Golec-Biernat:1998zce} and BGK~\cite{Bartels:2002cj} models in the $k_T$ factorization formula of $F_2$, instead of the original dipole factorization formula.
+As discussed below, this allows us to fit the model with exact gluon kinematics.
+Since inclusive observables do not reveal the $k_T$ dependence well, we also consider a less inclusive observable which is more sensitive to the $k_T$ dependence of the gluon distribution.
+The resulting models are put to the test by applying them to the predictions of dijet DIS at EIC, including effects of the Sudakov form factor, which resums logarithms of the small transverse momentum.
+
+The paper is organized as follows.  In the next section, we present theoretical
+framework which we used and, in particular, outline differences of the
+$k_T$-factorization and the dipole-factorization.  In
+Sec.~\ref{sec:F2fits}, results of the new fits to HERA data in the
+$k_T$-factorization formula are presented. 
+In Sec.~\ref{sec:dijetsEIC}, we apply the results from the previous section to
+compute distributions for dijet production in DIS at the Electron-Ion Collider
+(EIC)~\cite{NAP25171} and make comparisons to our earlier study of Ref.~\cite{vanHameren:2021sqc}.
 
@@
 \section{The framework}
-
-A notable example is the Golec-Biernat--W\"sthoff saturation model~\cite{Golec-Biernat:1998zce}~(also \cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}).
-The model was originally proposed in the position space version of the $k_T$-factorization formula, and the object which corresponds to the gluon density of the $k_T$-factorization is called dipole cross section.
+\commentPending{Missing a general factorization formula}
+In general, a factorization formula has the form
+\begin{equation}
+    \sigma=H \otimes \phi,
+\end{equation}
+where $\otimes$ denotes convolution.
+In this form one achieves two things.
+Firstly, one can confine long distance effects in one of the factors (let $\phi$ be such an object), and leaves $H$ as an perturbatively calculable object.
+Secondly, one may factorize out a (to some extent) process independent object.
+In the present study, the dipole cross section and the gluon densities both  contain nonperturbative part and are, to an extent, process independent~\footnote{They are not universal, however they may appear in different processes.
+(see for example Refs.~\cite{Dominguez:2011wm,Kotko:2015ura})}.
+In this section, we will outline two factorizations; the $k_T$ factorization and the dipole factorization. \\
+As it was mentioned earlier, we use the GBW and BGK models.  
+The models were originally formulated in the position-space version of the
+$k_T$-factorization formula. %, and the object which corresponds to the gluon
+%density of the $k_T$-factorization is called the dipole cross section. 
 In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
 \begin{align}
+\label{eq:gbw-dipole}
 \sigma_{\mathrm{GBW}}(x,r)&=\sigma_0\left(1-e^{-r^2/R^2_0}\right)&\mathrm{where}&
@@
 \end{align}
-%\comment{here I use $R_0$ instead of $Q_s$ since for BGK below, $Q_s\neq 1/R_0$. }
-The dipole cross section is related to the gluon density by the Fourier transform: 
+%
+The dipole cross section is related to the gluon density by the Fourier
+transform
+%
 \begin{equation}
-\alpha_s\mathcal{F}(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
+\alpha_s\fdp(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
 \label{eq:dipole-gluon}
 \end{equation}
-%An important feature of the GBW model is that it describes the phenomenon of saturation in a simple form. 
-The essence of GBW model is encoded in the $x$-dependent saturation scale $Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and the scaling region.
-A further development was made by Bartels, Golec-Biernat and Kowalski~(BGK)~\cite{Bartels:2002cj} which incorporates the DGLAP evolution by modifying the exponent to 
+%
+The essence of the GBW model is encoded in the $x$-dependent saturation scale
+$Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and
+the scaling region.  A extension of the above model was proposed by Bartels, Golec-Biernat
+and Kowalski~(BGK)~\cite{Bartels:2002cj} who incorporated the DGLAP evolution
+in the GBW cross section~(\ref{eq:gbw-dipole}) by modifying the exponent to 
+%
 \begin{equation}
@@
 \end{align}
+%
 thus improving the description of data at higher $Q^2$.\\
-While these models enjoyed much success in phenomenology of DIS, including the diffractive and photo-production processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, as later discussed in detail, derivation of the dipole-factorization formula from the $k_T$-factorization involves with certain simplification and introduction of massive light quarks.
 
-Now, let us introduce $q'\equiv q+x p$. 
-Then, one  decomposes $k$ and $\kappa$ (Fig.~\ref{fig:gluon-kinem}) as
+While these models enjoyed much success in phenomenology of DIS, including the
+diffractive and photo-production
+processes~\cite{Golec-Biernat:1998zce,Golec-Biernat:1999qor}, it is worth
+mentioning that they both use certain kinematic approximation which follows from
+subtle differences in the dipole factorization and the $k_T$-factorization.  In
+the following, we will investigate effects of these approximations.
+
+Firstly, let us outline the factorization formulas.
+With $q'\equiv q+x p$, one decomposes $k$ and $\kappa$, defined in
+Fig.~\ref{fig:gluon-kinem}, as
+%
 \begin{align}
@@
 \begin{multline}
-	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \mathcal{F}(x/z,k_T^2)\Theta(1-x/z)\\
+	F_2(x,Q^2)=\sum_f e_f^2 \frac{Q^2}{2\pi}\int\frac{dk^2_t}{k_T^2}\int^1_0d\beta\int d{\kappa'}_t\alpha_s(\mu^2) \fdp(x/z,k_T^2)\Theta(1-x/z)\\
 	\left[\left(\beta^2+(1-\beta)^2\right)\left(\frac{I_1}{2\pi}-\frac{I_2}{2\pi}\right)
@@
 \begin{equation}
-	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}.
+	\frac{1}{z}=1+\frac{{\kappa'}^2_t+m_f^2}{\beta(1-\beta)Q^2}+\frac{k^2_t}{Q^2}\,.
 	\label{eq:z}
 \end{equation}
-(see Ref.~\cite{ Kimber:2001uaa,Kwiecinski:1997ee} for detail.)
-\sout{\color{red} We need an appendix with expressions for $I_i$}
-%and
 
-%Hereafter, we will call Eq.~(\ref{eq:angle-integrated}) $k_T$-factorizaton formula.
-One should note, that gluons are not probed directly, thus the argument of the gluon density is $x/z$ rather than $x$.
-If one, instead, uses $ 1/z=\left(1+4 m_f^2/Q^2\right)$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, 
-the above formula can be written in the impact parameter space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} (i.e. dipole-factorizaton formula)
+One should note, that gluons are not probed directly, thus the argument of the
+gluon density is $x/z$ rather than $x$.  If one, instead, uses $ 1/z=1+4
+m_f^2/Q^2$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, the
+above formula can be written in the impact parameter
+space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} ({\it i.e.} as a
+dipole-factorization formula)
+%
 \begin{equation}
-F_2\left(x,Q^2\right)\sim\int^1_0d\beta \int d^2\mathbf{r}\left|\Psi\left(\tilde{x},\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(\tilde{x},r\right),
+  F_2\left(x,Q^2\right)=\sum_f e_f^2 \frac{Q^2}{4\pi^2} \int^1_0d\beta \int \frac{d^2\mathbf{r}}{(2\pi)^2} \left|\Psi\left(\tilde{x},\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(\tilde{x},r\right),
   \label{eq:dipole-factorization}
 \end{equation}
-where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$, describes splitting of the incoming photon into a $q\overline{q}$ pair with light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole cross section, $\sigma_{\mathrm{dipole}}\left(x,r\right)$, describes the interaction of the colour dipole of the size $r$ with the proton.
-In Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero vale of $m_f$ was used even for light flavours, which is necessary to partially substitute $k_T$ and ${\kappa'}_T$ in Eq~(\ref{eq:z}).
-\\
 
-The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}).
-In this study, we use Eq.~(\ref{eq:angle-integrated}), where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
-Comparing, the GBW and BGK models, one identifies that, the GBW model is effectively the BGK model with $\alpha_s(\mu^2)xg(x,\mu^2)\rightarrow \alpha_s(Q_0^2)xg(x,Q_0^2)$.
-For this reason, we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is constant for the GBW model, and thus explicitly multiply by running coupling;
+where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$,
+describes splitting of the incoming photon into a $q\overline{q}$ pair with
+light-cone momenta fractions $\beta$ and $1-\beta$ respectively, and the dipole
+cross section, $\sigma_{\mathrm{dipole}}\left(\tilde x,r\right)$, describes the
+interaction of the colour dipole of the size $r$ with the proton. In
+Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero value
+of $m_f$ was used even for light flavours, which is necessary to partially
+substitute $k_T$ and ${\kappa'}_T$ in Eq.~(\ref{eq:z}).
+%The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}), while 
+In the present study, we use Eq.~(\ref{eq:angle-integrated}) to fit the models, where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
+%Comparing, the GBW and BGK models, one identifies that, the GBW model is effectively the BGK model with 
+%\begin{equation}
+%\begin{split}
+%    \alpha_s(\mu^2)xg(x,\mu^2)\rightarrow &\alpha_s(Q_0^2)xg(x,Q_0^2)\\
+%    &=\alpha_s x^{-\lambda}(1-x)^{5.6}.
+%\end{split}
+%\end{equation}
+\commentPending{??}{\color{blue}response: the argument on why we consider $\alpha$ as a constant is removed, as it is not a solid argument.}
+%For this reason,
+In order to account for the running coupling in Eq.~(\ref{eq:angle-integrated}), 
+we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is
+constant for the GBW model, and thus explicitly multiply by the running coupling
 %
 \begin{equation}
-\alpha_s(\mu^2)\mathcal{F}(x,k_T^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\mathcal{F}(x,k_T^2)}{0.2},
+\alpha_s(\mu^2)\fdp(x,k_T^2)\rightarrow \alpha_s(\mu)\frac{\alpha_s\fdp(x,k_T^2)}{0.2},
 \end{equation}
-where %0.2 is an arbitrary normalization, and 
+where
 %
-\comment{Question: alphas=0.2}
-
 \begin{equation}
@@
 and  $\Lambda_{\mathrm{QCD}}^2=0.09\;\GeV^2$.
-The factor 0.2 is an arbitrary normalization and the effect is absorbed by $\sigma_0$ and hence, bears no importance.
-(For a more detailed analysis of dipole gluon density from the BGK model see.
-Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
+
+The factor 0.2 is an arbitrary normalization whose effect is absorbed by $\sigma_0$ and hence, bears no importance.
+(For a more detailed analysis of the dipole gluon density from the BGK model see Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
 Their treatment is also different from the original BGK paper~\cite{Bartels:2002cj}.
@@
 \section{Fits to $F_2$ data}
-\label{Results}
+\label{sec:F2fits}
 
-The GBW and BGK models were fitted to the $F_2$ data from HERA~\cite{Abt:2017nkc}.
-A numerical program was written with help of CERNLIB~\cite{Kolbig:1972zz}, GSL~\cite{GSL}, CUBA~\cite{Hahn:2004fe} and ROOT~\cite{Brun:1997pa} libraries to evaluate $F_2$.
-The data were selected to be in the range $0.045\leq Q^2\leq 650\;\mathrm{GeV^2}$, $x<0.01$.
-As with the previous fit~\cite{Goda:2022wsc}, the $c$ and $b$ flavours were taken into account with the mass $1.3$ and $4.6\;\mathrm{GeV}$, respectively.
-As discussed earlier, we take the light quarks to be massless.
-The fitting was performed using MnMigrad and MnSimplex of ROOT::Minuit2~\cite{James:2004xla}.
+We fitted the GBW and BGK models to the $F_2$ data from
+HERA~\cite{Abt:2017nkc}. A numerical program was written with help of
+CERNLIB~(DPSIPG)~\cite{Kolbig:1972zz}, GSL~\cite{GSL}, CUBA~\cite{Hahn:2004fe}
+and ROOT~\cite{Brun:1997pa} libraries to evaluate $F_2$. The data were selected
+to be in the range $0.045\leq Q^2\leq 650\;\mathrm{GeV^2}$, $x<0.01$.  As with
+the previous fit~\cite{Goda:2022wsc}, the $c$ and $b$ flavours were taken into
+account with the mass $1.3$ and $4.6\;\mathrm{GeV}$, respectively. As discussed
+earlier, we take the light quarks to be massless.  The fitting was performed
+using MnMigrad and MnSimplex of ROOT::Minuit2~\cite{James:2004xla}.
 
-The fits were performed for the following cases
+We studied the following cases
+%
 \begin{itemize}
@@
 \end{itemize} 
-and, as a reference, we provide the following results from Ref.~\cite{Goda:2022wsc};
+%
+and, as a reference, we provide the following results from
+Ref.~\cite{Goda:2022wsc};
+%
 \begin{itemize}
 \item GBW model with massless light quarks in the dipole-factorization ($r$-GBW),
-\item GBW model with massive light quarks in the dipole-factorizations ($r$-GBW-massive),
+\item GBW model with massive light quarks in the dipole-factorization ($r$-GBW-massive),
 \item  BGK model in  the dipole-factorization ($r$-BGK).
@@
 
-The results of fits are summarized in Tab.~\ref{tab:table}. 
+The results of the fits are summarized in Tab.~\ref{tab:table}. 
 The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
-It was pointed out in Ref.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
+This is in line with the observation made in Refs.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
 
@@
 While the GBW model remains almost unaffected, the BGK model seems to show slightly more change. The difference in $\sigma_0$ is similar to that of GBW model, and other parameters changed moderately.
-\sout{\comment{Describet what's in the figuers...} }
-In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole gluon density and the saturation scale for the GBW and BGK models are shown.
-The dipole cross section and the gluon density are both normalized by $\sigma_0$ in order to see the effects  of other parameters better,
-and the saturation scale is defined as a ridge of the dipole gluon density on the $(x,k_T^2)$ plane.\\
-One can see, in the plots on the left side, the effects of the changes (or rather no changes) in the parameters of the GBW model.
-The difference between the rc-$k_T$-GBW and $r$-GBW are negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.\\
+
+In Fig.~\ref{fig:GBW-BGK}, the plots of the dipole cross section, the dipole
+gluon density and the saturation scale for the GBW and BGK models are shown. The
+dipole cross section and the gluon density are both normalized by $\sigma_0$ in
+order to see the effects  of other parameters better, and the saturation scale
+is defined as a ridge of the dipole gluon density in the $(x,k_T^2)$ plane.
+
+In the plots on the left side, one can see the effects of the changes in the parameters of the GBW model.
+The difference between the rc-$k_T$-GBW and $r$-GBW are negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.
+
 On th right side of Fig.~\ref{fig:GBW-BGK}, the same plots for the BGK model are shown.
@@
 Nevertheless, the difference is more prominent in the small-$x$ region.
+
 Comparisons of the results with the $F_2$ data are shown in Figs.~\ref{fig:GBW-Grid} and~\ref{fig:BGK-Grid}.
@@
   models. Note, the dipole cross section and the gluon density are normalized by
-  $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
+  $\sigma_0^{-1}$.} 
 \label{fig:GBW-BGK}
@@
 \end{figure}
-For the rest of this section, let us have a closer look at $\sigma_0$. 
-Recalling that the difference between the $k_T$-factorization formula and the dipole-factorization formula is in $x/z$, where this enters in the GBW formalism as $\tilde{x}$.
-It is easy to see that, as $x$ grows, the dipole cross section gets suppressed (Keeping in mind the suppression by the photon wave function in the large-$r$ region.).
-Such effect was discussed previously in Ref.~\cite{Kutak:2004ym} in the context of the BK equation.
-In fact, this suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for such modification of $x$, so that in the small-$Q^2$ limit, the total cross section remains finite.
-Since 
+
+Let us now take a closer look at the parameter $\sigma_0$. Recall that the
+difference between the $k_T$-factorization formula and the dipole-factorization
+formula is in $x/z$, Eq.~(\ref{}), and this enters in the GBW formalism as
+$\tilde{x}$. It is easy to see that, as $x$ grows, the dipole cross section gets
+suppressed. (Keeping in mind the suppression by the photon wave function in the
+large-$r$ region.) Such effect was discussed previously in
+Ref.~\cite{Kutak:2004ym} in the context of the BK equation. In fact, this
+suppression is the motivation given in Ref.~\cite{Golec-Biernat:1998zce} for
+such modification of $x$, so that in the small-$Q^2$ limit, the total cross
+section remains finite. Since 
+%
 \begin{equation}
@@
 \end{equation}
-the $k_T$-factorization case receives more suppression. Consequently, the normalization factor $\sigma_0$ rises to compensate the suppression. 
-Therefore, one can understand the change in $\sigma_0$ as a direct consequence of the key difference between the $k_t$-factorization and the dipole-factorization.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-\section{Dijet process at EIC}
-\label{Dijet process at EIC}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+the $k_T$-factorization case receives more suppression. Consequently, the
+normalization factor $\sigma_0$ rises to compensate the suppression.  Therefore,
+one can understand the change in $\sigma_0$ as a direct consequence of the key
+difference between the $k_T$-factorization and the dipole-factorization.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Dijet production at EIC}
+\label{sec:dijetsEIC}
 
@@
     \end{subfigure}
-    \caption{\footnotesize Weizs\"acker-Williams gluon density at $x=10^{-3}$.
+    \caption{ Weizs\"acker-Williams gluon density at $x=10^{-3}$.
 Top row: comparison of the dipole-factorization fit and $k_T$-factorization fit results.
-Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
+Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.
 }
@@
 
-In order to study the $k_T$-dependence better we investigate less inclusive processes.
-To this end, we will apply the obtained dipole cross section to the electron-dijet correlation at the electron-ion collider~(EIC), following closely the method of Ref.~\cite{vanHameren:2021sqc}.
-At the leading order, the dijet DIS in small-$x$ limit is dominated by $q\overline{q}$ jets~\cite{}.
-This process is therefore closely related to the dipole picture we discussed earlier (see.
-Ref.~\cite{Dominguez:2011wm}).
-In the Breit frame where the photon momentum is $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance $p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon transverse momentum $k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.
-This makes dijets an interesting observable.
-For the region where $p_T\ll P_T\sim p_{1T},\,p_{2T}$, one may use power counting to take leading order in $p_T/P_T$, which leads to the transverse-momentum-dependent~(TMD) factorization .
+The $F_2$ structure function is an inclusive object and is weakly sensitive to
+the shape of the gluon density. To probe the latter, we shall now 
+apply the dipole cross section obtained to the electron-dijet correlation at the
+electron-ion collider~(EIC), following closely the method of
+Ref.~\cite{vanHameren:2021sqc}.
 
-\sout{\comment{process}}
+We consider dijet production in DIS
+%
+\begin{equation}
+  %\label{eq:}
+  e+p\rightarrow e+J_1+J_2+X\,,
+\end{equation}
+%
+At the leading order, in the small-$x$ limit, this process is
+dominated by $q\overline{q}$ jets~\cite{Dominguez:2011wm}.  It is
+therefore closely related to the dipole picture we discussed earlier. In the Breit frame, where the photon momentum is
+given by $q=(0,0,0,Q)$, at the leading order, the jets momentum imbalance
+$p_T\equiv\left|p_{1T}+p_{2T}\right|$ equals the gluon transverse momentum
+$k_T$, where $p_{1T}$ and $p_{2T}$ are transverse momenta of the jets.  This
+makes dijets an interesting process. For the region where $p_T\ll P_T\sim
+p_{1T},\,p_{2T}$, one may use power counting to take leading order in $p_T/P_T$,
+which leads to the transverse-momentum-dependent~(TMD) factorization.
 
-\sout{\comment{factorization formula for dijets in DIS involving WW gluon}}
+\commentPending{mention why Sudakov is important for dijet production}\\
+{\color{blue} There is a line before Eq.~(\ref{eq:ww-sud}) ?}
 
-\sout{\comment{mention why Sudakov is important for dijet production}}
-
-In the large-$N_c$ limit of the TMD factorization, there are two types of gluon densities, namely the dipole gluon density and the Weizs\"acker-Williams (WW) gluon density~\cite{Dominguez:2010xd,Dominguez:2011wm,vanHameren:2016ftb,Xiao:2017ggh}.
-It was shown in Ref.~\cite{Dominguez:2011wm}, that the dijet process in DIS can directly probe the WW gluon,$\fww(x,k^2)$, where the differential cross section factorizes as
+In the large-$N_c$ limit of the TMD factorization, there are two types of gluon
+densities, namely the dipole gluon density and the Weizs\"acker-Williams (WW)
+gluon
+density~\cite{Dominguez:2010xd,Dominguez:2011wm,vanHameren:2016ftb,Xiao:2017ggh}.
+It was shown in Ref.~\cite{Dominguez:2011wm}, that the dijet process in DIS can
+directly probe the WW gluon, $\fww(x,k^2)$, where the differential cross section
+factorizes as
+%
 \begin{equation}
-	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g\rightarrow q\overline{q}},
+	\frac{d\sigma^{\gamma^*p\rightarrow q\overline{q}X}}{d \mathrm{P.S.}}=\fww(x,k_T^2)H_{\gamma^*g^*\rightarrow q\overline{q}},
         \label{eq:TMD}
 \end{equation}
-with the hard function $H_{\gamma^*g\rightarrow q\overline{q}}$ describing interactions of an off-shell photon with an on-shell gluon producing a $q\overline{q}$ pair.
-$\fww(x,k^2)$, has an interpretation as a number density of gluons inside a proton, while $\fdp(x,k_T^2)$ does not have such an interpretation~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
+%
+with the hard function $H_{\gamma^*g^*\rightarrow q\overline{q}}$ describing
+interactions of an off-shell photon with an off-shell gluon producing a
+$q\overline{q}$ pair.  $\fww(x,k^2)$, has an interpretation as a number density
+of gluons inside a proton, while $\fdp(x,k_T^2)$ does not have such an
+interpretation~\cite{Dominguez:2010xd,Dominguez:2011wm,Xiao:2017ggh}.
 
-Under the Gaussian approximation and assuming $\theta$-like profile of the proton, one can write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
+We carry out our study in the framework of the {\it Improved
+Transverse-Momentum-Dependent} (ITMD)
+factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.  The latter is
+implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we use to
+compute the cross sections.  The ITMD factorization is an generalization of the
+TMD factorization where the momentum
+imbalance in TMD is restricted to be
+small~\cite{Kotko:2015ura,vanHameren:2016ftb}. That is to say ITMD resums
+$(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus
+extends the region of applicability up to $k_T\sim P_T$. The difference of
+Eq.~(\ref{eq:TMD}) from the regular TMD is that the hard function has an
+off-shell gluon $g^*$, thus rendering the $k_T$ dependence in the hard function
+as well~\cite{Kotko:2015ura}.
+
+Under the Gaussian approximation and assuming $\theta$-like profile of the
+proton, one can
+write~\cite{vanHameren:2016ftb,Xiao:2017ggh,Dominguez:2010xd,Dominguez:2011wm}
+%
 \begin{equation}
@@
 
-For the region where TMD factorization is applicable, $Q_s\sim k_T\ll P_T\sim Q$, one needs to resum the large Sudakov logarithms $\log(k_T/Q)$, as well as $\log(1/x)$~\cite{Dominguez:2011wm}. 
-It was shown in Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent resummation of such logarithms are possible owing to the separation of corresponding regions.  
-Resummation of the Sudakov logarithms is achieved by the formula~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya}
+For the region where TMD factorization is applicable, $Q_s\sim k_T\ll P_T\sim
+Q$, one needs to resum the large Sudakov logarithms $\log(k_T/Q)$, as well as
+$\log(1/x)$~\cite{Dominguez:2011wm}. It was shown in
+Refs.~\cite{Mueller:2012uf,Mueller:2013wwa,Xiao:2017yya} that consistent
+resummation of such logarithms is possible owing to the separation of
+corresponding regions.  Resummation of the Sudakov logarithms is achieved by the
+formula
+%
 \begin{equation}
@@
 \end{equation}
+%
 where, we use the Sudakov form factor~\cite{Mueller:2013wwa,Xiao:2017yya},
+%
 \begin{equation}
@@
 \end{equation}
-in which $\gamma_E$ is the Euler-Mascheroni constant, and we use $\alpha_s=0.2$.
-
-The present study is carried out in the framework of small-$x$-Improved Transverse-Momentum-Dependent (ITMD) factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.
-ITMD factorization is implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we will use to compute the cross section. 
-ITMD is an generalization of TMD where the momentum imbalance in TMD is restricted to be small~\cite{Kotko:2015ura,vanHameren:2016ftb}.
-That is to say ITMD resums $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus extends the region of applicability up to $k_T\sim P_T$.
-In other words, the hard function in Eq.~(\ref{eq:TMD}) no longer has the on-shell gluon, but instead has an off-shell gluon $g^*$, thus rendering the $k_T$ dependence in the hard function as well~\cite{Kotko:2015ura}.
-
-%It was discussed in Ref.~\cite{vanHameren:2021sqc}, that with the above points and the fact that genuine twists are suppressed when transverse momenta are large \comment{Also, $Q$ but as it was also said, that Q is low here(p.5,\cite{vanHameren:2021sqc}.
-)  Also it was mentioned the cut on $p_T$ is selected for this.
-I assume it is $p_{1T}, p_{2T}$ that are relevant?}, ITMD is suitable for studying dijets.
-
-Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of jets and the final state electron in DIS ($e+p\rightarrow e+J_1+J_2+X$), where it was argued that this observable is sensitive to the soft emissions and the saturation effects.
-However, in this study, we will not test the saturation effect~(\textit{i.e.}, $A$ dependence), and focus only on the proton case.
-The kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
+%
+in which $\gamma_E$ is the Euler-Mascheroni constant, and we set $\alpha_s=0.2$. 
+Following Ref.~\cite{vanHameren:2021sqc}, we study the azimuthal correlations of
+jets and the final state electron in DIS , where
+it was argued that this observable is sensitive to the soft emissions and the
+saturation effects. In this study we focus only on the proton case.  The
+kinematical cuts suggested in Ref.~\cite{vanHameren:2021sqc} were
+%
 \begin{align*}
@@
 \comment{Question: normalization}
-Grids of the Weizs\"acker-Williams gluon density were produced by evaluating Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).
-The gluon density at $x=10^{-3}$ is plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr} and running-coupling BK~(rcBK) gluon density~\cite{}.
-Clearly, the GBW and BGK models falls much more quickly than the KS and rcBK gluon density.
-In general, expected behaviour in the large-$k_T$ region is $\sim k_T^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm}, while $\sigma_{\mathrm{GBW}}$ behaves like $\sim e^{-k_T^2}$.
-As in Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_T$ region and suppresses in the large-$k_T$ region.
-In other words, it broadens the distribution.
-In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the effect of broadening by the Sudakov factor is significantly more pronounced in the case of the GBW and BGK models.
-The hard-scale-dependent GBW and BGK models, as a consequence, become closer to the KS and rcBK gluons (\textit{cf.} Fig.~2 of Ref.~\cite{vanHameren:2021sqc}).
 
-Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} correspond to Fig.~4 in Ref.~\cite{vanHameren:2021sqc} ($e$-jets azimuthal correlation). 
-In the top row of Fig.~\ref{fig:je-breit}, we see, for both the GBW and BGK models, better agreements of results with the KS and rcBK for the new $k_T$-factorization fits.
-However the overall normalization of the gluon density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
-Nevertheless, it shows clearly the effect of the parameter $\sigma_0$.
-In the middle and the bottom row, it shows the effects of the Sudakov form factor, which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by lowering the cross section.
-Fig.~\ref{fig:je-lab} shows the $e$-jets correlation in the lab frame.
-Here, the difference between KS and GBW and BGK are more prominent, while rcBK shows similar pattern to the GBW and BGK models.
-%Unlike in the previous plots, the new fits in the $k_T$-factorization shows only limited improvement.
-The effects of the Sudakov factor is similar to those in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at smaller $\Delta \phi$ region the effect is reversed (i.e.
-The cross sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here, they are significantly increased).
-\\
-%\comment{regarding this differences between Breit and lab frames, what does "\dots since it (Breit) suppresses the LO contributions, i.e. process dominated by a quark jet." mean?}
+Grids of the Weizs\"acker-Williams gluon density were produced by evaluating
+Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).  The gluon density at $x=10^{-3}$ is
+plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS
+gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr} and running-coupling BK~(rcBK)
+gluon density~\cite{Balitsky:2006wa,Albacete:2010sy}. Clearly, the GBW and BGK models falls much more quickly
+than the KS and rcBK gluon density. In general, expected behaviour in the
+large-$k_T$ region is $\sim k_T^{-2}$~\cite{Dominguez:2010xd,Dominguez:2011wm},
+while $\sigma_{\mathrm{GBW}}$ behaves like $\sim e^{-k_T^2}$.  As in
+Ref.~\cite{vanHameren:2021sqc}, the Sudakov factor enhances in the small-$k_T$
+region and suppresses in the large-$k_T$ region. In other words, it broadens the
+distribution. In comparison to the result of Ref.~\cite{vanHameren:2021sqc}, the
+effect of broadening by the Sudakov factor is significantly more pronounced in
+the case of the GBW and BGK models. The hard-scale-dependent GBW and BGK models,
+as a consequence, become closer to the KS and rcBK gluons, \textit{cf.} Fig.~2
+of Ref.~\cite{vanHameren:2021sqc}.
+
+Figs.~\ref{fig:je-breit} and~\ref{fig:je-lab} show electron-jets azimuthal
+correlation in the Breit and in the lab frame respectively.  In the top row of Fig.~\ref{fig:je-breit}, we see, for both the
+GBW and BGK models, better agreements of results with the KS and rcBK for the
+new $k_T$-factorization fits. However the overall normalization of the gluon
+density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
+Nevertheless, it shows clearly the effect of the parameter $\sigma_0$. In the
+middle and the bottom row, it shows the effects of the Sudakov form factor,
+which qualitatively agrees with that of Ref.~\cite{vanHameren:2021sqc}, by
+lowering the cross section.
+
+Fig.~\ref{fig:je-lab} shows the electron-jets
+correlation in the lab frame. Here, the difference between KS and GBW and BGK
+is more prominent, while rcBK shows similar pattern to the GBW and BGK models.
+The effects of the Sudakov factor is similar to those
+in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at
+smaller $\Delta \phi$ region the effect is reversed ({\it i.e.} the cross
+sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here,
+they are significantly increased).
 
@@
 	\end{subfigure}
-	\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the Breit frame.
+	\caption{ Azimuthal correlation of the jets and the scattered electron in the Breit frame.
 Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.}
 	\label{fig:je-breit}
@@
 	\end{subfigure}
-\caption{\footnotesize Azimuthal correlation of the jets and the scattered electron in the lab frame.
+\caption{ Azimuthal correlation of the jets and the scattered electron in the lab frame.
 Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.}
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.}
 \label{fig:je-lab}
@@
 
-Finally, Fig.~\ref{fig:jj-breit} shows the jet-jet correlations in the Breit frame.
-Again, the GBW and BGK models show considerable deviation from the KS gluon.
-The difference from the previous plot is the disagreement of the GBW/BGK models and the rcBK in the small-$\Delta\phi$ region.
-Similarly to the previous plots, the Sudakov factor affects the models somewhat differently from the KS gluon in Ref.~\cite{vanHameren:2021sqc}.
-The effect enhances the cross section considerably in the small-$\Delta\phi$ region, making it closer to KS gluon result.
-The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are natural as back-to-back configuration in the respective observable corresponds to the small-$k_T$ region of gluon densities, and as it can be seen clearly in Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in the large-$k_T$ region.
-That is to say that the enhancement in the small-$\Delta\phi$ region is a direct consequence of the broadening by the Sudakov factor.
+Finally, Fig.~\ref{fig:jj-breit} shows the jet-jet correlations in the Breit
+frame. Again, the GBW and BGK models exhibit considerable deviation from the KS
+gluon. The difference from the previous plot is the disagreement of the GBW/BGK
+models and the rcBK in the small-$\Delta\phi$ region. Similarly to the previous
+plots, the Sudakov factor affects the models somewhat differently from the KS
+gluon in Ref.~\cite{vanHameren:2021sqc}.  The effect enhances the cross section
+considerably in the small-$\Delta\phi$ region, making it closer to KS gluon
+result.
+
+The results shown in Figs.~\ref{fig:je-lab} and~\ref{fig:jj-breit} are
+natural as back-to-back configuration in the respective observable corresponds
+to the small-$k_T$ region of gluon densities, and as it can be seen clearly in
+Fig.~\ref{fig:ww}, the GBW and BGK gluons do not fare well in the large-$k_T$
+region.  That is to say that the enhancement in the small-$\Delta\phi$ region is
+a direct consequence of the broadening by the Sudakov factor.
 
@@
 	\end{subfigure}
-\caption{\footnotesize Azimuthal correlation of the jets in the Breit frame.
+\caption{Azimuthal correlation of the jets in the Breit frame.
 Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
 Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{}.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.
 }
@@
 
-\comment{Question: rcBK}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
 
-\comment{Question: what about pieces of derivation removed from the main part?}
+We have fitted the GBW and BGK saturation models to HERA data~\cite{Abt:2017nkc}
+using the $k_T$-factorization for the structure function $F_2$.  The main
+difference between the $k_T$- and the dipole-factorizations is an argument of
+the gluon, that is $x/z$ appearing in the former being replaced by
+$x(1+4m_f^2/Q^2)$ in the latter. 
+%
+In fact the massive light quarks used in
+Ref.~\cite{Golec-Biernat:1998zce} partially simulate the factor $1/z$, and our 
+fit result indicates such effect, as expected.
 
-\section{Summary}
-We have fitted the GBW\cite{Golec-Biernat:1998zce}
-and BGK~\cite{Bartels:2002cj} models to HERA
-data~\cite{Abt:2017nkc} in the context of the $k_T$-factorization of $F_2$.  The
-main difference between the $k_T$- and dipole-factorizations is an argument of
-the gluon, that is, $x/z$ being replaced by $x(1+4m_f^2/Q^2)$ in the
-dipole-factorization. It was discussed that massive light quarks used in
-Ref.~\cite{Golec-Biernat:1998zce} partially simulates the factor $1/z$, and the
-fit result indicates such effect as expected. It is quite remarkable that with
-such simplicity, the dipole-factorization can reproduce the result of the
-$k_T$-factorization formula well.
-The only major difference is in the normalization parameter $\sigma_0$ which increases significantly for the $k_T$-factorization case.
-It was also observed that the explicit inclusion of the running coupling has significant effect in the fit quality particularly in the large-$Q^2$ region where the GBW model performs poorly.
+It is quite remarkable that with such simplicity, the dipole-factorization can
+reproduce the result of the $k_T$-factorization formula well. We have found that
+the only major difference is in the normalization parameter $\sigma_0$ which
+increases significantly for the $k_T$-factorization case. We have also observed
+that the explicit inclusion of the running coupling has significant effect on
+the fit quality, particularly in the large-$Q^2$ region, where the GBW model
+performs poorly.
 
-We have applied the new result for the prediction of the dijet process in DIS at EIC.
-Additionally, effects of the Sudakov form factor were investigated.
-Results of the $e$-jets correlation in the Breit frame agree qualitatively to that of Ref.~\cite{vanHameren:2021sqc}.
-Other results, namely the $e$-jets in the lab frame and the jet-jet correlation in the Breit frame, show considerable effects of the Sudakov form factor which broaden the gluon density.
+We have applied the new result from our fits for the prediction of the dijet
+process in DIS at EIC. Additionally, effects of the Sudakov form factor were
+investigated for that process. Results of the electron-jets correlation in the
+Breit frame agree qualitatively to those of Ref.~\cite{vanHameren:2021sqc}.
+Other results, namely the electron-jets in the lab frame and the jet-jet
+correlation in the Breit frame, show considerable effects of the Sudakov form
+factor which broaden the gluon density.
 
+\comment{A few more closing sentences. (SS)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgment}
-\comment{Add what we had in the previous paper}
-We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren for the clarification of details of Ref.~\cite{vanHameren:2021sqc} and the use of the KaTie package.
-The project is partially supported by
-the European Union’s Horizon 2020 research and innovation program under grant agreement No. 824093.
-TG and SS are partially supported by the Polish National Science Centre grant no. 2017/27/B/ST2/02004.
-KK acknowledges the support of The Kosciuszko Foundation for the Academic year 22/23 for the
-project ”Entropy of dense system of quarks and gluons”.% Furthermore, KK  acknowledges the hospitality of the Nuclear Theory group at the BNL, where part of the  project was realized.
+We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and
+for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren
+for the clarification of details of Ref.~\cite{vanHameren:2021sqc} and 
+usage of the KaTie package. The project is partially supported by the European
+Union’s Horizon 2020 research and innovation program under grant agreement No.
+824093.  TG and SS are partially supported by the Polish National Science Centre
+grant no. 2017/27/B/ST2/02004.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
 \section{$I_i$ in Eq.~(\ref{eq:angle-integrated})}
-$I_1,\, I_2,\,  I_3,\,  I_4$ in Eq.~(\ref{eq:angle-integrated}) are defined in Ref.~\cite{Kimber:2001uaa} as
+
+The functions $I_1,\, I_2,\,  I_3,\,  I_4$ used in
+Eq.~(\ref{eq:angle-integrated}) are defined  as~\cite{Kimber:2001uaa}
+%
 \begin{equation}
@@
 \end{equation}
+%
 for
+%
 \begin{equation}
@@
 \end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newpage
 \bibliographystyle{unsrt}

### 2023-05-08 saturation-ver3/Functions/main.cc

@@ -232,8 +232,9 @@ int main(int argc, char** argv){
 	printf("***************************\n");
 	goal=10;
 	for(int k=0;k<5;k++){
-		Fix_Release(min, theFCN, N_PAR-skip, 0, goal);
-
+		Fix_Release(min, theFCN, N_PAR-skip, 1, goal);
+		
+		save_res(((std::string)argv[1])+"/result.txt",&min,&theFCN,N_PAR-skip);	
 		if(min.IsValid()&&(min.UserState().CovarianceStatus()==3 )){
 			printf(" %.3e/%.3e = %.3e\n", min.UserState().Edm(),  (min.UserState().Fval()),min.UserState().Edm()/ (min.UserState().Fval()));
 			break;

### 2023-05-19 Paper/draft.tex
paper update

@@
 
-\title{Effects of gluon kinematics and the Sudakov form factor\\ on the dipole amplitude}
+\title{
+Effects of gluon kinematics and the Sudakov\\
+form factor on the dipole amplitude
+}
 
@@
 Golec-Biernat--W\"usthoff, and Bartels--Golec-Biernat--Kowalski saturation
-models. The resulting parameters show some differences, particularly, the
+models. The resulting parameters show some differences, particularly, in the
 normalization of the dipole cross section $\sigma_0$. The refitted models are
@@
 \comment{preprint number (SS)}\\
+\comment{the information on energy and cuts is missing on the plots (KK)}
+\comment{I reformulated some sentences added references and  interpretation of the curves where we use the KS gluon.  }
 
@@
 \begin{tikzpicture}
+  \draw(-0.75in,0.25in)node[left,scale=0.02in]{$q$};
   \draw[snake=coil,segment aspect=0,segment length=0.1in](-0.875in , 0.5in)--(-0.5in,0.in);
@@
 }
-\caption{Kinematic variables of the gluon contribution to $F_2$. The momentum fraction of gluon is $x/z$ as it has to contribute via the quark box.
-}
+\caption{Kinematic variables of the inclusive DIS. \commentPending{Photon momentum (TG)}}
 \label{fig:gluon-kinem}
@@
 effects can be isolated into objects called {\it collinear parton distribution
-functions}~(PDFs)~\cite{Roberts:1990ww,Collins:2011zzd}.  The collinear PDFs are not
-fully perturbatively calculable but they obey perturbative evolution equations
-and are process independent~\cite{Collins:2011zzd}. That is to say that one needs
-to measure them in experiments, but the PDFs obtained in one experiment can be
-used as input in another.
+functions}~(PDFs)~\cite{Roberts:1990ww,Collins:2011zzd}.  The collinear PDFs are
+not fully perturbatively calculable but they obey perturbative evolution
+equations and are process independent~\cite{Collins:2011zzd}. That is to say
+that one needs to measure them in experiments, but the PDFs obtained in one
+experiment can be used as input in another.
 
-One of the main type of processes that is suited particularly well to the studies
-of proton structure is the {\it deep inelastic
+One of the main type of processes that is suited particularly well to the
+studies of proton structure is the {\it deep inelastic
 scattering}~(DIS)~\cite{Roberts:1990ww,Collins:2011zzd}. The data from HERA has
 enabled us to answer many questions in that domain and largely improved our
-picture of interior of a proton. 
-It is therefore very exiting that the next generation of a DIS machines,
-the election-ion collider~(EIC)~\cite{NAP25171} is making its way and will soon
-allow us to uncover more details about the hadron structure.
+picture of interior of a proton.  It is therefore very exiting that the next
+generation of a DIS machines, the Election Ion Collider~(EIC)~\cite{NAP25171} is
+making its way and will soon allow us to uncover more details about the hadron
+structure.
 
-With an increase of the of the center of mass energy at fixed value of the
-photon virtuality, $Q$, one shall probe  the region of the small Bjorken scaling
-variable, $x$.  
-In that region, dominated by gluons\cite{Roberts:1990ww,Collins:2011zzd,
-Kovchegov:2012mbw}, the appropriate theoretical formalism to use is the Color
-Glass Condensate~\cite{McLerran:1993ni, Ayala:1995kg, Kovchegov:1996ty,Jalilian-Marian:1996mkd,Iancu:2000hn,Iancu:2001ad,Ferreiro:2001qy,Iancu:2002xk} or, if the density of gluons is still moderate, the
-High Energy Factorization also called $k_T$-factorization~\cite{Catani:1990xk,Catani:1990eg,Collins:1991ty,Catani:1993ww,Catani:1993rn,Catani:1994sq}.
-
-In the above frameworks, the interaction of the photon with gluons happens
-through a box of quarks, as depicted in Fig.~\ref{fig:gluon-kinem}. An object,
-which is central to the description of this process is called the dipole gluon
-density, $\fdp(x,k_T^2)$, which is a type of {\it transverse momentum
-dependent} PDFs (TMD
+At large center of mass energy and fixed value of the photon virtuality, $Q$,
+one probes  the region of small Bjorken scaling variable, $x$.  In that region,
+dominated by gluons\cite{Roberts:1990ww,Collins:2011zzd, Kovchegov:2012mbw}, the
+approach of High Energy Factorization, also called
+$k_T$-factorization~\cite{Catani:1990xk,Catani:1990eg,Collins:1991ty,Catani:1993ww,Catani:1993rn,Catani:1994sq},
+has proven to be suited particularly well.  In this framework, the interaction
+of the photon with gluons happens through a box of quarks, as depicted in
+Fig.~\ref{fig:gluon-kinem}. An object, which is central to the description of
+this process is called the dipole gluon density, $\fdp(x,k_T^2)$, which is a
+type of {\it transverse momentum dependent} PDFs (TMD
 PDFs)~\cite{Bomhof:2006dp,Dominguez:2010xd,Dominguez:2011wm,Xiao:2017yya}. 
+%
+Due to its clear picture, one often uses a position-space counterpart of the gluon density, called {\it dipole cross section}. 
 %
@@
 
-Much effort has been made
-to study this object, notably the work of Balitsky, Fadin, Kuraev and Lipatov
-(BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has predicted sharp rise of cross
-sections with $1/x$.  However, such rise violates unitarity and the Froissart
+Much effort has been made to study this object, notably the work of Balitsky,
+Fadin, Kuraev and Lipatov (BFKL)~\cite{Balitsky:1978ic, Kuraev:1977fs} has
+predicted sharp rise of cross sections with $1/x$.  However, such rise violates
+unitarity and the Froissart
 bound~\cite{Roberts:1990ww,Collins:2011zzd,Kovchegov:2012mbw,Barone:1993sy}. In
-\cite{Gribov:1983ivg} it has been recognized that gluon recombination can tame
-the growth of gluons \cite{Gribov:1983ivg}. The interplay of linear and
+Ref.~\cite{Gribov:1983ivg} it has been recognized that gluon recombination can
+tame the growth of gluons. The interplay of linear and
 nonlinear terms leads to a phenomenon called {\it gluon saturation} and
@@
 Balitsky-Kovchegov~(BK)~\cite{Balitsky:1995ub,Kovchegov:1999yj} equation or
-JIMWLK\cite{Kovner:1999bj,Kovner:2000pt,Iancu:2000hn,JalilianMarian:1997dw,JalilianMarian:1997gr,JalilianMarian:1997jx} equation.
+JIMWLK\cite{Kovner:1999bj,Kovner:2000pt,Iancu:2000hn,JalilianMarian:1997dw,JalilianMarian:1997gr,JalilianMarian:1997jx}
+equation.
 
-Due to its clear picture, one often uses a position space counter part of the gluon density, called {\it dipole cross section}.
-Despite the success of the aforementioned evolution equations, there exists a number of phenomenological models of the dipole cross section, which are popular due to to their simplicity.
-\commentPending{More about saturation models}
-A notable example of a dipole saturation model is the one proposed by
-Golec-Biernat and Wu\"sthoff (GBW)~\cite{Golec-Biernat:1998zce} and the one proposed by
-Bartels, Golec-Biernat and Kowalski (BGK)~\cite{Bartels:2002cj}.
-We will use these two models in this study.
-There are other models, with different considerations, such as impact parameter dependence~({\it cf.}
-\cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}).
+Despite the success of the aforementioned evolution equations, there exist a
+number of phenomenological models of the dipole cross section, which are popular
+due to to their simplicity.  A notable example is the model proposed by
+Golec-Biernat and Wu\"sthoff (GBW)~\cite{Golec-Biernat:1998zce} and its
+extension by Bartels, Golec-Biernat and Kowalski (BGK)~\cite{Bartels:2002cj}. We
+will use these two specific models in our study. We note, however, that other
+saturation models have been discussed in the
+literature~\cite{Kowalski:2003hm,McLerran:1993ni,Forshaw:1999uf,Iancu:2003ge}.
 
-\commentPending{Section about what we did: fits of saturation models with exact
-kinematics, use of those results + Sudakov for EIC predictions.}
-
-In the present study, we fit the GBW~\cite{Golec-Biernat:1998zce} and BGK~\cite{Bartels:2002cj} models in the $k_T$ factorization formula of $F_2$, instead of the original dipole factorization formula.
-As discussed below, this allows us to fit the model with exact gluon kinematics.
-Since inclusive observables do not reveal the $k_T$ dependence well, we also consider a less inclusive observable which is more sensitive to the $k_T$ dependence of the gluon distribution.
-The resulting models are put to the test by applying them to the predictions of dijet DIS at EIC, including effects of the Sudakov form factor, which resums logarithms of the small transverse momentum.
+In the present study, we fit the GBW and BGK models to HERA
+data~\cite{Abt:2017nkc} in the $k_T$-factorization formula of $F_2$, instead of
+the original dipole factorization formula. As discussed below, this allows us to relatively easy investigate the role 
+of the  exact gluon kinematics.  Since inclusive observables do not
+reveal the $k_T$ dependence well, in order to demonstrate the effects of exact kinematics we consider a less inclusive observable
+which is more sensitive to the $k_T$ dependence of the gluon distribution.  The
+resulting models are used for predictions of dijet production in DIS at EIC,
+including effects of the Sudakov form factor, which resums logarithms of the
+small transverse momentum. 
+%
+This process is known to be sensitive to another type of gluon density, called
+Weitzs\"acker-Williams~\cite{Dominguez:2010xd,Dominguez:2011wm}. For that
+process, we study, in particular, the angular correlation of jets, and that of
+the scattered electron and the jets.
 
 The paper is organized as follows.  In the next section, we present theoretical
-framework which we used and, in particular, outline differences of the
-$k_T$-factorization and the dipole-factorization.  In
-Sec.~\ref{sec:F2fits}, results of the new fits to HERA data in the
-$k_T$-factorization formula are presented. 
-In Sec.~\ref{sec:dijetsEIC}, we apply the results from the previous section to
-compute distributions for dijet production in DIS at the Electron-Ion Collider
-(EIC)~\cite{NAP25171} and make comparisons to our earlier study of Ref.~\cite{vanHameren:2021sqc}.
+framework which we use and outline differences between the $k_T$-factorization
+and the dipole factorization.  In Sec.~\ref{sec:F2fits}, results of the new fits
+to HERA data in the $k_T$-factorization formula are presented.  In
+Sec.~\ref{sec:dijetsEIC}, we apply the results from the previous section to
+compute distributions for dijet production in DIS at the EIC and make
+comparisons to our earlier study of Ref.~\cite{vanHameren:2021sqc}.
 
@@
 \section{The framework}
-\commentPending{Missing a general factorization formula}
-In general, a factorization formula has the form
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The DIS cross section (structure function) factorises and can be written in a
+form
+%
 \begin{equation}
-    \sigma=H \otimes \phi,
+   d\sigma = \sum_{a}  \phi_{a/h} \otimes H_{\gamma a \to X} ,
 \end{equation}
-where $\otimes$ denotes convolution.
-In this form one achieves two things.
-Firstly, one can confine long distance effects in one of the factors (let $\phi$ be such an object), and leaves $H$ as an perturbatively calculable object.
-Secondly, one may factorize out a (to some extent) process independent object.
-In the present study, the dipole cross section and the gluon densities both  contain nonperturbative part and are, to an extent, process independent~\footnote{They are not universal, however they may appear in different processes.
-(see for example Refs.~\cite{Dominguez:2011wm,Kotko:2015ura})}.
-In this section, we will outline two factorizations; the $k_T$ factorization and the dipole factorization. \\
-As it was mentioned earlier, we use the GBW and BGK models.  
-The models were originally formulated in the position-space version of the
-$k_T$-factorization formula. %, and the object which corresponds to the gluon
-%density of the $k_T$-factorization is called the dipole cross section. 
-In the GBW model, the dipole cross section has the form~\cite{Golec-Biernat:1998zce}
+%
+where the hard function, $H_{\gamma a \to X}$, involving a parton $a$ in the
+initial state, is calculable perturbatively, and $\phi_{a/h}$ is the parton
+distribution function of $a$ in a hadron $h$.  
+%
+The symbol $\otimes$ denotes appropriate convolution. All nonperturbative
+effects are absorbed in $\phi_{a/h}$, while $H_{\gamma a \to X}$ can be computed
+order by order in $\alpha_s$.
+
+We will study factorization in two versions: defined in momentum and position
+space respectively.  As mentioned earlier, in the fit we use the GBW and BGK models.  The models were
+originally formulated in the position-space version of the $k_T$-factorization
+formula.  In the GBW model, the dipole cross section has the
+form~\cite{Golec-Biernat:1998zce}
+%
 \begin{align}
@@
 %
-The dipole cross section is related to the gluon density by the Fourier
+The dipole cross section is related to the dipole gluon density by the Fourier
 transform
@@
 \alpha_s\fdp(x,k_T^2)=\frac{N_c}{4\pi}\int\frac{d^2\mathbf{r}}{(2\pi)^2}e^{i\mathbf{k}_t\cdot \mathbf{r} }\nabla_{\mathbf{r}}^2\sigma_{\mathrm{dipole}}(x,r).
-\label{eq:dipole-gluon}
+\label{eq:dipole gluon}
 \end{equation}
@@
 $Q_s^2(x)=Q^2_0(x_0/x)^{-\lambda}$, which separates the saturation region and
-the scaling region.  A extension of the above model was proposed by Bartels, Golec-Biernat
-and Kowalski~(BGK)~\cite{Bartels:2002cj} who incorporated the DGLAP evolution
-in the GBW cross section~(\ref{eq:gbw-dipole}) by modifying the exponent to 
+the scaling region.  An extension of the above model was proposed by Bartels, Golec-Biernat
+and Kowalski~\cite{Bartels:2002cj} who incorporated the DGLAP evolution
+in the GBW dipole cross section~(\ref{eq:gbw-dipole}) by modifying the exponent
+to 
 %
@@
 \end{align}
-For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure function, $F_2$ for transversely and longitudinally polarized photons, factorize, with a change of variable  ${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$, in the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
+%
+For the contribution depicted in Fig.~\ref{fig:gluon-kinem}, the structure
+function $F_2$ factorizes with a change of variable
+${\boldsymbol{\kappa}'}_t\equiv{\boldsymbol{\kappa}_t}-(1-\beta)\mathbf{k}_t$,
+to the form~\cite{ Kimber:2001uaa,Kwiecinski:1997ee}
+%
 \begin{multline}
@@
 
-One should note, that gluons are not probed directly, thus the argument of the
-gluon density is $x/z$ rather than $x$.  If one, instead, uses $ 1/z=1+4
+One should note that the gluons are not probed directly, thus the argument of
+the gluon density is $x/z$ rather than $x$.  If one, instead, uses $ 1/z=1+4
 m_f^2/Q^2$ and assumes that $\mu$ is independent of $\kappa'$ and $k_T$, the
 above formula can be written in the impact parameter
-space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} ({\it i.e.} as a
-dipole-factorization formula)
+space~\cite{Golec-Biernat:1998zce,Nikolaev:1990ja} ({\it i.e.} as a dipole
+factorization formula)
 %
@@
   F_2\left(x,Q^2\right)=\sum_f e_f^2 \frac{Q^2}{4\pi^2} \int^1_0d\beta \int \frac{d^2\mathbf{r}}{(2\pi)^2} \left|\Psi\left(\tilde{x},\beta,Q^2\right)\right|^2\sigma_{\mathrm{dipole}}\left(\tilde{x},r\right),
-  \label{eq:dipole-factorization}
+  \label{eq:dipole factorization}
 \end{equation}
-
+%
 where the photon wave function, $\left|\Psi\left(x,\beta,Q^2\right)\right|^2$,
@@
 cross section, $\sigma_{\mathrm{dipole}}\left(\tilde x,r\right)$, describes the
-interaction of the colour dipole of the size $r$ with the proton. In
+interaction of the colour dipole of size $r$ with the proton. In
 Ref.~\cite{Golec-Biernat:1998zce}, $\tilde{x}=x(1+4m_f/Q^2)$ with nonzero value
@@
 substitute $k_T$ and ${\kappa'}_T$ in Eq.~(\ref{eq:z}).
-%The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole-factorization}), while 
-In the present study, we use Eq.~(\ref{eq:angle-integrated}) to fit the models, where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole-gluon}).
+%The original GBW and BGK models were fitted in the dipole factorization, Eq.~(\ref{eq:dipole factorization}), while 
+In the present study, we use Eq.~(\ref{eq:angle-integrated}) to fit the models, where the gluon density is obtained by evaluating Eq.~(\ref{eq:dipole gluon}).
 %Comparing, the GBW and BGK models, one identifies that, the GBW model is effectively the BGK model with 
@@
 %\end{equation}
-\commentPending{??}{\color{blue}response: the argument on why we consider $\alpha$ as a constant is removed, as it is not a solid argument.}
-%For this reason,
-In order to account for the running coupling in Eq.~(\ref{eq:angle-integrated}), 
-we assume that $\alpha_s$ in Eq.~(\ref{eq:dipole-gluon}) is
-constant for the GBW model, and thus explicitly multiply by the running coupling
+
+Considering the small-$r$ limit of the GBW model, 
+\begin{equation}
+    \left.\sigma_{\mathrm{GBW}}\left(x,r\right)\right|_{r\ll Q_s}\approx r^2
+    Q_s^2/4\,,
+\end{equation}
+comparison to 
+\begin{equation}
+\left. \sigma_{\mathrm{dipole}}\left(x,r\right)\right|_{r\ll
+Q_s}\approx\frac{r^2 \pi^2\alpha_s(\mu^2)xg(x,\mu^2)}{3}\,,
+\end{equation} 
+%
+from BGK, suggests that the GBW model is an approximation in which
+$\alpha_s(\mu^2)$ and $xg(x,\mu^2)$ are independent of
+$r$~\cite{Bartels:2002cj}.  
+%
+For this reason, in one version of the model discussed below, we shall account
+for the running coupling in Eq.~(\ref{eq:angle-integrated}), by assuming that
+$\alpha_s$ in Eq.~(\ref{eq:dipole gluon}) is constant for the GBW model, and
+thus explicitly multiply it by the running coupling
 %
@@
 
-The factor 0.2 is an arbitrary normalization whose effect is absorbed by $\sigma_0$ and hence, bears no importance.
-(For a more detailed analysis of the dipole gluon density from the BGK model see Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the coupling constant was treated differently, and the large $k_T$-region was matched to the derivative of $xg(x)$, while we have used series transformation to accelerate the high-$k_T$ integration.
-Their treatment is also different from the original BGK paper~\cite{Bartels:2002cj}.
-As a consequence their gluon density is positive in the large $k_T$-region and the overall large-$k_T$ behaviour is significantly different.}
-)
-While there is some ambiguity on what the argument of $\alpha_s(\mu^2)$ should be, we follow Ref.~\cite{Kwiecinski:1997ee} and use
+The factor 0.2 is an arbitrary normalization, whose effect is absorbed by
+$\sigma_0$, and hence bears no importance.  (For a more detailed analysis of the
+dipole gluon density from the BGK model see
+Ref.~\cite{Luszczak:2022fkf}\footnote{In Ref.~\cite{Luszczak:2022fkf}, the
+coupling constant was treated differently, and the large $k_T$-region was
+matched to the derivative of $xg(x)$, while we have used series transformation
+to accelerate the high-$k_T$ integration. Their treatment is also different from
+the original BGK paper~\cite{Bartels:2002cj}. As a consequence their gluon
+density is positive in the large $k_T$-region and the overall large-$k_T$
+behaviour is significantly different.}) While there is some ambiguity on what
+the argument of $\alpha_s(\mu^2)$ should be, we follow
+Ref.~\cite{Kwiecinski:1997ee} and use
+%
 \begin{equation}
@@
 \end{equation}
+%
 where we add $\mu^2_0=4\;\GeV^2$ in order to freeze the coupling at low scales.
@@
 CERNLIB~(DPSIPG)~\cite{Kolbig:1972zz}, GSL~\cite{GSL}, CUBA~\cite{Hahn:2004fe}
-and ROOT~\cite{Brun:1997pa} libraries to evaluate $F_2$. The data were selected
-to be in the range $0.045\leq Q^2\leq 650\;\mathrm{GeV^2}$, $x<0.01$.  As with
-the previous fit~\cite{Goda:2022wsc}, the $c$ and $b$ flavours were taken into
-account with the mass $1.3$ and $4.6\;\mathrm{GeV}$, respectively. As discussed
-earlier, we take the light quarks to be massless.  The fitting was performed
-using MnMigrad and MnSimplex of ROOT::Minuit2~\cite{James:2004xla}.
+and ROOT~\cite{Brun:1997pa} libraries to evaluate $F_2$. The fitting was
+performed using MnMigrad and MnSimplex of ROOT::Minuit2~\cite{James:2004xla}.
+
+The data were selected to be in the range $0.045\leq Q^2\leq
+650\;\mathrm{GeV^2}$, $x<0.01$.  As with the previous fit~\cite{Goda:2022wsc},
+the $c$ and $b$ flavours were taken into account with the mass $1.3$ and
+$4.6\;\mathrm{GeV}$, respectively. As discussed earlier, we take the light
+quarks to be massless.
 
@@
 \begin{itemize}
-\item GBW model with massless light quarks in the dipole-factorization ($r$-GBW),
-\item GBW model with massive light quarks in the dipole-factorization ($r$-GBW-massive),
-\item  BGK model in  the dipole-factorization ($r$-BGK).
+\item GBW model with massless light quarks in the dipole factorization ($r$-GBW),
+\item GBW model with massive light quarks in the dipole factorization ($r$-GBW-massive),
+\item  BGK model in  the dipole factorization ($r$-BGK).
 \end{itemize}
@@
 \caption{Fit parameters of respective models. The parameters of the
-dipole-factorization cases are from Ref.~\cite{Goda:2022wsc}.}
+dipole factorization cases are from Ref.~\cite{Goda:2022wsc}.}
 \label{tab:table}
@@
 The results of the fits are summarized in Tab.~\ref{tab:table}. 
-The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while the rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
+The fit quality of $k_T$-GBW is almost unchanged w.r.t. $r$-GBW, while rc-$k_T$-GBW shows remarkable improvement, almost halving the $\chi^2$ value.
 This is in line with the observation made in Refs.~\cite{Albacete:2004gw,Albacete:2007yr,Albacete:2010sy} that in the BK evolution, the running coupling correction have considerable effects.
@@
 
-In the plots on the left side, one can see the effects of the changes in the parameters of the GBW model.
-The difference between the rc-$k_T$-GBW and $r$-GBW are negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.
+In the plots on the left side, one can see the effects of the changes in the
+parameters of the GBW model. The difference between the rc-$k_T$-GBW and $r$-GBW
+is negligible, while the $k_T$-GBW is slightly shifted, compared to others, by the change in $x_0$.
 
-On th right side of Fig.~\ref{fig:GBW-BGK}, the same plots for the BGK model are shown.
-Unlike in the GBW model, the connection between the differences shown in the plots and the differences in the parameters are not clear.
-Nevertheless, the difference is more prominent in the small-$x$ region.
+On th right side of Fig.~\ref{fig:GBW-BGK}, the same plots are shown for the BGK
+model. Unlike in the GBW case, the connection between the differences shown in
+the plots and the differences in the parameters is less clear. Nevertheless, the
+difference is more prominent in the small-$x$ region.
 
-Comparisons of the results with the $F_2$ data are shown in Figs.~\ref{fig:GBW-Grid} and~\ref{fig:BGK-Grid}.
-In Fig.~\ref{fig:GBW-Grid}, the difference between $r$-GBW and $k_T$-GBW are not visible, while rc-$k_T$-GBW shows sizable difference from the others, particularly in the large-$Q^2$ region. 
-Recalling that the parameters of rc-$k_T$-GBW and $r$-GBW are very similar, the difference in $F_2$ is almost entirely due to the coupling constant.
-The improvement in the fit quality is depicted as a histogram of the $\chi^2$-vale per number of points at the bottom of Fig.~\ref{fig:GBW-Grid}.
-Here, the improvement in the large-$Q^2$ region is very clear.
-In Fig.~\ref{fig:BGK-Grid}, the difference between $r$-BGK and $k_T$-BGK are hardly visible.
-In the histogram at the bottom, one can see some differences, but they cancel out mostly, making little improvement overall.
+Comparisons of the results with the $F_2$ data are shown in
+Figs.~\ref{fig:GBW-Grid} and~\ref{fig:BGK-Grid}.  In Fig.~\ref{fig:GBW-Grid},
+the differences between $r$-GBW and $k_T$-GBW are not visible, while
+rc-$k_T$-GBW shows sizable difference from the others, particularly in the
+large-$Q^2$ region.  Recalling that the parameters of rc-$k_T$-GBW and $r$-GBW
+are very similar, the difference in $F_2$ is almost entirely due to the coupling
+constant. The improvement in the fit quality is depicted as a histogram of the
+$\chi^2$-vale per number of points at the bottom of Fig.~\ref{fig:GBW-Grid}.
+Here, the improvement in the large-$Q^2$ region is very clear.  In
+Fig.~\ref{fig:BGK-Grid}, the difference between $r$-BGK and $k_T$-BGK are hardly
+visible. In the histogram at the bottom, one can see some differences, but they
+cancel out mostly, making little improvement overall.
 
@@
   10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
-  models. Note, the dipole cross section and the gluon density are normalized by
-  $\sigma_0^{-1}$.} 
+  models. Note that the dipole cross section and the gluon density are
+  normalized with $\sigma_0^{-1}$.} 
 \label{fig:GBW-BGK}
@@
 %\end{subfigure}
-\caption{Comparison of GBW $F_2$ with HERA data. The histogram shows the $\chi^2$ value per data point in each frame.
- Improvement by the running coupling ($k_T$ run) is clearly visible in the high-$Q^2$region, while the new fit ($k_T$) shows only marginal improvement .  }
+\caption{Comparison of $F_2$ fro GBW with HERA data. The histogram shows the
+$\chi^2$ value per data point in each frame.  Improvement by the running
+coupling (rc-$k_T$) is clearly visible in the high-$Q^2$region, while the new
+fit ($k_T$) shows only marginal improvement.}
 \label{fig:GBW-Grid}
@@
 %\end{subfigure}
-\caption{Comparison of BGK $F_2$ with HERA data.
-The histogram shows the $\chi^2$ value per data point in each frame.
-While the overall fit quality remain similar, the fit quality in each frame change noticeably.
-Particularly the $k_T$-formula case ($k_T$) shows better fit in the small-$Q^2$ region.}
+\caption{Comparison of $F_2$ from BGK with HERA data. The histogram shows the
+$\chi^2$ value per data point in each frame. The overall fit quality
+remain similar but the quality in each frame changes noticeably. In
+particularly, the $k_T$-formula ($k_T$) shows better quality at small $Q^2$.}
 \label{fig:BGK-Grid}
@@
 Let us now take a closer look at the parameter $\sigma_0$. Recall that the
-difference between the $k_T$-factorization formula and the dipole-factorization
-formula is in $x/z$, Eq.~(\ref{}), and this enters in the GBW formalism as
+difference between the $k_T$-factorization formula and the dipole factorization
+formula is in $x/z$, and this enters in the GBW formalism as
 $\tilde{x}$. It is easy to see that, as $x$ grows, the dipole cross section gets
@@
 one can understand the change in $\sigma_0$ as a direct consequence of the key
-difference between the $k_T$-factorization and the dipole-factorization.
+difference between the $k_T$-factorization and the dipole factorization.
 
@@
     \end{subfigure}
-    \caption{ Weizs\"acker-Williams gluon density at $x=10^{-3}$.
-Top row: comparison of the dipole-factorization fit and $k_T$-factorization fit results.
-Bottom row: comparison of the respective models with and without the Sudakov factor, at $\mu=17,\;67 \mathrm{GeV}$.The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.
-}
+    \caption{ Weizs\"acker-Williams gluon density at $x=10^{-3}$. Top row:
+    comparison of the dipole factorization fit and $k_T$-factorization fit
+    results. Bottom row: comparison of the respective models with and without
+    the Sudakov factor, at $\mu=17,\;67\ \mathrm{GeV}$.The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Hentschinski:2022rsa}. }
     \label{fig:ww}
@@
 
-The $F_2$ structure function is an inclusive object and is weakly sensitive to
-the shape of the gluon density. To probe the latter, we shall now 
-apply the dipole cross section obtained to the electron-dijet correlation at the
-electron-ion collider~(EIC), following closely the method of
-Ref.~\cite{vanHameren:2021sqc}.
+\begin{figure}[p]
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotGBW1} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotBGK1} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotGBW2}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotGBW3}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotBGK2}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{plots/plotBGK3}
+	\end{subfigure}
+	\caption{ Azimuthal correlation of the jets and the scattered electron in the Breit frame.
+Top: Comparison of dipole factorization fit and $k_T$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Hentschinski:2022rsa}.}
+	\label{fig:je-breit}
+\end{figure}
+
+\begin{figure}[p]
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW1Lab} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK1Lab} 
+	\end{subfigure}
+
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW2Lab}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW3Lab}
+	\end{subfigure}
+
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK2Lab}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK3Lab}
+	\end{subfigure}
+\caption{ Azimuthal correlation of the jets and the scattered electron in the lab frame.
+Top: Comparison of dipole factorization fit and $k_T$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Hentschinski:2022rsa}.}
+\label{fig:je-lab}
+\end{figure}
+
+\begin{figure}[p]
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW1Jets} 
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK1Jets} 
+	\end{subfigure}
+
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW2Jets}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotGBW3Jets}
+	\end{subfigure}
+
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK2Jets}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\includegraphics[width=\textwidth]{plots/plotBGK3Jets}
+	\end{subfigure}
+\caption{Azimuthal correlation of the jets in the Breit frame.
+Top: Comparison of dipole factorization fit and $k_T$-factorization fit.
+Middle \& Bottom: Effect of the Sudakov form factor.
+The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Hentschinski:2022rsa}.
+}
+\label{fig:jj-breit}
+\end{figure}
+
+The $F_2$ structure function is an inclusive object and it is weakly sensitive
+to the shape of the gluon density. To probe the shape better, we shall now apply the
+dipole cross sections obtained in the previous section to the electron-dijet
+correlation at EIC, following closely the method of Ref.~\cite{vanHameren:2021sqc}.
 
@@
   %\label{eq:}
-  e+p\rightarrow e+J_1+J_2+X\,,
+  e+p\rightarrow e+J_1+J_2+X\,.
 \end{equation}
@@
 which leads to the transverse-momentum-dependent~(TMD) factorization.
-
-\commentPending{mention why Sudakov is important for dijet production}\\
-{\color{blue} There is a line before Eq.~(\ref{eq:ww-sud}) ?}
 
@@
 Transverse-Momentum-Dependent} (ITMD)
-factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.  The latter is
+factorization~\cite{Kotko:2015ura,vanHameren:2016ftb}.  This is
 implemented in the program KaTie~\cite{vanHameren:2016kkz}, which we use to
-compute the cross sections.  The ITMD factorization is an generalization of the
-TMD factorization where the momentum
-imbalance in TMD is restricted to be
-small~\cite{Kotko:2015ura,vanHameren:2016ftb}. That is to say ITMD resums
+compute the cross sections.  The ITMD factorization is a generalization of the
+TMD factorization, where the momentum imbalance in TMD is restricted to be
+small~\cite{Kotko:2015ura,vanHameren:2016ftb}. That is to say, ITMD resums
 $(Q_s/k_T)^n$ and $(k_T/P_T)^n$~\cite{Kotko:2015ura,vanHameren:2016ftb}, thus
@@
 Eq.~(\ref{eq:TMD}) from the regular TMD is that the hard function has an
-off-shell gluon $g^*$, thus rendering the $k_T$ dependence in the hard function
+off-shell gluon, $g^*$, thus rendering the $k_T$ dependence in the hard function
 as well~\cite{Kotko:2015ura}.
@@
 
-\comment{Question: normalization}
+\comment{Normalization (SS) Comment in context of Figs. 6, 7, 8 (TG)}
+
+\comment{Another rcBK (TG)}
 
@@
 Eqs.~(\ref{eq:ww}) and~(\ref{eq:ww-sud}).  The gluon density at $x=10^{-3}$ is
-plotted in Fig.~\ref{fig:ww} with hard-scale-independent KS
-gluon~\cite{vanHameren:2021sqc,Abdulov:2021ivr} and running-coupling BK~(rcBK)
-gluon density~\cite{Balitsky:2006wa,Albacete:2010sy}. Clearly, the GBW and BGK models falls much more quickly
+plotted in Fig.~\ref{fig:ww} with the hard-scale-independent Kutak-Sapeta (KS)
+gluon~\cite{Kutak:2012rf,vanHameren:2021sqc,Abdulov:2021ivr} and running-coupling BK~(rcBK)
+gluon density~\cite{Balitsky:2006wa,Albacete:2010sy,Hentschinski:2022rsa}.
+Both of these gluon densities are solutions of evolution equations and treat better perturbative tail at large $k_T$.
+Furthermore KS gluon takes into account resummed corrections of higher orders i.e.
+kinematical constraint and nonsingular at low $z$ elements of DGLAP  splitting function \cite{Kwiecinski:1997ee}.
+Clearly, the GBW and BGK models falls much more quickly
 than the KS and rcBK gluon density. In general, expected behaviour in the
@@
 new $k_T$-factorization fits. However the overall normalization of the gluon
-density depends on the coupling $\alpha_s$, which we assumed to be 0.2.
+density depends on the coupling $\alpha_s$, which we assumed to be~0.2.
 Nevertheless, it shows clearly the effect of the parameter $\sigma_0$. In the
@@
 correlation in the lab frame. Here, the difference between KS and GBW and BGK
-is more prominent, while rcBK shows similar pattern to the GBW and BGK models.
-The effects of the Sudakov factor is similar to those
+is more prominent, while rcBK shows similar pattern to the GBW and BGK models and therefore we can attribute the effects to importance of higher order corrections as are accounted for in KS gluon.
+The effects of the Sudakov factor are similar to those
 in Ref.~\cite{vanHameren:2021sqc} at relatively high $\Delta \phi$, while at
-smaller $\Delta \phi$ region the effect is reversed ({\it i.e.} the cross
+smaller $\Delta \phi$, the effect is reversed ({\it i.e.} the cross
 sections were slightly lowered in Ref.~\cite{vanHameren:2021sqc}, while here,
 they are significantly increased).
-
-\begin{figure}[p]
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotGBW1} 
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotBGK1} 
-	\end{subfigure}
-%	\caption{ }
-%\end{figure}
-%\begin{figure}[t]
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotGBW2}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotGBW3}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotBGK2}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{plots/plotBGK3}
-	\end{subfigure}
-	\caption{ Azimuthal correlation of the jets and the scattered electron in the Breit frame.
-Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
-Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.}
-	\label{fig:je-breit}
-\end{figure}
-
-\begin{figure}[p]
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW1Lab} 
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK1Lab} 
-	\end{subfigure}
-
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW2Lab}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW3Lab}
-	\end{subfigure}
-
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK2Lab}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK3Lab}
-	\end{subfigure}
-\caption{ Azimuthal correlation of the jets and the scattered electron in the lab frame.
-Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
-Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.}
-\label{fig:je-lab}
-\end{figure}
 
@@
 
-\begin{figure}[p]
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW1Jets} 
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK1Jets} 
-	\end{subfigure}
-
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW2Jets}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotGBW3Jets}
-	\end{subfigure}
-
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK2Jets}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\includegraphics[width=\textwidth]{plots/plotBGK3Jets}
-	\end{subfigure}
-\caption{Azimuthal correlation of the jets in the Breit frame.
-Top: Comparison of dipole-factorization fit and $k_T$-factorization fit.
-Middle \& Bottom: Effect of the Sudakov form factor.
-The green dotted line is the KS gluon~\cite{vanHameren:2021sqc}, and the green dashed line is the rcBK gluon~\cite{Albacete:2010sy}.
-}
-\label{fig:jj-breit}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 using the $k_T$-factorization for the structure function $F_2$.  The main
-difference between the $k_T$- and the dipole-factorizations is an argument of
+difference between the $k_T$- and the dipole factorizations is an argument of
 the gluon, that is $x/z$ appearing in the former being replaced by
@@
 %
-In fact the massive light quarks used in
-Ref.~\cite{Golec-Biernat:1998zce} partially simulate the factor $1/z$, and our 
-fit result indicates such effect, as expected.
+In fact, the massive light quarks used in Ref.~\cite{Golec-Biernat:1998zce}
+partially simulate the factor $1/z$, and our fit result indicates such effect,
+as expected.
 
-It is quite remarkable that with such simplicity, the dipole-factorization can
-reproduce the result of the $k_T$-factorization formula well. We have found that
-the only major difference is in the normalization parameter $\sigma_0$ which
+We find that the dipole factorization can
+reproduce the result of the $k_T$-factorization formula quite well. We have found that
+the only major difference is in the normalization parameter $\sigma_0$, which
 increases significantly for the $k_T$-factorization case. We have also observed
 that the explicit inclusion of the running coupling has significant effect on
-the fit quality, particularly in the large-$Q^2$ region, where the GBW model
+fit quality, particularly in the large-$Q^2$ region, where the GBW model
 performs poorly.
 
-We have applied the new result from our fits for the prediction of the dijet
+We have applied the new results from our fits for the prediction of the dijet
 process in DIS at EIC. Additionally, effects of the Sudakov form factor were
 investigated for that process. Results of the electron-jets correlation in the
-Breit frame agree qualitatively to those of Ref.~\cite{vanHameren:2021sqc}.
+Breit frame agree qualitatively with those of Ref.~\cite{vanHameren:2021sqc}.
 Other results, namely the electron-jets in the lab frame and the jet-jet
 correlation in the Breit frame, show considerable effects of the Sudakov form
-factor which broaden the gluon density.
+factor, which broadens the gluon density.
 
@@
 \section*{Acknowledgment}
-We are grateful to Krzysztof Golec-Biernat for numerous useful discussions and
-for careful reading of the manuscript, and Piotr Kotko and Andreas van Hameren
-for the clarification of details of Ref.~\cite{vanHameren:2021sqc} and 
-usage of the KaTie package. The project is partially supported by the European
+We are grateful to Krzysztof Golec-Biernat, Piotr Kotko and Andreas van Hameren
+for useful discussions. The project is partially supported by the European
 Union’s Horizon 2020 research and innovation program under grant agreement No.

### 2023-07-14 saturation-ver3/Functions/fcn.h
clean up

@@ -16,7 +16,7 @@
 //extern double F2_kt(const  double,const  double,const double, const double(&)[]);
 //extern double F2_r(const double,double,double,double*);
 class KtFCN : public ROOT::Minuit2::FCNBase {
-	
+//This class is described in Minuit user's guide
 	
 	private:	
 		double *__restrict Q2_DATA=(double*)malloc(0);
@@ -37,14 +37,9 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 	public:
 		unsigned MAX_N=0;
 		int flag=0;
+		
 		explicit KtFCN(std::string data_file,std::string dir ){
-			
-				//std::string file_name=dir+"/log.txt";
-				//file=fopen(file_name.c_str(),"a");
-				directory=dir;
-			
-
-		//KtFCN(char* data_file){
+			directory=dir;
 			data_alloc(500);
 			const double alpha =1.0/137 ;//fine structure const 1/137;
 			const double xmp0 = 0.93827;//proton mass in GeV
@@ -52,16 +47,14 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 			unsigned i=0;
 			unsigned j=0;
 			double fac;
-			//std::fstream file;
-			//file.open(data_file, std::fstream::in);
 			FILE* file=fopen(data_file.c_str(),"r");
 			double wdata;
-			//while((!file.eof())&&(j<597)){
 			if(file==NULL){
 				printf("file not found.\n");
 				exit(1);
 			}
 			while((!feof(file))&&(j<597)){
+				//see Abt et al. where the data come from 
 				fscanf(file,"%lf %lf %lf %lf %lf", (Q2_DATA+i),(X_DATA+i),&wdata,(CS_DATA+i),(ERR_DATA+i)); 
 				if((X_DATA[i]<=X_DATA_MAX)&&( Q2_DATA[i]<=Q2_MAX)){
 					fac = pow(Q2_DATA[i],2)*(1-X_DATA[i])/ (4*pow(PI,2)*alpha*(Q2_DATA[i]+pow(2*X_DATA[i]*xmp0,2)));
@@ -149,7 +142,7 @@ class KtFCN : public ROOT::Minuit2::FCNBase {
 ///////////////////////////////////////////////////////////////////////////////////////////		
 			double arr[MAX_N];
[…]

### 2023-07-14 saturation-ver3/Functions/interpolation-gluon.cc

@@ -1,4 +1,3 @@
-#include"control.h"
 #include"interpolation-gluon.hh"
 
 

### 2023-08-14 saturation-ver3/Functions/UQD.cc
running GBW grid added

@@ -183,13 +183,14 @@ int main(int argc, char** argv){
  double x=0 ,k2=0 ,q2=100;
  FILE* file=fopen(argv[2],"w");
  
-for(int k=0;k<25;k++){
-	q2=0.2*pow(1e+5/0.2,((double)k)/2.4e+1);
+
 
 	for(int i=0;i<sigma.x_npts;i++){
 		x=sigma.x_array[i];
 		for(int j=0;j<sigma.k2_npts;j++){
 			k2=sigma.k2_array[j];
+		for(int k=0;k<25;k++){
+			q2=0.2*pow(1e+5/0.2,((double)k)/2.4e+1);
 			fprintf(file,"%.5e\t%.5e\t%.5e\t%.5e\n",log(x),log(k2),log(q2),sigma(x,k2,q2)/k2 );
 		}//fprintf(file,"\n" );
 	}

### 2023-08-14 saturation-ver3/Functions/plot/plot-dp.cc

@@ -19,8 +19,8 @@
 #include<cuba.h>
 
 extern double  INT_PREC;
-#include"clenshaw.hh"
-#include"gauss.hh"
+//#include"clenshaw.hh"
+//#include"gauss.hh"
 
 #include"kt-formula.hh"
 #include"options.h"

### 2023-08-14 saturation-ver3/Functions/plot/plot-ww.cc

@@ -19,8 +19,8 @@
 #include<cuba.h>
 
 extern double  INT_PREC;
-#include"clenshaw.hh"
-#include"gauss.hh"
+//#include"clenshaw.hh"
+//#include"gauss.hh"
 
 
 #include"kt-formula.hh"

### 2023-08-14 dijet-HERA-1/plot2.sh
hera katie

@@ -1,0 +1,17 @@
+#! /usr/bin/env bash
+
+for i in GBWkt GBWr GBWSkt GBWSr BGKkt  BGKr BGKSkt BGKSr KS rcBK
+do
+	cd ${i}
+	#parallel ./main.out :::  seed=2023 seed=5432 seed=1357 seed=2468
+	#parallel ./main.out :::  seed=1904 seed=794 seed=1192 seed=1702
+	#./main.out   seed=1234 
+	#rm -f eventfile.dat *.hst
+	#../run.sh merge raw*
+	../create_eventfile.out lhef,pb raw*
+	echo ${i} ' done'
+	cd ..
+done
+
+
+

### 2023-08-14 dijet-HERA-1/plot3.sh

@@ -1,0 +1,29 @@
+#! /usr/bin/env bash
+./plotting.txt GBWkt "GBW \$k_t\$" BGKkt "BGK \$k_t\$" BGKGBW 
+
+./plotting.txt BGKr "BGK \$r\$" BGKkt "BGK \$k_t\$" BGK 
+
+#./plotting.txt BGKSkt "BGK+S " BGKkt "BGK" BGKS 
+
+./plotting.txt GBWr "GBW \$r\$" GBWkt "GBW \$k_t\$" GBW 
+
+#./plotting.txt GBWSkt "GBW+S " GBWkt "GBW" GBWS 
+
+#./plotting.txt BGKSkt "BGK+S " KS "KS" KS 
+
+#./plotting.txt BGKSkt "BGK+S " rcBK "rcBK" rcBK 
+./plotting.txt GBWkt "GBW \$k_t\$" rcGBWkt "rcGBW \$k_t\$"  rcGBWkt
+
+./plotting.txt BGKkt "BGK \$k_t\$" BGKSkt "BGK+S \$k_t\$" BGKkt
+
+./plotting.txt GBWkt "GBW \$k_t\$" GBWSkt "GBW+S \$k_t\$" GBWkt
+
+##############################################################
+
+./plotting3.txt GBWkt "GBW \$k_t\$" rcGBWkt "rcGBW \$k_t\$" rcGBWSkt "rcGBW+S \$k_t\$" rcGBW
+
+./plotting3.txt BGKr "BGK \$r\$" BGKkt "BGK \$k_t\$" BGKSkt "BGK+S \$k_t\$" BGK3
+
+./plotting3.txt GBWr "GBW \$r\$" GBWkt "GBW \$k_t\$" GBWSkt "GBW+S \$k_t\$" GBW3
+
+./plotting3.txt KS "KS " rcBK "rcBK" BGKSkt "BGK+S \$k_t\$" rcBKKS
